### 2020-07-14 proposal draft .Rmd
new changes for testing

---
title: "Proposal Draft"
author: "Yuru"
date: "15/05/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
    fig_height: 4
    fig_width: 6
    fontsize: 12pt
  word_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE)
```

add a comment

## Abstract

With correct model speciﬁcation being an ongoing issue for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of this misspeciﬁcation. Based on previous research on this topic, this paper conducts both numerical and empirical analyses to explore the impact of the form and degree of model misspeciﬁcation on probabilistic forecasts that are optimal under a given score. In particular, the role of optimal forecasts in predicting Value-at-Risk and the VIX Volatility Index, and in optimizing portfolio allocation, is to be investigated.

Results at the current stage have shown that the greater the degree of model misspeciﬁcation is, the more beneficial is optimal prediction. Empirical analysis shows that after the global financial crisis, predictions that are optimal according to a censored scoring rule that rewards predictive accuracy in a tail are substantially more accurate than the alternatives, including likelihood-based predictions. This indicates the potentially signiﬁcant contribution to ﬁnancial analyses of this method.

## 1. Introduction

This research paper will explore the question: ‘When do optimal probabilistic forecasts work’; with particular attention given to the usefulness of optimal predictions in ﬁnancial markets. This work builds on recent research on this topic by Loaiza-Maya et al. (2020). Correct model speciﬁcation is a challenge in forecasting, especially for likelihood-based predictions since, in practice, the assumed model underpinning the likelihood function will almost certainly diﬀer from the unknown true data generation process (DGP). As an alternative to likelihood-based prediction, scoring rules have recently been proposed as a basis for producing probabilistic forecasts that perform well according to that score, even in the presence of model misspeciﬁcation; see Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al. (2020).

The ‘optimal’ probabilistic forecast discussed in this paper will refer to a predictive probability distribution that is optimal according to a user- speciﬁed scoring rule. In particular, this paper seeks to document the eﬀects of the form and degree of model misspeciﬁcation on optimal forecast performance using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and copula models. The assumed predictive model is ﬁxed as ARCH (1) for both the simulation and empirical analyses. Motivated by the practical usage of predictive distributions in ﬁnancial analyses, this paper will assess optimal forecast performance in Value-at-Risk (VaR), the Volatility Index (VIX) and portfolio optimization applications, using empirical data extending over a period of time that precedes the global ﬁnancial crisis (GFC) and extends to the latest period in which COVID-19 has impacted on ﬁnancial markets. The empirical results are expected to make contributions to existing ﬁnancial analyses of risks and returns.

## 2. Research aims and questions

This research paper aims to discover whether optimal prediction performs the same under varying degrees of misspecification of the true DGP in simulation experiments; specifically as the true DGP is varied from Gaussian ARCH(1), to Gaussian GARCH(1,1), to GARCH(1,1) with marginal skewness introduced by inversion copula, whilst the assumed predictive model remains fixed at Gaussian ARCH(1).

The paper also aims to show how optimal prediction performs in diﬀerent ﬁnancial market situations with the empirical data used in this research covering two important periods in ﬁnancial markets, namely the GFC and the COVID-19 pandemic.

## 3. Literature review

Scoring rules can be used to estimate parameters and to evaluate probabilistic forecasts. A variety of proper scoring rules allows users to produce probability predictions based on their interests, and to compare these predictions, as long as they refer to the same forecast quantity. Some commonly used scoring roles are discussed in Gneiting & Raftery (2007), such as the logarithmic score (LS) and the continuously ranked probability score (CRPS). Similarly, Diks, Panchenko & van Dijk, (2011) introduce the censored likelihood score (CSL), which focuses on any probability regions of interest to the user, including the tails of the predictive distribution.

Loaiza-Maya, Martin & Frazier, (2019) introduce scoring rules to Bayesian prediction as an alternative to using the conventional likelihood function for updating the prior probability. They conduct both numerical and empirical analyses using the scoring rules mentioned above and show that the degree of model misspeciﬁcation plays an important role in terms of how the ‘Focused’ Bayesian method performs relative to misspecified likelihood-based predictions.

Loaiza-Maya et al., (2020) extend the above discussion to frequentist probability forecasting. They address questions about when we can/cannot beneﬁt from optimal probabilistic forecasts out of sample and introduce the concepts of ‘coherence’ and ‘strict coherence’. In short, coherence means when the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score. Strict coherence is when the optimal prediction is strictly preferable given that score.

To continue the research in this vein, my paper will mainly be guided by Loaiza-Maya et al., (2020) and Loaiza- Maya, Martin & Frazier, (2019). Three speciﬁc applications of optimal prediction will be conducted and I will further explore the impact of model misspeciﬁcation on optimal prediction as the true DGP changes in particular ways.

## 4. Numerical investigation

### 4.1 Simulation experiments design

The purpose of this simulation is to mimic the behavior of financial returns and volatility and to discover how optimal probabilistic forecasts perform under different forms and degrees of model misspeciﬁcation. GARCH models capture the volatility clustering and serial dependence, and the negative marginal skewness will be introduced using an inversion copula with degree of skewness controlled by the shape parameter.

The methodology in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) is adopted here, with specific simulation scenarios listed as follows ($t_{\nu}$ indicates a Student-t distribution with $\nu$ degrees of freedom):

```{r, out.width="600px",fig.align='center'}
knitr::include_graphics("Picture 1.png")
```

We conduct each simulation scenario as follows (Loaiza-Maya et al., 2020):

  1.	Generate T = 6000 observations for $y_t$ from the true DGP

  2.	Use $y_{1:1000}$ to estimate $\hat \theta$ in the assumed predictive model based on the positively-oriented score $S_i$

$${\hat \theta^{[i]}}:=arg\max_{\theta \in \Theta}\bar S_i({\theta})---(1)$$  
$$\bar S_i(\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\theta}^{t-1},y_t)---(2)$$

  3.	Produce the one-step-ahead predictive $P^{t-1}_{\hat \theta_1^{[i]}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (3)(4)(5)

$$S_{LS}(P_{\theta}^{t-1},y_t)=lnp(y_t|\mathscr{F}_{t-1},\theta) ---(3)$$

$$S_{CRPS}(P_{\theta}^{t-1},y_t)=-\int_{-\infty}^{+\infty}[P(y|\mathscr{F}_{t-1},\theta)-I(y \ge y_t)]^2dy ---(4)$$

$$S_{CLS}(P_{\theta}^{t-1},y_t)=lnp(y_t|\mathscr{F}_{t-1},\theta)I(y_t \in A)+[ln\int_{A^c}p(y|\mathscr{F}_{t-1},\theta)dy]I(y_t \in A^c) --- (5)$$

  4.	Expand estimation window by one observation and repeat step 2-3 $\tau = T-1000$ times and compute:

$$\bar S_j(\hat \theta^{[i]})=\frac{1}{\tau}\sum^T_{t=T-{\tau}+1}S_j (P^{t-1}_{\hat \theta_1^{[i]}},y_t) --- (6)$$

#### 4.1.1 Simulation analysis: preliminary results

##### Average Scores

Results of Table 1-3 are recorded for scenario (i) and Table 4-6 are for scenario (ii) with degree of model misspecification listed in an ascending order. The first column shows $S_i$ that we used to produce predictions and the first row shows $S_j$. The bolded value(s) is the largest one(s) in each column, indicating the optimal prediction(s) based on this score.

In Table 1 and 4, the least misspecified cases, we observe the same predictive accuracy according to a given score when different scoring rules are used to produce predictions such as values in column 5. While in the most misspecified cases (Table 3 and 6), we improve the predictive accuracy by using scoring rules. The results in Table 1-6, then illustrate that we can gain more from optimal prediction according to a given score when the degree of model misspeciﬁcation is greater. It is true for both types of model misspeciﬁcation.

```{r, message=FALSE}
library(formattable)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(tsibbledata)
library(feasts)
library(normtest)
library(moments)
library(ggthemes)
library(ggpubr)
library(knitr)
library(kableExtra)
```

```{r}
# Editting the matlab written csv files

GARCH_t12 <- read.csv("GARCH_t12__table.csv")
GARCH_t12 <- rename(GARCH_t12, "In-sample optimizers" = Row, "FSR 10%" = FSR10, "FSR 20%"=FSR20, "FSR 80%"=FSR80,"FSR 90%"=FSR90)
GARCH_t12$`In-sample optimizers`<-c("LS","CRPS","FSR 10%","FSR 20%","FSR 80%","FSR 90%")

GARCH_t3 <- read.csv("GARCH_t3_table.csv")
GARCH_t3 <- rename(GARCH_t3, "In-sample optimizers" = Row, "FSR 10%" = FSR10, "FSR 20%"=FSR20, "FSR 80%"=FSR80,"FSR 90%"=FSR90)
GARCH_t3$`In-sample optimizers`<-c("LS","CRPS","FSR 10%","FSR 20%","FSR 80%","FSR 90%")

ARCH_table <- read.csv("ARCH_table.csv")
ARCH_table <- rename(ARCH_table, "In-sample optimizers" = Row, "FSR 10%" = FSR10, "FSR 20%"=FSR20, "FSR 80%"=FSR80,"FSR 90%"=FSR90)
ARCH_table$`In-sample optimizers`<-c("LS","CRPS","FSR 10%","FSR 20%","FSR 80%","FSR 90%")

Copula5_table <- read.csv("Copula5_table.csv")
Copula5_table <- rename(Copula5_table, "In-sample optimizers" = Row, "FSR 10%" = FSR10, "FSR 20%"=FSR20, "FSR 80%"=FSR80,"FSR 90%"=FSR90)
Copula5_table$`In-sample optimizers`<-c("LS","CRPS","FSR 10%","FSR 20%","FSR 80%","FSR 90%")

Copula3_table <- read.csv("Copula3_table.csv")
Copula3_table <- rename(Copula3_table, "In-sample optimizers" = Row, "FSR 10%" = FSR10, "FSR 20%"=FSR20, "FSR 80%"=FSR80,"FSR 90%"=FSR90)
Copula3_table$`In-sample optimizers`<-c("LS","CRPS","FSR 10%","FSR 20%","FSR 80%","FSR 90%")

Copula0_table <- read.csv("Copula0_table.csv")
Copula0_table <- rename(Copula0_table, "In-sample optimizers" = Row, "FSR 10%" = FSR10, "FSR 20%"=FSR20, "FSR 80%"=FSR80,"FSR 90%"=FSR90)
Copula0_table$`In-sample optimizers`<-c("LS","CRPS","FSR 10%","FSR 20%","FSR 80%","FSR 90%")

```

```{r}
ARCH_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"html",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"html",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR 10%` = cell_spec(format(`FSR 10%`,4),"html",bold = ifelse(`FSR 10%`==max(`FSR 10%`),TRUE,FALSE)),
    `FSR 20%` = cell_spec(format(`FSR 20%`,4),"html",bold = ifelse(`FSR 20%`==max(`FSR 20%`),TRUE,FALSE)),
    `FSR 80%` = cell_spec(format(`FSR 80%`,4),"html",bold = ifelse(`FSR 80%`==max(`FSR 80%`),TRUE,FALSE)),
    `FSR 90%` = cell_spec(format(`FSR 90%`,4),"html",bold = ifelse(`FSR 90%`==max(`FSR 90%`),TRUE,FALSE))
  ) %>%
  kable("html",escape = F) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 1: the true DGP is ARCH(1)"=7))
```

```{r}
GARCH_t12 %>% 
  mutate(
    LS = cell_spec(format(LS,4),"html",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"html",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR 10%` = cell_spec(format(`FSR 10%`,4),"html",bold = ifelse(`FSR 10%`==max(`FSR 10%`),TRUE,FALSE)),
    `FSR 20%` = cell_spec(format(`FSR 20%`,4),"html",bold = ifelse(`FSR 20%`==max(`FSR 20%`),TRUE,FALSE)),
    `FSR 80%` = cell_spec(format(`FSR 80%`,4),"html",bold = ifelse(`FSR 80%`==max(`FSR 80%`),TRUE,FALSE)),
    `FSR 90%` = cell_spec(format(`FSR 90%`,4),"html",bold = ifelse(`FSR 90%`==max(`FSR 90%`),TRUE,FALSE))
  ) %>%
  kable("html",escape = F) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 2: the true DGP is GARCH(1,1) with degree of freedom = 12"=7))
```

```{r}
GARCH_t3 %>% 
  mutate(
    LS = cell_spec(format(LS,4),"html",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"html",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR 10%` = cell_spec(format(`FSR 10%`,4),"html",bold = ifelse(`FSR 10%`==max(`FSR 10%`),TRUE,FALSE)),
    `FSR 20%` = cell_spec(format(`FSR 20%`,4),"html",bold = ifelse(`FSR 20%`==max(`FSR 20%`),TRUE,FALSE)),
    `FSR 80%` = cell_spec(format(`FSR 80%`,4),"html",bold = ifelse(`FSR 80%`==max(`FSR 80%`),TRUE,FALSE)),
    `FSR 90%` = cell_spec(format(`FSR 90%`,4),"html",bold = ifelse(`FSR 90%`==max(`FSR 90%`),TRUE,FALSE))
  ) %>%
  kable("html",escape = F) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 3: the true DGP is GARCH(1,1) with degree of freedom = 3"=7))
```

```{r}

Copula0_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"html",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"html",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR 10%` = cell_spec(format(`FSR 10%`,4),"html",bold = ifelse(`FSR 10%`==max(`FSR 10%`),TRUE,FALSE)),
    `FSR 20%` = cell_spec(format(`FSR 20%`,4),"html",bold = ifelse(`FSR 20%`==max(`FSR 20%`),TRUE,FALSE)),
    `FSR 80%` = cell_spec(format(`FSR 80%`,4),"html",bold = ifelse(`FSR 80%`==max(`FSR 80%`),TRUE,FALSE)),
    `FSR 90%` = cell_spec(format(`FSR 90%`,4),"html",bold = ifelse(`FSR 90%`==max(`FSR 90%`),TRUE,FALSE))
  ) %>%
  kable("html",escape = F) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 4: the true DGP is copula with shape parameter = 0"=7))
```

```{r}
Copula3_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"html",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"html",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR 10%` = cell_spec(format(`FSR 10%`,4),"html",bold = ifelse(`FSR 10%`==max(`FSR 10%`),TRUE,FALSE)),
    `FSR 20%` = cell_spec(format(`FSR 20%`,4),"html",bold = ifelse(`FSR 20%`==max(`FSR 20%`),TRUE,FALSE)),
    `FSR 80%` = cell_spec(format(`FSR 80%`,4),"html",bold = ifelse(`FSR 80%`==max(`FSR 80%`),TRUE,FALSE)),
    `FSR 90%` = cell_spec(format(`FSR 90%`,4),"html",bold = ifelse(`FSR 90%`==max(`FSR 90%`),TRUE,FALSE))
  ) %>%
  kable("html",escape = F) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 5: the true DGP is copula with shape parameter = -3"=7))
```

```{r}
Copula5_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"html",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"html",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR 10%` = cell_spec(format(`FSR 10%`,4),"html",bold = ifelse(`FSR 10%`==max(`FSR 10%`),TRUE,FALSE)),
    `FSR 20%` = cell_spec(format(`FSR 20%`,4),"html",bold = ifelse(`FSR 20%`==max(`FSR 20%`),TRUE,FALSE)),
    `FSR 80%` = cell_spec(format(`FSR 80%`,4),"html",bold = ifelse(`FSR 80%`==max(`FSR 80%`),TRUE,FALSE)),
    `FSR 90%` = cell_spec(format(`FSR 90%`,4),"html",bold = ifelse(`FSR 90%`==max(`FSR 90%`),TRUE,FALSE))
  ) %>%
  kable("html",escape = F) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 6: the true DGP is copula with shape parameter = -5"=7))
```

##### Score traces

The above tables show the average scores at the end of evaluations, while score trace figures demonstrate how these average scores change through the whole evaluation process. The left panel shows how listed scores perform in terms of forecasting 10% tail of the true distribution and the right panel illustrates the performance of scores in 90% tail. The least misspecified case is the first row and the last row is the most misspecified case. The figures show that we can benefit more from using FSR in terms of improving accuracy of predicting tails in both forms when the degree of model misspecification is larger.

```{r, out.width="600px",fig.align='center'}
knitr::include_graphics("figure 1.png")
```

```{r, out.width="600px",fig.align='center'}
knitr::include_graphics("figure 2.png")
```

## 5. Empirical investigation

### 5.1 Empirical analysis design

The design of empirical analysis closely follows the simulation experiments. That is, we only change the simulated true DGP to the continuously compounded logarithmic returns of S&P500 over a time period that precedes the GFC and extends to the latest period in which COVID-19 has impacts on financial market.

#### 5.1.1 Empirical analysis: preliminary results

##### Descriptive statistics

```{r}
# data cleaning and import 
sp <- read.csv("^GSPC.csv")
sp <- sp %>% dplyr::select("Date","Adj.Close")

sp$log.returns <- c(NA,diff(log(sp$Adj.Close)))
logret <- sp[-c(1:41),c(1,3)] # delete the adjusted price col, only keep 6000 obs

# export the dataset to csv. including only trading days and log returns 
temp <- logret[,c(2)]
temp <- data.frame(temp)
write_csv(temp,"sp500log.csv")
```

```{r, results='hide'}
# descriptive statistics 
summary(logret$log.returns) # ----> need to be tabulated 
range(logret$log.returns)
# some test results aginst normal dist h_null
# JB test
jb.norm.test(logret$log.returns)
# Ljung box test
Box.test(logret$log.returns,lag = 2,type = "Lj",fitdf = 1)

skewness(logret$log.returns)
kurtosis(logret$log.returns)
```

```{r}
sum <- data.frame(Stock="S&P500",Min=-0.1276522,Median=0.0006105,Mean=0.0002453,Max=0.1095720,Skewness= -0.3807978,Kurtosis=13.5123,JB.Test=27772,LB.Test=60.627)
formattable(sum)
```

```{r,message=FALSE,fig.align='center'}

# time series plot
logret$Date <- as.Date(logret$Date,format = "%Y-%m-%d")

logret %>% ggplot(aes(x = Date, y = log.returns)) +
  geom_line()+theme_classic()+labs(x="Year",y="Daily log returns")+
  ggtitle("Figure 9: S&P500 daily log returns")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_y_continuous(labels = scales::percent) + 
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.12,label="Global Financial Crisis",color="red",size=3)+
  annotate(geom = 'text',x=as.Date("2020-04-01"),y=-0.12,label="COVID-19",color="red",size=2)+
  theme_clean()+
  labs(caption = "Figure 9: the time series plot of S&P500 daily log returns")

# histogram plots
logret %>% ggplot()+geom_histogram(aes(x=log.returns))+xlim(-0.13,0.13)+ggtitle("Figure 10")+
  scale_x_continuous(labels = scales::percent)+theme_clean()+
  labs(caption = "Figure 10: the distribution of S&P500 log returns is asymmetric")

# ACF plots to see the autocorrelation 
logret <- logret %>% 
  mutate(trading_day = row_number()) %>%
  as_tsibble(index = trading_day,regular = TRUE)

logret %>% ACF((log.returns)^2) %>% autoplot() + ggtitle("Figure 11:Squared log returns autocorrelation")+xlab("number of lags")+ylab("ACF")+theme_clean()+labs(caption = "Figure 11: the autocorrelation plot shows there is a strong serial correlation in volatility of S&P500")
```

##### Average scores

```{r}
sp_table <- read.csv("sp_table.csv")
sp_table <- rename(sp_table, "In-sample optimizers" = Row,"FSR 10%" = FSR10, "FSR 20%"=FSR20, "FSR 80%"=FSR80,"FSR 90%"=FSR90)
sp_table$`In-sample optimizers`<-c("LS","CRPS","FSR 10%","FSR 20%","FSR 80%","FSR 90%")

sp_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"html",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"html",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR 10%` = cell_spec(format(`FSR 10%`,4),"html",bold = ifelse(`FSR 10%`==max(`FSR 10%`),TRUE,FALSE)),
    `FSR 20%` = cell_spec(format(`FSR 20%`,4),"html",bold = ifelse(`FSR 20%`==max(`FSR 20%`),TRUE,FALSE)),
    `FSR 80%` = cell_spec(format(`FSR 80%`,4),"html",bold = ifelse(`FSR 80%`==max(`FSR 80%`),TRUE,FALSE)),
    `FSR 90%` = cell_spec(format(`FSR 90%`,4),"html",bold = ifelse(`FSR 90%`==max(`FSR 90%`),TRUE,FALSE))
  ) %>%
  kable("html",escape = F) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 9: Average scores for S&P500"=7))
```

The average score table, similar to simulation analysis, is produced for daily logarithmic returns of S&P500. For example, in column 4 (FSR 10%), a focused score at 10% will produce the optimal prediction in terms of forecasting the 10% tail of the returns’ distribution. The results in this table indicate that we expect to gain considerably from optimal probabilistic forecasts in practice.

##### Score traces

```{r,fig.width=10,fig.height=5}
# to compress all the calculated plotting average scores together in the same df 
trace_fsr10 <- read.csv("fsr10.csv")
trace_fsr20 <- read.csv("fsr20.csv")
trace_10ls <- read.csv("fsr10_ls.csv")
trace_10crps <- read.csv("fsr10_crps.csv")

fsr10 <- data.frame(trace_fsr10,trace_fsr20,trace_10ls,trace_10crps)

# add back dates to the fsr10 df, initial step = 1000

fsr10 <- fsr10 %>% mutate(Date = logret$Date[1001:6000])

# plot scores --- lower tail 
fsr10$Date <- as.Date(fsr10$Date,format = "%Y-%m-%d")

color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple","CRPS"="green")

fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
  labs(x="Year",y="Average Scores",color="legend")+
  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_color_manual(values = color1)+
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
  theme_clean()

# plot scores --- upper tail 
trace_fsr90 <- read.csv("fsr90.csv")
trace_fsr80 <- read.csv("fsr80.csv")
trace_90ls <- read.csv("fsr90_ls.csv")
trace_90crps <- read.csv("fsr90_crps.csv")

fsr90 <- data.frame(trace_fsr90,trace_fsr80,trace_90ls,trace_90crps)

# add back dates to the fsr10 df, initial step = 1000

fsr90 <- fsr90 %>% mutate(Date = logret$Date[1001:6000])

# plot scores --- lower tail 
fsr90$Date <- as.Date(fsr90$Date,format = "%Y-%m-%d")

color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple","CRPS"="green")

fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
  labs(x="Year",y="",color="legend")+
  #ggtitle("Figure 12: S&P500 Score traces-upper tail")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_color_manual(values = color2)+
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.05,label="Global Financial Crisis",color="darkred")+
  theme_clean()

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 12(a) Lower Tail","Figure 12(b) Upper Tail"))

```

The score traces illustrate a very interesting phenomenon. The FSR focused on the 10% and 90% tails are strictly superior to alternative forecasts produced by other scores after the GFC and continue to perform well until the very recent date. It indicates that optimal probabilistic forecasts might predict financial markets better in and after times of stock market turbulance, which could represent a great contribution to the existing financial analyses of risks and returns.

## 6. Timeline

```{r, out.width="600px",fig.align='center'}
knitr::include_graphics("timeline.png")
```

## References

Diks, C., Panchenko, V., & van Dijk, D. (2011). Likelihood-based scoring rules for comparing density forecasts in tails. Journal of Econometrics, 163(2), 215-230. doi: 10.1016/j.jeconom.2011.04.001

Gneiting, T., & Raftery, A. (2007). Strictly Proper Scoring Rules, Prediction, and Estimation. Journal of the American Statistical Association, 102(477), 359-378. doi: 10.1198/016214506000001437

Loaiza-Maya, R., Martin, G., & Frazier, D. (2019). Focused Bayesian Prediction. Retrieved from http://arxiv.org/abs/1912.12571

Loaiza-Maya, et al. (2020). Optimal Probabilistic Forecasts: when do they work? Manuscript in preparation.

### 2020-07-16 new table formatting.Rmd
new changes need to be done in the draft due

---
title: "Untitled"
author: "Yuru"
date: "14/07/2020"
output:
  pdf_document: default

editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(formattable)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(tsibbledata)
library(feasts)
library(normtest)
library(moments)
library(ggthemes)
library(ggpubr)
library(knitr)
library(kableExtra)
```

succeed to get the latex table knit to PDF, but might need to adjust the font size to keep the bold values and the unbold values the same size. the line space looks weird as well (for FSR90 row).

need to put the notation explanation in the thesis to specify what FSR10, FSR20 means. consider a footnote.

https://stackoverflow.com/questions/47888885/kableextra-how-to-use-cell-spec-from-a-user-defined-range

# latex table

```{r successful}
ARCH_table <- read.csv("ARCH_table.csv")
ARCH_table <- rename(ARCH_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
ARCH_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

ARCH_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    FSR10 = cell_spec(format(FSR10,4),"latex",bold = ifelse(FSR10==max(FSR10),TRUE,FALSE)),
    FSR20 = cell_spec(format(FSR20,4),"latex",bold = ifelse(FSR20==max(FSR20),TRUE,FALSE)),
    FSR80 = cell_spec(format(FSR80,4),"latex",bold = ifelse(FSR80==max(FSR80),TRUE,FALSE)),
    FSR90 = cell_spec(format(FSR90,4),"latex",bold = ifelse(FSR90==max(FSR90),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs=T) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 1: the true DGP is ARCH(1)"=7))
```

# fomula table 
Math notation - formula table for the simulation design

https://stackoverflow.com/questions/46305256/r-math-notation-in-data-frame

if not working, then may consider store the formula as a character/string in the dataframe then tabulate it.

# insert pdf pictures 
try to insert pdf pictures:

```{r img}
knitr::include_graphics("figure 1.pdf")
```

change the pdf size when generating the pictures from Matlab

# citation and reference 
\@ref(fig:img)

### 2020-07-16 Table_Format_Thesis.Rmd
the initial documents used in the proposal

---
title: "Updated May 7"
author: "Yuru"
date: "04/04/2020"
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(formattable)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(tsibbledata)
library(feasts)
library(normtest)
library(moments)
library(ggthemes)
library(ggpubr)
library(knitr)
library(kableExtra)
```

# Simulation Analysis

## Simulation Design

```{r}
# Editting the matlab written csv files

GARCH_t12 <- read.csv("GARCH_t12__table.csv")
GARCH_t3 <- read.csv("GARCH_t3_table.csv")
ARCH_table <- read.csv("ARCH_table.csv")

Copula5_table <- read.csv("Copula5_table.csv")
Copula3_table <- read.csv("Copula3_table.csv")
Copula0_table <- read.csv("Copula0_table.csv")

# bold the maximum
max_bold <- formatter("span",style = x~style("font-weight"=ifelse(x == max(x),"bold",NA)))

```

#### Table 1:

True DGP is ARCH with standard normal errors, assumed DGP is ARCH with standard normal errors

```{r}
formattable(ARCH_table,list(LS = max_bold,CRPS = max_bold,FSR10 = max_bold,FSR20 = max_bold,FSR80 = max_bold,FSR90 = max_bold))
```

#### Table 2:

True DGP is GARCH, and error term is t distribution with 3 dof, assumed DGP is ARCH with standard normal errors

```{r}
formattable(GARCH_t3,list(LS = max_bold,CRPS = max_bold,FSR10 = max_bold,FSR20 = max_bold,FSR80 = max_bold,FSR90 = max_bold))
```

#### Table 3:

True DGP is GARCH, and error term is t distribution with 12 dof, assumed DGP is ARCH with standard normal errors

```{r}
formattable(GARCH_t12,list(LS = max_bold,CRPS = max_bold,FSR10 = max_bold,FSR20 = max_bold,FSR80 = max_bold,FSR90 = max_bold))
```

#### Table 4:

True DGP is Copula with shape = -5. assumed DGP is ARCH with standard normal errors

```{r}
formattable(Copula5_table,list(LS = max_bold,CRPS = max_bold,FSR10 = max_bold,FSR20 = max_bold,FSR80 = max_bold,FSR90 = max_bold))
```

#### Table 5:

True DGP is Copula with shape = -3. assumed DGP is ARCH with standard normal errors

```{r}
formattable(Copula3_table,list(LS = max_bold,CRPS = max_bold,FSR10 = max_bold,FSR20 = max_bold,FSR80 = max_bold,FSR90 = max_bold))
```

#### Table 6:

True DGP is Copula with shape = 0 (no asymmetry). assumed DGP is ARCH with standard normal errors

```{r}
formattable(Copula0_table,list(LS = max_bold,CRPS = max_bold,FSR10 = max_bold,FSR20 = max_bold,FSR80 = max_bold,FSR90 = max_bold))
```

# Score traces figure

The following graph shows how the average scores keep changing as we change the true data generation processes. The estimated model is kept as ARCH(1) all the time.

Left column: Score traces for lower tail (10%)

Right column: Score traces for upper tail (90%)

The out-of-sample optimizer is set as FSR10% for lower tail and FSR90% for upper tail. The chosen in-sample optimizers are listed in the graph and highlighted in different colors.

## GARCH DGP

#### Figure 1

![figure1](GARCH figure.jpg)

## Copula DGP

#### Figure 2

![figure2](Copula figure.jpg)

# Predictive Probability figures

## Copula true DGP family

#### Figure 3

![figure 3](pred_den_Copula0.jpg)

#### Figure 4

![figure 4](pred_den_Copula3.jpg)

#### Figure 5

![figure 5](pred_den_copula5.jpg)

## GARCH true DGP family

#### Figure 6

![figure 6](pred_den_arch.jpg)

#### Figure 7

![figure 7](pred_den_garch12.jpg)

#### Figure 8

![figure 8](pred_den_garch3.jpg)

# VaR with simulation data

Only backtesting VaR for the most misspecified models in each misspecification type.

### VaR for Copula with shape = -5

#### Table 7

```{r}
copula5var <- read.csv("copula5var.csv")

VaR_0.1 <- as.numeric(copula5var[,c(1,5,9,13,17,21)])
VaR_0.2 <- as.numeric(copula5var[,c(2,6,10,14,18,22)])
VaR_0.8 <- as.numeric(copula5var[,c(3,7,11,15,19,23)])
VaR_0.9 <- as.numeric(copula5var[,c(4,8,12,16,20,24)])

optimizers <- c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

df <- data.frame(optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)

max_bold1 <- formatter("span",style=x~style("font-weight"=ifelse(abs(x-0.1)==min(abs(x-0.1)),"bold",NA)))

max_bold2 <- formatter("span",style=x~style("font-weight"=ifelse(abs(x-0.2)==min(abs(x-0.2)),"bold",NA)))

max_bold8 <- formatter("span",style=x~style("font-weight"=ifelse(abs(x-0.8)==min(abs(x-0.8)),"bold",NA)))

max_bold9 <- formatter("span",style=x~style("font-weight"=ifelse(abs(x-0.9)==min(abs(x-0.9)),"bold",NA)))

formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
```

### VaR for GARCH with degree of freedom = 3

#### Table 8

```{r}
garch3var <- read.csv("garch3var.csv")

VaR_0.1 <- as.numeric(garch3var[,c(1,5,9,13,17,21)])
VaR_0.2 <- as.numeric(garch3var[,c(2,6,10,14,18,22)])
VaR_0.8 <- as.numeric(garch3var[,c(3,7,11,15,19,23)])
VaR_0.9 <- as.numeric(garch3var[,c(4,8,12,16,20,24)])

df <- data.frame(optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)

formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
```

# Empirical Analysis

S&P500 from the U.S. stock markets, with daily trading frequency. The returns are calculated as continuously compounded log returns.

In order to keep consistent with the simulation example, the sample size is chosen as 6000.

## Descriptive Statistics 
```{r}
# data cleaning and import 
sp <- read.csv("^GSPC.csv")
sp <- sp %>% dplyr::select("Date","Adj.Close")

sp$log.returns <- c(NA,diff(log(sp$Adj.Close)))
logret <- sp[-c(1:41),c(1,3)] # delete the adjusted price col, only keep 6000 obs

# export the dataset to csv. including only trading days and log returns 
temp <- logret[,c(2)]
temp <- data.frame(temp)
write_csv(temp,"sp500log.csv")
```

```{r, results='hide'}
# descriptive statistics 
summary(logret$log.returns) # ----> need to be tabulated 
range(logret$log.returns)
# some test results aginst normal dist h_null
# JB test
jb.norm.test(logret$log.returns)
# Ljung box test
Box.test(logret$log.returns,lag = 2,type = "Lj",fitdf = 1)

skewness(logret$log.returns)
kurtosis(logret$log.returns)
```

### Summarize Table

#### Table 9

```{r}
sum <- data.frame(Stock="S&P500",Min=-0.1276522,Median=0.0006105,Mean=0.0002453,Max=0.1095720,Skewness= -0.3807978,Kurtosis=13.5123,JB.Test=27772,LB.Test=60.627)
formattable(sum)
```

### Descriptive Plots

```{r,message=FALSE}

# time series plot
logret$Date <- as.Date(logret$Date,format = "%Y-%m-%d")

logret %>% ggplot(aes(x = Date, y = log.returns)) +
  geom_line()+theme_classic()+labs(x="Year",y="Daily log returns")+
  ggtitle("Figure 9: S&P500 Daily log returns")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_y_continuous(labels = scales::percent) + 
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.12,label="Global Financial Crisis",color="red",size=3)+
  annotate(geom = 'text',x=as.Date("2020-04-01"),y=-0.12,label="COVID-19",color="red",size=2)+
  theme_clean()

# histogram plots
logret %>% ggplot()+geom_histogram(aes(x=log.returns))+xlim(-0.13,0.13)+ggtitle("Figure 10")+
  scale_x_continuous(labels = scales::percent)

# ACF plots to see the autocorrelation 
logret <- logret %>% 
  mutate(trading_day = row_number()) %>%
  as_tsibble(index = trading_day,regular = TRUE)

logret %>% ACF((log.returns)^2) %>% autoplot() + ggtitle("Figure 11:Squared log returns autocorrelation")+xlab("number of lags")+ylab("ACF")
```

### Score Tables

#### Table 10

```{r}
sp_table <- read.csv("sp_table.csv")
max_bold <- formatter("span",style = x~style("font-weight"=ifelse(x == max(x),"bold",NA)))

formattable(sp_table,list(LS = max_bold,CRPS = max_bold,FSR10 = max_bold,FSR20 = max_bold,FSR80 = max_bold,FSR90 = max_bold))
```

### Score traces figure

```{r,fig.width=10,fig.height=5}
# to compress all the calculated plotting average scores together in the same df 
trace_fsr10 <- read.csv("fsr10.csv")
trace_fsr20 <- read.csv("fsr20.csv")
trace_10ls <- read.csv("fsr10_ls.csv")
trace_10crps <- read.csv("fsr10_crps.csv")

fsr10 <- data.frame(trace_fsr10,trace_fsr20,trace_10ls,trace_10crps)

# add back dates to the fsr10 df, initial step = 1000

fsr10 <- fsr10 %>% mutate(Date = logret$Date[1001:6000])

# plot scores --- lower tail 
fsr10$Date <- as.Date(fsr10$Date,format = "%Y-%m-%d")

color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple","CRPS"="green")

fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
  labs(x="Year",y="Average Scores",color="legend")+
  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_color_manual(values = color1)+
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
  theme_clean()

# plot scores --- upper tail 
trace_fsr90 <- read.csv("fsr90.csv")
trace_fsr80 <- read.csv("fsr80.csv")
trace_90ls <- read.csv("fsr90_ls.csv")
trace_90crps <- read.csv("fsr90_crps.csv")

fsr90 <- data.frame(trace_fsr90,trace_fsr80,trace_90ls,trace_90crps)

# add back dates to the fsr10 df, initial step = 1000

fsr90 <- fsr90 %>% mutate(Date = logret$Date[1001:6000])

# plot scores --- lower tail 
fsr90$Date <- as.Date(fsr90$Date,format = "%Y-%m-%d")

color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple","CRPS"="green")

fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
  labs(x="Year",y="",color="legend")+
  #ggtitle("Figure 12: S&P500 Score traces-upper tail")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_color_manual(values = color2)+
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.05,label="Global Financial Crisis",color="darkred")+
  theme_clean()

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 12(a) Lower Tail","Figure 12(b) Upper Tail"))

```

### VaR for S&P500

#### Table 11: Before 2008 GFC

```{r}
spvar <- read.csv("spvar1_table.csv")

VaR_0.1 <- as.numeric(spvar[,c(1,5,9,13,17,21)])
VaR_0.2 <- as.numeric(spvar[,c(2,6,10,14,18,22)])
VaR_0.8 <- as.numeric(spvar[,c(3,7,11,15,19,23)])
VaR_0.9 <- as.numeric(spvar[,c(4,8,12,16,20,24)])

df <- data.frame(optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)

formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
```

#### Table 12: After 2008 GFC

```{r}
spvar <- read.csv("spvar2_table.csv")
spvar <- round(spvar,digits = 4)

VaR_0.1 <- as.numeric(spvar[,c(1,5,9,13,17,21)])
VaR_0.2 <- as.numeric(spvar[,c(2,6,10,14,18,22)])
VaR_0.8 <- as.numeric(spvar[,c(3,7,11,15,19,23)])
VaR_0.9 <- as.numeric(spvar[,c(4,8,12,16,20,24)])

df <- data.frame(optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)

formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
```

### 2020-07-16 table_formatting.Rmd
the initial documents used in the proposal

---
title: "Table_formatting"
author: "Yuru"
date: "03/04/2020"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Editting the matlab writen csv table

```{r}
table1 <- read.csv("check1.csv")
colmax <- apply(table1,2,max)
row.names(table1) <- colnames(table1)

GARCH_t12 <- read.csv("GARCH_t12__table.csv")
#row.names(GARCH_t12) <- colnames(GARCH_t12)

GARCH_t3 <- read.csv("GARCH_t3_table.csv")
#row.names(GARCH_t3) <- colnames(GARCH_t3)

ARCH_table <- read.csv("ARCH_table.csv")
ar#row.names(ARCH_table) <- colnames(ARCH_table)

Copula_table <- read.csv("Copula_table.csv")
#row.names(Copula_table) <- colnames(Copula_table)

library(huxtable)
table1_hux <- as_hux(table1,add_colnames = TRUE,add_rownames = TRUE)
table1_hux
table1_hux <- set_number_format(table1_hux,c(2:7),c(2:7),4)

# compare the values in the table to the maximum 
for (columns in 2:7){
for (rows in 2:7) {
  if(identical(table1_hux[rows,columns],colmax[columns]) == 'TRUE'){
    table1_hux <- set_bold(table1_hux,rows,columns,TRUE,byrow = FALSE)
  }
}}

table1_hux

GARCH_t12 <- as_hux(GARCH_t12,add_colnames = TRUE)
GARCH_t3 <- as_hux(GARCH_t3,add_colnames = TRUE)
ARCH_table <- as_hux(ARCH_table,add_colnames = TRUE)
Copula_table <- as_hux(Copula_table,add_colnames = TRUE)
```

```{r}
# set the maximum in each column to bold text
for (columns in 1:5){
  for (rows in 1:5) {
    if (table1_hux[rows+1,columns+1] > table1_hux[rows,columns]){
      max = data.frame(rows+1,columns+1)}
    #else if (table1_hux[rows+1,columns+1] == #table1_hux[rows,columns]){
      #max = data.frame
   # }
    else {max = data.frame(rows,columns)
    }
  table1_hux <- set_bold(table1_hux,max[1,1],max[1,2],TRUE,byrow = FALSE)
  }
  # reset max to be zero dataframe
  max = data.frame(0,0)
}

```

```{r}
# set the maximum in each column to bold text

# find the maximum in each column

max <- matrix(0,nrow=1,ncol=6)
# index <- matrix(nrow=6,ncol = 6)

for (columns in 1:5){
  for (rows in 1:5) {
    if (table1_hux[rows+1,columns+1] > table1_hux[rows,columns]){
      max[1,columns] <- table1_hux[rows+1,columns+1]}

    else {max[1,columns] <- table1_hux[rows,columns]
    }
  }
}

for (columns in 1:5){
  for (rows in 1:5) {
    if (table1_hux[rows+1,columns+1] > table1_hux[rows,columns]){
      max}

    else {max = data.frame(rows,columns)
    }
  table1_hux <- set_bold(table1_hux,max[1,1],max[1,2],TRUE,byrow = FALSE)
  }
  # reset max to be zero dataframe
  max = data.frame(0,0)
}

```

```{r}
# set the maximum in each column to bold text
#（2）
for (columns in 1:5){
#此处循环寻找处整列中的最大值
for (rows in 1:5) {
if (table1_hux[rows+1,columns] > table1_hux[rows,columns]){
#【依据Java的标准】你在循环体内定义的变量max，可能在（1）处用不了，需要在（2）处定义一个变量
max = data.frame(rows+1,columns)}
#else if (table1_hux[rows+1,columns+1] == #table1_hux[rows,columns]){
#max = data.frame
else {max = data.frame(rows,columns)}
#table1_hux <- set_bold(table1_hux,max[1,1],max[1,2],TRUE,byrow = FALSE)
  }
#依据上个循环找出的最大值，再次循环整列来和最大值做比较，相等即为要找的位置
for (rows in 1:6) {
#（1）
temp = data.frame(rows,columns)
if (max == temp){
table1_hux <- set_bold(table1_hux,rows,columns,TRUE,byrow = FALSE)
}
}
max = data.frame(0,0)
}
```

```{r}
# THIS IS THE RIGHT CODE!!!!!
# find the maximum of each column and store this in a 1x6 matrix

colmax <- apply(table1,2,max)

# compare the values in the table to the maximum 
for (columns in 1:6){
for (rows in 1:6) {
  if(table1_hux[rows,columns] >= colmax[columns]){
    table1_hux <- set_bold(table1_hux,rows,columns,TRUE,byrow = FALSE)
  }
}}

table1_hux
```

```{r}
#for (columns in 1:1){
  max1 = -100
  for (rows in 1:5) {
    if(max1 >= table1_hux[rows+1,columns]){
      max1 = max1
    }
    else {max1 = table1_hux[rows,columns]}
  }

for (columns in 1:6) {
  for (rows in 1:6) {
    if (table1_hux[rows,columns] == max1){
    table1_hux <- set_bold(table1_hux,rows,columns,TRUE,byrow = FALSE)
  }
  }
}
table1_hux

  if (table1_hux[rows,columns] == max1){
    table1_hux <- set_bold(table1_hux,rows,columns,TRUE,byrow = FALSE)
  }
#}

```

### 2020-07-16 kable temp.R

@@ -1,0 +1,5 @@
+
+models <- data.frame()
+models$copula <- c('$\\sigma_{t}=\\sigma_{t-1}^2$') # just a test, not the right model
+models$GARCH <- c('$y_{t}=\\epsilon$')
+kable(models, "latex",align = "c",booktabs=TRUE,escape = F,caption = '$\\Gamma$')

### 2020-07-18 proposal draft .Rmd
VIX data cleaning

@@
 ```
-
-add a comment
 
@@
 ```{r, message=FALSE}
-library(formattable)
+#library(formattable)
 library(dplyr)
@@
 Loaiza-Maya, et al. (2020). Optimal Probabilistic Forecasts: when do they work? Manuscript in preparation.
+
+## VIX analysis
+
+```{r,message=F}
+# data cleaning and import 
+vix <- read.csv("^VIX.csv")
+vix <- vix %>% dplyr::select("Date","Adj.Close")
+
+vix$logvix <- log(vix$Adj.Close)
+
+# previous day log vix values
+prev <- matrix(0,nrow = nrow(vix)+1,ncol = 1)
+for (i in 1:nrow(vix)){
+  prev[1,1] <- c("NA")
+  prev[i+1,1] <- vix$logvix[i]
+}
+prev <- as.data.frame(prev)
+prev <- prev[-c(1:178,6179),1]
+
+require(zoo)
+MA5 <- rollmean(vix$logvix,5,align = "center")
+MA5 <- as.data.frame(MA5) # average of past week
+MA5 <- MA5[-c(1:174),1] # including only 6000 obs
+
+MA22 <- rollmean(vix$logvix,22,align = "center")
+MA22 <- as.data.frame(MA22) # average of past month
+MA22 <- MA22[-c(1:157),1] # including only 6000 obs
+
+logvix <- vix[-c(1:178),c(1,3)] # delete the adjusted vix col, only keep 6000 obs
+logvix <- cbind(logvix,prev,MA5,MA22)
+# export the dataset to csv. including only trading days and log returns 
+temp <- logvix[,2:5]
+write_csv(temp,"vixlog.csv")
+# the logvix, previous log vix and moving average values have the same length in the final file. 
+```

### 2020-07-19 proposal draft .Rmd
time index fixed for MA

@@
 
-require(zoo)
-MA5 <- rollmean(vix$logvix,5,align = "center")
+# need to be very careful about the time index -- dependent variable starting with t+1
+MA5 <- matrix(0,nrow=nrow(vix)-5,ncol = 1)
+for (i in 1:(nrow(vix)-5)){
+  sum = 0
+  for (j in 1:5){
+    sum = sum + vix$logvix[i+j-1]
+  }
+  MA5[i,1] = (1/5)*sum
+}
+
+MA22 <- matrix(0,nrow = nrow(vix)-22,ncol = 1)
+for (i in 1:(nrow(vix)-22)){
+  sum = 0
+  for (j in 1:22){
+    sum = sum + vix$logvix[i+j-1]
+  }
+  MA22[i,1] = (1/22)*sum
+}
+
+#require(zoo)
+#MA5 <- rollmean(vix$logvix,5,align = "center")
 MA5 <- as.data.frame(MA5) # average of past week
-MA5 <- MA5[-c(1:174),1] # including only 6000 obs
+MA5 <- MA5[-c(1:173),1] # including only 6000 obs
 
-MA22 <- rollmean(vix$logvix,22,align = "center")
+#MA22 <- rollmean(vix$logvix,22,align = "center")
 MA22 <- as.data.frame(MA22) # average of past month
-MA22 <- MA22[-c(1:157),1] # including only 6000 obs
+MA22 <- MA22[-c(1:156),1] # including only 6000 obs
 

### 2020-07-20 proposal draft .Rmd
Vix average score tables + score trace figures

@@
 ```{r, message=FALSE}
-#library(formattable)
+library(formattable)
 library(dplyr)
@@
 ```
+
+```{r}
+vix_table <- read.csv("vix_table.csv")
+vix_table <- rename(vix_table, "In-sample optimizers" = Row,"FSR 10%" = FSR10, "FSR 20%"=FSR20, "FSR 80%"=FSR80,"FSR 90%"=FSR90)
+vix_table$`In-sample optimizers`<-c("LS","CRPS","FSR 10%","FSR 20%","FSR 80%","FSR 90%")
+
+vix_table %>% 
+  mutate(
+    LS = cell_spec(format(LS,4),"html",bold = ifelse(LS == max(LS),TRUE,FALSE)),
+    CRPS = cell_spec(format(CRPS,4),"html",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
+    `FSR 10%` = cell_spec(format(`FSR 10%`,4),"html",bold = ifelse(`FSR 10%`==max(`FSR 10%`),TRUE,FALSE)),
+    `FSR 20%` = cell_spec(format(`FSR 20%`,4),"html",bold = ifelse(`FSR 20%`==max(`FSR 20%`),TRUE,FALSE)),
+    `FSR 80%` = cell_spec(format(`FSR 80%`,4),"html",bold = ifelse(`FSR 80%`==max(`FSR 80%`),TRUE,FALSE)),
+    `FSR 90%` = cell_spec(format(`FSR 90%`,4),"html",bold = ifelse(`FSR 90%`==max(`FSR 90%`),TRUE,FALSE))
+  ) %>%
+  kable("html",escape = F) %>%
+  kable_styling("bordered",full_width = F)%>%
+  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
+  add_header_above(c("Table ?: Average scores for VIX"=7))
+```
+
+```{r,fig.width=10,fig.height=5}
+# to compress all the calculated plotting average scores together in the same df 
+trace_fsr10 <- read.csv("vixfsr10.csv")
+trace_fsr20 <- read.csv("vixfsr20.csv")
+trace_10ls <- read.csv("vixfsr10_ls.csv")
+trace_10crps <- read.csv("vixfsr10_crps.csv")
+
+fsr10 <- data.frame(trace_fsr10,trace_fsr20,trace_10ls,trace_10crps)
+
+# add back dates to the fsr10 df, initial step = 1000
+
+fsr10 <- fsr10 %>% mutate(Date = vix$Date[1001:6000])
+
+# plot scores --- lower tail 
+fsr10$Date <- as.Date(fsr10$Date,format = "%Y-%m-%d")
+
+color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple","CRPS"="green")
+
+fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
+  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
+  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
+  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
+  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
+  labs(x="Year",y="Average Scores",color="legend")+
+  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
+  scale_x_date(date_breaks = "years",date_labels = "%y")+
+  scale_color_manual(values = color1)+
+  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
+  theme_clean()
+
+# plot scores --- upper tail 
+trace_fsr90 <- read.csv("vixfsr90.csv")
+trace_fsr80 <- read.csv("vixfsr80.csv")
+trace_90ls <- read.csv("vixfsr90_ls.csv")
+trace_90crps <- read.csv("vixfsr90_crps.csv")
+
+fsr90 <- data.frame(trace_fsr90,trace_fsr80,trace_90ls,trace_90crps)
+
+# add back dates to the fsr10 df, initial step = 1000
+
+fsr90 <- fsr90 %>% mutate(Date = vix$Date[1001:6000])
+
+# plot scores --- lower tail 
+fsr90$Date <- as.Date(fsr90$Date,format = "%Y-%m-%d")
+
+color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple","CRPS"="green")
+
+fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
+  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
+  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
+  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
+  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
+  labs(x="Year",y="",color="legend")+
+  #ggtitle("Figure 12: S&P500 Score traces-upper tail")+
+  scale_x_date(date_breaks = "years",date_labels = "%y")+
+  scale_color_manual(values = color2)+
+  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.05,label="Global Financial Crisis",color="darkred")+
+  theme_clean()
+
+# put two plots side by side 
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure ?(a) Lower Tail","Figure ?(b) Upper Tail"))
+
+```

### 2020-07-21 new table formatting.Rmd
simulation design table DONE!
add cover page and insert resized matlab figure in-line.

@@
   pdf_document: default
-
 editor_options:
@@
 ```
+
+```{r}
+knitr::include_graphics("draft cover page.pdf")
+```
+
+\pagebreak
 
@@
 # insert pdf pictures 
-try to insert pdf pictures:
+try to insert pdf pictures:https://au.mathworks.com/matlabcentral/answers/47357-save-figure-in-a-certain-size
 
@@
 \@ref(fig:img)
+
+# simulation design table
+
+\begin{table}[!h]
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
+\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & copula \\
+& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^0.5 * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline
+
+\textbf{Assumed Model} & $y_t = \sigma_t \epsilon_t$ & $y_t = \sigma_t \epsilon_t$\\ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
+\end{tabular}
+\end{table}

### 2020-07-21 Draft.Rmd
initial version of thesis draft

---
title: "Draft"
author: "Yuru"
date: "22/07/2020"
output: 
  pdf_document:
    fig_height: 4
    fig_width: 6
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE)
```

```{r}
knitr::include_graphics("draft cover page.pdf")
```

\pagebreak

```{r, message=FALSE}
library(formattable)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(tsibbledata)
library(feasts)
library(normtest)
library(moments)
library(ggthemes)
library(ggpubr)
library(knitr)
library(kableExtra)
```

# Simulation section

### Simulation design table

\begin{table}[!h]
\centering
\begin{tabular}{|c|c|c|}
\hline
          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & copula \\
& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^0.5 * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline

\textbf{Assumed Model} & $y_t = \sigma_t \epsilon_t$ & $y_t = \sigma_t \epsilon_t$\\ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
\end{tabular}
\end{table}

```{r}
# Editting the matlab written csv files

GARCH_t12 <- read.csv("GARCH_t12__table.csv")
GARCH_t12 <- rename(GARCH_t12, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
GARCH_t12$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

GARCH_t3 <- read.csv("GARCH_t3_table.csv")
GARCH_t3 <- rename(GARCH_t3, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
GARCH_t3$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

ARCH_table <- read.csv("ARCH_table.csv")
ARCH_table <- rename(ARCH_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
ARCH_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

Copula5_table <- read.csv("Copula5_table.csv")
Copula5_table <- rename(Copula5_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
Copula5_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

Copula3_table <- read.csv("Copula3_table.csv")
Copula3_table <- rename(Copula3_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
Copula3_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

Copula0_table <- read.csv("Copula0_table.csv")
Copula0_table <- rename(Copula0_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
Copula0_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

```

```{r}
ARCH_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 1: the true DGP is ARCH(1)"=7))
```

```{r}
GARCH_t12 %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 2: the true DGP is GARCH(1,1) with degree of freedom = 12"=7))
```

```{r}
GARCH_t3 %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 3: the true DGP is GARCH(1,1) with degree of freedom = 3"=7))
```

```{r}

Copula0_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 4: the true DGP is copula with shape parameter = 0"=7))
```

```{r}
Copula3_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 5: the true DGP is copula with shape parameter = -3"=7))
```

```{r}
Copula5_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 6: the true DGP is copula with shape parameter = -5"=7))
```

# Score trace for simulation

```{r, out.width="600px",fig.align='center'}
knitr::include_graphics("figure 1.pdf")
```

```{r, out.width="600px",fig.align='center'}
# knitr::include_graphics("figure 2.pdf")
```

# Probabilistic density over time

```{r, out.width="600px",fig.align='center'}
# knitr::include_graphics("figure 1.pdf")
```

```{r, out.width="600px",fig.align='center'}
# knitr::include_graphics("figure 2.pdf")
```

# Empirical Analysis
## S&P500

```{r}
# data cleaning and import 
sp <- read.csv("^GSPC.csv")
sp <- sp %>% dplyr::select("Date","Adj.Close")

sp$log.returns <- c(NA,diff(log(sp$Adj.Close)))
logret <- sp[-c(1:41),c(1,3)] # delete the adjusted price col, only keep 6000 obs

# export the dataset to csv. including only trading days and log returns 
temp <- logret[,c(2)]
temp <- data.frame(temp)
write_csv(temp,"sp500log.csv")
```

```{r, results='hide'}
# descriptive statistics 
summary(logret$log.returns) # ----> need to be tabulated 
range(logret$log.returns)
# some test results aginst normal dist h_null
# JB test
jb.norm.test(logret$log.returns)
# Ljung box test
Box.test(logret$log.returns,lag = 2,type = "Lj",fitdf = 1)

skewness(logret$log.returns)
kurtosis(logret$log.returns)
```

```{r}
sum <- data.frame(Stock="S&P500",Min=-0.1276522,Median=0.0006105,Mean=0.0002453,Max=0.1095720,Skewness= -0.3807978,Kurtosis=13.5123,JB.Test=27772,LB.Test=60.627)
formattable(sum)
```

```{r,message=FALSE,fig.align='center'}

# time series plot
logret$Date <- as.Date(logret$Date,format = "%Y-%m-%d")

logret %>% ggplot(aes(x = Date, y = log.returns)) +
  geom_line()+theme_classic()+labs(x="Year",y="Daily log returns")+
  ggtitle("Figure 9: S&P500 daily log returns")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_y_continuous(labels = scales::percent) + 
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.12,label="Global Financial Crisis",color="red",size=3)+
  annotate(geom = 'text',x=as.Date("2020-04-01"),y=-0.12,label="COVID-19",color="red",size=2)+
  theme_clean()+
  labs(caption = "Figure 9: the time series plot of S&P500 daily log returns")

# histogram plots
logret %>% ggplot()+geom_histogram(aes(x=log.returns))+xlim(-0.13,0.13)+ggtitle("Figure 10")+
  scale_x_continuous(labels = scales::percent)+theme_clean()+
  labs(caption = "Figure 10: the distribution of S&P500 log returns is asymmetric")

# ACF plots to see the autocorrelation 
logret <- logret %>% 
  mutate(trading_day = row_number()) %>%
  as_tsibble(index = trading_day,regular = TRUE)

logret %>% ACF((log.returns)^2) %>% autoplot() + ggtitle("Figure 11:Squared log returns autocorrelation")+xlab("number of lags")+ylab("ACF")+theme_clean()+labs(caption = "Figure 11: the autocorrelation plot shows there is a strong serial correlation in volatility of S&P500")
```

##### Average scores

```{r}
sp_table <- read.csv("sp_table.csv")
sp_table <- rename(sp_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
sp_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

sp_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 9: Average scores for S&P500"=7))
```

The average score table, similar to simulation analysis, is produced for daily logarithmic returns of S&P500. For example, in column 4 (FSR10), a focused score at 10% will produce the optimal prediction in terms of forecasting the 10% tail of the returns’ distribution. The results in this table indicate that we expect to gain considerably from optimal probabilistic forecasts in practice.

##### Score traces

```{r,fig.width=10,fig.height=5}
# to compress all the calculated plotting average scores together in the same df 
trace_fsr10 <- read.csv("fsr10.csv")
trace_fsr20 <- read.csv("fsr20.csv")
trace_10ls <- read.csv("fsr10_ls.csv")
trace_10crps <- read.csv("fsr10_crps.csv")

fsr10 <- data.frame(trace_fsr10,trace_fsr20,trace_10ls,trace_10crps)

# add back dates to the fsr10 df, initial step = 1000

fsr10 <- fsr10 %>% mutate(Date = logret$Date[1001:6000])

# plot scores --- lower tail 
fsr10$Date <- as.Date(fsr10$Date,format = "%Y-%m-%d")

color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple","CRPS"="green")

fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
  labs(x="Year",y="Average Scores",color="legend")+
  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_color_manual(values = color1)+
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
  theme_clean()

# plot scores --- upper tail 
trace_fsr90 <- read.csv("fsr90.csv")
trace_fsr80 <- read.csv("fsr80.csv")
trace_90ls <- read.csv("fsr90_ls.csv")
trace_90crps <- read.csv("fsr90_crps.csv")

fsr90 <- data.frame(trace_fsr90,trace_fsr80,trace_90ls,trace_90crps)

# add back dates to the fsr10 df, initial step = 1000

fsr90 <- fsr90 %>% mutate(Date = logret$Date[1001:6000])

# plot scores --- lower tail 
fsr90$Date <- as.Date(fsr90$Date,format = "%Y-%m-%d")

color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple","CRPS"="green")

fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
  labs(x="Year",y="",color="legend")+
  #ggtitle("Figure 12: S&P500 Score traces-upper tail")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_color_manual(values = color2)+
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.05,label="Global Financial Crisis",color="darkred")+
  theme_clean()

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 12(a) Lower Tail","Figure 12(b) Upper Tail"))

```

## VIX

The following tables and figures are produced by CBOE VIX data from 13 Aug,1996 - 16 July,2020 with daily frequency.

Initial sample size = 1000

Out-of-sample size = 5000

### Predictive model: 
Let $y_t$ = $log(VIX_t)$, then 
$$y_{t+1}=\beta_0+\beta_1y_t+\beta_2y_{t-5,t}+\beta_3y_{t-22,t}+\sigma_{t+1}z_{t+1}, \\z_{t+1} \sim N(0,1)$$ 
$$\hat y_{t+1}=\hat \beta_0+ \hat \beta_1y_t+\hat \beta_2y_{t-5,t}+\hat \beta_3y_{t-22,t}$$
$$\hat y_{t+2}=\hat \beta_0+\hat \beta_1 \hat y_{t+1}+\hat \beta_2y_{t-4,t+1}+\hat \beta_3y_{t-21,t+1}$$
$$y_{t-5,t}=\frac{1}{5}(y_t+...+y_{t-4})$$
$$y_{t-22,t}=\frac{1}{22}(y_t+...+y_{t-21})$$

```{r,message=F}
# data cleaning and import 
vix <- read.csv("^VIX.csv")
vix <- vix %>% dplyr::select("Date","Adj.Close")

vix$logvix <- log(vix$Adj.Close)

# previous day log vix values
prev <- matrix(0,nrow = nrow(vix)+1,ncol = 1)
for (i in 1:nrow(vix)){
  prev[1,1] <- c("NA")
  prev[i+1,1] <- vix$logvix[i]
}
prev <- as.data.frame(prev)
prev <- prev[-c(1:178,6179),1]

# need to be very careful about the time index -- dependent variable starting with t+1
MA5 <- matrix(0,nrow=nrow(vix)-5,ncol = 1)
for (i in 1:(nrow(vix)-5)){
  sum = 0
  for (j in 1:5){
    sum = sum + vix$logvix[i+j-1]
  }
  MA5[i,1] = (1/5)*sum
}

MA22 <- matrix(0,nrow = nrow(vix)-22,ncol = 1)
for (i in 1:(nrow(vix)-22)){
  sum = 0
  for (j in 1:22){
    sum = sum + vix$logvix[i+j-1]
  }
  MA22[i,1] = (1/22)*sum
}

#require(zoo)
#MA5 <- rollmean(vix$logvix,5,align = "center")
MA5 <- as.data.frame(MA5) # average of past week
MA5 <- MA5[-c(1:173),1] # including only 6000 obs

#MA22 <- rollmean(vix$logvix,22,align = "center")
MA22 <- as.data.frame(MA22) # average of past month
MA22 <- MA22[-c(1:156),1] # including only 6000 obs

logvix <- vix[-c(1:178),c(1,3)] # delete the adjusted vix col, only keep 6000 obs
logvix <- cbind(logvix,prev,MA5,MA22)
# export the dataset to csv. including only trading days and log returns

# temp <- logvix[,2:5]
# write_csv(temp,"vixlog.csv")

# the logvix, previous log vix and moving average values have the same length in the final file. 
```

```{r, results='hide'}
# descriptive statistics 
summary(vix$logvix) # ----> need to be tabulated 
# summary(vix$Adj.Close)
range(vix$logvix)
# some test results aginst normal dist h_null
# JB test
jb.norm.test(vix$logvix)
# Ljung box test
Box.test(vix$logvix,lag = 2,type = "Lj",fitdf = 1)

vixsk <- skewness(vix$logvix)
vixkt <- kurtosis(vix$logvix)
```

```{r}
sum <- data.frame(Series="Log(VIX)",Min = 2.213, Median = 2.916, Max = 4.415,Skewness= vixsk,Kurtosis=vixkt,JB.Test=415.06,LB.Test=11744)
formattable(sum)
```

```{r,message=FALSE,fig.align='center'}

# time series plot
logvix$Date <- as.Date(logvix$Date,format = "%Y-%m-%d")

logvix %>% ggplot(aes(x = Date, y = logvix)) +
  geom_line()+theme_classic()+labs(x="Year",y="Daily log(VIX) values")+
  ggtitle("Figure ?: Daily values for Log(VIX)")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  #scale_y_continuous(labels = scales::percent) + 
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=2,label="Global Financial Crisis",color="red",size=3)+
  annotate(geom = 'text',x=as.Date("2020-04-01"),y=2,label="COVID-19",color="red",size=3)+
  theme_clean()+
  labs(caption = "Figure ?: the time series plot of daily log(VIX) values")

# histogram plots
logvix %>% ggplot()+geom_histogram(aes(x=logvix))+ggtitle("Figure ?")+
  #scale_x_continuous(labels = scales::percent)+
  theme_clean()+
  labs(caption = "Figure ?: the distribution of log(VIX) is asymmetric")

# ACF plots to see the autocorrelation 
logvix <- logvix %>% 
  mutate(trading_day = row_number()) %>%
  as_tsibble(index = trading_day,regular = TRUE)

logvix %>% ACF((logvix)^2) %>% autoplot() + ggtitle("Figure ?:autocorrelation of log(VIX)")+xlab("number of lags")+ylab("ACF")+theme_clean()+labs(caption = "Figure 11: the autocorrelation plot shows there is a strong serial correlation in variance of log(VIX)")
```

```{r}
vix_table <- read.csv("vix_table.csv")
vix_table <- rename(vix_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
vix_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")

vix_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T) %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table ?: Average scores for VIX"=7))
```

The lower (upper) tail shows the prediction evaluation of 4 scoring rules by FSR10 (FSR90).

The scoring rules used for optimization are {MLE, CRPS, FSR10(90), FSR20(80)}.

```{r,fig.width=10,fig.height=5}
# to compress all the calculated plotting average scores together in the same df 
trace_fsr10 <- read.csv("vixfsr10.csv")
trace_fsr20 <- read.csv("vixfsr20.csv")
trace_10ls <- read.csv("vixfsr10_ls.csv")
trace_10crps <- read.csv("vixfsr10_crps.csv")

fsr10 <- data.frame(trace_fsr10,trace_fsr20,trace_10ls,trace_10crps)

# add back dates to the fsr10 df, initial step = 1000

fsr10 <- fsr10 %>% mutate(Date = vix$Date[1001:6000])

# plot scores --- lower tail 
fsr10$Date <- as.Date(fsr10$Date,format = "%Y-%m-%d")

color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple","CRPS"="green")

fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
  labs(x="Year",y="Average Scores",color="legend")+
  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_color_manual(values = color1)+
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
  theme_clean()

# plot scores --- upper tail 
trace_fsr90 <- read.csv("vixfsr90.csv")
trace_fsr80 <- read.csv("vixfsr80.csv")
trace_90ls <- read.csv("vixfsr90_ls.csv")
trace_90crps <- read.csv("vixfsr90_crps.csv")

fsr90 <- data.frame(trace_fsr90,trace_fsr80,trace_90ls,trace_90crps)

# add back dates to the fsr10 df, initial step = 1000

fsr90 <- fsr90 %>% mutate(Date = vix$Date[1001:6000])

# plot scores --- lower tail 
fsr90$Date <- as.Date(fsr90$Date,format = "%Y-%m-%d")

color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple","CRPS"="green")

fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
  labs(x="Year",y="",color="legend")+
  #ggtitle("Figure 12: S&P500 Score traces-upper tail")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_color_manual(values = color2)+
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.05,label="Global Financial Crisis",color="darkred")+
  theme_clean()

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure ?(a) Lower Tail","Figure ?(b) Upper Tail"))

```

# Reference

### 2020-07-21 Draft.Rmd
fixed formattable table for descriptive analysis problem

@@
 sum <- data.frame(Stock="S&P500",Min=-0.1276522,Median=0.0006105,Mean=0.0002453,Max=0.1095720,Skewness= -0.3807978,Kurtosis=13.5123,JB.Test=27772,LB.Test=60.627)
-formattable(sum)
+sum %>% 
+  kable("latex",booktabs = T) %>% kable_styling("bordered")
 ```
@@
 sum <- data.frame(Series="Log(VIX)",Min = 2.213, Median = 2.916, Max = 4.415,Skewness= vixsk,Kurtosis=vixkt,JB.Test=415.06,LB.Test=11744)
-formattable(sum)
+sum %>% 
+  kable("latex",booktabs = T) %>% kable_styling("bordered")
 ```

### 2020-07-23 Draft.Rmd
delete default knitr title page
fixed the weird line space in kable. it automatically add a line after 5 rows.

--- 2020-07-21 Draft.Rmd
@@
 ---
-title: "Draft"
-author: "Yuru"
-date: "22/07/2020"
 output: 
@@
   chunk_output_type: console
+compact-title: false
 ---
@@
   ) %>%
-  kable("latex",escape = F, booktabs = T) %>%
+  kable("latex",escape = F, booktabs = T, linesep = "") %>%
   kable_styling("bordered",full_width = F)%>%
@@
 sum <- data.frame(Stock="S&P500",Min=-0.1276522,Median=0.0006105,Mean=0.0002453,Max=0.1095720,Skewness= -0.3807978,Kurtosis=13.5123,JB.Test=27772,LB.Test=60.627)
-formattable(sum)
+sum %>% 
+  kable("latex",booktabs = T) %>% 
+  kable_styling("bordered") %>% 
+  add_header_above(c("Table ?: Descriptive statistics"=9))
 ```
@@
 ```{r}
-sum <- data.frame(Series="Log(VIX)",Min = 2.213, Median = 2.916, Max = 4.415,Skewness= vixsk,Kurtosis=vixkt,JB.Test=415.06,LB.Test=11744)
-formattable(sum)
+sum <- data.frame(Series="Log(VIX)",Min = 2.213, Median = 2.916, Mean = 2.935, Max = 4.415,Skewness= vixsk,Kurtosis=vixkt,JB.Test=415.06,LB.Test=11744)
+sum %>% 
+  kable("latex",booktabs = T) %>% 
+  kable_styling("bordered")%>% 
+  add_header_above(c("Table ?: Descriptive statistics"=9))
 ```

### 2020-07-27 Draft.Rmd
automatically number equations in r
include newly writen part of the thesis (need to review) and VaR analysis for both simulation and sp500 (table need to be fixed for knitting)

@@
 ---
+compact-title: no
+editor_options:
+  chunk_output_type: console
 output:
@@
     fig_width: 6
-editor_options: 
-  chunk_output_type: console
-compact-title: false
 ---
@@
 
-# Simulation section
+# Abstract
 
-### Simulation design table
+\pagebreak
+
+# 1. Introduction
+
+# 2. Scoring rule in prediction
+## 2.1 Overview and notation
+
+Scoring rules can be used in both estimation and prediction.
+In estimation, an optimum estimator $\hat \theta$ can be obtained by maximizing a scoring rule $S_n$.
+That is, $\hat \theta_n=arg \max_\theta S_n(\theta)$.
+$\hat \theta \to \theta$ as $n \to \infty$ under asymptotic situations.
+While in prediction, scoring rules assign a numerical value to density forecasts, addressing both sharpness and calibration.
+For a positively oriented score, higher value will be assigned to a better forecast between two competing candidates.
+A variety of proper scoring rules allows users to produce probability predictions based on their interests, and to compare these predictions, as long as they refer to the same forecast quantity.
+Forecasts candidates are often compared by their average scores.
+Therefore, the crucial importance of the propreity of scoring rules must be emphasized.Gneiting & Raftery, (2007) illustrate the importance of propreity via a case study in weather forecasts and point out that improper scoring rules will assign higher average score to an incorrect density forecast.
+A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and it is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q.
+P and Q are predictive distributions and Q is the best forecast given all the available information.
+S(P,Q) means the expected value of S(P,$\cdot$) under Q (Gneiting & Raftery, 2007).
+
+Some commonly used proper scoring rules are the logarithmic score (LS), the continuously ranked probability score (CRPS) and censored likelihood score (CSL) or focused score (FSR) in a sense that CSL is used for focusing on a certain region(s) of densities.
+
+The logarithmic score is defined as (1) where $p_t$ is the density forecasts.
+It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of nonlinear utility function used is a concern for forecasters (Bickel, 2007).
+\begin{align}
+S_{LS}(p_t, y_{t+1}) = log[p_t(y_{t+1})]
+\end{align}
+However, logarithmic score is criticized by its unboundness and its local property.
+Its useness is also questioned in (Bernardo, 1979), since he shows that every proper scoring rule is equivalent to logarithmic score.
+Gneiting & Raftery, (2007) argue that logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized one.
+Therefore, Gneiting & Raftery, (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in (2) where P is the cumulative distriubtion function, I is the indication function, and x is the materialized events.
+
+\begin{align}
+CRPS(P,x)=-\int_{-\infty}^{\infty}(P(y)-I(y\geq x))^2dy
+\end{align}
+
+The formula can be simplifed to (3) if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
+\begin{align}
+CRPS(N,x)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x-\mu}{\sigma})-\frac{x-\mu}{\sigma}(2\Phi(\frac{x-\mu}{\sigma})-1)]
+\end{align}
+where $\phi$ and $\Phi$ are the probability density function and cumulative density function of the Gaussian predictive distribution.
+
+Continuously ranked probability score is defined as a negatively oriented scoring rule, but it can be easily transformed to positively oriented score for convenient comparison among scoring rules as shown in (4).
+
+\begin{align}
+CRPS^*(N,x)=\sigma[-\frac{1}{\sqrt{\pi}}+2\phi(\frac{x-\mu}{\sigma})+\frac{x-\mu}{\sigma}(2\Phi(\frac{x-\mu}{\sigma})-1)]
+\end{align}
+
+Both logarithmic score and continuously ranked probability score are used for producing and evaluating the entire predictive density.
+In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011).
+Diks, Panchenko & van Dijk, (2011) propose a new proper scoring rule, censored likelihood score, which allows users to assess the forecasts only in the interested region(s) instead of using weights to emphasize a particular part of the entire density forecast.
+It is defined as in (5) where $p_t$ is the predictive probability density function, $A_t$ is the interested region(s) and $A_t^c$ is the complement of $A_t$.
+
+\begin{align}
+S_{CSL}(p_t, y_{t+1})=I(y_{t+1} \in A_t)log[ p_t(y_{t+1})]+I(y_{t+1} \in A_t^c)log[\int_{A_t^c} p_t(s)ds]
+\end{align}
+
+[ref 5] prove that weighted density forecasts based on optimizing the censored likelihood score outperform those on logarithmic score and continuously ranked probability score.
+
+## 2.2 Illustration example 
+### 2.2.1 Simulation overview
+
+Density forecasts provide more complete information of uncertainty of a prediction than point and interval forecasts.
+Moreover, the tails of a density have a great importance in finance.
+It forms the foundation of risk management, such as Value-at-Risk (VaR), and asset allocation.
+It can also be used in derivatives pricing.
+(reference ?) --- find some papers.
+
+[ref 5] provide empirical results showing that using censored likelihood score can improve 99% Value-at-Risk estimation.
+Moreover, Loaiza-Maya, Martin & Frazier, (2019) propose a new method, Focused Bayes, in Bayeisian prediction by replacing the conventional likelihood function with the censored likelihood score.
+Their results show that Focused Bayes outperform exact Bayes which is using logarithmic score for updating the prior probability.
+Their work also points out the degree of model misspecification play a role in the performance of Focused Bayes.
+
+Loaiza-Maya et al., (2020) extend the above discussion to frequentist probability forecasting.
+They address questions about when we can/cannot benefit from optimal probabilistic forecasts out of sample.
+A predictive probability distribution is said to be optimal if it is optimal based on a user-specified scoring rule, not generally speaking.
+
+Building on the previous research in this field, we conduct a numerical analysis first in section 2.2.2 and 2.2.3 to further investigate the effects of the form and degree of model misspecification on optimal forecast performance using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and copula models.
+
+### 2.2.2 Simulation design
+
+In order to prepare the financial application analysis in following sections of this paper, we simulate a time series dependnet variable $y_t$ that mimic the behavior of financial returns and volatility.
+Specifically, GARCH models can capture the volatility clustering and serial dependence, and the negative marginal skewness will be introducted using an inversion copula with degree of skewness controlled by the shape parameter showed below.
+In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model.
+
+Specific simulation scenarios are listed as follows ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom):
 
@@
 \end{table}
+
+The methodology in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) is adopted. We conduct each simulation scenario as follows (Loaiza-Maya et al., 2020):
+
+  1.	Generate T = 6000 observations for $y_t$ from the true DGP
+
+  2.	Use $y_{1:1000}$ to estimate $\hat \theta$ in the assumed predictive model based on the positively-oriented score $S_i$
+
+\begin{align}
+{\hat \theta^{[i]}}:=arg\max_{\theta \in \Theta}\bar S_i({\theta})
+\end{align}
+
+\begin{align}
+\bar S_i(\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\theta}^{t-1},y_t)
+\end{align}
+
+  3.	Produce the one-step-ahead predictive $P^{t-1}_{\hat \theta_1^{[i]}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (?)(?)(?)
+
+....
+
+### 2.2.3 Simulation results
 
@@
 # Probabilistic density over time 
+### 6.1.3 Predictive Densities
 
-```{r, out.width="600px",fig.align='center'}
-# knitr::include_graphics("figure 1.pdf")
+The predictive density plots provide a straightforward way to visualize how optimal probabilistic forecast matches the shape of true DGP distribution at diﬀerent time.
+
+```{r, out.width="600px"}
+knitr::include_graphics("figure 3.png")
 ```
 
-```{r, out.width="600px",fig.align='center'}
-# knitr::include_graphics("figure 2.pdf")
+```{r, out.width="600px"}
+knitr::include_graphics("figure 4.png")
 ```
+
+```{r, out.width="600px"}
+knitr::include_graphics("figure 5.png")
+```
+
+```{r, out.width="600px"}
+knitr::include_graphics("figure 6.png")
+```
+
+```{r, out.width="600px"}
+knitr::include_graphics("figure 7.png")
+```
+
+```{r, out.width="600px"}
+knitr::include_graphics("figure 8.png")
+```
+
+# Value-at-Risk 
+```{r, eval=False}
+copula5var <- read.csv("copula5var.csv")
+
+VaR0.1 <- as.numeric(copula5var[,c(1,5,9,13,17,21)])
+VaR0.2 <- as.numeric(copula5var[,c(2,6,10,14,18,22)])
+VaR0.8 <- as.numeric(copula5var[,c(3,7,11,15,19,23)])
+VaR0.9 <- as.numeric(copula5var[,c(4,8,12,16,20,24)])
+
+Optimizers <- c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+
+df <- data.frame(Optimizers,VaR0.1,VaR0.2,VaR0.8,VaR0.9)
+# df <- rename(df,"VaR at 10%"=VaR0.1, "VaR at 20%"=VaR0.2, "VaR at 80%"=VaR0.8, "VaR at 90%"=VaR0.9)
+
+df %>% 
+  mutate(
+    `VaR0.1` = cell_spec(format(`VaR0.1`,4),"latex",bold = ifelse(abs(`VaR0.1`-0.1) == min(abs(`VaR0.1`-0.1)),TRUE,FALSE)),
+    `VaR0.2` = cell_spec(format(`VaR0.2`,4),"latex",bold = ifelse(abs(`VaR0.2`-0.2) == min(abs(`VaR0.2`-0.2)),TRUE,FALSE)),
+    `VaR0.8` = cell_spec(format(`VaR0.8`,4),"latex",bold = ifelse(abs(`VaR0.8`-0.8) == min(abs(`VaR0.8`-0.8)),TRUE,FALSE)),
+    `VaR0.9` = cell_spec(format(`VaR0.9`,4),"latex",bold = ifelse(abs(`VaR0.9`-0.9) == min(abs(`VaR0.9`-0.9)),TRUE,FALSE))
+  ) %>%
+  kable("latex",escape = F, booktabs=T, linesep = "") %>%
+  kable_styling("bordered",full_width = F) %>%
+  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
+  add_header_above(c("Table 7: Value-at-Risk when true DGP is copula (shape = -5)"=5))
+```
+
+```{r, eval=False}
+garch3var <- read.csv("garch3var.csv")
+
+VaR0.1 <- as.numeric(garch3var[,c(1,5,9,13,17,21)])
+VaR0.2 <- as.numeric(garch3var[,c(2,6,10,14,18,22)])
+VaR0.8 <- as.numeric(garch3var[,c(3,7,11,15,19,23)])
+VaR0.9 <- as.numeric(garch3var[,c(4,8,12,16,20,24)])
+
+df <- data.frame(Optimizers,VaR0.1,VaR0.2,VaR0.8,VaR0.9)
+df <- rename(df,"VaR at 10%"=VaR0.1, "VaR at 20%"=VaR0.2, "VaR at 80%"=VaR0.8, "VaR at 90%"=VaR0.9)
+
+df %>% 
+  mutate(
+    `VaR0.1` = cell_spec(format(`VaR0.1`,4),"latex",bold = ifelse(abs(`VaR0.1`-0.1) == min(abs(`VaR0.1`-0.1)),TRUE,FALSE)),
+    `VaR0.2` = cell_spec(format(`VaR0.2`,4),"latex",bold = ifelse(abs(`VaR0.2`-0.2) == min(abs(`VaR0.2`-0.2)),TRUE,FALSE)),
+    `VaR0.8` = cell_spec(format(`VaR0.8`,4),"latex",bold = ifelse(abs(`VaR0.8`-0.8) == min(abs(`VaR0.8`-0.8)),TRUE,FALSE)),
+    `VaR0.9` = cell_spec(format(`VaR0.9`,4),"latex",bold = ifelse(abs(`VaR0.9`-0.9) == min(abs(`VaR0.9`-0.9)),TRUE,FALSE))
+  ) %>%
+  kable("latex",escape = F, booktabs=T, linesep = "") %>%
+  kable_styling("bordered",full_width = F) %>%
+  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
+  add_header_above(c("Table 8: Value-at-Risk when true DGP is GARCH(1,1) with degree of freedom = 3"=5))
+```
+
+The values showed in these tables refer to the proportion of exceedances over the value at risk indicated by the column.
+Thus, the closer the values to nominal VaR levels, the more accurate are the optimal predictions.
+We can see that in two different forms of model misspecification, FSR is strictly superior to other scores in the upper tails, while in the lower tails, the difference is quite small when not strictly preferable.
+This result helps us understand what to expect in practical VaR analysis.
 
@@
 
+```
+
+# VaR analysis of S&P500
+
+#### Table 11: Before 2008 GFC
+
+```{r}
+spvar <- read.csv("spvar1_table.csv")
+
+VaR_0.1 <- as.numeric(spvar[,c(1,5,9,13,17,21)])
+VaR_0.2 <- as.numeric(spvar[,c(2,6,10,14,18,22)])
+VaR_0.8 <- as.numeric(spvar[,c(3,7,11,15,19,23)])
+VaR_0.9 <- as.numeric(spvar[,c(4,8,12,16,20,24)])
+
+df <- data.frame(optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
+
+formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
+```
+
+#### Table 12: After 2008 GFC
+
+```{r}
+spvar <- read.csv("spvar2_table.csv")
+spvar <- round(spvar,digits = 4)
+
+VaR_0.1 <- as.numeric(spvar[,c(1,5,9,13,17,21)])
+VaR_0.2 <- as.numeric(spvar[,c(2,6,10,14,18,22)])
+VaR_0.8 <- as.numeric(spvar[,c(3,7,11,15,19,23)])
+VaR_0.9 <- as.numeric(spvar[,c(4,8,12,16,20,24)])
+
+df <- data.frame(optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
+
+formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
 ```
@@
 
-# Reference
+# References
+
+DON'T forget alphabetical order!!
+
+cite packages used in the draft
+```{r}
+citation("formattable")
+```

### 2020-07-27 Draft.Rmd
fixed the VaR tables and add more texts to simulation result part. re-arrange the descriptive plots (need to make it better later)

@@
   chunk_output_type: console
+  header-includes: usepackage{amsmath}
 output:
   pdf_document:
-    fig_height: 4
-    fig_width: 6
+    fig_height: 3
+    fig_width: 4
 ---
@@
 
-\textbf{Assumed Model} & $y_t = \sigma_t \epsilon_t$ & $y_t = \sigma_t \epsilon_t$\\ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
+\textbf{Assumed Model} & $y_t = \beta+\sigma_t \epsilon_t$ & $y_t = \beta +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
 \end{tabular}
@@
 
-The methodology in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) is adopted. We conduct each simulation scenario as follows (Loaiza-Maya et al., 2020):
+The tails of density are important for risk management in finance so that we decide to apply focused scoring rule (FSR) to 10%, 20%, 80% and 90% tails of the distribution, corresponding to short and long portfolios in finance respectively.
+The methodology in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) is adopted.
+We conduct each simulation scenario as follows (Loaiza-Maya et al., 2020):
 
@@
 
-  2.	Use $y_{1:1000}$ to estimate $\hat \theta$ in the assumed predictive model based on the positively-oriented score $S_i$
+  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}$ in the assumed predictive model based on the positively-oriented score $S_i$ where $\boldsymbol{\hat \theta} = \{\hat \beta, \hat \alpha_0, \hat \alpha_1\}$
 
@@
 ### 2.2.3 Simulation results
+
+Loaiza-Maya et al., (2020) introduce the concepts of ‘coherence’ and ‘strict coherence’ for conveniently documenting the optimal forecasts’ performance.
+Coherence means when the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score.
+Strict coherence is when the optimal prediction is strictly preferable given that score.
+Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on $S_1, S_2$, then the prediction is said to coherent if
+$$\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)$$
+
+$$\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)$$
+
+It is said to be strictly coherent if the equality doesn't hold in (?)(?).
+
+\textbf{[need to mention some results from opt paper - one sentence]}
+
+The first column of following tables shows $S_i$ that we used to produce predictions and the first row shows $S_j$, which is used for forecasts evaluation.
+The bolded value(s) is the maximum(s) in each column.
+We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the score indicated by the column name.
 
@@
 
+The results from Table 1-3 show one particular type of model misspecification.
+That is, the underlying model ARCH(1) cannot capture the volatility clustering feature of the true data generation process (DGP), thus misspecification.
+Besides, with the degree of freedom increases, the data generated from GARCH(1,1) model is more like data that are from ARCH(1) and therefore, the degree of model misspecification decreases.
+When degree of freedom is large enough, we consider ARCH(1) as a correct specified model as shown in Table 1.
+
+From Table 3.
+we could observe strict coherence when degree of model misspecification is high and coherence in Table 1 which is stated as correct specification case.
+These results are consistent with conclusions from (Loiaza-Maya et al., 2020).
+It simply means that we can improve prediction accuracy in the presence of model misspecification ??
+, and gain more from using optimal forecasts method while the degree of model misspecification is high.
+
 ```{r}
@@
 
+\textbf{[need copula paper citation here to explain more]}
+
+Table 4-6 show another type of model misspecification where the underlying model cannot capture the asymmetric feature of the true DGP.
+The results give similar conclusions to Table 1-3.
+It proves that optimal forecasts perform in the same way even when we have different types of model mispecification.
+
 # Score trace for simulation
+
+As stated in previous literature, focused score
 
@@
 # Value-at-Risk
-```{r, eval=False}
+
+```{r}
 copula5var <- read.csv("copula5var.csv")
 
-VaR0.1 <- as.numeric(copula5var[,c(1,5,9,13,17,21)])
-VaR0.2 <- as.numeric(copula5var[,c(2,6,10,14,18,22)])
-VaR0.8 <- as.numeric(copula5var[,c(3,7,11,15,19,23)])
-VaR0.9 <- as.numeric(copula5var[,c(4,8,12,16,20,24)])
+VaR_0.1 <- as.numeric(copula5var[,c(1,5,9,13,17,21)])
+VaR_0.2 <- as.numeric(copula5var[,c(2,6,10,14,18,22)])
+VaR_0.8 <- as.numeric(copula5var[,c(3,7,11,15,19,23)])
+VaR_0.9 <- as.numeric(copula5var[,c(4,8,12,16,20,24)])
 
@@
 
-df <- data.frame(Optimizers,VaR0.1,VaR0.2,VaR0.8,VaR0.9)
-# df <- rename(df,"VaR at 10%"=VaR0.1, "VaR at 20%"=VaR0.2, "VaR at 80%"=VaR0.8, "VaR at 90%"=VaR0.9)
+df <- data.frame(Optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
+df <- rename(df,"VaR at 10\\%"=VaR_0.1, "VaR at 20\\%"=VaR_0.2, "VaR at 80\\%"=VaR_0.8, "VaR at 90\\%"=VaR_0.9)
 
@@
   mutate(
-    `VaR0.1` = cell_spec(format(`VaR0.1`,4),"latex",bold = ifelse(abs(`VaR0.1`-0.1) == min(abs(`VaR0.1`-0.1)),TRUE,FALSE)),
-    `VaR0.2` = cell_spec(format(`VaR0.2`,4),"latex",bold = ifelse(abs(`VaR0.2`-0.2) == min(abs(`VaR0.2`-0.2)),TRUE,FALSE)),
-    `VaR0.8` = cell_spec(format(`VaR0.8`,4),"latex",bold = ifelse(abs(`VaR0.8`-0.8) == min(abs(`VaR0.8`-0.8)),TRUE,FALSE)),
-    `VaR0.9` = cell_spec(format(`VaR0.9`,4),"latex",bold = ifelse(abs(`VaR0.9`-0.9) == min(abs(`VaR0.9`-0.9)),TRUE,FALSE))
+    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
+    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
+    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
+    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
   ) %>%
-  kable("latex",escape = F, booktabs=T, linesep = "") %>%
+  kable("latex",escape = F,booktabs=T, linesep = "") %>%
   kable_styling("bordered",full_width = F) %>%
@@
 
-```{r, eval=False}
+```{r}
 garch3var <- read.csv("garch3var.csv")
@@
 df <- data.frame(Optimizers,VaR0.1,VaR0.2,VaR0.8,VaR0.9)
-df <- rename(df,"VaR at 10%"=VaR0.1, "VaR at 20%"=VaR0.2, "VaR at 80%"=VaR0.8, "VaR at 90%"=VaR0.9)
+df <- rename(df,"VaR at 10\\%"=VaR0.1, "VaR at 20\\%"=VaR0.2, "VaR at 80\\%"=VaR0.8, "VaR at 90\\%"=VaR0.9)
 
@@
   mutate(
-    `VaR0.1` = cell_spec(format(`VaR0.1`,4),"latex",bold = ifelse(abs(`VaR0.1`-0.1) == min(abs(`VaR0.1`-0.1)),TRUE,FALSE)),
-    `VaR0.2` = cell_spec(format(`VaR0.2`,4),"latex",bold = ifelse(abs(`VaR0.2`-0.2) == min(abs(`VaR0.2`-0.2)),TRUE,FALSE)),
-    `VaR0.8` = cell_spec(format(`VaR0.8`,4),"latex",bold = ifelse(abs(`VaR0.8`-0.8) == min(abs(`VaR0.8`-0.8)),TRUE,FALSE)),
-    `VaR0.9` = cell_spec(format(`VaR0.9`,4),"latex",bold = ifelse(abs(`VaR0.9`-0.9) == min(abs(`VaR0.9`-0.9)),TRUE,FALSE))
+    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
+    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
+    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
+    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
   ) %>%
@@
 
-logret %>% ggplot(aes(x = Date, y = log.returns)) +
+p1 <- logret %>% ggplot(aes(x = Date, y = log.returns)) +
   geom_line()+theme_classic()+labs(x="Year",y="Daily log returns")+
-  ggtitle("Figure 9: S&P500 daily log returns")+
+  #ggtitle("Figure 9: S&P500 daily log returns")+
   scale_x_date(date_breaks = "years",date_labels = "%y")+
@@
   annotate(geom = 'text',x=as.Date("2020-04-01"),y=-0.12,label="COVID-19",color="red",size=2)+
-  theme_clean()+
-  labs(caption = "Figure 9: the time series plot of S&P500 daily log returns")
+  theme_clean()
+  #+labs(caption = "Figure 9: the time series plot of S&P500 daily log returns")
 
 # histogram plots
-logret %>% ggplot()+geom_histogram(aes(x=log.returns))+xlim(-0.13,0.13)+ggtitle("Figure 10")+
-  scale_x_continuous(labels = scales::percent)+theme_clean()+
-  labs(caption = "Figure 10: the distribution of S&P500 log returns is asymmetric")
+p2 <- logret %>% ggplot()+geom_histogram(aes(x=log.returns))+xlim(-0.13,0.13)+
+  #ggtitle("Figure 10")+
+  scale_x_continuous(labels = scales::percent)+theme_clean()
+  #+labs(caption = "Figure 10: the distribution of S&P500 log returns is asymmetric")
 
@@
 
-logret %>% ACF((log.returns)^2) %>% autoplot() + ggtitle("Figure 11:Squared log returns autocorrelation")+xlab("number of lags")+ylab("ACF")+theme_clean()+labs(caption = "Figure 11: the autocorrelation plot shows there is a strong serial correlation in volatility of S&P500")
+p3 <- logret %>% ACF((log.returns)^2) %>% autoplot() + 
+  #ggtitle("Figure 11:Squared log returns autocorrelation")+
+  xlab("number of lags")+ylab("ACF")+theme_clean()
+# +labs(caption = "Figure 11: the autocorrelation plot shows there is a strong serial correlation in volatility of S&P500")
+
+ggarrange(p1,p2,p3,ncol=2,nrow = 2, labels = c("A: Time series plot","B: Histogram","C: ACF"),legend = "bottom")
 ```
@@
 
-df <- data.frame(optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
+df <- data.frame(Optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
+df <- rename(df,"VaR at 10\\%"=VaR_0.1, "VaR at 20\\%"=VaR_0.2, "VaR at 80\\%"=VaR_0.8, "VaR at 90\\%"=VaR_0.9)
 
-formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
+df %>% 
+  mutate(
+    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
+    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
+    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
+    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
+  ) %>%
+  kable("latex",escape = F, booktabs=T, linesep = "") %>%
+  kable_styling("bordered",full_width = F) %>%
+  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
+  add_header_above(c("Table ?: VaR for S&P500 before GFC"=5))
+
+# formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
 ```
@@
 
-df <- data.frame(optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
+df <- data.frame(Optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
+df <- rename(df,"VaR at 10\\%"=VaR_0.1, "VaR at 20\\%"=VaR_0.2, "VaR at 80\\%"=VaR_0.8, "VaR at 90\\%"=VaR_0.9)
 
-formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
+df %>% 
+  mutate(
+    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
+    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
+    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
+    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
+  ) %>%
+  kable("latex",escape = F, booktabs=T, linesep = "") %>%
+  kable_styling("bordered",full_width = F) %>%
+  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
+  add_header_above(c("Table ?: VaR for S&P500 after GFC"=5))
+
+# formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
 ```

### 2020-07-28 Draft.Rmd
re-arrange the structure of the draft, add new texts content

@@
   pdf_document:
-    fig_height: 3
-    fig_width: 4
+    fig_height: 3.5
+    fig_width: 4.5
 ---
@@
 
-Specific simulation scenarios are listed as follows ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom):
+Specific simulation scenarios are listed in following table ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).
 
@@
 \hline
+\multicolumn{3}{|c|}{Simulation design} \\ \hline
           & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
@@
 ### 2.2.3 Simulation results
+#### 2.2.3.1 Average score tables
 
@@
 , and gain more from using optimal forecasts method while the degree of model misspecification is high.
+In other words, we are expected to gain more from using focused score when we observe 'strict coherence' while comparing two forecasts.
 
@@
 
-# Score trace for simulation
+#### 2.2.3.2 Score traces plots
 
-As stated in previous literature, focused score
+As stated in previous literature, focused score tends to outperform CRPS and logarithmic score in predicting tails.
+Therefore, we provide score trace plots to exhibit the comparison of LS, CRPS and FSR’s performance in predicting the 10 percentile and 90 percentile in figure 1 and 2.
+In the left panel, it shows the performance of each score evaluated by FSR 10%.
+That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B.
+The right panel shows the same thing but is based on performance of predicting 90 percentile.
+From figure 1 and 2, we could see that FSR makes no difference if the degree of model misspecification is very small but as it increases, FSR starts to outperform CRPS and MLE (LS) in predicting tails.
+The more misspecified the model is, the more benefits can we gain from using FSR.
+It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model in the fact that in practice, a correct model does not exist.
 
-```{r, out.width="600px",fig.align='center'}
+```{r}
+# need to adjust the size. 
 knitr::include_graphics("figure 1.pdf")
@@
 
-```{r, out.width="600px",fig.align='center'}
-# knitr::include_graphics("figure 2.pdf")
+```{r}
+knitr::include_graphics("figure 2.pdf")
 ```
 
-# Probabilistic density over time 
-### 6.1.3 Predictive Densities
+Moreover, the predictive density plots (Appendix 1) in figure 3 to 8, further support our conclusions drawn from the average score tables and score trace plots.
+They show that predictions obtained from optimizing focused scores aim to match the shape of tails of the true distribution and therefore, outperform predictions from using LS.
 
-The predictive density plots provide a straightforward way to visualize how optimal probabilistic forecast matches the shape of true DGP distribution at diﬀerent time.
+## 2.3 Empirical analysis
 
-```{r, out.width="600px"}
-knitr::include_graphics("figure 3.png")
-```
+From the results in section 2.2, we can conclude that optimal forecasts based on focused score can improve the prediction accuracy in tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification.
+In section 2.3, we apply this method to an empirical setting and investigate how it performs in practice.
 
-```{r, out.width="600px"}
-knitr::include_graphics("figure 4.png")
-```
+The data used in the analysis is the continuously compounded daily log returns of S&P500 listed in U.S.A financial market over a time period that precedes the 2008 Global financial crisis (GFC) and extends to the latest period in which COVID-19 has impacts on financial market.
+The methodology used here is the same as in the section 2.2.2 with initial training sample size set to be 1000 and 5000 out-of-sample observations.
 
-```{r, out.width="600px"}
-knitr::include_graphics("figure 5.png")
-```
-
-```{r, out.width="600px"}
-knitr::include_graphics("figure 6.png")
-```
-
-```{r, out.width="600px"}
-knitr::include_graphics("figure 7.png")
-```
-
-```{r, out.width="600px"}
-knitr::include_graphics("figure 8.png")
-```
-
-# Value-at-Risk
-
-```{r}
-copula5var <- read.csv("copula5var.csv")
-
-VaR_0.1 <- as.numeric(copula5var[,c(1,5,9,13,17,21)])
-VaR_0.2 <- as.numeric(copula5var[,c(2,6,10,14,18,22)])
-VaR_0.8 <- as.numeric(copula5var[,c(3,7,11,15,19,23)])
-VaR_0.9 <- as.numeric(copula5var[,c(4,8,12,16,20,24)])
-
-Optimizers <- c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
-
-df <- data.frame(Optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
-df <- rename(df,"VaR at 10\\%"=VaR_0.1, "VaR at 20\\%"=VaR_0.2, "VaR at 80\\%"=VaR_0.8, "VaR at 90\\%"=VaR_0.9)
-
-df %>% 
-  mutate(
-    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
-    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
-    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
-    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F,booktabs=T, linesep = "") %>%
-  kable_styling("bordered",full_width = F) %>%
-  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 7: Value-at-Risk when true DGP is copula (shape = -5)"=5))
-```
-
-```{r}
-garch3var <- read.csv("garch3var.csv")
-
-VaR0.1 <- as.numeric(garch3var[,c(1,5,9,13,17,21)])
-VaR0.2 <- as.numeric(garch3var[,c(2,6,10,14,18,22)])
-VaR0.8 <- as.numeric(garch3var[,c(3,7,11,15,19,23)])
-VaR0.9 <- as.numeric(garch3var[,c(4,8,12,16,20,24)])
-
-df <- data.frame(Optimizers,VaR0.1,VaR0.2,VaR0.8,VaR0.9)
-df <- rename(df,"VaR at 10\\%"=VaR0.1, "VaR at 20\\%"=VaR0.2, "VaR at 80\\%"=VaR0.8, "VaR at 90\\%"=VaR0.9)
-
-df %>% 
-  mutate(
-    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
-    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
-    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
-    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs=T, linesep = "") %>%
-  kable_styling("bordered",full_width = F) %>%
-  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 8: Value-at-Risk when true DGP is GARCH(1,1) with degree of freedom = 3"=5))
-```
-
-The values showed in these tables refer to the proportion of exceedances over the value at risk indicated by the column.
-Thus, the closer the values to nominal VaR levels, the more accurate are the optimal predictions.
-We can see that in two different forms of model misspecification, FSR is strictly superior to other scores in the upper tails, while in the lower tails, the difference is quite small when not strictly preferable.
-This result helps us understand what to expect in practical VaR analysis.
-
-# Empirical Analysis
-## S&P500
+### 2.3.1 Empirical analysis results
 
@@
 
-```{r,message=FALSE,fig.align='center'}
+```{r,message=FALSE,fig.align="center"}
 
@@
 
-##### Average scores
+The descriptive statistics shows that the distribution of S&P500 log returns are negatively skewed and have fat tails and strong serial correlation.
+Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.
+
+The reality is always the most complicated and the underlying ARCH(1) should have a high degree of model misspecification.
+Therefore, we should expect that predictions produced by optimizing FSR do a better job in predicting two tails of the distribution.
+The results of Table 9 support our conjecture.
+However, the difference between using FSR10(80) and FSR20(90) is very small.
 
@@
 
-The average score table, similar to simulation analysis, is produced for daily logarithmic returns of S&P500.
-For example, in column 4 (FSR10), a focused score at 10% will produce the optimal prediction in terms of forecasting the 10% tail of the returns’ distribution.
-The results in this table indicate that we expect to gain considerably from optimal probabilistic forecasts in practice.
-
-##### Score traces
+Unlike simulation, the score trace plots show how different scoring rules perform in real time points which correspond to some important events.
+In figure 12, one interesting phenomenon is that after the GFC, focused score performs much better than CRPS and MLE in terms of predicting both upper and lower tails.
+And this 'jump' effect continues until the very recent date.
+It indicates that optimal probabilistic forecasts might predict financial markets better in and after times of stock market turbulance, which could represent a great contribution to the existing financial analyses of risks and returns.
 
@@
 
-# VaR analysis of S&P500
+# 3. Finanical application: Value-at-Risk
+## 3.1 Overview of Value-at-Risk
 
-#### Table 11: Before 2008 GFC
+## 3.2 Value-at-Risk for simulation analysis
+We illustrate our Value-at-Risk analysis by firstly using simulation data from section 2.
+
+```{r}
+copula5var <- read.csv("copula5var.csv")
+
+VaR_0.1 <- as.numeric(copula5var[,c(1,5,9,13,17,21)])
+VaR_0.2 <- as.numeric(copula5var[,c(2,6,10,14,18,22)])
+VaR_0.8 <- as.numeric(copula5var[,c(3,7,11,15,19,23)])
+VaR_0.9 <- as.numeric(copula5var[,c(4,8,12,16,20,24)])
+
+Optimizers <- c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+
+df <- data.frame(Optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
+df <- rename(df,"VaR at 10\\%"=VaR_0.1, "VaR at 20\\%"=VaR_0.2, "VaR at 80\\%"=VaR_0.8, "VaR at 90\\%"=VaR_0.9)
+
+df %>% 
+  mutate(
+    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
+    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
+    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
+    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
+  ) %>%
+  kable("latex",escape = F,booktabs=T, linesep = "") %>%
+  kable_styling("bordered",full_width = F) %>%
+  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
+  add_header_above(c("Table 7: VaR when true DGP is copula (shape = -5)"=5))
+```
+
+```{r}
+garch3var <- read.csv("garch3var.csv")
+
+VaR0.1 <- as.numeric(garch3var[,c(1,5,9,13,17,21)])
+VaR0.2 <- as.numeric(garch3var[,c(2,6,10,14,18,22)])
+VaR0.8 <- as.numeric(garch3var[,c(3,7,11,15,19,23)])
+VaR0.9 <- as.numeric(garch3var[,c(4,8,12,16,20,24)])
+
+df <- data.frame(Optimizers,VaR0.1,VaR0.2,VaR0.8,VaR0.9)
+df <- rename(df,"VaR at 10\\%"=VaR0.1, "VaR at 20\\%"=VaR0.2, "VaR at 80\\%"=VaR0.8, "VaR at 90\\%"=VaR0.9)
+
+df %>% 
+  mutate(
+    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
+    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
+    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
+    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
+  ) %>%
+  kable("latex",escape = F, booktabs=T, linesep = "") %>%
+  kable_styling("bordered",full_width = F) %>%
+  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
+  add_header_above(c("Table 8: VaR when true DGP is GARCH with degree of freedom = 3"=5))
+```
+
+The values showed in these tables refer to the proportion of exceedances over the value at risk indicated by the column.
+Thus, the closer the values to nominal VaR levels, the more accurate are the optimal predictions.
+We can see that in two different forms of model misspecification, FSR is strictly superior to other scores in the upper tails, while in the lower tails, the difference is quite small when not strictly preferable.
+This result helps us understand what to expect in practical VaR analysis.
+
+## 3.3 Value-at-Risk for empirical analysis
 
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table ?: VaR for S&P500 before GFC"=5))
+  add_header_above(c("Table 11: VaR for S&P500 before GFC"=5))
 
@@
 ```
-
-#### Table 12: After 2008 GFC
 
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table ?: VaR for S&P500 after GFC"=5))
+  add_header_above(c("Table 12: VaR for S&P500 after GFC"=5))
 
@@
 
-## VIX
+# 4. VIX analysis 
+## 4.1 Background and notation
+
+Previously, we investigate how scoring rules perform in predicting financial returns and volatility. However, the volatility modelled/simulated in (G)ARCH models are ...
+
+VIX is different from volatility modelled through any models. It is a measure for implied volatility, which is non-parametric.
+
+## 4.2 Model specification
+
+The difference and similarity between realised volatility and VIX. why we can use model for RV to model VIX.
 
@@
 ```
+
+# Appendix 
+## Appendix 1: Predictive Densities
+
+The predictive density plots provide a straightforward way to visualize how optimal probabilistic forecast matches the shape of true DGP distribution through the simulation.
+Here we provide 4 different ‘time points’ to show how these scoring rules work, especially the focused score in figure 3 to 8.
+The blue line is the marginal distribution from the true DGP, and these figures show that predictive density produced from optimizing LS fits the area with high probability mass the best, which is also what LS is designed for.
+However, it performs poorly in terms of predicting tails when the degree of model misspecification is high in both GARCH and copula examples.
+This is when we benefit from using focused score, and we can see from figure 5 and 8 that predictions produced from optimizing focused score aim to match the shape of two tails of the true distribution.
+They outperform predictions from using Maximum likelihood estimation (MLE).
+
+```{r}
+knitr::include_graphics("figure 3.pdf")
+```
+
+```{r}
+knitr::include_graphics("figure 4.pdf")
+```
+
+```{r}
+knitr::include_graphics("figure 5.pdf")
+```
+
+```{r}
+knitr::include_graphics("figure 6.pdf")
+```
+
+```{r}
+knitr::include_graphics("figure 7.pdf")
+```
+
+```{r}
+knitr::include_graphics("figure 8.pdf")
+```

### 2020-07-29 Draft.Rmd
fixed the descriptive figures size, and add VaR part text and fixed the \mathcal script thing

@@
   chunk_output_type: console
-  header-includes: usepackage{amsmath}
+  header-includes: 
+  - \usepackage{amsmath}
 output:
@@
 \hline
-\multicolumn{3}{|c|}{Simulation design} \\ \hline
+\multicolumn{3}{|c|}{\textbf{Simulation design}} \\ \hline
           & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
@@
 
-  3.	Produce the one-step-ahead predictive $P^{t-1}_{\hat \theta_1^{[i]}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (?)(?)(?)
+  3.	Produce the one-step-ahead predictive $P^{t-1}_{\hat \theta_1^{[i]}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (8)(9)(10):
 
-....
+\begin{align}
+S_{LS}(P_\theta^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\theta)
+\end{align}
+
+\begin{align}
+S_{CRPS}^*(P_\theta^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\theta)-I(y \geq y_t)]^2dy
+\end{align}
+
+\begin{align}
+S_{FSR}(P_\theta^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\theta)dy}]I(y_t \in A^c)
+\end{align}
+
+4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores:
+
+\begin{align}
+\bar S_j(\hat \theta^{[i]})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\hat \theta^{[i]}}^{t-1},y_t)
+\end{align}
 
@@
 Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on $S_1, S_2$, then the prediction is said to coherent if
-$$\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)$$
 
-$$\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)$$
+\begin{align}
+\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
+\end{align}
 
-It is said to be strictly coherent if the equality doesn't hold in (?)(?).
+\begin{align}
+\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)
+\end{align}
+
+It is said to be strictly coherent if the equality doesn't hold in (11)(12).
 
@@
 
-```{r,message=FALSE,fig.align="center"}
+```{r,message=FALSE,fig.width=10,fig.height=5}
 
@@
 
-ggarrange(p1,p2,p3,ncol=2,nrow = 2, labels = c("A: Time series plot","B: Histogram","C: ACF"),legend = "bottom")
+figure <- ggarrange(p1,                                                 
+          ggarrange(p2, p3, ncol = 2, labels = c("B", "C")), 
+          nrow = 2, 
+          labels = "A"                                        
+          ) 
+annotate_figure(figure, 
+                top = text_grob("Descriptive figures",face = "bold"),
+                fig.lab = "Figure 11",fig.lab.face = "bold"
+                )
 ```
@@
 
+Value-at risk (VaR) is a commonly used risk measurement in finance.
+It can be obtained from a probability density function of returns over a chosen investment horizon.
+More formally, it is the p-quantile of a predictive distribution of a portfolio’s profit/loss over a holding period (Dowd, 2005).
+\begin{align}
+VaR = -q_p \\p=1-\alpha
+\end{align}
+It indicates that investors will not lose more than the amount as shown in VaR.
+It represents the worst level at a given level of confidence, $\alpha$.
+There are different methods to estimate VaR, but it is clear that predictive density plays an important role here.
+Therefore, a more accurate prediction would improve the accuracy of VaR estimation.
+
+We implement VaR analysis by using VaR backtesting method.
+It evaluates the prediction accuracy with the proportion of exceedances ($y_t < VaR_t$).
+That is, an accurate prediction of the $\alpha$% VaR is observed if $\alpha$% proportion of exceedances.
+We illustrate how optimal forecasts perform in estimating VaR by using simulation data from section 2 first.
+
 ## 3.2 Value-at-Risk for simulation analysis
-We illustrate our Value-at-Risk analysis by firstly using simulation data from section 2.
 
+The following tables include VaR estimation at \{10%, 20%, 80%, 90%\} corresponding to the 10% and 20% loss of long and short portfolios.
 ```{r}
@@
 Thus, the closer the values to nominal VaR levels, the more accurate are the optimal predictions.
-We can see that in two different forms of model misspecification, FSR is strictly superior to other scores in the upper tails, while in the lower tails, the difference is quite small when not strictly preferable.
+We can see that in two different forms of model misspecification displayed in Table 7 and 8, focused score can provide the most accurate VaR estimation in the upper tail, while in lower tail, it is not short of advantages too much compared with CRPS.
 This result helps us understand what to expect in practical VaR analysis.
@@
 ## 3.3 Value-at-Risk for empirical analysis
+
+We now implement the VaR analysis to continuously compounded daily log returns of S&P500 in U.S.A financial market.
+Learning from score trace plots in section 2.3.1, the 2008 GFC is the turning point of the optimal forecasts performance.
+Therefore, we separate the VaR analysis to two different time periods, before GFC and after GFC.
 
@@
 
-# 4. VIX analysis 
+The results from Table 11 and 12 show that the focused score perform well enough in terms of forecasting the two tails of S&P500 log return distribution, but also CRPS is a very robusted scoring rule which can provide relatively accurate predictions.
+If we think of the marginal distribution of S&P500 estimated by histogram in section 2.3.1, the above results could be a consequence of less observations in two tails, which increases the difficulty of focusing on the tails.
+
+# 4. Empirical analysis in VIX
 ## 4.1 Background and notation
@@
 
-```{r,message=FALSE,fig.align='center'}
+```{r,message=FALSE,fig.width=10,fig.height=5}
 
@@
 
-logvix %>% ggplot(aes(x = Date, y = logvix)) +
+p1 <- logvix %>% ggplot(aes(x = Date, y = logvix)) +
   geom_line()+theme_classic()+labs(x="Year",y="Daily log(VIX) values")+
-  ggtitle("Figure ?: Daily values for Log(VIX)")+
+  #ggtitle("Figure ?: Daily values for Log(VIX)")+
   scale_x_date(date_breaks = "years",date_labels = "%y")+
@@
   annotate(geom = 'text',x=as.Date("2020-04-01"),y=2,label="COVID-19",color="red",size=3)+
-  theme_clean()+
-  labs(caption = "Figure ?: the time series plot of daily log(VIX) values")
+  theme_clean()
 
 # histogram plots
-logvix %>% ggplot()+geom_histogram(aes(x=logvix))+ggtitle("Figure ?")+
-  #scale_x_continuous(labels = scales::percent)+
-  theme_clean()+
-  labs(caption = "Figure ?: the distribution of log(VIX) is asymmetric")
+p2 <- logvix %>% ggplot()+geom_histogram(aes(x=logvix))+
+  theme_clean()
 
@@
 
-logvix %>% ACF((logvix)^2) %>% autoplot() + ggtitle("Figure ?:autocorrelation of log(VIX)")+xlab("number of lags")+ylab("ACF")+theme_clean()+labs(caption = "Figure 11: the autocorrelation plot shows there is a strong serial correlation in variance of log(VIX)")
+p3 <- logvix %>% ACF((logvix)^2) %>% autoplot()+
+      xlab("number of lags")+ylab("ACF")+theme_clean()
+
+figure <- ggarrange(p1,                                                 
+          ggarrange(p2, p3, ncol = 2, labels = c("B", "C")), 
+          nrow = 2, 
+          labels = "A"                                        
+          ) 
+annotate_figure(figure, 
+                top = text_grob("Descriptive figures",face = "bold"),
+                fig.lab = "Figure 13",fig.lab.face = "bold"
+                )
 ```

### 2020-07-31 Draft.Rmd
new intro + update S&P500 series

@@
   chunk_output_type: console
-  header-includes: 
-  - \usepackage{amsmath}
+  header-includes: \usepackage{amsmath}
 output:
@@
 
+With correct model specification being an ongoing issue for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of this misspecification.
+Based on previous research on this topic, this paper conducts both numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score.
+In particular, the role of optimal forecasts in predicting Value-at-Risk and the VIX Volatility Index, and in optimizing portfolio allocation, is to be investigated.
+Results at the current stage have shown that the greater the degree of model misspecification is, the more beneficial is optimal prediction.
+Empirical analysis shows that after the global financial crisis, predictions that are optimal according to a censored scoring rule that rewards predictive accuracy in a tail are substantially more accurate than the alternatives, including likelihood-based predictions.
+This indicates the potentially significant contribution to financial analyses of this method.
+
 \pagebreak
@@
 # 1. Introduction
+
+This research paper will explore the question: ‘When do optimal probabilistic forecasts work’; with particular attention given to the usefulness of optimal predictions in financial markets.
+This work builds on recent research on this topic by Loaiza-Maya et al.
+(2020).
+Probabilistic forecasts can provide complete information about future uncertainty, which could be more valuable than point and interval forecasts to forecasters.
+However, both Bayesian and frequentist prediction assume that the underlying model correctly specifies the process that has generated the observations.
+While in practice, the assumed model underpinning the likelihood function will almost certainly differ from the unknown true data generation process (DGP).
+This model misspecification problem has been an ongoing issue for conventional likelihood-based prediction.
+
+As an alternative to likelihood-based prediction, scoring rules have been introduced before to produce and evaluate probabilistic forecasts.
+A variety of proper scoring rules allows users to produce probability predictions based on their interests, and to compare these predictions, as long as they refer to the same forecast quantity (Gneiting & Raftery, 2007).
+Some recent and previous researches show that forecasts produced based on a given scoring rule can be improved for both Bayesian and frequentist prediction, even in the presence of model misspecification; see Loaiza-Maya, Martin & Frazier (2019), Loaiza-Maya et al.
+(2020) and (ref 5).
+Among all these, censored likelihood score (CSL) or focused score (FSR) proposed by (ref 1) captures our attention since its ‘focusing’ feature shows great values in financial risk management.
+In other words, CSL/FSR allows a forecaster to focus on predicting any region of his/her interests more accurately and therefore, it is expected to make great contributions to risk estimation in finance.
+
+The ‘optimal’ probabilistic forecast has been discussed in Loaiza-Maya et al.
+(2020).
+It refers to a predictive probability distribution that is optimal according to a user-specified scoring rule.
+However, the discussion of whether the optimal forecasts’ performance differs among different types of model misspecification is left to blank, and the financial application of optimal forecasts can be further investigated among different financial instruments.
+
+This research paper extends the work of Loaiza-Maya et al.
+(2020) to investigate the effects of the form and degree of model misspecification on optimal forecast performance and to conduct empirical analysis on how optimal forecasts perform in Value-at-Risk (VaR), the Volatility Index (VIX) and portfolio optimization applications, using empirical data extending over a period of time that precedes the global financial crisis (GFC) and extends to the latest period in which COVID-19 has impacted on financial markets.
+
+Section 2 documents how scoring rules work in producing and evaluating the optimal forecasts under both simulation and empirical settings.
+The background and notation of scoring rules used in this paper are provided at the start.
+Besides, the simulation analysis investigates the effects of different forms and degrees of model misspecification on optimal forecast performance using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and copula models.
+The assumed predictive model is fixed as ARCH (1) for the purpose of manipulating the degree of model misspecification.
+The performance of optimal forecasts in practice is also shown in this section, conducted with S&P500 daily log return data.
+In section 3, we look at the financial application of scoring rules in VaR using both simulated and S&P500 observations with same methodology adopted in section 2.
+The analysis of VIX is provided in section 4, and the predictive model is HAR-RV model with different error term specifications.
+We conclude and discuss any possible caveats in section 5.
 
@@
 Therefore, Gneiting & Raftery, (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in (2) where P is the cumulative distriubtion function, I is the indication function, and x is the materialized events.
-
 \begin{align}
@@
 \end{align}
-
 The formula can be simplifed to (3) if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
@@
 Continuously ranked probability score is defined as a negatively oriented scoring rule, but it can be easily transformed to positively oriented score for convenient comparison among scoring rules as shown in (4).
-
 \begin{align}
@@
 \end{align}
-
 Both logarithmic score and continuously ranked probability score are used for producing and evaluating the entire predictive density.
@@
 It is defined as in (5) where $p_t$ is the predictive probability density function, $A_t$ is the interested region(s) and $A_t^c$ is the complement of $A_t$.
-
 \begin{align}
@@
 \end{align}
-
 [ref 5] prove that weighted density forecasts based on optimizing the censored likelihood score outperform those on logarithmic score and continuously ranked probability score.
@@
 
-\textbf{Assumed Model} & $y_t = \beta+\sigma_t \epsilon_t$ & $y_t = \beta +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
+\textbf{Assumed Model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
 \end{tabular}
@@
 
-  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}$ in the assumed predictive model based on the positively-oriented score $S_i$ where $\boldsymbol{\hat \theta} = \{\hat \beta, \hat \alpha_0, \hat \alpha_1\}$
+  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}$ in the assumed predictive model based on the positively-oriented score $S_i$ where $\boldsymbol{\hat \theta} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}$
 
@@
 4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
-
 \begin{align}
@@
 Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on $S_1, S_2$, then the prediction is said to coherent if
-
 \begin{align}
@@
 sp$log.returns <- c(NA,diff(log(sp$Adj.Close)))
-logret <- sp[-c(1:41),c(1,3)] # delete the adjusted price col, only keep 6000 obs
+logret <- sp[-c(1:188),c(1,3)] # delete the adjusted price col, only keep 6000 obs
 
@@
 # descriptive statistics 
-summary(logret$log.returns) # ----> need to be tabulated 
-range(logret$log.returns)
+summary <- summary(logret$log.returns) # ----> need to be tabulated 
+# range(logret$log.returns)
 # some test results aginst normal dist h_null
@@
 
-skewness(logret$log.returns)
-kurtosis(logret$log.returns)
-```
-
-```{r}
-sum <- data.frame(Stock="S&P500",Min=-0.1276522,Median=0.0006105,Mean=0.0002453,Max=0.1095720,Skewness= -0.3807978,Kurtosis=13.5123,JB.Test=27772,LB.Test=60.627)
+sk <- skewness(logret$log.returns)
+kt <- kurtosis(logret$log.returns)
+```
+
+```{r}
+sum <- data.frame(Stock="S&P500",Min=as.numeric(summary[1]),Median=as.numeric(summary[3]),Mean=as.numeric(summary[4]),Max=as.numeric(summary[5]),Skewness=sk,Kurtosis=kt,JB.Test=28270,LB.Test=61.489)
 sum %>% 
@@
   #ggtitle("Figure 11:Squared log returns autocorrelation")+
-  xlab("number of lags")+ylab("ACF")+theme_clean()
+  xlab("number of lags")+ylab("ACF for variance")+theme_clean()
 # +labs(caption = "Figure 11: the autocorrelation plot shows there is a strong serial correlation in volatility of S&P500")
@@
 
-Value-at risk (VaR) is a commonly used risk measurement in finance.
+Value-at-Risk (VaR) is a commonly used risk measurement in finance.
 It can be obtained from a probability density function of returns over a chosen investment horizon.
-More formally, it is the p-quantile of a predictive distribution of a portfolio’s profit/loss over a holding period (Dowd, 2005).
+It is the p-quantile of a predictive distribution of a portfolio’s profit/loss over a holding period, according to a given confidence interval $\alpha$ (Dowd, 2005).
 \begin{align}
@@
 It indicates that investors will not lose more than the amount as shown in VaR.
-It represents the worst level at a given level of confidence, $\alpha$.
+It represents the worst level of the investments with $\alpha$ confidence level.
 There are different methods to estimate VaR, but it is clear that predictive density plays an important role here.
-Therefore, a more accurate prediction would improve the accuracy of VaR estimation.
+Therefore, a more accurate prediction can contribute to improving the accuracy of VaR estimation.
+
+[ref 5] conduct combining density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the focused score outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.
 
@@
 It evaluates the prediction accuracy with the proportion of exceedances ($y_t < VaR_t$).
-That is, an accurate prediction of the $\alpha$% VaR is observed if $\alpha$% proportion of exceedances.
-We illustrate how optimal forecasts perform in estimating VaR by using simulation data from section 2 first.
+That is, an accurate estimation of the p% VaR is observed if the proportion of exceedances equals to p%.
+We illustrate how optimal forecasts perform in estimating VaR by using simulation data from section 2 first and expect outperformance of focused scoring rules.
 
@@
 
-The following tables include VaR estimation at \{10%, 20%, 80%, 90%\} corresponding to the 10% and 20% loss of long and short portfolios.
+The following tables include VaR estimations at \{10%, 20%, 80%, 90%\} corresponding to the 10% and 20% loss of long and short portfolios.
 ```{r}
@@
 
-The values showed in these tables refer to the proportion of exceedances over the value at risk indicated by the column.
-Thus, the closer the values to nominal VaR levels, the more accurate are the optimal predictions.
-We can see that in two different forms of model misspecification displayed in Table 7 and 8, focused score can provide the most accurate VaR estimation in the upper tail, while in lower tail, it is not short of advantages too much compared with CRPS.
-This result helps us understand what to expect in practical VaR analysis.
+The values showed in these tables refer to the out-of-sample proportion of exceedances over the nominal VaR level indicated by the column name.
+The closer the proportion of exceedances to nominal VaR levels, the more accurate are VaR estimations, and thus the more accurate are the optimal probablistic forecasts.
+We can see that in two different forms of model misspecification displayed in Table 7 and 8, focused score can provide the most accurate VaR estimation in the upper tail, while in lower tail, it is not short of advantages by too much compared with CRPS.
+These results help us understand what to expect in empirical VaR analysis.
 
@@
 We now implement the VaR analysis to continuously compounded daily log returns of S&P500 in U.S.A financial market.
-Learning from score trace plots in section 2.3.1, the 2008 GFC is the turning point of the optimal forecasts performance.
+Learning from score trace plots in section 2.3.1, the 2008 GFC is the turning point of the optimal forecasts performance, especially for focused scores.
 Therefore, we separate the VaR analysis to two different time periods, before GFC and after GFC.
@@
 
-The results from Table 11 and 12 show that the focused score perform well enough in terms of forecasting the two tails of S&P500 log return distribution, but also CRPS is a very robusted scoring rule which can provide relatively accurate predictions.
-If we think of the marginal distribution of S&P500 estimated by histogram in section 2.3.1, the above results could be a consequence of less observations in two tails, which increases the difficulty of focusing on the tails.
+The results from Table 11 and 12 show that the focused score perform well enough in terms of estimating VaR for both long and short portfolios of S&P500, but also CRPS is a very robusted scoring rule which can provide relatively accurate predictions.
+Moreover, in Table 12, focused score seems to perform better in 20% and 80% which have higher probability mass.
+If we think of the marginal distribution of S&P500 estimated by histogram in section 2.3.1, the above results could be a consequence of the very sparsed marginal distribution, which increases the difficulty of 'focusing' on the 10% and 90% tails.
 
@@
 
-Previously, we investigate how scoring rules perform in predicting financial returns and volatility. However, the volatility modelled/simulated in (G)ARCH models are ...
-
-VIX is different from volatility modelled through any models. It is a measure for implied volatility, which is non-parametric.
-
-## 4.2 Model specification
-
-The difference and similarity between realised volatility and VIX. why we can use model for RV to model VIX.
-
-The following tables and figures are produced by CBOE VIX data from 13 Aug,1996 - 16 July,2020 with daily frequency.
-
-Initial sample size = 1000
-
-Out-of-sample size = 5000
-
-### Predictive model: 
-Let $y_t$ = $log(VIX_t)$, then 
-$$y_{t+1}=\beta_0+\beta_1y_t+\beta_2y_{t-5,t}+\beta_3y_{t-22,t}+\sigma_{t+1}z_{t+1}, \\z_{t+1} \sim N(0,1)$$ 
-$$\hat y_{t+1}=\hat \beta_0+ \hat \beta_1y_t+\hat \beta_2y_{t-5,t}+\hat \beta_3y_{t-22,t}$$
-$$\hat y_{t+2}=\hat \beta_0+\hat \beta_1 \hat y_{t+1}+\hat \beta_2y_{t-4,t+1}+\hat \beta_3y_{t-21,t+1}$$
-$$y_{t-5,t}=\frac{1}{5}(y_t+...+y_{t-4})$$
-$$y_{t-22,t}=\frac{1}{22}(y_t+...+y_{t-21})$$
+Time-varying volatility is an important part in finance modelling and an accurate prediction will give investors a better understanding of the risks they take on.
+GARCH-type models used in section 2 and 3 are conditional deterministic.
+That is, $\sigma_t^2$ is a deterministic function of given past returns.
+They neglect the fact that volatility in stock markets and derivative markets can have long memory, which means it slowly reverts to its long-run mean.
+They do not exploit the information in intraday data.
+Therefore, it is better off if we model volatility in a continuous-time model where $lnP_t$ is allowed to vary continuously over time.
+
+The realized volatility (RV) approach to modelling volatility allows us to exploit the information in intraday data, consider long memory feature, sudden jumps in the market and market microstructure.
+When the price follows the process as:
+\begin{align}
+d\ln(P_t)=\mu_tdt+\sigma_tdw_t
+\end{align}
+
+RV is a direct estimate of integrated volatility (IV) for $lnP_t$ based on continuously recorded observations of $P_t$ over the day.
+\begin{align}
+RV_t = \sum^{1/\Delta t}_{j=1}r^2_{t-1+j\Delta t} \xrightarrow{p} \int_{t-1}^t\sigma_s^2ds = IV_t \ as\ \Delta t \to 0
+\end{align}
+When considering the sudden jumps, that is, the price follows the process in (18).
+RV is also a consistent estimate of quadratic variation (QV) where $\kappa_s$ represents the sudden jump on day t and $q_t$ is the jump occasions.
+\begin{align}
+d\ln(P_t)=\mu_tdt+\sigma_tdw_t+\kappa_tdq_t
+\end{align}
+
+\begin{align}
+RV_t=\sum^{1/\Delta t}_{j=1}r^2_{t-1+j\Delta t} \xrightarrow{p} \int_{t-1}^t\sigma_s^2ds\ + \sum_{s=1}^{q_t}\kappa_s^2= QV_t=IV_t+\sum_{s=1}^{q_t}\kappa_s^2 \ as\ \Delta t \to 0
+\end{align}
+In addition to the fact that volatility is a direct measure of the risk of portfolios, it is also important for pricing derivatives, such as options, since it is the only unknown parameter to estimate.
+The famous Black-Scholes model assumes a constant volatility over time which does not hold in practice.
+Implied volatility allows us to incorporate the jumps and continuous variation of volatility over time.
+In other words, implied volatility is an estimate of QV extracted from option prices.
+
+VIX index estimates QV that is implied by option prices under a risk-neutral (18) process, using a finite number of strikes of S&P500 index [reference from CBOE].
+It acknowledges the fact that assumptions of Black-Scholes model do not hold and the occurance of jumps.
+Since both VIX and RV are estimations of QV, it is reasonable to model VIX with a HAR-RV model which is usually used for modelling RV in the literature.
+
+## 4.2 VIX descriptive statistics
+
+We collect daily VIX index data from (ref: CBOE) starting from 27 Aug, 1996 to 31 July, 2020. And the descriptive statistics of $log(VIX_t)$ is shown as below:
 
@@
 prev <- as.data.frame(prev)
-prev <- prev[-c(1:178,6179),1]
+prev <- prev[-c(1:188,6189),1]
 
@@
 MA5 <- as.data.frame(MA5) # average of past week
-MA5 <- MA5[-c(1:173),1] # including only 6000 obs
+MA5 <- MA5[-c(1:183),1] # including only 6000 obs
 
@@
 MA22 <- as.data.frame(MA22) # average of past month
-MA22 <- MA22[-c(1:156),1] # including only 6000 obs
-
-logvix <- vix[-c(1:178),c(1,3)] # delete the adjusted vix col, only keep 6000 obs
+MA22 <- MA22[-c(1:166),1] # including only 6000 obs
+
+logvix <- vix[-c(1:188),c(1,3)] # delete the adjusted vix col, only keep 6000 obs
 logvix <- cbind(logvix,prev,MA5,MA22)
@@
 
-# temp <- logvix[,2:5]
-# write_csv(temp,"vixlog.csv")
+temp <- logvix[,2:5]
+write_csv(temp,"vixlog.csv")
 
@@
 # descriptive statistics 
-summary(vix$logvix) # ----> need to be tabulated 
-# summary(vix$Adj.Close)
-range(vix$logvix)
+summary <- summary(vix$logvix) # ----> need to be tabulated 
+# range(vix$logvix)
 # some test results aginst normal dist h_null
@@
 ```{r}
-sum <- data.frame(Series="Log(VIX)",Min = 2.213, Median = 2.916, Mean = 2.935, Max = 4.415,Skewness= vixsk,Kurtosis=vixkt,JB.Test=415.06,LB.Test=11744)
+sum <- data.frame(Series="Log(VIX)",Min = as.numeric(summary[1]), Median = as.numeric(summary[3]), Mean = as.numeric(summary[4]), Max = as.numeric(summary[6]),Skewness= vixsk,Kurtosis=vixkt,JB.Test=410.77,LB.Test=11765)
 sum %>% 
@@
 
+Table ?
+and Figure 13 shows that $log(VIX_t)$ is volatile and shows persistence over time.
+It is positively-skewed and the autocorrelation of its volatility is slowly decaying.
+From the descriptive statistics, we can see that the features of VIX is similar to what we have observed from S&P500.
+Similarly, there are unusual jumps happened during GFC and COVID-19.
+Thus we expect that focused score could outperform MLE and CRPS in predicting tails as before and significantly improve accuracy after GFC.
+
+## 4.3 Model specification
+
+Proposed by Corsi,(2003), HAR-RV model is a simple additive linear model which takes lagged squared returns as regressors.
+It does not belong to the class of long memory models, but it is able to produce the volatility persistence that is almost indistinguishable from what observed in financial markets through the simple AR-type structure.
+
+We design the VIX analysis with different error term specification of HAR-RV:
+
+1. $z_t \sim N(0,1)$
+
+2. $z_t \sim Student-t(\mu,\sigma,\nu)$
+
+3. $z_t \sim$ skewed Student-t distribution
+
+4. $z_t \sim GARCH$ 
+\begin{align}
+log(VIX_{t+1})=\beta_0+\beta_1log(VIX_t)+\beta_2log(VIX_{t-5,t})+\beta_3log(VIX_{t-22,t})+\sigma_{t+1}z_{t+1}
+\end{align}
+\begin{align}
+log(VIX_{t-5,t})=\frac{1}{5}[log(VIX_t)+...+log(VIX_{t-4})]
+\end{align}
+\begin{align}
+log(VIX_{t-22,t})=\frac{1}{22}[log(VIX_t)+...+log(VIX_{t-21})]
+\end{align}
+
+By using the same methodology in section 2 with initial sample size $\tau = 1000$ and out-of-sample size $T-\tau+1=5000$, we produce the following average score table, Table ?
+and score trace plot, Figure ?.
+
+### 4.3.1 Results of specification 1: Normal error
+
 ```{r}
@@
 
-The lower (upper) tail shows the prediction evaluation of 4 scoring rules by FSR10 (FSR90).
-
+From Table ?, the results are not surprising focused score performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
+
+The score trace plot, Figure ?, shows the prediction of optimizing four scoring rules evaluated by FSR10 (left panel) and FSR90 (right panel).
+It indicates how accurate these predictions are in 10 percentile and 90 percentile.
 The scoring rules used for optimization are {MLE, CRPS, FSR10(90), FSR20(80)}.
+
+In the lower tail, it seems that there is not much difference among four predictions, but if zoom in, we can see that FSR is at the top of other scores, which means it can still provide the most accurate prediction.
+However, we only gain very little from using it.
+On the contrary, in the upper tail, FSR has a much higher effect on improving accuracy after GFC and this effect continues.
+One possible reason could be that considering the marginal distribution shown in figure 13.B of $log(VIX_t)$, both LS and CRPS can predict the lower tail better if there is higher probability mass at that end.
+Thus, the benefits of using FSR is not significant.
 
@@
 
+### 4.3.2 Results of specification 2: Student-t
+
+# 5. Conclusion
+
+Caveats: 
+1. The VaR is conditional distribution while the focused score is unconditional distribution due to the computation burden.
+
+2. The practical meaning of the VaR is more often focused on around 1%, while at this very small tail, the focused score gets less and less accurate since the observations are less, harder to focus.
+
+\pagebreak 
 # References
@@
 
+\pagebreak
 # Appendix 

### 2020-08-04 Draft.Rmd
draft paragraph changes (all of them) and correct the notation for HAR model error term

@@
 ```{r, message=FALSE}
-library(formattable)
+# library(formattable)
 library(dplyr)
@@
 Some recent and previous researches show that forecasts produced based on a given scoring rule can be improved for both Bayesian and frequentist prediction, even in the presence of model misspecification; see Loaiza-Maya, Martin & Frazier (2019), Loaiza-Maya et al.
-(2020) and (ref 5).
-Among all these, censored likelihood score (CSL) or focused score (FSR) proposed by (ref 1) captures our attention since its ‘focusing’ feature shows great values in financial risk management.
+(2020) and Opschoor, van Dijk & van der Wel (2017).
+Among all these, censored likelihood score (CSL) or focused score (FSR) proposed by Diks, Panchenko & van Dijk (2011), captures our attention since its ‘focusing’ feature shows great values in financial risk management.
 In other words, CSL/FSR allows a forecaster to focus on predicting any region of his/her interests more accurately and therefore, it is expected to make great contributions to risk estimation in finance.
@@
 Scoring rules can be used in both estimation and prediction.
-In estimation, an optimum estimator $\hat \theta$ can be obtained by maximizing a scoring rule $S_n$.
-That is, $\hat \theta_n=arg \max_\theta S_n(\theta)$.
-$\hat \theta \to \theta$ as $n \to \infty$ under asymptotic situations.
-While in prediction, scoring rules assign a numerical value to density forecasts, addressing both sharpness and calibration.
+In estimation, an optimum estimator $\hat \theta$ can be obtained by maximizing a scoring rule $S_n$ on the condition that $S_n$ is positively oriented.
+That is, $\hat \theta_n=arg \max_\theta S_n(\theta)$, $\hat \theta \to \theta$ as $n \to \infty$.
+While in prediction, scoring rules assign a numerical value to density forecasts, simultaneously addressing both sharpness and calibration (Gneiting & Reftery, 2007).
 For a positively oriented score, higher value will be assigned to a better forecast between two competing candidates.
-A variety of proper scoring rules allows users to produce probability predictions based on their interests, and to compare these predictions, as long as they refer to the same forecast quantity.
-Forecasts candidates are often compared by their average scores.
-Therefore, the crucial importance of the propreity of scoring rules must be emphasized.Gneiting & Raftery, (2007) illustrate the importance of propreity via a case study in weather forecasts and point out that improper scoring rules will assign higher average score to an incorrect density forecast.
-A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and it is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q.
-P and Q are predictive distributions and Q is the best forecast given all the available information.
-S(P,Q) means the expected value of S(P,$\cdot$) under Q (Gneiting & Raftery, 2007).
-
-Some commonly used proper scoring rules are the logarithmic score (LS), the continuously ranked probability score (CRPS) and censored likelihood score (CSL) or focused score (FSR) in a sense that CSL is used for focusing on a certain region(s) of densities.
-
-The logarithmic score is defined as (1) where $p_t$ is the density forecasts.
+The crucial importance of the propreity of scoring rules must be emphasized for the purpose of ranking and comparing forecasts based on scoring rules.
+Gneiting & Raftery, (2007) illustrate the importance of propreity via a case study in weather forecasts and point out that improper scoring rules will assign higher average score to an incorrect density forecast and consequently, mess up the prediction evaluation.
+Suppose P and Q are predictive distributions and Q is the best forecast given all the available information.
+S(P,Q) denotes the expected value of S(P,$\cdot$) under Q.
+A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q (Gneiting & Raftery, 2007).
+
+Some commonly used proper scoring rules are the logarithmic score (LS), the continuously ranked probability score (CRPS) and censored likelihood score (CSL) or focused score (FSR) in a sense that CSL focuses on predicting a certain region(s) of densities.
+
+The logarithmic score is defined as (1) where $p_t$ is the probabilistic density forecast.
 It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of nonlinear utility function used is a concern for forecasters (Bickel, 2007).
@@
 However, logarithmic score is criticized by its unboundness and its local property.
-Its useness is also questioned in (Bernardo, 1979), since he shows that every proper scoring rule is equivalent to logarithmic score.
-Gneiting & Raftery, (2007) argue that logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized one.
+Bernardo (1979) states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state".
+Gneiting & Raftery (2007) also argue that logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event.
 Therefore, Gneiting & Raftery, (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in (2) where P is the cumulative distriubtion function, I is the indication function, and x is the materialized events.
@@
 
-Continuously ranked probability score is defined as a negatively oriented scoring rule, but it can be easily transformed to positively oriented score for convenient comparison among scoring rules as shown in (4).
+CRPS is defined as a negatively oriented scoring rule, but it can be easily transformed to positively oriented form as shown in (4) for convenient comparison among scoring rules in following sections.
 \begin{align}
@@
 \end{align}
-Both logarithmic score and continuously ranked probability score are used for producing and evaluating the entire predictive density.
+Both LS and CRPS are used for producing and evaluating the entire predictive density.
 In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011).
@@
 \end{align}
-[ref 5] prove that weighted density forecasts based on optimizing the censored likelihood score outperform those on logarithmic score and continuously ranked probability score.
-
-## 2.2 Illustration example 
-### 2.2.1 Simulation overview
-
-Density forecasts provide more complete information of uncertainty of a prediction than point and interval forecasts.
-Moreover, the tails of a density have a great importance in finance.
-It forms the foundation of risk management, such as Value-at-Risk (VaR), and asset allocation.
-It can also be used in derivatives pricing.
-(reference ?) --- find some papers.
-
-[ref 5] provide empirical results showing that using censored likelihood score can improve 99% Value-at-Risk estimation.
-Moreover, Loaiza-Maya, Martin & Frazier, (2019) propose a new method, Focused Bayes, in Bayeisian prediction by replacing the conventional likelihood function with the censored likelihood score.
-Their results show that Focused Bayes outperform exact Bayes which is using logarithmic score for updating the prior probability.
-Their work also points out the degree of model misspecification play a role in the performance of Focused Bayes.
-
-Loaiza-Maya et al., (2020) extend the above discussion to frequentist probability forecasting.
+Opschoor, van Dijk & van der Wel (2017) prove that weighted density forecasts based on optimizing the censored likelihood score outperform those on LS and CRPS.
+
+## 2.2 Numerical investigation
+### 2.2.1 Simulation design
+
+Loaiza-Maya, Martin & Frazier (2019) propose a new method, Focused Bayes, in Bayeisian prediction by replacing the conventional likelihood function with the censored likelihood score.
+In their simulated and empirical analysis, Focused Bayes outperforms exact Bayes which is using logarithmic score for updating the prior probability and they also point out the model misspecification plays a role in the performance of Focused Bayes since focusing incorrectly can harm.
+
+Loaiza-Maya et al.(2020) extend the above discussion to frequentist probability forecasting.
 They address questions about when we can/cannot benefit from optimal probabilistic forecasts out of sample.
-A predictive probability distribution is said to be optimal if it is optimal based on a user-specified scoring rule, not generally speaking.
-
-Building on the previous research in this field, we conduct a numerical analysis first in section 2.2.2 and 2.2.3 to further investigate the effects of the form and degree of model misspecification on optimal forecast performance using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and copula models.
-
-### 2.2.2 Simulation design
-
-In order to prepare the financial application analysis in following sections of this paper, we simulate a time series dependnet variable $y_t$ that mimic the behavior of financial returns and volatility.
-Specifically, GARCH models can capture the volatility clustering and serial dependence, and the negative marginal skewness will be introducted using an inversion copula with degree of skewness controlled by the shape parameter showed below.
+Loaiza-Maya et al.(2020) introduce the concepts of ‘coherence’ and ‘strict coherence’ for conveniently documenting the optimal forecasts’ performance.
+Coherence means when the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score.
+Strict coherence is when the optimal prediction is strictly preferable given that score.
+Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules: $S_1, S_2$, then the prediction is said to be coherent if
+\begin{align}
+\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
+\end{align}
+\begin{align}
+\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)
+\end{align}
+It is said to be strictly coherent if the equality doesn't hold in (6)(7).
+
+Building on the previous research in this field, we conduct a numerical analysis first in this sub section to further investigate the effects of the form and degree of model misspecification on optimal forecast performance.
+In order to prepare the financial application analysis in following sections of this paper, we simulate a time series dependnet variable $y_t$ that mimics the behavior of financial returns and volatility.
+Specifically, GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock return's distribution, and the negative marginal skewness will be incorporated by an inversion copula with degree of skewness controlled by the shape parameter.
 In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model.
@@
 \textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & copula \\
-& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^0.5 * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline
+& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline
 
@@
 The tails of density are important for risk management in finance so that we decide to apply focused scoring rule (FSR) to 10%, 20%, 80% and 90% tails of the distribution, corresponding to short and long portfolios in finance respectively.
-The methodology in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) is adopted.
-We conduct each simulation scenario as follows (Loaiza-Maya et al., 2020):
+The methodology in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) is adopted here.
+We conduct each simulation scenario as follows:
 
@@
 \begin{align}
-{\hat \theta^{[i]}}:=arg\max_{\theta \in \Theta}\bar S_i({\theta})
-\end{align}
-
-\begin{align}
-\bar S_i(\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\theta}^{t-1},y_t)
-\end{align}
-
-  3.	Produce the one-step-ahead predictive $P^{t-1}_{\hat \theta_1^{[i]}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (8)(9)(10):
-
-\begin{align}
-S_{LS}(P_\theta^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\theta)
-\end{align}
-
-\begin{align}
-S_{CRPS}^*(P_\theta^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\theta)-I(y \geq y_t)]^2dy
-\end{align}
-
-\begin{align}
-S_{FSR}(P_\theta^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\theta)dy}]I(y_t \in A^c)
-\end{align}
-
+\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
+\end{align}
+\begin{align}
+\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
+\end{align}
+  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (10)(11)(12):
+
+\begin{align}
+S_{LS}(P_{\boldsymbol\theta^{t-1}},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
+\end{align}
+\begin{align}
+S_{CRPS}^*(P_{\boldsymbol\theta^{t-1}},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
+\end{align}
+\begin{align}
+S_{FSR}(P_{\boldsymbol\theta^{t-1}},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
+\end{align}
 4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
 \begin{align}
-\bar S_j(\hat \theta^{[i]})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\hat \theta^{[i]}}^{t-1},y_t)
-\end{align}
-
-### 2.2.3 Simulation results
-#### 2.2.3.1 Average score tables
-
-Loaiza-Maya et al., (2020) introduce the concepts of ‘coherence’ and ‘strict coherence’ for conveniently documenting the optimal forecasts’ performance.
-Coherence means when the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score.
-Strict coherence is when the optimal prediction is strictly preferable given that score.
-Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on $S_1, S_2$, then the prediction is said to coherent if
-\begin{align}
-\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
-\end{align}
-
-\begin{align}
-\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)
-\end{align}
-
-It is said to be strictly coherent if the equality doesn't hold in (11)(12).
-
-\textbf{[need to mention some results from opt paper - one sentence]}
+\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
+\end{align}
+
+### 2.2.2 Simulation results
+#### 2.2.2.1 Average score tables
 
 The first column of following tables shows $S_i$ that we used to produce predictions and the first row shows $S_j$, which is used for forecasts evaluation.
-The bolded value(s) is the maximum(s) in each column.
-We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the score indicated by the column name.
+The bolded value(s) is the maximum(s) of $\bar S_j(\boldsymbol{\hat \theta^{[i]}})$ in each column.
+We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the evaluating scoring rule indicated by the column name.
 
@@
 
-The results from Table 1-3 show one particular type of model misspecification.
-That is, the underlying model ARCH(1) cannot capture the volatility clustering feature of the true data generation process (DGP), thus misspecification.
-Besides, with the degree of freedom increases, the data generated from GARCH(1,1) model is more like data that are from ARCH(1) and therefore, the degree of model misspecification decreases.
-When degree of freedom is large enough, we consider ARCH(1) as a correct specified model as shown in Table 1.
-
-From Table 3.
-we could observe strict coherence when degree of model misspecification is high and coherence in Table 1 which is stated as correct specification case.
-These results are consistent with conclusions from (Loiaza-Maya et al., 2020).
-It simply means that we can improve prediction accuracy in the presence of model misspecification ??
-, and gain more from using optimal forecasts method while the degree of model misspecification is high.
-In other words, we are expected to gain more from using focused score when we observe 'strict coherence' while comparing two forecasts.
-
 ```{r}
@@
 
-\textbf{[need copula paper citation here to explain more]}
+The results from Table 1-3 show one particular type of model misspecification.
+That is, the underlying model ARCH(1) cannot capture the volatility clustering feature of the true data generation process (DGP), thus misspecification.
+Besides, with the degree of freedom increases, the data generated from GARCH(1,1) model is more like data that are from ARCH(1) and therefore, the degree of model misspecification decreases.
+When degree of freedom is large enough, we consider ARCH(1) as a correct specified model as shown in Table 1.
+
+From Table 3.
+we could observe strict coherence when degree of model misspecification is high and coherence in Table 1 which is stated as correct specification case.
+These results are consistent with conclusions from Loiaza-Maya et al.(2020).
+It simply means that we can improve prediction accuracy by using FSR in the presence of model misspecification under certain conditions.
+That is, we are expected to gain more from optimal forecasts while the degree of model misspecification is high.
 
@@
 
-#### 2.2.3.2 Score traces plots
+#### 2.2.2.2 Score traces plots
 
@@
 The right panel shows the same thing but is based on performance of predicting 90 percentile.
-From figure 1 and 2, we could see that FSR makes no difference if the degree of model misspecification is very small but as it increases, FSR starts to outperform CRPS and MLE (LS) in predicting tails.
+From figure 1 and 2, we could see that FSR almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, FSR starts to outperform CRPS and MLE (LS) in predicting tails.
 The more misspecified the model is, the more benefits can we gain from using FSR.
-It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model in the fact that in practice, a correct model does not exist.
+It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.
 
@@
 
-Moreover, the predictive density plots (Appendix 1) in figure 3 to 8, further support our conclusions drawn from the average score tables and score trace plots.
-They show that predictions obtained from optimizing focused scores aim to match the shape of tails of the true distribution and therefore, outperform predictions from using LS.
+Moreover, the predictive density plots (Appendix 1) in figure 3 to 8, further support our conclusions drawn from the average score tables and score trace plots in above sections.
+They show that predictions obtained from optimizing focused scores aim to match the shape of tails of the true distribution and the changes over time/iterations.
 
@@
 
-The data used in the analysis is the continuously compounded daily log returns of S&P500 listed in U.S.A financial market over a time period that precedes the 2008 Global financial crisis (GFC) and extends to the latest period in which COVID-19 has impacts on financial market.
-The methodology used here is the same as in the section 2.2.2 with initial training sample size set to be 1000 and 5000 out-of-sample observations.
+The data used in the analysis is the continuously compounded daily log returns of S&P500 listed in U.S.A financial market over a broad time period from 27 Sep,1996 to 30 July,2020.
+It aims to include two very volatile periods, 2008 Global financial crisis (GFC) and the recent COVID-19 pandemic.
+The methodology used here is the same as in the section 2.2 with initial training sample size set to be 1000 and 5000 out-of-sample observations.
 
@@
   kable_styling("bordered") %>% 
-  add_header_above(c("Table ?: Descriptive statistics"=9))
+  add_header_above(c("Table 7: Descriptive statistics"=9))
 ```
@@
                 top = text_grob("Descriptive figures",face = "bold"),
-                fig.lab = "Figure 11",fig.lab.face = "bold"
+                fig.lab = "Figure 9",fig.lab.face = "bold"
                 )
@@
 
-The descriptive statistics shows that the distribution of S&P500 log returns are negatively skewed and have fat tails and strong serial correlation.
+The descriptive statistics show that the distribution of S&P500 log returns are negatively skewed and have fat tails and strong serial correlation in its volatility.
 Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.
 
-The reality is always the most complicated and the underlying ARCH(1) should have a high degree of model misspecification.
+We still use ARCH(1) model in section 2.2 as the assumed predictive model since it is a reasonable model to predict stock returns and volatility and more importantly, it is misspecified with a high degree of model misspecification.
 Therefore, we should expect that predictions produced by optimizing FSR do a better job in predicting two tails of the distribution.
-The results of Table 9 support our conjecture.
+The results of Table 8 support our conjecture.
 However, the difference between using FSR10(80) and FSR20(90) is very small.
@@
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 9: Average scores for S&P500"=7))
-```
-
-Unlike simulation, the score trace plots show how different scoring rules perform in real time points which correspond to some important events.
-In figure 12, one interesting phenomenon is that after the GFC, focused score performs much better than CRPS and MLE in terms of predicting both upper and lower tails.
+  add_header_above(c("Table 8: Average scores for S&P500"=7))
+```
+
+Unlike simulation, the score trace plots show how different scoring rules perform in real time points which correspond to some historical events.
+In figure 10, one interesting phenomenon is that after the GFC, focused score performs much better than CRPS and MLE compared with before, in terms of predicting both upper and lower tails.
 And this 'jump' effect continues until the very recent date.
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 12(a) Lower Tail","Figure 12(b) Upper Tail"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 10(a) Lower Tail","Figure 10(b) Upper Tail"))
 
@@
 
-Value-at-Risk (VaR) is a commonly used risk measurement in finance.
+Density forecasts have great practical values in finance.
+It forms the foundation of risk management, such as Value-at-Risk (VaR) and is useful for asset allocation and derivative pricing.
+VaR is a commonly used risk measurement in finance.
 It can be obtained from a probability density function of returns over a chosen investment horizon.
@@
 It indicates that investors will not lose more than the amount as shown in VaR.
-It represents the worst level of the investments with $\alpha$ confidence level.
+It represents the worst level of the investments with the given $\alpha$ confidence level.
 There are different methods to estimate VaR, but it is clear that predictive density plays an important role here.
@@
 
-[ref 5] conduct combining density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the focused score outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.
-
+Opschoor, van Dijk & van der Wel (2017) conduct combining density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the focused score outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.
+
+We illustrate how optimal forecasts perform in estimating VaR by usig predictions produced in section 2.2 and 2.3 and expect optimal forecasts based on FSR would give us a better prediction in tails.
 We implement VaR analysis by using VaR backtesting method.
-It evaluates the prediction accuracy with the proportion of exceedances ($y_t < VaR_t$).
-That is, an accurate estimation of the p% VaR is observed if the proportion of exceedances equals to p%.
-We illustrate how optimal forecasts perform in estimating VaR by using simulation data from section 2 first and expect outperformance of focused scoring rules.
+Specifically, we follow the steps as bellow:
+
+1. Using the predictive densities produced in section 2.2 and 2.3: $p(y_{1001}|y_{1000})...p(y_{5000}|y_{4999})$;
+
+2. Construct the VaR at \{10%, 20%, 80%, 90%\} using predictive densities in step 1;
+
+3.
+Compare the true values of $y_{1001}...y_{5000}$ with $VaR_t$ and calculate the proportion of exceedances ($y_t < VaR_t$); An accurate estimation of the p% VaR is observed if the proportion of exceedances equals to p%.
 
@@
 
-The following tables include VaR estimations at \{10%, 20%, 80%, 90%\} corresponding to the 10% and 20% loss of long and short portfolios.
+The following tables include VaR estimations at \{10%, 20%, 80%, 90%\} corresponding to the 10% and 20% expected loss of long and short portfolios.
+The values showed in these tables refer to the out-of-sample proportion of exceedances over the nominal VaR level indicated by the column name.
+The closer the proportion of exceedances to nominal VaR levels, the more accurate are VaR estimations, and thus the more accurate are the optimal probablistic forecasts.
+We can see that in two different forms of model misspecification displayed in Table 9 and 10, focused score can provide the most accurate VaR estimation in the upper tail, while in lower tail, it is not short of advantages by too much compared with CRPS.
+These results help us understand what to expect in empirical VaR analysis.
+
 ```{r}
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 7: VaR when true DGP is copula (shape = -5)"=5))
+  add_header_above(c("Table 9: VaR when true DGP is copula (shape = -5)"=5))
 ```
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 8: VaR when true DGP is GARCH with degree of freedom = 3"=5))
-```
-
-The values showed in these tables refer to the out-of-sample proportion of exceedances over the nominal VaR level indicated by the column name.
-The closer the proportion of exceedances to nominal VaR levels, the more accurate are VaR estimations, and thus the more accurate are the optimal probablistic forecasts.
-We can see that in two different forms of model misspecification displayed in Table 7 and 8, focused score can provide the most accurate VaR estimation in the upper tail, while in lower tail, it is not short of advantages by too much compared with CRPS.
-These results help us understand what to expect in empirical VaR analysis.
+  add_header_above(c("Table 10: VaR when true DGP is GARCH with degree of freedom = 3"=5))
+```
 
@@
 Therefore, we separate the VaR analysis to two different time periods, before GFC and after GFC.
+The results from Table 11 and 12 show that the focused score perform well enough in terms of estimating VaR for both long and short portfolios of S&P500, but also CRPS is a very robusted scoring rule which can provide relatively accurate predictions.
+Moreover, in Table 12, focused score seems to perform better in 20% and 80% which have higher probability mass.
+If we think of the marginal distribution of S&P500 estimated by histogram in section 2.3.1, the above results could be a consequence of the very sparsed marginal distribution, which increases the difficulty of 'focusing' on the 10% and 90% tails.
 
@@
 
-The results from Table 11 and 12 show that the focused score perform well enough in terms of estimating VaR for both long and short portfolios of S&P500, but also CRPS is a very robusted scoring rule which can provide relatively accurate predictions.
-Moreover, in Table 12, focused score seems to perform better in 20% and 80% which have higher probability mass.
-If we think of the marginal distribution of S&P500 estimated by histogram in section 2.3.1, the above results could be a consequence of the very sparsed marginal distribution, which increases the difficulty of 'focusing' on the 10% and 90% tails.
-
 # 4. Empirical analysis in VIX
@@
 They neglect the fact that volatility in stock markets and derivative markets can have long memory, which means it slowly reverts to its long-run mean.
-They do not exploit the information in intraday data.
-Therefore, it is better off if we model volatility in a continuous-time model where $lnP_t$ is allowed to vary continuously over time.
+They record changes usually in daily frequency and do not exploit the information in intraday data.
+Therefore, it is better off if we model volatility in a continuous-time model where $lnP_t$ and $\sigma_t$ are allowed to vary continuously over time.
 
@@
 \end{align}
-
 RV is a direct estimate of integrated volatility (IV) for $lnP_t$ based on continuously recorded observations of $P_t$ over the day.
@@
 \end{align}
-
 \begin{align}
@@
 
-VIX index estimates QV that is implied by option prices under a risk-neutral (18) process, using a finite number of strikes of S&P500 index [reference from CBOE].
-It acknowledges the fact that assumptions of Black-Scholes model do not hold and the occurance of jumps.
-Since both VIX and RV are estimations of QV, it is reasonable to model VIX with a HAR-RV model which is usually used for modelling RV in the literature.
+VIX index estimates QV that is implied by option prices under a risk-neutral (18) process, using a finite number of strikes of S&P500 index (Chicago Board Options Exchange, 2020).
+It acknowledges the occurance of jumps and the fact that assumptions of Black-Scholes model do not hold.
+Since both VIX and RV are estimations of QV, it is reasonable to model VIX with a HAR-RV model which is usually used for modelling RV in the literature (Corsi, 2009; Maneesoonthorn, Martin, Forbes & Grose, 2012; Martin, Reidy & Wright, 2009; Andersen, Bollerslev & Diebold, 2007).
 
 ## 4.2 VIX descriptive statistics 
-
-We collect daily VIX index data from (ref: CBOE) starting from 27 Aug, 1996 to 31 July, 2020. And the descriptive statistics of $log(VIX_t)$ is shown as below:
+We collect daily VIX index data starting from 27 Aug,1996 to 30 July,2020. And the descriptive statistics of $log(VIX_t)$ are shown in Table 13 and Figure 11:
+
+Table 13 and Figure 11 shows that $log(VIX_t)$ is volatile and shows persistence over time.
+It is positively-skewed and the autocorrelation of its volatility is slowly decaying.
+From the descriptive statistics, we can see that the features of VIX is similar to what we have observed from S&P500.
+Similarly, there are unusual jumps happened during GFC and COVID-19.
+Thus, we expect that focused score could outperform MLE and CRPS in predicting tails as before and significantly improve accuracy after GFC.
 
@@
   kable_styling("bordered")%>% 
-  add_header_above(c("Table ?: Descriptive statistics"=9))
+  add_header_above(c("Table 13: Descriptive statistics"=9))
 ```
@@
                 top = text_grob("Descriptive figures",face = "bold"),
-                fig.lab = "Figure 13",fig.lab.face = "bold"
+                fig.lab = "Figure 11",fig.lab.face = "bold"
                 )
@@
 
-Table ?
-and Figure 13 shows that $log(VIX_t)$ is volatile and shows persistence over time.
-It is positively-skewed and the autocorrelation of its volatility is slowly decaying.
-From the descriptive statistics, we can see that the features of VIX is similar to what we have observed from S&P500.
-Similarly, there are unusual jumps happened during GFC and COVID-19.
-Thus we expect that focused score could outperform MLE and CRPS in predicting tails as before and significantly improve accuracy after GFC.
-
 ## 4.3 Model specification
 
-Proposed by Corsi,(2003), HAR-RV model is a simple additive linear model which takes lagged squared returns as regressors.
+Proposed by Corsi (2009), HAR-RV model is a simple additive linear model which takes lagged squared returns as regressors.
 It does not belong to the class of long memory models, but it is able to produce the volatility persistence that is almost indistinguishable from what observed in financial markets through the simple AR-type structure.
@@
 We design the VIX analysis with different error term specification of HAR-RV: 
-
-1. $z_t \sim N(0,1)$
-
-2. $z_t \sim Student-t(\mu,\sigma,\nu)$
-
-3. $z_t \sim$ skewed Student-t distribution
-
-4. $z_t \sim GARCH$ 
 \begin{align}
@@
 
-By using the same methodology in section 2 with initial sample size $\tau = 1000$ and out-of-sample size $T-\tau+1=5000$, we produce the following average score table, Table ?
-and score trace plot, Figure ?.
+1. $z_{t+1} \sim N(0,1)$ and constant $\sigma$
+
+2. $z_{t+1} \sim Student-t(\mu,\sigma,\nu)$ and constant $\sigma$
+
+3. $z_{t+1} \sim$ skewed Student-t distribution and constant $\sigma$
+
+4. $z_{t+1} \sim N(0,1)$ and time-varying $\sigma_{t+1}$ following GARCH process
+
+By using the same methodology in section 2 with initial sample size = 1000 and out-of-sample size $\tau=T-1000=5000$, we produce and evaluate predictive densities with the assumed model as HAR-RV.
 
@@
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table ?: Average scores for VIX"=7))
-```
-
-From Table ?, the results are not surprising focused score performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
-
-The score trace plot, Figure ?, shows the prediction of optimizing four scoring rules evaluated by FSR10 (left panel) and FSR90 (right panel).
-It indicates how accurate these predictions are in 10 percentile and 90 percentile.
-The scoring rules used for optimization are {MLE, CRPS, FSR10(90), FSR20(80)}.
-
-In the lower tail, it seems that there is not much difference among four predictions, but if zoom in, we can see that FSR is at the top of other scores, which means it can still provide the most accurate prediction.
-However, we only gain very little from using it.
-On the contrary, in the upper tail, FSR has a much higher effect on improving accuracy after GFC and this effect continues.
-One possible reason could be that considering the marginal distribution shown in figure 13.B of $log(VIX_t)$, both LS and CRPS can predict the lower tail better if there is higher probability mass at that end.
-Thus, the benefits of using FSR is not significant.
+  add_header_above(c("Table 14: Average scores for VIX"=7))
+```
 
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure ?(a) Lower Tail","Figure ?(b) Upper Tail"))
-
-```
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 12(a) Lower Tail","Figure 12(b) Upper Tail"))
+
+```
+
+In Table 14, as expected, FSR performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
+The score trace plot, Figure 12, shows the prediction of optimizing four scoring rules evaluated by FSR10 (left panel) and FSR90 (right panel).
+It indicates how accurate these predictions according to their performance in 10 percentile and 90 percentile.
+In the lower tail, it seems that there is not much difference among four predictions, but if zoom in, we can see that FSR is at the top of other scores, which means it can still provide the most accurate prediction.
+However, we only gain very little from using it.
+On the contrary, in the upper tail, FSR has a much higher effect on improving accuracy after GFC and this effect continues.
+One possible explanation could be that both LS and CRPS can predict the lower tail better if there is higher probability mass at the area, then the benefit of using FSR is not significant.
+Considering the marginal distribution shown in figure 13.B of $log(VIX_t)$, we observe much more observations in the lower end than in the upper end so that it might be the reason why we observe the little improvement in the lower tail in Figure 12(a).
 
 ### 4.3.2 Results of specification 2: Student-t
+...
 
@@
 
+Conclusions:
+
+1.
+Optimal forecasts perform almost the same in two different types of model misspecification investigated in this paper and the more misspecified the model is, the more benefits can we gain from using focused score in improving the tail prediction accuracy.
+
+2. Focused score improves the prediction accuracy by a lot after the stock market turbulance and can give better Value-at-Risk estimation.
+
+3. In terms of modelling VIX index, the HAR model with normal error term shows that focused score really makes a difference in predicting upper tail but no great improvement observed in the lower end.
+
 Caveats:
+
 1. The VaR is conditional distribution while the focused score is unconditional distribution due to the computation burden.
 
-2. The practical meaning of the VaR is more often focused on around 1%, while at this very small tail, the focused score gets less and less accurate since the observations are less, harder to focus.
+2.
+The practical usage of VaR is often around 1%, while at this very small tail, the focused score might get less and less accurate since there are less observations and consequently, harder to focus on tails.
 
 \pagebreak
+
 # References
 
-DON'T forget alphabetical order!!
-
-cite packages used in the draft
-```{r}
-citation("formattable")
-```
+```{r}
+#DON'T forget alphabetical order!! 
+#cite packages used in the draft
+#citation("knitr")
+```
+Andersen, T., Bollerslev, T., & Diebold, F.
+(2007).
+Roughing it Up: Including Jump Components in the Measurement, Modeling and Forecasting of Return Volatility.
+SSRN Electronic Journal.
+doi: 10.2139/ssrn.1150061
+
+Bernardo, J. (1979). Expected Information as Expected Utility. The Annals of Statistics, 7(3), 686-690. doi: 10.1214/aos/1176344689
+
+Bickel, E.J. (2007). Some Comparisons among Quadratic, Spherical and Logarithmic Scoring Rules. Decision Analysis, 4(2), 49-65. doi: 10.1287/deca.1070.0089
+
+Chicago Board Options Exchange. (2018). VIX FAQs. Retrieved from http://www.cboe.com/products/vix-index-volatility/vix-options-and-futures/vix-index/vix-faqs#1
+
+Corsi, F. (2009). A Simple Approximate Long-Memory Model of Realized Volatility. Journal of Financial Econometrics, 7(2), 174-196. doi: 10.1093/jjfinec/nbp001
+
+Diks, C., Panchenko, V., & van Dijk, D. (2011). Likelihood-based scoring rules for comparing density forecasts in tails. Journal of Econometrics, 163(2), 215-230. doi: 10.1016/j.jeconom.2011.04.001
+
+Dowd, K. (2005). Measuring market risk. Chichester: John Wiley.
+
+Fan, Y., & Patton, A. (2014). Copulas in Econometrics. Annual Review of Economics, 6(1), 179-200. doi: 10.1146/annurev-economics-080213-041221
+
+Gneiting, T., & Raftery, A. (2007). Strictly Proper Scoring Rules, Prediction, and Estimation. Journal of the American Statistical Association, 102(477), 359-378. doi: 10.1198/016214506000001437
+
+Gneiting, T., & Ranjan, R.
+(2011).
+Comparing Density Forecasts Using Threshold- and Quantile-Weighted Scoring Rules.
+Journal of Business & Economic Statistics, 29(3), 411-422.
+doi: 10.1198/jbes.2010.08110
+
+Loaiza-Maya, et al. (2020). Optimal Probabilistic Forecasts: when do they work? Manuscript in preparation.
+
+Loaiza-Maya, R., Martin, G., & Frazier, D. (2019). Focused Bayesian Prediction. Retrieved from http://arxiv.org/abs/1912.12571 (http://arxiv.org/abs/1912.12571)
+
+Maneesoonthorn, W., Martin, G., Forbes, C., & Grose, S. (2012). Probabilistic forecasts of volatility and its risk premia. Journal of Econometrics, 171(2), 217-236. doi: 10.1016/j.jeconom.2012.06.006
+
+Martin, G., Reidy, A., & Wright, J.
+(2009).
+Does the option market produce superior forecasts of noise-corrected volatility measures?.
+Journal of Applied Econometrics, 24(1), 77-104.
+doi: 10.1002/jae.1033
+
+Opschoor, A., van Dijk, D., & van der Wel, M. (2017). Combining density forecasts using focused scoring rules. Journal of Applied Econometrics, 32(7), 1298-1313. doi: 10.1002/jae.2575
+
+Smith, M., & Maneesoonthorn, W.
+(2018).
+Inversion copulas from nonlinear state space models with an application to inflation forecasting.
+International Journal of Forecasting, 34(3), 389-407.
+doi: 10.1016/j.ijforecast.2018.01.002
+
+Yahoo! finance. (2020). CBOE Volatility Index [Data file]. Retrieved from https://finance.yahoo.com/quote/%5EVIX/history?period1=1042761600&period2=1072915200&interval=1d&filter=history&frequency=1d
+
+Yahoo! finance. (2020). S&P 500 [Data file]. Retrieved from https://finance.yahoo.com/quote/%5EGSPC?p=^GSPC&.tsrc=fin-srch
 
 \pagebreak
+
 # Appendix 

### 2020-08-09 Draft.Rmd
Final submitted version of draft

@@
   warning = FALSE)
+
+# devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8", 
+                    #  filename = 'render_toc.R')
 ```
@@
 
-With correct model specification being an ongoing issue for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of this misspecification.
+With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification.
 Based on previous research on this topic, this paper conducts both numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score.
 In particular, the role of optimal forecasts in predicting Value-at-Risk and the VIX Volatility Index, and in optimizing portfolio allocation, is to be investigated.
-Results at the current stage have shown that the greater the degree of model misspecification is, the more beneficial is optimal prediction.
-Empirical analysis shows that after the global financial crisis, predictions that are optimal according to a censored scoring rule that rewards predictive accuracy in a tail are substantially more accurate than the alternatives, including likelihood-based predictions.
-This indicates the potentially significant contribution to financial analyses of this method.
+Results at the current stage have shown that the greater the degree of model misspecification, the more beneficial is optimal prediction.
+Empirical analysis shows that after the global financial crisis, predictions that are optimal according to the censored scoring rule that rewards predictive accuracy in a tail are substantially more accurate at predicting observations in said tail than the alternatives, including likelihood-based predictions.
+This indicates the potentially significant contribution to financial analyses of this approach.
 
@@
 
+```{r toc, echo=FALSE} 
+# render_toc("Draft.Rmd")
+```
+
 # 1. Introduction
 
-This research paper will explore the question: ‘When do optimal probabilistic forecasts work’; with particular attention given to the usefulness of optimal predictions in financial markets.
-This work builds on recent research on this topic by Loaiza-Maya et al.
+This research paper will explore the question: ‘When do optimal probabilistic forecasts work’, with particular attention given to the usefulness of optimal forecasts in financial applications.
+
+Probabilistic forecasts can provide complete information about future uncertainty, which can be more valuable than point and interval forecasts to forecasters.
+However, previous approaches to prediction - including probabilistic methods - typically assume that the predictive model correctly specifies the process that has generated the observations.
+In practice, the assumed model underpinning the likelihood function will almost certainly differ from the unknown true data generating process (DGP).
+This model misspecification problem has been an ongoing issue for conventional likelihood-based prediction.
+
+As an alternative to likelihood-based prediction, scoring rules have been proposed as a means of producing probabilistic forecasts.
+A variety of alternative proper scoring rules allows users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand (Gneiting & Raftery, 2007).
+Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.
 (2020).
-Probabilistic forecasts can provide complete information about future uncertainty, which could be more valuable than point and interval forecasts to forecasters.
-However, both Bayesian and frequentist prediction assume that the underlying model correctly specifies the process that has generated the observations.
-While in practice, the assumed model underpinning the likelihood function will almost certainly differ from the unknown true data generation process (DGP).
-This model misspecification problem has been an ongoing issue for conventional likelihood-based prediction.
-
-As an alternative to likelihood-based prediction, scoring rules have been introduced before to produce and evaluate probabilistic forecasts.
-A variety of proper scoring rules allows users to produce probability predictions based on their interests, and to compare these predictions, as long as they refer to the same forecast quantity (Gneiting & Raftery, 2007).
-Some recent and previous researches show that forecasts produced based on a given scoring rule can be improved for both Bayesian and frequentist prediction, even in the presence of model misspecification; see Loaiza-Maya, Martin & Frazier (2019), Loaiza-Maya et al.
-(2020) and Opschoor, van Dijk & van der Wel (2017).
-Among all these, censored likelihood score (CSL) or focused score (FSR) proposed by Diks, Panchenko & van Dijk (2011), captures our attention since its ‘focusing’ feature shows great values in financial risk management.
-In other words, CSL/FSR allows a forecaster to focus on predicting any region of his/her interests more accurately and therefore, it is expected to make great contributions to risk estimation in finance.
+Among all these investigations, it is the censored likelihood score (CLS) or the focused score (FSR) proposed originally by Diks, Panchenko & van Dijk (2011), that captures our attention, since its ‘focusing’ feature has great potential in financial risk management.
+In other words, CLS/FSR allows a forecaster to focus on predicting any particular region of interest more accurately and, therefore, is expected to make an important contribution to risk prediction in financial settings.
 
@@
 It refers to a predictive probability distribution that is optimal according to a user-specified scoring rule.
-However, the discussion of whether the optimal forecasts’ performance differs among different types of model misspecification is left to blank, and the financial application of optimal forecasts can be further investigated among different financial instruments.
+Whilst some empirical investigations were undertaken, these were primarily illustrative, with there being much scope left for exploring the performance of optimal methods in forecasting different types of financial measures, and under different assumed models.
 
 This research paper extends the work of Loaiza-Maya et al.
-(2020) to investigate the effects of the form and degree of model misspecification on optimal forecast performance and to conduct empirical analysis on how optimal forecasts perform in Value-at-Risk (VaR), the Volatility Index (VIX) and portfolio optimization applications, using empirical data extending over a period of time that precedes the global financial crisis (GFC) and extends to the latest period in which COVID-19 has impacted on financial markets.
-
-Section 2 documents how scoring rules work in producing and evaluating the optimal forecasts under both simulation and empirical settings.
-The background and notation of scoring rules used in this paper are provided at the start.
-Besides, the simulation analysis investigates the effects of different forms and degrees of model misspecification on optimal forecast performance using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and copula models.
-The assumed predictive model is fixed as ARCH (1) for the purpose of manipulating the degree of model misspecification.
-The performance of optimal forecasts in practice is also shown in this section, conducted with S&P500 daily log return data.
-In section 3, we look at the financial application of scoring rules in VaR using both simulated and S&P500 observations with same methodology adopted in section 2.
-The analysis of VIX is provided in section 4, and the predictive model is HAR-RV model with different error term specifications.
-We conclude and discuss any possible caveats in section 5.
-
-# 2. Scoring rule in prediction
+(2020) by investigating the effect of the form and degree of model misspecification on optimal forecast performance in particular financial settings; in particular by conducting an empirical analysis of how optimal forecasts perform in Value-at-Risk (VaR), Volatility Index (VIX) and portfolio optimization applications.
+Importantly, the empirical dataset used extends over a period of time that precedes the 2008 global financial crisis (GFC) and that includes the latest period in which COVID-19 has had an impact on financial markets.
+
+The paper proceeds as follows.
+Section 2 explains the basic idea about how scoring rules are applied in producing and evaluating density forecasts, and provides the definitions of some commonly used scoring rules.
+Section 3 focuses on investigating the effects of different forms and degrees of model misspecification on the performance of optimal forecasts, using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and copula models.
+The assumed predictive model is fixed as ARCH(1) for the purpose of manipulating the degree of model misspecification.
+Although the simulation design is introduced in this section, it forms the foundation of methodologies used in all experiments conducted in other sections of this paper.
+In Section 4, we emulate the simulation exercise on an empirical example for financial returns of the S&P 500 index, including the prediction of the Value-at-Risk (VaR).
+The results illustrate the practical contributions to financial risk management.
+The empirical analysis of the VIX is provided in Section 5, where the predictive model is the heterogeneous autoregressive-realized volatility (HAR-RV) model with different error term specifications.
+We conclude and discuss any possible caveats in Section 6.
+
+# 2. Scoring rules in prediction
 ## 2.1 Overview and notation
 
-Scoring rules can be used in both estimation and prediction.
-In estimation, an optimum estimator $\hat \theta$ can be obtained by maximizing a scoring rule $S_n$ on the condition that $S_n$ is positively oriented.
-That is, $\hat \theta_n=arg \max_\theta S_n(\theta)$, $\hat \theta \to \theta$ as $n \to \infty$.
-While in prediction, scoring rules assign a numerical value to density forecasts, simultaneously addressing both sharpness and calibration (Gneiting & Reftery, 2007).
-For a positively oriented score, higher value will be assigned to a better forecast between two competing candidates.
-The crucial importance of the propreity of scoring rules must be emphasized for the purpose of ranking and comparing forecasts based on scoring rules.
-Gneiting & Raftery, (2007) illustrate the importance of propreity via a case study in weather forecasts and point out that improper scoring rules will assign higher average score to an incorrect density forecast and consequently, mess up the prediction evaluation.
+Scoring rules are a type of criterion function that can be used in producing and evaluating probabilistic predictions.
+The crucial importance of the propriety of scoring rules must be emphasized for the usage of scoring rules.
 Suppose P and Q are predictive distributions and Q is the best forecast given all the available information.
@@
 
-Some commonly used proper scoring rules are the logarithmic score (LS), the continuously ranked probability score (CRPS) and censored likelihood score (CSL) or focused score (FSR) in a sense that CSL focuses on predicting a certain region(s) of densities.
-
-The logarithmic score is defined as (1) where $p_t$ is the probabilistic density forecast.
-It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of nonlinear utility function used is a concern for forecasters (Bickel, 2007).
-\begin{align}
-S_{LS}(p_t, y_{t+1}) = log[p_t(y_{t+1})]
-\end{align}
-However, logarithmic score is criticized by its unboundness and its local property.
+An optimal estimator $\hat \theta_n$ can be obtained by maximizing a scoring rule $S_n(\theta)$ on the condition that $S_n$ is positively oriented. 
+\begin{align}
+\hat \theta_n=arg \max_\theta S_n(\theta)
+\end{align}
+Under certain conditions, including that the scoring rule is 'proper', $\hat \theta_n \to \theta_0 \ as \ T \to \infty$,
+where $\theta_0$ is the true parameter and T is the total sample size of a time series variable $y_t$.
+This idea is adopted in both Bayesian and frequentist predictions, where scoring rules replace the role conventionally played by the likelihood function in producing probabilistic forecasts; see Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.
+(2020).
+
+In addition, in terms of evaluating predictions, scoring rules assign numerical values to density forecasts, addressing both sharpness and calibration simultaneously (Gneiting & Reftery, 2007).
+It is usually the average score ($\bar S_n$) that is used to directly compare predictive accuracy among predictions produced by optimizing different scoring rules.
+For a positively oriented score, for example, a higher value will be assigned to a better forecast between two competing candidates.
+The idea of optimal probabilistic forecasts is that the forecasts produced from a model that is 'optimized' based on a user-specified proper scoring rule will perform the best out-of-sample - according to that same score (Loaiza-Maya et al.,2020).
+The propriety of scoring rules used in optimal forecasts is important, since improper scoring rules will assign a higher average score to an incorrect density forecast
+(Gneiting & Raftery, 2007). Consequently, forecasts based on improper scoring rules will not be 'optimal'.
+
+## 2.2 Some commonly used scoring rules 
+A variety of scoring rules have been developed to tackle different problems.
+Some commonly used proper scoring rules are adopted in the analyses in this paper, such as the logarithmic score (LS), the continuously ranked probability score (CRPS) and the censored likelihood score (CLS).
+
+The logarithmic score is defined as (2) where $p_t$ is the predictive density. 
+\begin{align}
+S_{LS}(p_{t-1}, y_t) = log[p_{t-1}(y_t)]
+\end{align}
+It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters (Bickel, 2007).
+Estimators based on the logarithmic score are equivalent to the maximum likelihood estimator (MLE) so that it is included as a benchmark in the following investigations of optimal forecasts' performance.
+
+However, the logarithmic score is criticized for its unboundedness and its local property.
 Bernardo (1979) states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state".
-Gneiting & Raftery (2007) also argue that logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event.
-Therefore, Gneiting & Raftery, (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in (2) where P is the cumulative distriubtion function, I is the indication function, and x is the materialized events.
-\begin{align}
-CRPS(P,x)=-\int_{-\infty}^{\infty}(P(y)-I(y\geq x))^2dy
-\end{align}
-The formula can be simplifed to (3) if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
-\begin{align}
-CRPS(N,x)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x-\mu}{\sigma})-\frac{x-\mu}{\sigma}(2\Phi(\frac{x-\mu}{\sigma})-1)]
-\end{align}
-where $\phi$ and $\Phi$ are the probability density function and cumulative density function of the Gaussian predictive distribution.
-
-CRPS is defined as a negatively oriented scoring rule, but it can be easily transformed to positively oriented form as shown in (4) for convenient comparison among scoring rules in following sections.
-\begin{align}
-CRPS^*(N,x)=\sigma[-\frac{1}{\sqrt{\pi}}+2\phi(\frac{x-\mu}{\sigma})+\frac{x-\mu}{\sigma}(2\Phi(\frac{x-\mu}{\sigma})-1)]
-\end{align}
-Both LS and CRPS are used for producing and evaluating the entire predictive density.
+Gneiting & Raftery (2007) also argue that the logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event.
+Therefore, Gneiting & Raftery (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in (3)
+\begin{align}
+CRPS(P_{t-1},x_t)=-\int_{-\infty}^{\infty}[P(y)-I(y\geq x_t)]^2dy
+\end{align}
+where P is the cumulative distribution function, *I* is the indicator function, and x is the materialized event.
+
+The formula can be simplified to (4) if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
+\begin{align}
+CRPS(N_{t-1},x_t)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x_t-\mu}{\sigma})-\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
+\end{align}
+where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the Gaussian predictive distribution.
+
+CRPS is defined as a negatively oriented scoring rule, but it can be easily transformed to a positively oriented form as shown in (5) for convenient comparison among scoring rules in the following sections.
+\begin{align}
+CRPS^*(N_{t-1},x_t)=\sigma[-\frac{1}{\sqrt{\pi}}+2\phi(\frac{x_t-\mu}{\sigma})+\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
+\end{align}
+Both LS and CRPS are used for producing and evaluating the entire predictive densities.
 In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011).
-Diks, Panchenko & van Dijk, (2011) propose a new proper scoring rule, censored likelihood score, which allows users to assess the forecasts only in the interested region(s) instead of using weights to emphasize a particular part of the entire density forecast.
-It is defined as in (5) where $p_t$ is the predictive probability density function, $A_t$ is the interested region(s) and $A_t^c$ is the complement of $A_t$.
-\begin{align}
-S_{CSL}(p_t, y_{t+1})=I(y_{t+1} \in A_t)log[ p_t(y_{t+1})]+I(y_{t+1} \in A_t^c)log[\int_{A_t^c} p_t(s)ds]
-\end{align}
-Opschoor, van Dijk & van der Wel (2017) prove that weighted density forecasts based on optimizing the censored likelihood score outperform those on LS and CRPS.
-
-## 2.2 Numerical investigation
-### 2.2.1 Simulation design
-
-Loaiza-Maya, Martin & Frazier (2019) propose a new method, Focused Bayes, in Bayeisian prediction by replacing the conventional likelihood function with the censored likelihood score.
-In their simulated and empirical analysis, Focused Bayes outperforms exact Bayes which is using logarithmic score for updating the prior probability and they also point out the model misspecification plays a role in the performance of Focused Bayes since focusing incorrectly can harm.
+Diks, Panchenko & van Dijk, (2011) propose the censored likelihood score, which allows users to assess forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast.
+Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy.
+It is defined as in (6)
+\begin{align}
+S_{CLS}(p_{t-1}, y_t)=I(y_{t} \in A_t)log[ p_{t-1}(y_{t})]+I(y_{t} \in A_t^c)log[\int_{A_t^c} p_{t-1}(s)ds]
+\end{align}
+where $p_t$ is the predictive probability density function, $A_t$ is the region of interest and $A_t^c$ is the complement of $A_t$.
+Opschoor, van Dijk & van der Wel (2017) prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.
+
+# 3. Numerical investigation of optimal predictions: simulated data 
+## 3.1 Simulation design
+
+Optimal forecasts can outperform predictions produced by conventional methods out of sample; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.(2020); but the underlying reasons driving this phenomenon are still under investigation.
+Loaiza-Maya, Martin & Frazier (2019) propose a new method, focused Bayesian prediction (FBP), which replaces the conventional likelihood function with the censored likelihood score.
+In their simulated and empirical analysis, Focused Bayes outperforms exact Bayes which uses the logarithmic score for updating the prior probability and they also point out that model misspecification plays a role in the performance of Focused Bayes since focusing incorrectly can harm.
 
@@
 Loaiza-Maya et al.(2020) introduce the concepts of ‘coherence’ and ‘strict coherence’ for conveniently documenting the optimal forecasts’ performance.
-Coherence means when the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score.
-Strict coherence is when the optimal prediction is strictly preferable given that score.
-Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules: $S_1, S_2$, then the prediction is said to be coherent if
+Coherence means that the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score.
+Strict coherence happens when the optimal prediction is strictly preferable given that score.
+Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules: $S_1$ and $S_2$.
+The predictive density $S_n(P^{t-1}_{\boldsymbol{\hat \theta_n}},y_t)$ is said to be coherent if
 \begin{align}
@@
 \end{align}
-It is said to be strictly coherent if the equality doesn't hold in (6)(7).
-
-Building on the previous research in this field, we conduct a numerical analysis first in this sub section to further investigate the effects of the form and degree of model misspecification on optimal forecast performance.
-In order to prepare the financial application analysis in following sections of this paper, we simulate a time series dependnet variable $y_t$ that mimics the behavior of financial returns and volatility.
-Specifically, GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock return's distribution, and the negative marginal skewness will be incorporated by an inversion copula with degree of skewness controlled by the shape parameter.
-In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model.
-
-Specific simulation scenarios are listed in following table ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).
+It is said to be strictly coherent if (7) and (8) are strict inequalities.
+
+Building on the previous research in this field, we conduct a numerical analysis in this section to further investigate the effects of the form and degree of model misspecification on the performance of optimal forecasts.
+In order to set the scene for the financial application analysis in following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and volatility.
+Specifically, GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock returns, and the negative marginal skewness will be incorporated by using an inversion copula model, with the degree of marginal skewness controlled by the shape parameter.
+In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP in Scenario (i) and (ii).
+
+Specific simulation scenarios are listed in the following table ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).
 
@@
 
-\textbf{Assumed Model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
+\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
 \end{tabular}
@@
 
-The tails of density are important for risk management in finance so that we decide to apply focused scoring rule (FSR) to 10%, 20%, 80% and 90% tails of the distribution, corresponding to short and long portfolios in finance respectively.
-The methodology in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) is adopted here.
+MLE is a frequently used estimation method in frequentist prediction.
+It often works with the log-likelihood, which corresponds to the logarithmic scoring rule.
+Therefore, we use the predictions produced by MLE (LS) as the benchmark of the following comparisons.
+Besdies, the tails of a density are important for risk management in finance so that we decide to apply the focused scoring rule to the 10%, 20%, 80% and 90% tails of the distribution, corresponding to the risks of long and short portfolios.
+Certain aspects of the methodology used in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) are adopted here.
 We conduct each simulation scenario as follows:
 
+Let $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ be the one-step-ahead prediction based on the assumed model, and $p(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$ ($P(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$) be the predictive probabilistic (cumulative probabilistic) distribution at time t.
+
   1.	Generate T = 6000 observations for $y_t$ from the true DGP
 
-  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}$ in the assumed predictive model based on the positively-oriented score $S_i$ where $\boldsymbol{\hat \theta} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}$
+  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}$ in the assumed predictive model based on the positively oriented score $S_i$ where $\boldsymbol{\hat \theta} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}$
 
@@
 \end{align}
-  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (10)(11)(12):
-
-\begin{align}
-S_{LS}(P_{\boldsymbol\theta^{t-1}},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
-\end{align}
-\begin{align}
-S_{CRPS}^*(P_{\boldsymbol\theta^{t-1}},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
-\end{align}
-\begin{align}
-S_{FSR}(P_{\boldsymbol\theta^{t-1}},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
+  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (11)(12)(13):
+
+\begin{align}
+S_{LS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
+\end{align}
+\begin{align}
+S_{CRPS}^*(P_{\boldsymbol\theta}^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
+\end{align}
+\begin{align}
+S_{FSR}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
 \end{align}
@@
 
-### 2.2.2 Simulation results
-#### 2.2.2.1 Average score tables
-
-The first column of following tables shows $S_i$ that we used to produce predictions and the first row shows $S_j$, which is used for forecasts evaluation.
-The bolded value(s) is the maximum(s) of $\bar S_j(\boldsymbol{\hat \theta^{[i]}})$ in each column.
+## 3.2 Simulation results
+### 3.2.1 Average out-of-sample scores
+
+The first column of each of the following tables presents the labels for the $S_i$ that we used to produce predictions and the third-row shows $S_j$, which is used for the forecast's evaluation.
+The bolded numbers are the largest values of $\bar S_j(\boldsymbol{\hat \theta^{[i]}})$ in each column.
 We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the evaluating scoring rule indicated by the column name.
@@
 The results from Table 1-3 show one particular type of model misspecification.
-That is, the underlying model ARCH(1) cannot capture the volatility clustering feature of the true data generation process (DGP), thus misspecification.
-Besides, with the degree of freedom increases, the data generated from GARCH(1,1) model is more like data that are from ARCH(1) and therefore, the degree of model misspecification decreases.
-When degree of freedom is large enough, we consider ARCH(1) as a correct specified model as shown in Table 1.
-
-From Table 3.
-we could observe strict coherence when degree of model misspecification is high and coherence in Table 1 which is stated as correct specification case.
-These results are consistent with conclusions from Loiaza-Maya et al.(2020).
+That is, the assumed predictive model, ARCH(1), cannot capture the long term volatility clustering feature of the data generated from GARCH(1,1) models, i.e.
+the true DGP.
+Hence, there is misspecification.
+When the degrees of freedom parameter in the error term of GARCH(1,1) is large enough, the ARCH(1) model is correctly specified as shown in Table 1.
+As the degrees of freedom decreases, the degree of model misspecification increases.
+
+From Table 1, the correct specification case, we could observe coherence and strict coherence in Table 3 when the degree of model misspecification is high.
+These results are consistent with conclusions from Loiaza-Maya et al.
+(2020).
 It simply means that we can improve prediction accuracy by using FSR in the presence of model misspecification under certain conditions.
-That is, we are expected to gain more from optimal forecasts while the degree of model misspecification is high.
-
-Table 4-6 show another type of model misspecification where the underlying model cannot capture the asymmetric feature of the true DGP.
+That is, we expect to gain more from optimal forecasts while the degree of model misspecification is high.
+
+Table 4-6 show another type of model misspecification where 
+the ARCH(1) model cannot capture the asymmetric feature of the data generated from copula models (the true DGP).
+From Table 4-6, as the shape parameter decreases, the degree of negative marginal skewness increases, and thus the degrees of model misspecification increases.
 The results give similar conclusions to Table 1-3.
-It proves that optimal forecasts perform in the same way even when we have different types of model mispecification.
-
-#### 2.2.2.2 Score traces plots
-
-As stated in previous literature, focused score tends to outperform CRPS and logarithmic score in predicting tails.
-Therefore, we provide score trace plots to exhibit the comparison of LS, CRPS and FSR’s performance in predicting the 10 percentile and 90 percentile in figure 1 and 2.
-In the left panel, it shows the performance of each score evaluated by FSR 10%.
+It proves that optimal forecasts perform in the same way even when we have different types of model misspecification.
+
+### 3.2.2 Trace plots
+
+The predictive accuracy of tails is important for financial risk management.
+Therefore, we provide score trace plots to exhibit the comparison of MLE, CRPS and FSR’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails.
+The results in Section 3.2.1 shows that when the degree of model misspecification is high, FSR can perform the best compared with MLE and CRPS in predicting tails.
+However, only the average score values at the end of each iteration of the simulation are recorded in the tables, while trace plots provide a dynamic view of how optimal forecasts perform.
+
+In the left panel of each trace plot, it shows the performance of each score evaluated by FSR 10%.
 That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B.
 The right panel shows the same thing but is based on performance of predicting 90 percentile.
-From figure 1 and 2, we could see that FSR almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, FSR starts to outperform CRPS and MLE (LS) in predicting tails.
+From Figure 1 and 2, we could see that FSR almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, FSR starts to outperform CRPS and MLE in predicting tails.
 The more misspecified the model is, the more benefits can we gain from using FSR.
@@
 # need to adjust the size. 
-knitr::include_graphics("figure 1.pdf")
+knitr::include_graphics("figure1.pdf")
 ```
@@
 
-Moreover, the predictive density plots (Appendix 1) in figure 3 to 8, further support our conclusions drawn from the average score tables and score trace plots in above sections.
-They show that predictions obtained from optimizing focused scores aim to match the shape of tails of the true distribution and the changes over time/iterations.
-
-## 2.3 Empirical analysis
-
-From the results in section 2.2, we can conclude that optimal forecasts based on focused score can improve the prediction accuracy in tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification.
-In section 2.3, we apply this method to an empirical setting and investigate how it performs in practice.
-
-The data used in the analysis is the continuously compounded daily log returns of S&P500 listed in U.S.A financial market over a broad time period from 27 Sep,1996 to 30 July,2020.
-It aims to include two very volatile periods, 2008 Global financial crisis (GFC) and the recent COVID-19 pandemic.
-The methodology used here is the same as in the section 2.2 with initial training sample size set to be 1000 and 5000 out-of-sample observations.
-
-### 2.3.1 Empirical analysis results
+Moreover, the predictive density plots (Appendix 1) in Figure 7 to 12, further support our conclusions drawn from the above average score tables and the trace plots.
+They show that predictions obtained from optimizing the focused score aim to match the shape of tails of the true distribution and the changes over time/iterations.
+
+# 4. Empirical analysis: financial returns 
+## 4.1 Overview and preliminary diagnostics
+
+From the results in Section 3.2, we can conclude that optimal forecasts based on the focused score can improve the prediction accuracy in tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification.
+In Section 4, we apply the same method adopted in Section 3 to an empirical setting and investigate how it performs in practice.
+
+The data used in the analysis is the continuously compounded daily log returns of S&P 500 listed in U.S.A financial market over a broad time period from 27 Sep,1996 to 30 July,2020.
+It aims to include two very volatile periods, the GFC and the recent COVID-19 pandemic.
+The initial training sample size and out-of-sample observations are kept consistent with what is in Section 3 with initial training sample size = 1000 and out-of-sample evaluations = 5000.
+
+## 4.2 Empirical results: predictive distributions for returns
 
@@
                 top = text_grob("Descriptive figures",face = "bold"),
-                fig.lab = "Figure 9",fig.lab.face = "bold"
+                fig.lab = "Figure 3",fig.lab.face = "bold"
                 )
@@
 
-The descriptive statistics show that the distribution of S&P500 log returns are negatively skewed and have fat tails and strong serial correlation in its volatility.
+The descriptive statistics show that the distribution of S&P 500 log returns is negatively skewed and has fat tails and strong serial correlation in its volatility.
 Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.
 
-We still use ARCH(1) model in section 2.2 as the assumed predictive model since it is a reasonable model to predict stock returns and volatility and more importantly, it is misspecified with a high degree of model misspecification.
-Therefore, we should expect that predictions produced by optimizing FSR do a better job in predicting two tails of the distribution.
+We still use ARCH(1) model in Section 3 as the assumed predictive model since it is a reasonable model to predict stock returns and volatility.
+More importantly, it is misspecified with a high degree of model misspecification.
+Therefore, based on the results shown in Section 3, we should expect that predictions produced by optimizing FSR do a better job in predicting two tails of the distribution.
 The results of Table 8 support our conjecture.
@@
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 8: Average scores for S&P500"=7))
-```
-
-Unlike simulation, the score trace plots show how different scoring rules perform in real time points which correspond to some historical events.
-In figure 10, one interesting phenomenon is that after the GFC, focused score performs much better than CRPS and MLE compared with before, in terms of predicting both upper and lower tails.
+  add_header_above(c("Table 8: Average scores for S&P 500"=7))
+```
+
+Unlike in the simulation example, the score trace plots now show how different scoring rules perform at time points that correspond to some actual historical events.
+In Figure 4, one interesting phenomenon is that after the GFC, the focused score performs much better than CRPS and MLE compared with before, in terms of predicting both upper and lower tails.
 And this 'jump' effect continues until the very recent date.
-It indicates that optimal probabilistic forecasts might predict financial markets better in and after times of stock market turbulance, which could represent a great contribution to the existing financial analyses of risks and returns.
+It indicates that optimal probabilistic forecasts might predict financial markets better in and after times of stock market turbulence, which could represent a great contribution to the existing financial analyses of risks and returns.
 
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 10(a) Lower Tail","Figure 10(b) Upper Tail"))
-
-```
-
-# 3. Finanical application: Value-at-Risk
-## 3.1 Overview of Value-at-Risk
-
-Density forecasts have great practical values in finance.
-It forms the foundation of risk management, such as Value-at-Risk (VaR) and is useful for asset allocation and derivative pricing.
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 4(a) Lower Tail","Figure 4(b) Upper Tail"))
+
+```
+
+## 4.3 Empirical results: prediction of Value-at-Risk
+### 4.3.1 Overview and preliminaries
+
+Density forecasts have great practical value in finance.
+They form the foundation of risk management, such as Value-at-Risk and are useful for asset allocation and derivative pricing.
 VaR is a commonly used risk measurement in finance.
 It can be obtained from a probability density function of returns over a chosen investment horizon.
-It is the p-quantile of a predictive distribution of a portfolio’s profit/loss over a holding period, according to a given confidence interval $\alpha$ (Dowd, 2005).
+It is the p-quantile ($q_p$) of a predictive distribution of a portfolio’s profit/loss over a holding period, according to a given confidence interval $\alpha$ (Dowd, 2005).
 \begin{align}
@@
 It indicates that investors will not lose more than the amount as shown in VaR.
-It represents the worst level of the investments with the given $\alpha$ confidence level.
+It represents the largest possible investment loss in a given investment horizon with the given $\alpha$ confidence level.
 There are different methods to estimate VaR, but it is clear that predictive density plays an important role here.
-Therefore, a more accurate prediction can contribute to improving the accuracy of VaR estimation.
-
-Opschoor, van Dijk & van der Wel (2017) conduct combining density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the focused score outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.
-
-We illustrate how optimal forecasts perform in estimating VaR by usig predictions produced in section 2.2 and 2.3 and expect optimal forecasts based on FSR would give us a better prediction in tails.
-We implement VaR analysis by using VaR backtesting method.
-Specifically, we follow the steps as bellow:
-
-1. Using the predictive densities produced in section 2.2 and 2.3: $p(y_{1001}|y_{1000})...p(y_{5000}|y_{4999})$;
-
-2. Construct the VaR at \{10%, 20%, 80%, 90%\} using predictive densities in step 1;
-
-3.
-Compare the true values of $y_{1001}...y_{5000}$ with $VaR_t$ and calculate the proportion of exceedances ($y_t < VaR_t$); An accurate estimation of the p% VaR is observed if the proportion of exceedances equals to p%.
-
-## 3.2 Value-at-Risk for simulation analysis
-
-The following tables include VaR estimations at \{10%, 20%, 80%, 90%\} corresponding to the 10% and 20% expected loss of long and short portfolios.
-The values showed in these tables refer to the out-of-sample proportion of exceedances over the nominal VaR level indicated by the column name.
-The closer the proportion of exceedances to nominal VaR levels, the more accurate are VaR estimations, and thus the more accurate are the optimal probablistic forecasts.
-We can see that in two different forms of model misspecification displayed in Table 9 and 10, focused score can provide the most accurate VaR estimation in the upper tail, while in lower tail, it is not short of advantages by too much compared with CRPS.
-These results help us understand what to expect in empirical VaR analysis.
+Therefore, a more accurate prediction can contribute to improving the accuracy of VaR prediction.
+
+Opschoor, van Dijk & van der Wel (2017) combine density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the focused score outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.
+
+We illustrate how optimal forecasts perform in estimating VaR by using predictions produced in simulation (Section 3) first, and expect that optimal forecasts based on FSR would give us a better prediction in tails.
+Specifically, VaR predictions at \{10%, 20%, 80%, 90%\} are conducted, since they correspond to the 10% and 20% expected loss of long and short portfolios.
+We assess VaR predictive accuracy by using the VaR backtesting method.
+The specific steps are as below:
+
+1. Using the sequence of predictive densities (p) produced by {LS, CRPS, FSR10, FSR20, FSR80, FSR90} in Section 3:
+
+    (a) $p_{LS}(y_{1001}|y_{1000})...p_{LS}(y_{5000}|y_{4999})$;
+    (b) $p_{CRPS}(y_{1001}|y_{1000})...p_{CRPS}(y_{5000}|y_{4999})$
+    (c) $p_{FSR10}(y_{1001}|y_{1000})...p_{FSR10}(y_{5000}|y_{4999})$
+    (d) $p_{FSR20}(y_{1001}|y_{1000})...p_{FSR20}(y_{5000}|y_{4999})$
+    (e) $p_{FSR80}(y_{1001}|y_{1000})...p_{FSR80}(y_{5000}|y_{4999})$
+    (f) $p_{FSR90}(y_{1001}|y_{1000})...p_{FSR90}(y_{5000}|y_{4999})$
+
+2. Construct the VaR at \{10%, 20%, 80%, 90%\} using predictive densities (a) - (f) in Step 1 for each scoring rule;
+
+3. Compare the true values of $y_{1001}...y_{5000}$ with $VaR_t$ and calculate the proportion of exceedances ($y_t < VaR_t$);
+
+The closer the proportion of exceedances, calculated in Step 3, to nominal VaR levels, the more accurate are VaR predictions and thus, the more accurate are the optimal probabilistic forecasts.
+An accurate prediction of the p% VaR is observed if the proportion of exceedances equals p%.
+
+Starting from the two different forms of model misspecification investigated in simulation analysis (Section 3), the values showed in the Table 9 and 10 refer to the out-of-sample proportion of exceedances over the nominal VaR level indicated by the column name.
+The focused score can provide the most accurate VaR prediction in the upper tail, while in the lower tail, it is not short of advantages by too much compared with CRPS.
+This conclusion does not vary much when we have different forms of model misspecification as illustrated in the Table 9 and 10.
 
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 9: VaR when true DGP is copula (shape = -5)"=5))
+  add_header_above(c("Table 9: the true DGP is copula (shape = -5)"=5))
 ```
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 10: VaR when true DGP is GARCH with degree of freedom = 3"=5))
-```
-
-## 3.3 Value-at-Risk for empirical analysis
-
-We now implement the VaR analysis to continuously compounded daily log returns of S&P500 in U.S.A financial market.
-Learning from score trace plots in section 2.3.1, the 2008 GFC is the turning point of the optimal forecasts performance, especially for focused scores.
-Therefore, we separate the VaR analysis to two different time periods, before GFC and after GFC.
-The results from Table 11 and 12 show that the focused score perform well enough in terms of estimating VaR for both long and short portfolios of S&P500, but also CRPS is a very robusted scoring rule which can provide relatively accurate predictions.
-Moreover, in Table 12, focused score seems to perform better in 20% and 80% which have higher probability mass.
-If we think of the marginal distribution of S&P500 estimated by histogram in section 2.3.1, the above results could be a consequence of the very sparsed marginal distribution, which increases the difficulty of 'focusing' on the 10% and 90% tails.
+  add_header_above(c("Table 10: the true DGP is GARCH with degree of freedom = 3"=5))
+```
+
+### 4.3.2 Empirical results: S&P 500
+
+The preliminary results obtained from the VaR predictions using simulated data in Section 4.3.1 help us understand what to expect in empirical VaR analysis.
+We now implement the VaR analysis to continuously compounded daily log returns of S&P 500 in U.S.A financial market.
+Learning from the trace plots in Section 4.2, the 2008 GFC is the turning point of the optimal forecasts' performance, especially for the focused scores.
+Therefore, we perform the VaR analysis over two different time periods, before the GFC and after the GFC.
+The results from Table 11 and 12 show that the focused score perform well enough in terms of estimating VaR for both long and short portfolios of S&P 500, but also CRPS is a very robust scoring rule which can provide relatively accurate predictions.
+Moreover, in Table 12, the focused score seems to perform better in 20% and 80% tails which have higher probability mass than 10% and 90% tails.
+If we think of the marginal distribution of S&P 500 estimated by histogram in Figure 3.B, the above results could be a consequence of the very sparse marginal distribution, which increases the difficulty of 'focusing' on the 10% and 90% tails.
 
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 11: VaR for S&P500 before GFC"=5))
+  add_header_above(c("Table 11: VaR for S&P 500 before the GFC"=5))
 
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 12: VaR for S&P500 after GFC"=5))
+  add_header_above(c("Table 12: VaR for S&P 500 after the GFC"=5))
 
@@
 
-# 4. Empirical analysis in VIX
-## 4.1 Background and notation
+## 4.4 Empirical results: optimal portfolio allocation 
+...
+
+# 5. Empirical analysis: VIX
+## 5.1 Background and notation
 
 Time-varying volatility is an important part in finance modelling and an accurate prediction will give investors a better understanding of the risks they take on.
-GARCH-type models used in section 2 and 3 are conditional deterministic.
+GARCH-type models used in Section 3 and 4 are conditionally deterministic.
 That is, $\sigma_t^2$ is a deterministic function of given past returns.
-They neglect the fact that volatility in stock markets and derivative markets can have long memory, which means it slowly reverts to its long-run mean.
+\begin{align}
+r_t=ln(\frac{P_t}{P_{t-1}})
+\end{align}
+\begin{align}
+r_t = \mu+\sigma_t\epsilon_t
+\end{align}
+\begin{align}
+\sigma_t^2=\alpha_0+\alpha_1(r_{t-1}-\mu)^2+\beta_1\sigma_{t-1}^2
+\end{align}
+where $P_t$ is the stock price and $\sigma_t$ is the volatility.
+
+GARCH models also neglect the fact that volatility in stock markets and derivative markets can have long memory, which means it slowly reverts to its long-run mean.
 They record changes usually in daily frequency and do not exploit the information in intraday data.
@@
 The realized volatility (RV) approach to modelling volatility allows us to exploit the information in intraday data, consider long memory feature, sudden jumps in the market and market microstructure.
-When the price follows the process as:
+When the price follows the process as (20):
 \begin{align}
@@
 \end{align}
-When considering the sudden jumps, that is, the price follows the process in (18).
+When considering the sudden jumps, that is, the price follows the process in (22).
 RV is also a consistent estimate of quadratic variation (QV) where $\kappa_s$ represents the sudden jump on day t and $q_t$ is the jump occasions.
@@
 
-VIX index estimates QV that is implied by option prices under a risk-neutral (18) process, using a finite number of strikes of S&P500 index (Chicago Board Options Exchange, 2020).
-It acknowledges the occurance of jumps and the fact that assumptions of Black-Scholes model do not hold.
-Since both VIX and RV are estimations of QV, it is reasonable to model VIX with a HAR-RV model which is usually used for modelling RV in the literature (Corsi, 2009; Maneesoonthorn, Martin, Forbes & Grose, 2012; Martin, Reidy & Wright, 2009; Andersen, Bollerslev & Diebold, 2007).
-
-## 4.2 VIX descriptive statistics 
-We collect daily VIX index data starting from 27 Aug,1996 to 30 July,2020. And the descriptive statistics of $log(VIX_t)$ are shown in Table 13 and Figure 11:
-
-Table 13 and Figure 11 shows that $log(VIX_t)$ is volatile and shows persistence over time.
-It is positively-skewed and the autocorrelation of its volatility is slowly decaying.
-From the descriptive statistics, we can see that the features of VIX is similar to what we have observed from S&P500.
-Similarly, there are unusual jumps happened during GFC and COVID-19.
-Thus, we expect that focused score could outperform MLE and CRPS in predicting tails as before and significantly improve accuracy after GFC.
+VIX index estimates QV that is implied by option prices under a risk-neutral (22) process, using a finite number of strike prices of S&P 500 index (Chicago Board Options Exchange, 2020).
+It acknowledges the occurrence of jumps and the fact that assumptions of the Black-Scholes model do not hold in practice.
+Since both the VIX and RV are estimations of QV, it is reasonable to model the VIX with a HAR-RV model which is usually used for modelling RV in the literature (Andersen, Bollerslev & Diebold, 2007; Corsi, 2009; Martin, Reidy & Wright, 2009; Maneesoonthorn, Martin, Forbes & Grose, 2012).
+
+## 5.2 Preliminary diagnostics
+We collect daily VIX index data starting from 27 Aug,1996 to 30 July,2020. And the descriptive statistics of $log(VIX_t)$ are shown in Table 13 and Figure 5:
+
+Table 13 and Figure 5 show that $log(VIX_t)$ is volatile and shows strong persistence over time.
+It is positively skewed and the autocorrelation of its volatility is slowly decaying.
+From the descriptive statistics, we can see that the features of the VIX is similar to what we have observed from S&P 500 log returns.
+Similarly, there are unusual jumps happened during the GFC and the COVID-19.
+Thus, we expect that the focused score could outperform MLE and CRPS in predicting tails as in Section 4.2 and significantly improve accuracy after the GFC.
 
@@
                 top = text_grob("Descriptive figures",face = "bold"),
-                fig.lab = "Figure 11",fig.lab.face = "bold"
+                fig.lab = "Figure 5",fig.lab.face = "bold"
                 )
@@
 
-## 4.3 Model specification
-
-Proposed by Corsi (2009), HAR-RV model is a simple additive linear model which takes lagged squared returns as regressors.
-It does not belong to the class of long memory models, but it is able to produce the volatility persistence that is almost indistinguishable from what observed in financial markets through the simple AR-type structure.
-
-We design the VIX analysis with different error term specification of HAR-RV: 
+## 5.3 Model specification
+
+Proposed by Corsi (2009), the HAR-RV model is a simple additive linear model which takes lagged squared returns as regressors.
+It does not belong to the class of long memory models, but it is able to produce the volatility persistence that is almost indistinguishable from what observed in financial markets through the simple autoregressive-type structure.
+
+We design the VIX analysis with different error term specifications of the HAR-RV model: 
 \begin{align}
@@
 
-2. $z_{t+1} \sim Student-t(\mu,\sigma,\nu)$ and constant $\sigma$
+2. $z_{t+1} \sim Student-t(0,1,\nu)$ and constant $\sigma$
 
@@
 
-By using the same methodology in section 2 with initial sample size = 1000 and out-of-sample size $\tau=T-1000=5000$, we produce and evaluate predictive densities with the assumed model as HAR-RV.
-
-### 4.3.1 Results of specification 1: Normal error
+By using the same methodology in Section 3 with initial sample size = 1000 and out-of-sample size $\tau=T-1000=5000$, we produce and evaluate predictive densities with the assumed model as HAR-RV.
+The results are shown in the following sections.
+
+## 5.4 Empirical results 
+### 5.4.1 Results of specification 1: Normal error
 
@@
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 14: Average scores for VIX"=7))
+  add_header_above(c("Table 14: Average scores for the VIX"=7))
 ```
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 12(a) Lower Tail","Figure 12(b) Upper Tail"))
-
-```
-
-In Table 14, as expected, FSR performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
-The score trace plot, Figure 12, shows the prediction of optimizing four scoring rules evaluated by FSR10 (left panel) and FSR90 (right panel).
-It indicates how accurate these predictions according to their performance in 10 percentile and 90 percentile.
-In the lower tail, it seems that there is not much difference among four predictions, but if zoom in, we can see that FSR is at the top of other scores, which means it can still provide the most accurate prediction.
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 6(a) Lower Tail","Figure 6(b) Upper Tail"))
+
+```
+
+In Table 14, FSR performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
+The score trace plot, Figure 6, shows the predictions of optimizing four scoring rules evaluated by FSR10 (left panel) and FSR90 (right panel).
+It indicates how accurate these predictions are, according to their performance in 10 percentile and 90 percentile.
+In the lower tail, it seems that there is not much difference among four predictions, but zooming in, we can see that FSR is at the top of other scores, which means it can still provide the most accurate prediction.
 However, we only gain very little from using it.
-On the contrary, in the upper tail, FSR has a much higher effect on improving accuracy after GFC and this effect continues.
-One possible explanation could be that both LS and CRPS can predict the lower tail better if there is higher probability mass at the area, then the benefit of using FSR is not significant.
-Considering the marginal distribution shown in figure 13.B of $log(VIX_t)$, we observe much more observations in the lower end than in the upper end so that it might be the reason why we observe the little improvement in the lower tail in Figure 12(a).
-
-### 4.3.2 Results of specification 2: Student-t
+On the contrary, in the upper tail, FSR has a much bigger effect on improving accuracy after the GFC and this effect continues.
+One possible explanation could be that both LS and CRPS can predict the lower tail better if there is higher probability mass at that area, then the benefit of using FSR is not significant.
+Considering the marginal distribution shown in Figure 5.B of $log(VIX_t)$, we observe much more observations in the lower end than in the upper end so that it might be the reason why we observe the little improvement in predicting the lower tail in Figure 6(a).
+
+### 5.4.2 Results of specification 2: Student-t
 ...
 
-# 5. Conclusion
+# 6. Conclusions
 
@@
 1.
-Optimal forecasts perform almost the same in two different types of model misspecification investigated in this paper and the more misspecified the model is, the more benefits can we gain from using focused score in improving the tail prediction accuracy.
-
-2. Focused score improves the prediction accuracy by a lot after the stock market turbulance and can give better Value-at-Risk estimation.
-
-3. In terms of modelling VIX index, the HAR model with normal error term shows that focused score really makes a difference in predicting upper tail but no great improvement observed in the lower end.
+Optimal forecasts produce identical results in two different types of model misspecification investigated in this paper.
+The results indicate that the more misspecified the model is, the more benefits can be gained from using the focused score in improving the tail prediction accuracy.
+
+2.
+Score-focused predictions provide more accurate tail predictive performance than the conventional likelihood-based counterparts do.
+This result is particularly in evidence after the stock market turbulence.
+Optimal forecasts also give better Value-at-Risk prediction.
+
+3.
+In terms of modelling VIX index, the HAR-RV model with normal error term shows that score-focused prediction really makes a difference in predicting the upper tail, but no great improvement observed in the lower end.
 
@@
 
-1. The VaR is conditional distribution while the focused score is unconditional distribution due to the computation burden.
+1. The CLS focused prediction is based on the tail region of the marginal distribution and not of the predictive distribution. Therefore, there is a little mismatch when predicting VaR.
 
@@
 
-The predictive density plots provide a straightforward way to visualize how optimal probabilistic forecast matches the shape of true DGP distribution through the simulation.
-Here we provide 4 different ‘time points’ to show how these scoring rules work, especially the focused score in figure 3 to 8.
+The predictive density plots provide a straightforward way to visualize how optimal probabilistic forecasts match the shape of the true DGP distribution through the simulation.
+Here we provide 4 different ‘time points’ to show how these scoring rules work, especially the focused score in Figure 7 to 12.
 The blue line is the marginal distribution from the true DGP, and these figures show that predictive density produced from optimizing LS fits the area with high probability mass the best, which is also what LS is designed for.
 However, it performs poorly in terms of predicting tails when the degree of model misspecification is high in both GARCH and copula examples.
-This is when we benefit from using focused score, and we can see from figure 5 and 8 that predictions produced from optimizing focused score aim to match the shape of two tails of the true distribution.
-They outperform predictions from using Maximum likelihood estimation (MLE).
+This is when we benefit from using the focused score, and we can see from Figure 9 and 12 that predictions produced from optimizing the focused score aim to match the shape of two tails of the true distribution.
+They outperform predictions from using the maximum likelihood estimation (MLE).
 

### 2020-08-10 Draft.Rmd
change the line space, fontsize, and margins to thesis requirement.

@@
   chunk_output_type: console
-  header-includes: \usepackage{amsmath}
+  header-includes: 
+  - \usepackage{amsmath}
+  - \usepackage{setspace}\doublespacing
+geometry: margin=1in
+fontsize: 12pt
 output:
@@
   kable("latex",booktabs = T) %>% 
-  kable_styling("bordered") %>% 
+  kable_styling("bordered",font_size = 10) %>% 
   add_header_above(c("Table 7: Descriptive statistics"=9))
@@
   kable("latex",booktabs = T) %>% 
-  kable_styling("bordered")%>% 
+  kable_styling("bordered",font_size = 10)%>% 
   add_header_above(c("Table 13: Descriptive statistics"=9))

### 2020-08-21 Draft.Rmd
add more vix results and fix the z distribution

@@
 We design the VIX analysis with different error term specifications of the HAR-RV model:
+
+1. $z_{t+1} \sim N(0,1)$ and constant $\sigma$
+
+2. $z_{t+1} \sim Student-t(0,1,\nu)$ and constant $\sigma$
+
+3. $z_{t+1} \sim N(0,1)$ and time-varying $\sigma_{t+1}$ following ARCH process
+
+4. $z_{t+1} \sim Student-t(0,1,\nu)$ and time-varying $\sigma_{t+1}$ following ARCH process
+^[Note: Specification senario 1 and 2 are based on equations (24)-(26); Specification 3 and 4 are based on equations (25)-(28)]
+
+\begin{align}
+log(VIX_{t+1})=\beta_0+\beta_1log(VIX_t)+\beta_2log(VIX_{t-5,t})+\beta_3log(VIX_{t-22,t})+\sigma z_{t+1}
+\end{align}
+\begin{align}
+log(VIX_{t-5,t})=\frac{1}{5}[log(VIX_t)+...+log(VIX_{t-4})]
+\end{align}
+\begin{align}
+log(VIX_{t-22,t})=\frac{1}{22}[log(VIX_t)+...+log(VIX_{t-21})]
+\end{align}
+
 \begin{align}
@@
 \begin{align}
-log(VIX_{t-5,t})=\frac{1}{5}[log(VIX_t)+...+log(VIX_{t-4})]
-\end{align}
-\begin{align}
-log(VIX_{t-22,t})=\frac{1}{22}[log(VIX_t)+...+log(VIX_{t-21})]
-\end{align}
-
-1. $z_{t+1} \sim N(0,1)$ and constant $\sigma$
-
-2. $z_{t+1} \sim Student-t(0,1,\nu)$ and constant $\sigma$
-
-3. $z_{t+1} \sim$ skewed Student-t distribution and constant $\sigma$
-
-4. $z_{t+1} \sim N(0,1)$ and time-varying $\sigma_{t+1}$ following GARCH process
-
+\sigma_{t+1}^2=\alpha_0+\alpha_1e^2_t
+\end{align}
 By using the same methodology in Section 3 with initial sample size = 1000 and out-of-sample size $\tau=T-1000=5000$, we produce and evaluate predictive densities with the assumed model as HAR-RV.
@@
 
-### 5.4.2 Results of specification 2: Student-t
-...
+### 5.4.2 Results of specification 2: Student-t error
+
+```{r}
+vix_table <- read.csv("vix_table_st.csv")
+vix_table <- rename(vix_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
+vix_table$`In-sample optimizers`<-c("LS","FSR10","FSR20","FSR80","FSR90")
+
+vix_table %>% 
+  mutate(
+    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
+    #CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
+    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
+    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
+    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
+    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
+  ) %>%
+  kable("latex",escape = F, booktabs = T, linesep = "") %>%
+  kable_styling("bordered",full_width = F)%>%
+  add_header_above(c("","Average out-of-sample scores"=5)) %>% 
+  add_header_above(c("Table 15: Average scores for the VIX Student-t error"=6))
+```
+
+```{r,fig.width=10,fig.height=5}
+# to compress all the calculated plotting average scores together in the same df 
+trace_fsr10 <- read.csv("vixfsr10_st.csv")
+trace_fsr20 <- read.csv("vixfsr20_st.csv")
+trace_10ls <- read.csv("vixfsr10_ls_st.csv")
+#trace_10crps <- read.csv("vixfsr10_crps.csv")
+
+fsr10 <- data.frame(trace_fsr10,trace_fsr20,trace_10ls)
+
+# add back dates to the fsr10 df, initial step = 1000
+
+fsr10 <- fsr10 %>% mutate(Date = vix$Date[1001:6000])
+
+# plot scores --- lower tail 
+fsr10$Date <- as.Date(fsr10$Date,format = "%Y-%m-%d")
+
+color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple")
+
+fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
+  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
+  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
+  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
+ # geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
+  labs(x="Year",y="Average Scores",color="legend")+
+  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
+  scale_x_date(date_breaks = "years",date_labels = "%y")+
+  scale_color_manual(values = color1)+
+  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
+  theme_clean()
+
+# plot scores --- upper tail 
+trace_fsr90 <- read.csv("vixfsr90_st.csv")
+trace_fsr80 <- read.csv("vixfsr80_st.csv")
+trace_90ls <- read.csv("vixfsr90_ls_st.csv")
+#trace_90crps <- read.csv("vixfsr90_crps_st.csv")
+
+fsr90 <- data.frame(trace_fsr90,trace_fsr80,trace_90ls)
+
+# add back dates to the fsr10 df, initial step = 1000
+
+fsr90 <- fsr90 %>% mutate(Date = vix$Date[1001:6000])
+
+# plot scores --- lower tail 
+fsr90$Date <- as.Date(fsr90$Date,format = "%Y-%m-%d")
+
+color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple")
+
+fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
+  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
+  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
+  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
+  # geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
+  labs(x="Year",y="",color="legend")+
+  #ggtitle("Figure 12: S&P500 Score traces-upper tail")+
+  scale_x_date(date_breaks = "years",date_labels = "%y")+
+  scale_color_manual(values = color2)+
+  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.05,label="Global Financial Crisis",color="darkred")+
+  theme_clean()
+
+# put two plots side by side 
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) Lower Tail","Figure 7(b) Upper Tail"))
+```
+
+### 5.4.3 Results of specification 3: time-varying volatility and normal error
+
+```{r}
+vix_table <- read.csv("vix_table_garch.csv")
+vix_table <- rename(vix_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
+vix_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+
+vix_table %>% 
+  mutate(
+    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
+    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
+    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
+    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
+    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
+    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
+  ) %>%
+  kable("latex",escape = F, booktabs = T, linesep = "") %>%
+  kable_styling("bordered",full_width = F)%>%
+  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
+  add_header_above(c("Table 16: Average scores for the VIX ARCH normal error"=7))
+```
+
+```{r,fig.width=10,fig.height=5}
+# to compress all the calculated plotting average scores together in the same df 
+trace_fsr10 <- read.csv("vixfsr10_garch.csv")
+trace_fsr20 <- read.csv("vixfsr20_garch.csv")
+trace_10ls <- read.csv("vixfsr10_ls_gar.csv")
+trace_10crps <- read.csv("vixfsr10_crps_gar.csv")
+
+fsr10 <- data.frame(trace_fsr10,trace_fsr20,trace_10ls,trace_10crps)
+
+# add back dates to the fsr10 df, initial step = 1000
+
+fsr10 <- fsr10 %>% mutate(Date = vix$Date[1001:6000])
+
+# plot scores --- lower tail 
+fsr10$Date <- as.Date(fsr10$Date,format = "%Y-%m-%d")
+
+color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple","CRPS"="green")
+
+fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
+  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
+  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
+  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
+  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
+  labs(x="Year",y="Average Scores",color="legend")+
+  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
+  scale_x_date(date_breaks = "years",date_labels = "%y")+
+  scale_color_manual(values = color1)+
+  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
+  theme_clean()
+
+# plot scores --- upper tail 
+trace_fsr90 <- read.csv("vixfsr90_gar.csv")
+trace_fsr80 <- read.csv("vixfsr80_gar.csv")
+trace_90ls <- read.csv("vixfsr90_ls_gar.csv")
+trace_90crps <- read.csv("vixfsr90_crps_gar.csv")
+
+fsr90 <- data.frame(trace_fsr90,trace_fsr80,trace_90ls,trace_90crps)
+
+# add back dates to the fsr10 df, initial step = 1000
+
+fsr90 <- fsr90 %>% mutate(Date = vix$Date[1001:6000])
+
+# plot scores --- lower tail 
+fsr90$Date <- as.Date(fsr90$Date,format = "%Y-%m-%d")
+
+color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple","CRPS"="green")
+
+fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
+  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
+  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
+  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
+  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
+  labs(x="Year",y="",color="legend")+
+  #ggtitle("Figure 12: S&P500 Score traces-upper tail")+
+  scale_x_date(date_breaks = "years",date_labels = "%y")+
+  scale_color_manual(values = color2)+
+  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.05,label="Global Financial Crisis",color="darkred")+
+  theme_clean()
+
+# put two plots side by side 
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) Lower Tail","Figure 8(b) Upper Tail"))
+
+```
+
+### 5.4.4 Results of specification 4: time-varying volatility and Student-t error
+
+```{r}
+vix_table <- read.csv("vix_table_gst.csv")
+vix_table <- rename(vix_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
+vix_table$`In-sample optimizers`<-c("LS","FSR10","FSR20","FSR80","FSR90")
+
+vix_table %>% 
+  mutate(
+    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
+    #CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
+    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
+    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
+    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
+    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
+  ) %>%
+  kable("latex",escape = F, booktabs = T, linesep = "") %>%
+  kable_styling("bordered",full_width = F)%>%
+  add_header_above(c("","Average out-of-sample scores"=5)) %>% 
+  add_header_above(c("Table 17: Average scores for the VIX ARCH Student-t error"=6))
+```
+
+```{r,fig.width=10,fig.height=5}
+# to compress all the calculated plotting average scores together in the same df 
+trace_fsr10 <- read.csv("vixfsr10_gst.csv")
+trace_fsr20 <- read.csv("vixfsr20_gst.csv")
+trace_10ls <- read.csv("vixfsr10_ls_gst.csv")
+#trace_10crps <- read.csv("vixfsr10_crps.csv")
+
+fsr10 <- data.frame(trace_fsr10,trace_fsr20,trace_10ls)
+
+# add back dates to the fsr10 df, initial step = 1000
+
+fsr10 <- fsr10 %>% mutate(Date = vix$Date[1001:6000])
+
+# plot scores --- lower tail 
+fsr10$Date <- as.Date(fsr10$Date,format = "%Y-%m-%d")
+
+color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple")
+
+fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
+  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
+  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
+  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
+  #geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
+  labs(x="Year",y="Average Scores",color="legend")+
+  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
+  scale_x_date(date_breaks = "years",date_labels = "%y")+
+  scale_color_manual(values = color1)+
+  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
+  theme_clean()
+
+# plot scores --- upper tail 
+trace_fsr90 <- read.csv("vixfsr90_gst.csv")
+trace_fsr80 <- read.csv("vixfsr80_gst.csv")
+trace_90ls <- read.csv("vixfsr90_ls_gst.csv")
+#trace_90crps <- read.csv("vixfsr90_crps.csv")
+
+fsr90 <- data.frame(trace_fsr90,trace_fsr80,trace_90ls)
+
+# add back dates to the fsr10 df, initial step = 1000
+
+fsr90 <- fsr90 %>% mutate(Date = vix$Date[1001:6000])
+
+# plot scores --- lower tail 
+fsr90$Date <- as.Date(fsr90$Date,format = "%Y-%m-%d")
+
+color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple")
+
+fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
+  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
+  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
+  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
+  #geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
+  labs(x="Year",y="",color="legend")+
+  #ggtitle("Figure 12: S&P500 Score traces-upper tail")+
+  scale_x_date(date_breaks = "years",date_labels = "%y")+
+  scale_color_manual(values = color2)+
+  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.05,label="Global Financial Crisis",color="darkred")+
+  theme_clean()
+
+# put two plots side by side 
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) Lower Tail","Figure 9(b) Upper Tail"))
+
+```
 
@@
 
+3. The integral of CRPS is hard to compute once we move away from the normal distribution assumption, since there is usually no closed form for the integral.
+
 \pagebreak
@@
 ```
+
 Andersen, T., Bollerslev, T., & Diebold, F.

### 2020-08-22 Final.Rmd
this is the original version of final thesis
add table of contents

--- 2020-08-21 Draft.Rmd
@@
   warning = FALSE)
-
-# devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8", 
-                    #  filename = 'render_toc.R')
-```
-
-```{r}
-knitr::include_graphics("draft cover page.pdf")
+```
+
+```{r}
+knitr::include_graphics("thesis cover page .pdf")
 ```
@@
 
-```{r toc, echo=FALSE} 
-# render_toc("Draft.Rmd")
-```
+```{=latex}
+% Trigger ToC creation in LaTex
+\setcounter{tocdepth}{2}
+\tableofcontents
+```
+
+\pagebreak
 
@@
   annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.12,label="Global Financial Crisis",color="red",size=3)+
-  annotate(geom = 'text',x=as.Date("2020-04-01"),y=-0.12,label="COVID-19",color="red",size=2)+
+  annotate(geom = 'text',x=as.Date("2020-03-11"),y=-0.12,label="COVID-19",color="red",size=2)+ # the date COVID-19 declared as pandemic
   theme_clean()
@@
   scale_color_manual(values = color1)+
-  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
+  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.15,label="Global Financial Crisis",color="darkred")+
+  annotate(geom = 'text',x=as.Date("2020-03-11"),y=0.15,label="COVID-19",color="darkred",size = 2)+
   theme_clean()
@@
   annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.05,label="Global Financial Crisis",color="darkred")+
+  annotate(geom = 'text',x=as.Date("2020-03-11"),y=-0.05,label="COVID-19",color="darkred",size = 2)+
   theme_clean()
@@
 
-## 4.4 Empirical results: optimal portfolio allocation 
-...
-
 # 5. Empirical analysis: VIX
@@
   annotate(geom = 'text',x=as.Date("2008-09-18"),y=2,label="Global Financial Crisis",color="red",size=3)+
-  annotate(geom = 'text',x=as.Date("2020-04-01"),y=2,label="COVID-19",color="red",size=3)+
+  annotate(geom = 'text',x=as.Date("2020-03-11"),y=2,label="COVID-19",color="red",size=3)+
   theme_clean()
@@
   annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
+  annotate(geom = 'text',x=as.Date("2020-03-11"),y=0.08,label="COVID-19",color="darkred",size = 2)+
   theme_clean()
@@
 3. The integral of CRPS is hard to compute once we move away from the normal distribution assumption, since there is usually no closed form for the integral.
+
+4. The reasons why we can gain considerabley after the GFC needs further investigation.
 

### 2020-08-29 Final.Rmd
minor text adjustments. fixed the margin problem of inserted pdf figures.

@@
 \end{align}
-  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (11)(12)(13):
+  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (11)(12)(13):
 
@@
 
+```{r,fig.align="center"}
+knitr::include_graphics("figure_pred.pdf")
+```
+
 Moreover, the predictive density plots (Appendix 1) in Figure 7 to 12, further support our conclusions drawn from the above average score tables and the trace plots.
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 4(a) Lower Tail","Figure 4(b) Upper Tail"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 4(a) 10 percentile","Figure 4(b) 90 percentile"))
 
@@
 
-1. Using the sequence of predictive densities (p) produced by {LS, CRPS, FSR10, FSR20, FSR80, FSR90} in Section 3:
-
-    (a) $p_{LS}(y_{1001}|y_{1000})...p_{LS}(y_{5000}|y_{4999})$;
-    (b) $p_{CRPS}(y_{1001}|y_{1000})...p_{CRPS}(y_{5000}|y_{4999})$
-    (c) $p_{FSR10}(y_{1001}|y_{1000})...p_{FSR10}(y_{5000}|y_{4999})$
-    (d) $p_{FSR20}(y_{1001}|y_{1000})...p_{FSR20}(y_{5000}|y_{4999})$
-    (e) $p_{FSR80}(y_{1001}|y_{1000})...p_{FSR80}(y_{5000}|y_{4999})$
-    (f) $p_{FSR90}(y_{1001}|y_{1000})...p_{FSR90}(y_{5000}|y_{4999})$
+1. Using the sequence of predictive densities (p) produced by $S_i$ in Section 3:
+
+- $S_i= \{LS, CRPS, FSR10, FSR20, FSR80, FSR90\}$;
+
+- Conditional out-of-sample predictives: $p_{S_i}(y_{1001}|y_{1000})...p_{S_i}(y_{5000}|y_{4999})$;
 
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 6(a) Lower Tail","Figure 6(b) Upper Tail"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 6(a) 10 percentile","Figure 6(b) 90 percentile"))
 
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) Lower Tail","Figure 7(b) Upper Tail"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) 10 percentile","Figure 7(b) 90 percentile"))
 ```
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) Lower Tail","Figure 8(b) Upper Tail"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) 10 percentile","Figure 8(b) 90 percentile"))
 
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) Lower Tail","Figure 9(b) Upper Tail"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) 10 percentile","Figure 9(b) 90 percentile"))
 

### 2020-09-06 Final.Rmd
fix the equation cross reference

@@
 Section 2 explains the basic idea about how scoring rules are applied in producing and evaluating density forecasts, and provides the definitions of some commonly used scoring rules.
-Section 3 focuses on investigating the effects of different forms and degrees of model misspecification on the performance of optimal forecasts, using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and copula models.
+Section 3 focuses on investigating the effects of different forms and degrees of model misspecification on the performance of optimal forecasts, using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and inversion copula models.
 The assumed predictive model is fixed as ARCH(1) for the purpose of manipulating the degree of model misspecification.
@@
 An optimal estimator $\hat \theta_n$ can be obtained by maximizing a scoring rule $S_n(\theta)$ on the condition that $S_n$ is positively oriented. 
-\begin{align}
+\begin{equation} \label{eq:1}
 \hat \theta_n=arg \max_\theta S_n(\theta)
-\end{align}
+\end{equation}
 Under certain conditions, including that the scoring rule is 'proper', $\hat \theta_n \to \theta_0 \ as \ T \to \infty$,
@@
 
-The logarithmic score is defined as (2) where $p_t$ is the predictive density. 
-\begin{align}
+The logarithmic score is defined as $\eqref{eq:ls}$ where $p_t$ is the predictive density. 
+\begin{equation} \label{eq:ls}
 S_{LS}(p_{t-1}, y_t) = log[p_{t-1}(y_t)]
-\end{align}
+\end{equation}
 It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters (Bickel, 2007).
-Estimators based on the logarithmic score are equivalent to the maximum likelihood estimator (MLE) so that it is included as a benchmark in the following investigations of optimal forecasts' performance.
-
+Maximum likelihood estimation (MLE), as a flexible and asymptotically optimal method in econometrics, is based on the logarithmic score so that it is included as a benchmark in the following numerical and empirical investigations of optimal forecasts’ performance.
+\begin{equation} \label{eq:mle}
+\hat \theta_{MLE}=arg \max_\theta \{log[p(\boldsymbol y|\theta)]\}
+\end{equation}
 However, the logarithmic score is criticized for its unboundedness and its local property.
@@
 Gneiting & Raftery (2007) also argue that the logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event.
-Therefore, Gneiting & Raftery (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in (3)
-\begin{align}
+Therefore, Gneiting & Raftery (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in $\eqref{eq:crps}$
+\begin{equation} \label{eq:crps}
 CRPS(P_{t-1},x_t)=-\int_{-\infty}^{\infty}[P(y)-I(y\geq x_t)]^2dy
-\end{align}
+\end{equation}
 where P is the cumulative distribution function, *I* is the indicator function, and x is the materialized event.
 
-The formula can be simplified to (4) if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
-\begin{align}
+The formula can be simplified to $\eqref{eq:crnorm}$ if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
+\begin{equation} \label{eq:crnorm}
 CRPS(N_{t-1},x_t)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x_t-\mu}{\sigma})-\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
-\end{align}
+\end{equation}
 where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the Gaussian predictive distribution.
 
-CRPS is defined as a negatively oriented scoring rule, but it can be easily transformed to a positively oriented form as shown in (5) for convenient comparison among scoring rules in the following sections.
-\begin{align}
+CRPS is defined as a negatively oriented scoring rule, but it can be easily transformed to a positively oriented form as shown in $\eqref{eq:trans}$ for convenient comparison among scoring rules in the following sections.
+\begin{equation} \label{eq:trans}
 CRPS^*(N_{t-1},x_t)=\sigma[-\frac{1}{\sqrt{\pi}}+2\phi(\frac{x_t-\mu}{\sigma})+\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
-\end{align}
+\end{equation}
 Both LS and CRPS are used for producing and evaluating the entire predictive densities.
@@
 Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy.
-It is defined as in (6)
-\begin{align}
+It is defined as in $\eqref{eq:fsr}$
+\begin{equation} \label{eq:fsr}
 S_{CLS}(p_{t-1}, y_t)=I(y_{t} \in A_t)log[ p_{t-1}(y_{t})]+I(y_{t} \in A_t^c)log[\int_{A_t^c} p_{t-1}(s)ds]
-\end{align}
+\end{equation}
 where $p_t$ is the predictive probability density function, $A_t$ is the region of interest and $A_t^c$ is the complement of $A_t$.
@@
 The predictive density $S_n(P^{t-1}_{\boldsymbol{\hat \theta_n}},y_t)$ is said to be coherent if
-\begin{align}
+\begin{equation} \label{eq:coh1}
 \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
-\end{align}
-\begin{align}
+\end{equation}
+\begin{equation} \label{eq:coh2}
 \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)
-\end{align}
-It is said to be strictly coherent if (7) and (8) are strict inequalities.
+\end{equation}
+It is said to be strictly coherent if $\eqref{eq:coh1}$ and $\eqref{eq:coh2}$ are strict inequalities.
 
@@
 Specifically, GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock returns, and the negative marginal skewness will be incorporated by using an inversion copula model, with the degree of marginal skewness controlled by the shape parameter.
+Copulas are functions used to describe the dependence among random variables, which “reweight” the marginal densities to produce a joint density that captures the dependence among random variables (Ref: Yanqin).
+It can be applied to conditional distributions for forecasting purposes as shown in $\eqref{eq:copula}$ where $X_t$ and $Y_t$ are random variables with conditional marginal densities denoted by $F_t$ and $G_t$, $\mathcal{F}_t$ is an information set available at time t, and $H_t$ denotes the conditional joint distribution of $X_t$ and $Y_t$ (Ref: Yanqin).
+\begin{equation} \label{eq:copula}
+H_t(x,y|\mathcal{F}_{t-1})=C_t(F_t(x|\mathcal{F}_{t-1}),G_t(y|\mathcal{F}_{t-1})|\mathcal{F}_{t-1})
+\end{equation}
+The copula-based model used in this section is the stochastic volatility inversion copula.
+It allows us to keep the dependence structure of a state space model and provides the flexibility of using an arbitrary marginal distribution that is not allowed if we use state space models alone (Ref: M).
+
 In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP in Scenario (i) and (ii).
@@
           & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
-\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & copula \\
+\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & Inversion copula \\
 & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline
@@
 
-\begin{align}
+\begin{equation} \label{eq:theta}
 \boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
-\end{align}
-\begin{align}
+\end{equation}
+\begin{equation} \label{eq:score}
 \bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
-\end{align}
-  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (11)(12)(13):
-
-\begin{align}
+\end{equation}
+  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:FSR}$:
+
+\begin{equation} \label{eq:LS}
 S_{LS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
-\end{align}
-\begin{align}
+\end{equation}
+\begin{equation} \label{eq:CRPS}
 S_{CRPS}^*(P_{\boldsymbol\theta}^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
-\end{align}
-\begin{align}
+\end{equation}
+\begin{equation} \label{eq:FSR}
 S_{FSR}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
-\end{align}
+\end{equation}
 4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
-\begin{align}
+\begin{equation} \label{eq:avgscore}
 \bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
-\end{align}
+\end{equation}
 
@@
 
-Moreover, the predictive density plots (Appendix 1) in Figure 7 to 12, further support our conclusions drawn from the above average score tables and the trace plots.
-They show that predictions obtained from optimizing the focused score aim to match the shape of tails of the true distribution and the changes over time/iterations.
+Moreover, the predictive density plots show that predictions obtained from optimizing the focused score aim to match the shape of tails of the true conditional predictive distributions.
+It indicates that the shape of the true conditional predictive distributions plays a role in deciding how much we can gain by using optimal forecasts.
+One must note that in practice, the shape of the true DGP is unknown, but it still is a vital reason why the performance of optimal forecasts varies.^[The predictive density plots in Appendix 1 show the changes of optimal forecasts over time/iterations.]
 
@@
 The initial training sample size and out-of-sample observations are kept consistent with what is in Section 3 with initial training sample size = 1000 and out-of-sample evaluations = 5000.
-
-## 4.2 Empirical results: predictive distributions for returns
 
@@
 Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.
+
+## 4.2 Empirical results: predictive distributions for returns
 
@@
 It is the p-quantile ($q_p$) of a predictive distribution of a portfolio’s profit/loss over a holding period, according to a given confidence interval $\alpha$ (Dowd, 2005).
-\begin{align}
+\begin{equation} \label{eq:var}
 VaR = -q_p \\p=1-\alpha
-\end{align}
+\end{equation}
 It indicates that investors will not lose more than the amount as shown in VaR.
@@
 
-2. Construct the VaR at \{10%, 20%, 80%, 90%\} using predictive densities (a) - (f) in Step 1 for each scoring rule;
+2. Construct the VaR at \{10%, 20%, 80%, 90%\} using predictive densities from Step 1 for each scoring rule;
 
@@
 That is, $\sigma_t^2$ is a deterministic function of given past returns.
-\begin{align}
+\begin{equation} \label{eq:ret}
 r_t=ln(\frac{P_t}{P_{t-1}})
-\end{align}
-\begin{align}
+\end{equation}
+\begin{equation} \label{eq:reg}
 r_t = \mu+\sigma_t\epsilon_t
-\end{align}
-\begin{align}
+\end{equation}
+\begin{equation} \label{eq:garch}
 \sigma_t^2=\alpha_0+\alpha_1(r_{t-1}-\mu)^2+\beta_1\sigma_{t-1}^2
-\end{align}
+\end{equation}
 where $P_t$ is the stock price and $\sigma_t$ is the volatility.
@@
 The realized volatility (RV) approach to modelling volatility allows us to exploit the information in intraday data, consider long memory feature, sudden jumps in the market and market microstructure.
-When the price follows the process as (20):
-\begin{align}
+When the price follows the process as $\eqref{eq:gbm}$:
+\begin{equation} \label{eq:gbm}
 d\ln(P_t)=\mu_tdt+\sigma_tdw_t
-\end{align}
+\end{equation}
 RV is a direct estimate of integrated volatility (IV) for $lnP_t$ based on continuously recorded observations of $P_t$ over the day.
-\begin{align}
+\begin{equation} \label{eq:RV}
 RV_t = \sum^{1/\Delta t}_{j=1}r^2_{t-1+j\Delta t} \xrightarrow{p} \int_{t-1}^t\sigma_s^2ds = IV_t \ as\ \Delta t \to 0
-\end{align}
-When considering the sudden jumps, that is, the price follows the process in (22).
+\end{equation}
+When considering the sudden jumps, that is, the price follows the process in $\eqref{eq:jump}$.
 RV is also a consistent estimate of quadratic variation (QV) where $\kappa_s$ represents the sudden jump on day t and $q_t$ is the jump occasions.
-\begin{align}
+\begin{equation} \label{eq:jump}
 d\ln(P_t)=\mu_tdt+\sigma_tdw_t+\kappa_tdq_t
-\end{align}
-\begin{align}
+\end{equation}
+\begin{equation} \label{eq:RV2}
 RV_t=\sum^{1/\Delta t}_{j=1}r^2_{t-1+j\Delta t} \xrightarrow{p} \int_{t-1}^t\sigma_s^2ds\ + \sum_{s=1}^{q_t}\kappa_s^2= QV_t=IV_t+\sum_{s=1}^{q_t}\kappa_s^2 \ as\ \Delta t \to 0
-\end{align}
+\end{equation}
 In addition to the fact that volatility is a direct measure of the risk of portfolios, it is also important for pricing derivatives, such as options, since it is the only unknown parameter to estimate.
@@
 
-VIX index estimates QV that is implied by option prices under a risk-neutral (22) process, using a finite number of strike prices of S&P 500 index (Chicago Board Options Exchange, 2020).
+VIX index estimates QV that is implied by option prices under a risk-neutral $\eqref{eq:jump}$ process, using a finite number of strike prices of S&P 500 index (Chicago Board Options Exchange, 2020).
 It acknowledges the occurrence of jumps and the fact that assumptions of the Black-Scholes model do not hold in practice.
@@
 
-2. $z_{t+1} \sim Student-t(0,1,\nu)$ and constant $\sigma$
+2.
+$z_{t+1} \sim Student-t(0,1,\nu)$ and constant $\sigma$ ^[We specify $z_{t+1}$ as standardised Student-t distribution so that $\sigma^2$ can reflect the variance of the predicted VIX series.
+The CRPS is removed in Specification 2 and 4, since there is no closed form for this score.]
 
@@
 4. $z_{t+1} \sim Student-t(0,1,\nu)$ and time-varying $\sigma_{t+1}$ following ARCH process
-^[Note: Specification senario 1 and 2 are based on equations (24)-(26); Specification 3 and 4 are based on equations (25)-(28)]
-
-\begin{align}
+^[Specification 1 and 2 are based on equations $\eqref{eq:HAR}$-$\eqref{eq:ma22}$; Specification 3 and 4 are based on equations $\eqref{eq:ma22}$-$\eqref{eq:arch}$]
+
+\begin{equation} \label{eq:HAR}
 log(VIX_{t+1})=\beta_0+\beta_1log(VIX_t)+\beta_2log(VIX_{t-5,t})+\beta_3log(VIX_{t-22,t})+\sigma z_{t+1}
-\end{align}
-\begin{align}
+\end{equation}
+\begin{equation} \label{eq:ma5}
 log(VIX_{t-5,t})=\frac{1}{5}[log(VIX_t)+...+log(VIX_{t-4})]
-\end{align}
-\begin{align}
+\end{equation}
+\begin{equation} \label{eq:ma22}
 log(VIX_{t-22,t})=\frac{1}{22}[log(VIX_t)+...+log(VIX_{t-21})]
-\end{align}
-
-\begin{align}
+\end{equation}
+
+\begin{equation} \label{eq:HAR2}
 log(VIX_{t+1})=\beta_0+\beta_1log(VIX_t)+\beta_2log(VIX_{t-5,t})+\beta_3log(VIX_{t-22,t})+\sigma_{t+1}z_{t+1}
-\end{align}
-\begin{align}
+\end{equation}
+\begin{equation} \label{eq:arch}
 \sigma_{t+1}^2=\alpha_0+\alpha_1e^2_t
-\end{align}
+\end{equation}
 By using the same methodology in Section 3 with initial sample size = 1000 and out-of-sample size $\tau=T-1000=5000$, we produce and evaluate predictive densities with the assumed model as HAR-RV.
@@
 ## 5.4 Empirical results 
-### 5.4.1 Results of specification 1: Normal error
+### 5.4.1 Results of specification 1
+
+Section 5.4.1 provides the result of Specification 1 where the predictive density of the VIX is normal distribution with a constant variance.
+In Table 14, FSR performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
+The score trace plot, Figure 6, shows the predictions of optimizing four scoring rules evaluated by FSR10 (left panel) and FSR90 (right panel).
+It indicates how accurate these predictions are, according to their performance in 10 percentile and 90 percentile.
+In the lower tail, it seems that there is not much difference among four predictions, but zooming in, we can see that FSR is at the top of other scores, which means it can still provide the most accurate prediction.
+However, we only gain very little from using it.
+On the contrary, in the upper tail, FSR has a much bigger effect on improving accuracy after the GFC and this effect continues.
+One possible explanation could be that both LS and CRPS can predict the lower tail better if there is higher probability mass at that area, then the benefit of using FSR is not significant.
+Considering the marginal distribution shown in Figure 5.B of $log(VIX_t)$, we observe much more observations in the lower end than in the upper end so that it might be the reason why we observe the little improvement in predicting the lower tail in Figure 6(a).
 
@@
 
-In Table 14, FSR performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
-The score trace plot, Figure 6, shows the predictions of optimizing four scoring rules evaluated by FSR10 (left panel) and FSR90 (right panel).
-It indicates how accurate these predictions are, according to their performance in 10 percentile and 90 percentile.
-In the lower tail, it seems that there is not much difference among four predictions, but zooming in, we can see that FSR is at the top of other scores, which means it can still provide the most accurate prediction.
-However, we only gain very little from using it.
-On the contrary, in the upper tail, FSR has a much bigger effect on improving accuracy after the GFC and this effect continues.
-One possible explanation could be that both LS and CRPS can predict the lower tail better if there is higher probability mass at that area, then the benefit of using FSR is not significant.
-Considering the marginal distribution shown in Figure 5.B of $log(VIX_t)$, we observe much more observations in the lower end than in the upper end so that it might be the reason why we observe the little improvement in predicting the lower tail in Figure 6(a).
-
-### 5.4.2 Results of specification 2: Student-t error
+### 5.4.2 Results of specification 2
+
+The numerical results in Section 3 show that the more misspecified the model is, the more benefits are gained in improving prediction accuracy.
+According to the marginal distribution estimated by histogram in Figure 5.B, the conditional prediction distribution of the VIX is likely to be positively skewed and has fatter tails than the normal distribution.
+Moving from Specification 1 to Specification 2, fatter tails are allowed in the predictive distribution and thus, the assumed model is less misspecified.
+Table 15 and Figure 7 show consistent performance of optimal forecasts compared with our investigations of simulated data and S&P 500 returns.
+That is, improvement of prediction accuracy by using FSR is still observed in the upper tail but the amount of improvement decreases as the degree of misspecification decreases.
 
@@
 
-### 5.4.3 Results of specification 3: time-varying volatility and normal error
+### 5.4.3 Results of specification 3 & 4:
 
@@
 
-### 5.4.4 Results of specification 4: time-varying volatility and Student-t error
-
 ```{r}
@@
 
+Specification 3 and 4 move from the constant variance of the predictive distribution to the time-varying variance, which is better specified since strong serial correlation of the volatility is observed in the VIX series as shown in Figure 5.C.
+Table 16 and Figure 8 illustrate the optimal forecast performance in Model specification 3.
+The amount of improvement decreased very slightly, compared with results of Specification 1 which also specifies a normal error term.
+Similar conclusions can be drawn from comparing Table 17 and Figure 9 with the results of Specification 2.
+
+The above comparisons indicate that the amount of improvement of prediction accuracy might mainly depend on how the shape of predictive density matches the shape of true density.
+Moreover, the significant improvement of prediction accuracy in the upper tail brings great values in financial applications.
+Firstly, high values of the VIX indicates that the stock market is expected to be more volatile (high volatility), which is an opportunity for either long or short position investors to gain profits or hedge risks, since no one can make money if the stock price doesn’t change at all.
+Besides, investors are typically risk averse, which makes the higher risk (upper tail) is more a concern or an interest to them, compared with the lower risk (lower tail).
+At last, CBOE provides futures contracts written on the VIX, and higher volatility indicates higher price of futures contracts.
+
 # 6. Conclusions
 
-Conclusions:
-
-1.
-Optimal forecasts produce identical results in two different types of model misspecification investigated in this paper.
-The results indicate that the more misspecified the model is, the more benefits can be gained from using the focused score in improving the tail prediction accuracy.
-
-2.
-Score-focused predictions provide more accurate tail predictive performance than the conventional likelihood-based counterparts do.
-This result is particularly in evidence after the stock market turbulence.
-Optimal forecasts also give better Value-at-Risk prediction.
-
-3.
-In terms of modelling VIX index, the HAR-RV model with normal error term shows that score-focused prediction really makes a difference in predicting the upper tail, but no great improvement observed in the lower end.
-
-Caveats:
-
-1. The CLS focused prediction is based on the tail region of the marginal distribution and not of the predictive distribution. Therefore, there is a little mismatch when predicting VaR.
-
-2.
-The practical usage of VaR is often around 1%, while at this very small tail, the focused score might get less and less accurate since there are less observations and consequently, harder to focus on tails.
-
-3. The integral of CRPS is hard to compute once we move away from the normal distribution assumption, since there is usually no closed form for the integral.
-
-4. The reasons why we can gain considerabley after the GFC needs further investigation.
+According to the numerical and empirical results, the benefits of optimal forecasts can be observed when we have model misspecification and their performance does not vary between two different types of model misspecification investigated in this paper.
+By mainly focusing on investigating the tail performance of optimal forecasts, the results show that the more misspecified the model is, the more benefits can be gained from using the focused score in improving the tail prediction accuracy in comparison with the conventional likelihood-based counterparts.
+This result is particularly in evidence after the stock market turbulence in both financial returns and the VIX index.
+What is interesting is that significant improvement of prediction accuracy is observed in both lower and upper tails of S&P 500 log returns but in the VIX index, it only shows up in the upper tail.
+
+One possible conjecture is that there are more observations in the lower tail of the VIX so that MLE or CRPS can still perform well and thus, less benefits are gained by using FSR.
+However, it is impossible to know what the shape of the true conditional predictive distribution looks like, but due to the connection between marginal density and conditional density, this might be a reasonable conjecture to make.
+Nevertheless, these results bring great values to financial applications.
+For the financial returns, optimal forecasts can give better VaR predictions and for the VIX index, the upper tail, which indicates higher volatility in the market, is more of an interest to investors in terms of making profits, hedging risks, and trading of derivatives.
+
+...
 
@@
 Yahoo! finance. (2020). S&P 500 [Data file]. Retrieved from https://finance.yahoo.com/quote/%5EGSPC?p=^GSPC&.tsrc=fin-srch
+
+...
 

### 2020-09-11 Final.Rmd
fix the problem of putting appendix after generated references

@@
     fig_width: 4.5
+    citation_package: natbib
+link-citations: yes
+bibliography: references.bib
 ---
@@
 
-# 3. Numerical investigation of optimal predictions: simulated data 
+# 3. Numerical investigation of optimal predictions
 ## 3.1 Simulation design
@@
 # data cleaning and import 
-sp <- read.csv("^GSPC.csv")
+sp <- read.csv("data/^GSPC.csv")
 sp <- sp %>% dplyr::select("Date","Adj.Close")
@@
 temp <- data.frame(temp)
-write_csv(temp,"sp500log.csv")
+write_csv(temp, "sp500log.csv")
 ```
@@
                 top = text_grob("Descriptive figures",face = "bold"),
-                fig.lab = "Figure 3",fig.lab.face = "bold"
+                fig.lab = "Figure 4",fig.lab.face = "bold"
                 )
@@
 Unlike in the simulation example, the score trace plots now show how different scoring rules perform at time points that correspond to some actual historical events.
-In Figure 4, one interesting phenomenon is that after the GFC, the focused score performs much better than CRPS and MLE compared with before, in terms of predicting both upper and lower tails.
+In Figure 5, one interesting phenomenon is that after the GFC, the focused score performs much better than CRPS and MLE compared with before, in terms of predicting both upper and lower tails.
 And this 'jump' effect continues until the very recent date.
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 4(a) 10 percentile","Figure 4(b) 90 percentile"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 5(a) 10 percentile","Figure 5(b) 90 percentile"))
 
@@
 Moreover, in Table 12, the focused score seems to perform better in 20% and 80% tails which have higher probability mass than 10% and 90% tails.
-If we think of the marginal distribution of S&P 500 estimated by histogram in Figure 3.B, the above results could be a consequence of the very sparse marginal distribution, which increases the difficulty of 'focusing' on the 10% and 90% tails.
+If we think of the marginal distribution of S&P 500 estimated by histogram in Figure 4.B, the above results could be a consequence of the very sparse marginal distribution, which increases the difficulty of 'focusing' on the 10% and 90% tails.
 
@@
 ## 5.2 Preliminary diagnostics
-We collect daily VIX index data starting from 27 Aug,1996 to 30 July,2020. And the descriptive statistics of $log(VIX_t)$ are shown in Table 13 and Figure 5:
-
-Table 13 and Figure 5 show that $log(VIX_t)$ is volatile and shows strong persistence over time.
+We collect daily VIX index data starting from 27 Aug,1996 to 30 July,2020. And the descriptive statistics of $log(VIX_t)$ are shown in Table 13 and Figure 6:
+
+Table 13 and Figure 6 show that $log(VIX_t)$ is volatile and shows strong persistence over time.
 It is positively skewed and the autocorrelation of its volatility is slowly decaying.
@@
 # data cleaning and import 
-vix <- read.csv("^VIX.csv")
+vix <- read.csv("data/^VIX.csv")
 vix <- vix %>% dplyr::select("Date","Adj.Close")
@@
                 top = text_grob("Descriptive figures",face = "bold"),
-                fig.lab = "Figure 5",fig.lab.face = "bold"
+                fig.lab = "Figure 6",fig.lab.face = "bold"
                 )
@@
 In Table 14, FSR performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
-The score trace plot, Figure 6, shows the predictions of optimizing four scoring rules evaluated by FSR10 (left panel) and FSR90 (right panel).
+The score trace plot, Figure 7, shows the predictions of optimizing four scoring rules evaluated by FSR10 (left panel) and FSR90 (right panel).
 It indicates how accurate these predictions are, according to their performance in 10 percentile and 90 percentile.
@@
 One possible explanation could be that both LS and CRPS can predict the lower tail better if there is higher probability mass at that area, then the benefit of using FSR is not significant.
-Considering the marginal distribution shown in Figure 5.B of $log(VIX_t)$, we observe much more observations in the lower end than in the upper end so that it might be the reason why we observe the little improvement in predicting the lower tail in Figure 6(a).
+Considering the marginal distribution shown in Figure 6.B of $log(VIX_t)$, we observe much more observations in the lower end than in the upper end so that it might be the reason why we observe the little improvement in predicting the lower tail in Figure 7(a).
 
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 6(a) 10 percentile","Figure 6(b) 90 percentile"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) 10 percentile","Figure 7(b) 90 percentile"))
 
@@
 The numerical results in Section 3 show that the more misspecified the model is, the more benefits are gained in improving prediction accuracy.
-According to the marginal distribution estimated by histogram in Figure 5.B, the conditional prediction distribution of the VIX is likely to be positively skewed and has fatter tails than the normal distribution.
+According to the marginal distribution estimated by histogram in Figure 6.B, the conditional prediction distribution of the VIX is likely to be positively skewed and has fatter tails than the normal distribution.
 Moving from Specification 1 to Specification 2, fatter tails are allowed in the predictive distribution and thus, the assumed model is less misspecified.
-Table 15 and Figure 7 show consistent performance of optimal forecasts compared with our investigations of simulated data and S&P 500 returns.
+Table 15 and Figure 8 show consistent performance of optimal forecasts compared with our investigations of simulated data and S&P 500 returns.
 That is, improvement of prediction accuracy by using FSR is still observed in the upper tail but the amount of improvement decreases as the degree of misspecification decreases.
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) 10 percentile","Figure 7(b) 90 percentile"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) 10 percentile","Figure 8(b) 90 percentile"))
 ```
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) 10 percentile","Figure 8(b) 90 percentile"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) 10 percentile","Figure 9(b) 90 percentile"))
 
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) 10 percentile","Figure 9(b) 90 percentile"))
-
-```
-
-Specification 3 and 4 move from the constant variance of the predictive distribution to the time-varying variance, which is better specified since strong serial correlation of the volatility is observed in the VIX series as shown in Figure 5.C.
-Table 16 and Figure 8 illustrate the optimal forecast performance in Model specification 3.
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 10(a) 10 percentile","Figure 10(b) 90 percentile"))
+
+```
+
+Specification 3 and 4 move from the constant variance of the predictive distribution to the time-varying variance, which is better specified since strong serial correlation of the volatility is observed in the VIX series as shown in Figure 6.C.
+Table 16 and Figure 9 illustrate the optimal forecast performance in Model specification 3.
 The amount of improvement decreased very slightly, compared with results of Specification 1 which also specifies a normal error term.
-Similar conclusions can be drawn from comparing Table 17 and Figure 9 with the results of Specification 2.
+Similar conclusions can be drawn from comparing Table 17 and Figure 10 with the results of Specification 2.
 
@@
 
-\pagebreak
-
-# References
-
-```{r}
-#DON'T forget alphabetical order!! 
-#cite packages used in the draft
-#citation("knitr")
-```
-
-Andersen, T., Bollerslev, T., & Diebold, F.
-(2007).
-Roughing it Up: Including Jump Components in the Measurement, Modeling and Forecasting of Return Volatility.
-SSRN Electronic Journal.
-doi: 10.2139/ssrn.1150061
-
-Bernardo, J. (1979). Expected Information as Expected Utility. The Annals of Statistics, 7(3), 686-690. doi: 10.1214/aos/1176344689
-
-Bickel, E.J. (2007). Some Comparisons among Quadratic, Spherical and Logarithmic Scoring Rules. Decision Analysis, 4(2), 49-65. doi: 10.1287/deca.1070.0089
-
-Chicago Board Options Exchange. (2018). VIX FAQs. Retrieved from http://www.cboe.com/products/vix-index-volatility/vix-options-and-futures/vix-index/vix-faqs#1
-
-Corsi, F. (2009). A Simple Approximate Long-Memory Model of Realized Volatility. Journal of Financial Econometrics, 7(2), 174-196. doi: 10.1093/jjfinec/nbp001
-
-Diks, C., Panchenko, V., & van Dijk, D. (2011). Likelihood-based scoring rules for comparing density forecasts in tails. Journal of Econometrics, 163(2), 215-230. doi: 10.1016/j.jeconom.2011.04.001
-
-Dowd, K. (2005). Measuring market risk. Chichester: John Wiley.
-
-Fan, Y., & Patton, A. (2014). Copulas in Econometrics. Annual Review of Economics, 6(1), 179-200. doi: 10.1146/annurev-economics-080213-041221
-
-Gneiting, T., & Raftery, A. (2007). Strictly Proper Scoring Rules, Prediction, and Estimation. Journal of the American Statistical Association, 102(477), 359-378. doi: 10.1198/016214506000001437
-
-Gneiting, T., & Ranjan, R.
-(2011).
-Comparing Density Forecasts Using Threshold- and Quantile-Weighted Scoring Rules.
-Journal of Business & Economic Statistics, 29(3), 411-422.
-doi: 10.1198/jbes.2010.08110
-
-Loaiza-Maya, et al. (2020). Optimal Probabilistic Forecasts: when do they work? Manuscript in preparation.
-
-Loaiza-Maya, R., Martin, G., & Frazier, D. (2019). Focused Bayesian Prediction. Retrieved from http://arxiv.org/abs/1912.12571 (http://arxiv.org/abs/1912.12571)
-
-Maneesoonthorn, W., Martin, G., Forbes, C., & Grose, S. (2012). Probabilistic forecasts of volatility and its risk premia. Journal of Econometrics, 171(2), 217-236. doi: 10.1016/j.jeconom.2012.06.006
-
-Martin, G., Reidy, A., & Wright, J.
-(2009).
-Does the option market produce superior forecasts of noise-corrected volatility measures?.
-Journal of Applied Econometrics, 24(1), 77-104.
-doi: 10.1002/jae.1033
-
-Opschoor, A., van Dijk, D., & van der Wel, M. (2017). Combining density forecasts using focused scoring rules. Journal of Applied Econometrics, 32(7), 1298-1313. doi: 10.1002/jae.2575
-
-Smith, M., & Maneesoonthorn, W.
-(2018).
-Inversion copulas from nonlinear state space models with an application to inflation forecasting.
-International Journal of Forecasting, 34(3), 389-407.
-doi: 10.1016/j.ijforecast.2018.01.002
-
-Yahoo! finance. (2020). CBOE Volatility Index [Data file]. Retrieved from https://finance.yahoo.com/quote/%5EVIX/history?period1=1042761600&period2=1072915200&interval=1d&filter=history&frequency=1d
-
-Yahoo! finance. (2020). S&P 500 [Data file]. Retrieved from https://finance.yahoo.com/quote/%5EGSPC?p=^GSPC&.tsrc=fin-srch
-
-...
-
-\pagebreak
-
-# Appendix 
-## Appendix 1: Predictive Densities
-
-The predictive density plots provide a straightforward way to visualize how optimal probabilistic forecasts match the shape of the true DGP distribution through the simulation.
-Here we provide 4 different ‘time points’ to show how these scoring rules work, especially the focused score in Figure 7 to 12.
-The blue line is the marginal distribution from the true DGP, and these figures show that predictive density produced from optimizing LS fits the area with high probability mass the best, which is also what LS is designed for.
-However, it performs poorly in terms of predicting tails when the degree of model misspecification is high in both GARCH and copula examples.
-This is when we benefit from using the focused score, and we can see from Figure 9 and 12 that predictions produced from optimizing the focused score aim to match the shape of two tails of the true distribution.
-They outperform predictions from using the maximum likelihood estimation (MLE).
-
-```{r}
-knitr::include_graphics("figure 3.pdf")
-```
-
-```{r}
-knitr::include_graphics("figure 4.pdf")
-```
-
-```{r}
-knitr::include_graphics("figure 5.pdf")
-```
-
-```{r}
-knitr::include_graphics("figure 6.pdf")
-```
-
-```{r}
-knitr::include_graphics("figure 7.pdf")
-```
-
-```{r}
-knitr::include_graphics("figure 8.pdf")
-```
+[@Diks2011]

### 2020-09-11 appendix.Rmd
fix the problem of putting appendix after generated references

--- 2020-08-09 Draft.Rmd
@@
 ---
-compact-title: no
-editor_options:
-  chunk_output_type: console
-  header-includes: \usepackage{amsmath}
+geometry: margin=1in
+fontsize: 12pt
 output:
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-  echo = FALSE,
-  eval = TRUE,
-  message = FALSE,
-  warning = FALSE)
-
-# devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8", 
-                    #  filename = 'render_toc.R')
-```
-
-```{r}
-knitr::include_graphics("draft cover page.pdf")
-```
-
-\pagebreak
-
-```{r, message=FALSE}
-# library(formattable)
-library(dplyr)
-library(tidyverse)
-library(ggplot2)
-library(tsibble)
-library(tsibbledata)
-library(feasts)
-library(normtest)
-library(moments)
-library(ggthemes)
-library(ggpubr)
-library(knitr)
-library(kableExtra)
-```
-
-# Abstract
-
-With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification.
-Based on previous research on this topic, this paper conducts both numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score.
-In particular, the role of optimal forecasts in predicting Value-at-Risk and the VIX Volatility Index, and in optimizing portfolio allocation, is to be investigated.
-Results at the current stage have shown that the greater the degree of model misspecification, the more beneficial is optimal prediction.
-Empirical analysis shows that after the global financial crisis, predictions that are optimal according to the censored scoring rule that rewards predictive accuracy in a tail are substantially more accurate at predicting observations in said tail than the alternatives, including likelihood-based predictions.
-This indicates the potentially significant contribution to financial analyses of this approach.
-
-\pagebreak
-
-```{r toc, echo=FALSE} 
-# render_toc("Draft.Rmd")
-```
-
-# 1. Introduction
-
-This research paper will explore the question: ‘When do optimal probabilistic forecasts work’, with particular attention given to the usefulness of optimal forecasts in financial applications.
-
-Probabilistic forecasts can provide complete information about future uncertainty, which can be more valuable than point and interval forecasts to forecasters.
-However, previous approaches to prediction - including probabilistic methods - typically assume that the predictive model correctly specifies the process that has generated the observations.
-In practice, the assumed model underpinning the likelihood function will almost certainly differ from the unknown true data generating process (DGP).
-This model misspecification problem has been an ongoing issue for conventional likelihood-based prediction.
-
-As an alternative to likelihood-based prediction, scoring rules have been proposed as a means of producing probabilistic forecasts.
-A variety of alternative proper scoring rules allows users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand (Gneiting & Raftery, 2007).
-Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.
-(2020).
-Among all these investigations, it is the censored likelihood score (CLS) or the focused score (FSR) proposed originally by Diks, Panchenko & van Dijk (2011), that captures our attention, since its ‘focusing’ feature has great potential in financial risk management.
-In other words, CLS/FSR allows a forecaster to focus on predicting any particular region of interest more accurately and, therefore, is expected to make an important contribution to risk prediction in financial settings.
-
-The ‘optimal’ probabilistic forecast has been discussed in Loaiza-Maya et al.
-(2020).
-It refers to a predictive probability distribution that is optimal according to a user-specified scoring rule.
-Whilst some empirical investigations were undertaken, these were primarily illustrative, with there being much scope left for exploring the performance of optimal methods in forecasting different types of financial measures, and under different assumed models.
-
-This research paper extends the work of Loaiza-Maya et al.
-(2020) by investigating the effect of the form and degree of model misspecification on optimal forecast performance in particular financial settings; in particular by conducting an empirical analysis of how optimal forecasts perform in Value-at-Risk (VaR), Volatility Index (VIX) and portfolio optimization applications.
-Importantly, the empirical dataset used extends over a period of time that precedes the 2008 global financial crisis (GFC) and that includes the latest period in which COVID-19 has had an impact on financial markets.
-
-The paper proceeds as follows.
-Section 2 explains the basic idea about how scoring rules are applied in producing and evaluating density forecasts, and provides the definitions of some commonly used scoring rules.
-Section 3 focuses on investigating the effects of different forms and degrees of model misspecification on the performance of optimal forecasts, using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and copula models.
-The assumed predictive model is fixed as ARCH(1) for the purpose of manipulating the degree of model misspecification.
-Although the simulation design is introduced in this section, it forms the foundation of methodologies used in all experiments conducted in other sections of this paper.
-In Section 4, we emulate the simulation exercise on an empirical example for financial returns of the S&P 500 index, including the prediction of the Value-at-Risk (VaR).
-The results illustrate the practical contributions to financial risk management.
-The empirical analysis of the VIX is provided in Section 5, where the predictive model is the heterogeneous autoregressive-realized volatility (HAR-RV) model with different error term specifications.
-We conclude and discuss any possible caveats in Section 6.
-
-# 2. Scoring rules in prediction
-## 2.1 Overview and notation
-
-Scoring rules are a type of criterion function that can be used in producing and evaluating probabilistic predictions.
-The crucial importance of the propriety of scoring rules must be emphasized for the usage of scoring rules.
-Suppose P and Q are predictive distributions and Q is the best forecast given all the available information.
-S(P,Q) denotes the expected value of S(P,$\cdot$) under Q.
-A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q (Gneiting & Raftery, 2007).
-
-An optimal estimator $\hat \theta_n$ can be obtained by maximizing a scoring rule $S_n(\theta)$ on the condition that $S_n$ is positively oriented. 
-\begin{align}
-\hat \theta_n=arg \max_\theta S_n(\theta)
-\end{align}
-Under certain conditions, including that the scoring rule is 'proper', $\hat \theta_n \to \theta_0 \ as \ T \to \infty$,
-where $\theta_0$ is the true parameter and T is the total sample size of a time series variable $y_t$.
-This idea is adopted in both Bayesian and frequentist predictions, where scoring rules replace the role conventionally played by the likelihood function in producing probabilistic forecasts; see Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.
-(2020).
-
-In addition, in terms of evaluating predictions, scoring rules assign numerical values to density forecasts, addressing both sharpness and calibration simultaneously (Gneiting & Reftery, 2007).
-It is usually the average score ($\bar S_n$) that is used to directly compare predictive accuracy among predictions produced by optimizing different scoring rules.
-For a positively oriented score, for example, a higher value will be assigned to a better forecast between two competing candidates.
-The idea of optimal probabilistic forecasts is that the forecasts produced from a model that is 'optimized' based on a user-specified proper scoring rule will perform the best out-of-sample - according to that same score (Loaiza-Maya et al.,2020).
-The propriety of scoring rules used in optimal forecasts is important, since improper scoring rules will assign a higher average score to an incorrect density forecast
-(Gneiting & Raftery, 2007). Consequently, forecasts based on improper scoring rules will not be 'optimal'.
-
-## 2.2 Some commonly used scoring rules 
-A variety of scoring rules have been developed to tackle different problems.
-Some commonly used proper scoring rules are adopted in the analyses in this paper, such as the logarithmic score (LS), the continuously ranked probability score (CRPS) and the censored likelihood score (CLS).
-
-The logarithmic score is defined as (2) where $p_t$ is the predictive density. 
-\begin{align}
-S_{LS}(p_{t-1}, y_t) = log[p_{t-1}(y_t)]
-\end{align}
-It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters (Bickel, 2007).
-Estimators based on the logarithmic score are equivalent to the maximum likelihood estimator (MLE) so that it is included as a benchmark in the following investigations of optimal forecasts' performance.
-
-However, the logarithmic score is criticized for its unboundedness and its local property.
-Bernardo (1979) states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state".
-Gneiting & Raftery (2007) also argue that the logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event.
-Therefore, Gneiting & Raftery (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in (3)
-\begin{align}
-CRPS(P_{t-1},x_t)=-\int_{-\infty}^{\infty}[P(y)-I(y\geq x_t)]^2dy
-\end{align}
-where P is the cumulative distribution function, *I* is the indicator function, and x is the materialized event.
-
-The formula can be simplified to (4) if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
-\begin{align}
-CRPS(N_{t-1},x_t)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x_t-\mu}{\sigma})-\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
-\end{align}
-where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the Gaussian predictive distribution.
-
-CRPS is defined as a negatively oriented scoring rule, but it can be easily transformed to a positively oriented form as shown in (5) for convenient comparison among scoring rules in the following sections.
-\begin{align}
-CRPS^*(N_{t-1},x_t)=\sigma[-\frac{1}{\sqrt{\pi}}+2\phi(\frac{x_t-\mu}{\sigma})+\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
-\end{align}
-Both LS and CRPS are used for producing and evaluating the entire predictive densities.
-In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011).
-Diks, Panchenko & van Dijk, (2011) propose the censored likelihood score, which allows users to assess forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast.
-Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy.
-It is defined as in (6)
-\begin{align}
-S_{CLS}(p_{t-1}, y_t)=I(y_{t} \in A_t)log[ p_{t-1}(y_{t})]+I(y_{t} \in A_t^c)log[\int_{A_t^c} p_{t-1}(s)ds]
-\end{align}
-where $p_t$ is the predictive probability density function, $A_t$ is the region of interest and $A_t^c$ is the complement of $A_t$.
-Opschoor, van Dijk & van der Wel (2017) prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.
-
-# 3. Numerical investigation of optimal predictions: simulated data 
-## 3.1 Simulation design
-
-Optimal forecasts can outperform predictions produced by conventional methods out of sample; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.(2020); but the underlying reasons driving this phenomenon are still under investigation.
-Loaiza-Maya, Martin & Frazier (2019) propose a new method, focused Bayesian prediction (FBP), which replaces the conventional likelihood function with the censored likelihood score.
-In their simulated and empirical analysis, Focused Bayes outperforms exact Bayes which uses the logarithmic score for updating the prior probability and they also point out that model misspecification plays a role in the performance of Focused Bayes since focusing incorrectly can harm.
-
-Loaiza-Maya et al.(2020) extend the above discussion to frequentist probability forecasting.
-They address questions about when we can/cannot benefit from optimal probabilistic forecasts out of sample.
-Loaiza-Maya et al.(2020) introduce the concepts of ‘coherence’ and ‘strict coherence’ for conveniently documenting the optimal forecasts’ performance.
-Coherence means that the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score.
-Strict coherence happens when the optimal prediction is strictly preferable given that score.
-Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules: $S_1$ and $S_2$.
-The predictive density $S_n(P^{t-1}_{\boldsymbol{\hat \theta_n}},y_t)$ is said to be coherent if
-\begin{align}
-\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
-\end{align}
-\begin{align}
-\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)
-\end{align}
-It is said to be strictly coherent if (7) and (8) are strict inequalities.
-
-Building on the previous research in this field, we conduct a numerical analysis in this section to further investigate the effects of the form and degree of model misspecification on the performance of optimal forecasts.
-In order to set the scene for the financial application analysis in following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and volatility.
-Specifically, GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock returns, and the negative marginal skewness will be incorporated by using an inversion copula model, with the degree of marginal skewness controlled by the shape parameter.
-In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP in Scenario (i) and (ii).
-
-Specific simulation scenarios are listed in the following table ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).
-
-\begin{table}[!h]
-\centering
-\begin{tabular}{|c|c|c|}
-\hline
-\multicolumn{3}{|c|}{\textbf{Simulation design}} \\ \hline
-          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
-\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & copula \\
-& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline
-
-\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
-\end{tabular}
-\end{table}
-
-MLE is a frequently used estimation method in frequentist prediction.
-It often works with the log-likelihood, which corresponds to the logarithmic scoring rule.
-Therefore, we use the predictions produced by MLE (LS) as the benchmark of the following comparisons.
-Besdies, the tails of a density are important for risk management in finance so that we decide to apply the focused scoring rule to the 10%, 20%, 80% and 90% tails of the distribution, corresponding to the risks of long and short portfolios.
-Certain aspects of the methodology used in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) are adopted here.
-We conduct each simulation scenario as follows:
-
-Let $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ be the one-step-ahead prediction based on the assumed model, and $p(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$ ($P(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$) be the predictive probabilistic (cumulative probabilistic) distribution at time t.
-
-  1.	Generate T = 6000 observations for $y_t$ from the true DGP
-
-  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}$ in the assumed predictive model based on the positively oriented score $S_i$ where $\boldsymbol{\hat \theta} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}$
-
-\begin{align}
-\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
-\end{align}
-\begin{align}
-\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
-\end{align}
-  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (11)(12)(13):
-
-\begin{align}
-S_{LS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
-\end{align}
-\begin{align}
-S_{CRPS}^*(P_{\boldsymbol\theta}^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
-\end{align}
-\begin{align}
-S_{FSR}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
-\end{align}
-4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
-\begin{align}
-\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
-\end{align}
-
-## 3.2 Simulation results
-### 3.2.1 Average out-of-sample scores
-
-The first column of each of the following tables presents the labels for the $S_i$ that we used to produce predictions and the third-row shows $S_j$, which is used for the forecast's evaluation.
-The bolded numbers are the largest values of $\bar S_j(\boldsymbol{\hat \theta^{[i]}})$ in each column.
-We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the evaluating scoring rule indicated by the column name.
-
-```{r}
-# Editting the matlab written csv files
-
-GARCH_t12 <- read.csv("GARCH_t12__table.csv")
-GARCH_t12 <- rename(GARCH_t12, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-GARCH_t12$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
-
-GARCH_t3 <- read.csv("GARCH_t3_table.csv")
-GARCH_t3 <- rename(GARCH_t3, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-GARCH_t3$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
-
-ARCH_table <- read.csv("ARCH_table.csv")
-ARCH_table <- rename(ARCH_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-ARCH_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
-
-Copula5_table <- read.csv("Copula5_table.csv")
-Copula5_table <- rename(Copula5_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-Copula5_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
-
-Copula3_table <- read.csv("Copula3_table.csv")
-Copula3_table <- rename(Copula3_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-Copula3_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
-
-Copula0_table <- read.csv("Copula0_table.csv")
-Copula0_table <- rename(Copula0_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-Copula0_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
-
-```
-
-```{r}
-ARCH_table %>% 
-  mutate(
-    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
-    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
-    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
-    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
-    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
-    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
-  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 1: the true DGP is ARCH(1)"=7))
-```
-
-```{r}
-GARCH_t12 %>% 
-  mutate(
-    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
-    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
-    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
-    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
-    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
-    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
-  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 2: the true DGP is GARCH(1,1) with degree of freedom = 12"=7))
-```
-
-```{r}
-GARCH_t3 %>% 
-  mutate(
-    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
-    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
-    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
-    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
-    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
-    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
-  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 3: the true DGP is GARCH(1,1) with degree of freedom = 3"=7))
-```
-
-```{r}
-
-Copula0_table %>% 
-  mutate(
-    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
-    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
-    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
-    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
-    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
-    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
-  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 4: the true DGP is copula with shape parameter = 0"=7))
-```
-
-```{r}
-Copula3_table %>% 
-  mutate(
-    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
-    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
-    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
-    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
-    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
-    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
-  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 5: the true DGP is copula with shape parameter = -3"=7))
-```
-
-```{r}
-Copula5_table %>% 
-  mutate(
-    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
-    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
-    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
-    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
-    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
-    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
-  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 6: the true DGP is copula with shape parameter = -5"=7))
-```
-
-The results from Table 1-3 show one particular type of model misspecification.
-That is, the assumed predictive model, ARCH(1), cannot capture the long term volatility clustering feature of the data generated from GARCH(1,1) models, i.e.
-the true DGP.
-Hence, there is misspecification.
-When the degrees of freedom parameter in the error term of GARCH(1,1) is large enough, the ARCH(1) model is correctly specified as shown in Table 1.
-As the degrees of freedom decreases, the degree of model misspecification increases.
-
-From Table 1, the correct specification case, we could observe coherence and strict coherence in Table 3 when the degree of model misspecification is high.
-These results are consistent with conclusions from Loiaza-Maya et al.
-(2020).
-It simply means that we can improve prediction accuracy by using FSR in the presence of model misspecification under certain conditions.
-That is, we expect to gain more from optimal forecasts while the degree of model misspecification is high.
-
-Table 4-6 show another type of model misspecification where 
-the ARCH(1) model cannot capture the asymmetric feature of the data generated from copula models (the true DGP).
-From Table 4-6, as the shape parameter decreases, the degree of negative marginal skewness increases, and thus the degrees of model misspecification increases.
-The results give similar conclusions to Table 1-3.
-It proves that optimal forecasts perform in the same way even when we have different types of model misspecification.
-
-### 3.2.2 Trace plots
-
-The predictive accuracy of tails is important for financial risk management.
-Therefore, we provide score trace plots to exhibit the comparison of MLE, CRPS and FSR’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails.
-The results in Section 3.2.1 shows that when the degree of model misspecification is high, FSR can perform the best compared with MLE and CRPS in predicting tails.
-However, only the average score values at the end of each iteration of the simulation are recorded in the tables, while trace plots provide a dynamic view of how optimal forecasts perform.
-
-In the left panel of each trace plot, it shows the performance of each score evaluated by FSR 10%.
-That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B.
-The right panel shows the same thing but is based on performance of predicting 90 percentile.
-From Figure 1 and 2, we could see that FSR almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, FSR starts to outperform CRPS and MLE in predicting tails.
-The more misspecified the model is, the more benefits can we gain from using FSR.
-It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.
-
-```{r}
-# need to adjust the size. 
-knitr::include_graphics("figure1.pdf")
-```
-
-```{r}
-knitr::include_graphics("figure 2.pdf")
-```
-
-Moreover, the predictive density plots (Appendix 1) in Figure 7 to 12, further support our conclusions drawn from the above average score tables and the trace plots.
-They show that predictions obtained from optimizing the focused score aim to match the shape of tails of the true distribution and the changes over time/iterations.
-
-# 4. Empirical analysis: financial returns 
-## 4.1 Overview and preliminary diagnostics
-
-From the results in Section 3.2, we can conclude that optimal forecasts based on the focused score can improve the prediction accuracy in tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification.
-In Section 4, we apply the same method adopted in Section 3 to an empirical setting and investigate how it performs in practice.
-
-The data used in the analysis is the continuously compounded daily log returns of S&P 500 listed in U.S.A financial market over a broad time period from 27 Sep,1996 to 30 July,2020.
-It aims to include two very volatile periods, the GFC and the recent COVID-19 pandemic.
-The initial training sample size and out-of-sample observations are kept consistent with what is in Section 3 with initial training sample size = 1000 and out-of-sample evaluations = 5000.
-
-## 4.2 Empirical results: predictive distributions for returns
-
-```{r}
-# data cleaning and import 
-sp <- read.csv("^GSPC.csv")
-sp <- sp %>% dplyr::select("Date","Adj.Close")
-
-sp$log.returns <- c(NA,diff(log(sp$Adj.Close)))
-logret <- sp[-c(1:188),c(1,3)] # delete the adjusted price col, only keep 6000 obs
-
-# export the dataset to csv. including only trading days and log returns 
-temp <- logret[,c(2)]
-temp <- data.frame(temp)
-write_csv(temp,"sp500log.csv")
-```
-
-```{r, results='hide'}
-# descriptive statistics 
-summary <- summary(logret$log.returns) # ----> need to be tabulated 
-# range(logret$log.returns)
-# some test results aginst normal dist h_null
-# JB test
-jb.norm.test(logret$log.returns)
-# Ljung box test
-Box.test(logret$log.returns,lag = 2,type = "Lj",fitdf = 1)
-
-sk <- skewness(logret$log.returns)
-kt <- kurtosis(logret$log.returns)
-```
-
-```{r}
-sum <- data.frame(Stock="S&P500",Min=as.numeric(summary[1]),Median=as.numeric(summary[3]),Mean=as.numeric(summary[4]),Max=as.numeric(summary[5]),Skewness=sk,Kurtosis=kt,JB.Test=28270,LB.Test=61.489)
-sum %>% 
-  kable("latex",booktabs = T) %>% 
-  kable_styling("bordered") %>% 
-  add_header_above(c("Table 7: Descriptive statistics"=9))
-```
-
-```{r,message=FALSE,fig.width=10,fig.height=5}
-
-# time series plot
-logret$Date <- as.Date(logret$Date,format = "%Y-%m-%d")
-
-p1 <- logret %>% ggplot(aes(x = Date, y = log.returns)) +
-  geom_line()+theme_classic()+labs(x="Year",y="Daily log returns")+
-  #ggtitle("Figure 9: S&P500 daily log returns")+
-  scale_x_date(date_breaks = "years",date_labels = "%y")+
-  scale_y_continuous(labels = scales::percent) + 
-  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.12,label="Global Financial Crisis",color="red",size=3)+
-  annotate(geom = 'text',x=as.Date("2020-04-01"),y=-0.12,label="COVID-19",color="red",size=2)+
-  theme_clean()
-  #+labs(caption = "Figure 9: the time series plot of S&P500 daily log returns")
-
-# histogram plots
-p2 <- logret %>% ggplot()+geom_histogram(aes(x=log.returns))+xlim(-0.13,0.13)+
-  #ggtitle("Figure 10")+
-  scale_x_continuous(labels = scales::percent)+theme_clean()
-  #+labs(caption = "Figure 10: the distribution of S&P500 log returns is asymmetric")
-
-# ACF plots to see the autocorrelation 
-logret <- logret %>% 
-  mutate(trading_day = row_number()) %>%
-  as_tsibble(index = trading_day,regular = TRUE)
-
-p3 <- logret %>% ACF((log.returns)^2) %>% autoplot() + 
-  #ggtitle("Figure 11:Squared log returns autocorrelation")+
-  xlab("number of lags")+ylab("ACF for variance")+theme_clean()
-# +labs(caption = "Figure 11: the autocorrelation plot shows there is a strong serial correlation in volatility of S&P500")
-
-figure <- ggarrange(p1,                                                 
-          ggarrange(p2, p3, ncol = 2, labels = c("B", "C")), 
-          nrow = 2, 
-          labels = "A"                                        
-          ) 
-annotate_figure(figure, 
-                top = text_grob("Descriptive figures",face = "bold"),
-                fig.lab = "Figure 3",fig.lab.face = "bold"
-                )
-```
-
-The descriptive statistics show that the distribution of S&P 500 log returns is negatively skewed and has fat tails and strong serial correlation in its volatility.
-Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.
-
-We still use ARCH(1) model in Section 3 as the assumed predictive model since it is a reasonable model to predict stock returns and volatility.
-More importantly, it is misspecified with a high degree of model misspecification.
-Therefore, based on the results shown in Section 3, we should expect that predictions produced by optimizing FSR do a better job in predicting two tails of the distribution.
-The results of Table 8 support our conjecture.
-However, the difference between using FSR10(80) and FSR20(90) is very small.
-
-```{r}
-sp_table <- read.csv("sp_table.csv")
-sp_table <- rename(sp_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-sp_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
-
-sp_table %>% 
-  mutate(
-    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
-    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
-    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
-    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
-    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
-    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
-  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 8: Average scores for S&P 500"=7))
-```
-
-Unlike in the simulation example, the score trace plots now show how different scoring rules perform at time points that correspond to some actual historical events.
-In Figure 4, one interesting phenomenon is that after the GFC, the focused score performs much better than CRPS and MLE compared with before, in terms of predicting both upper and lower tails.
-And this 'jump' effect continues until the very recent date.
-It indicates that optimal probabilistic forecasts might predict financial markets better in and after times of stock market turbulence, which could represent a great contribution to the existing financial analyses of risks and returns.
-
-```{r,fig.width=10,fig.height=5}
-# to compress all the calculated plotting average scores together in the same df 
-trace_fsr10 <- read.csv("fsr10.csv")
-trace_fsr20 <- read.csv("fsr20.csv")
-trace_10ls <- read.csv("fsr10_ls.csv")
-trace_10crps <- read.csv("fsr10_crps.csv")
-
-fsr10 <- data.frame(trace_fsr10,trace_fsr20,trace_10ls,trace_10crps)
-
-# add back dates to the fsr10 df, initial step = 1000
-
-fsr10 <- fsr10 %>% mutate(Date = logret$Date[1001:6000])
-
-# plot scores --- lower tail 
-fsr10$Date <- as.Date(fsr10$Date,format = "%Y-%m-%d")
-
-color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple","CRPS"="green")
-
-fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
-  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
-  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
-  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
-  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
-  labs(x="Year",y="Average Scores",color="legend")+
-  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
-  scale_x_date(date_breaks = "years",date_labels = "%y")+
-  scale_color_manual(values = color1)+
-  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
-  theme_clean()
-
-# plot scores --- upper tail 
-trace_fsr90 <- read.csv("fsr90.csv")
-trace_fsr80 <- read.csv("fsr80.csv")
-trace_90ls <- read.csv("fsr90_ls.csv")
-trace_90crps <- read.csv("fsr90_crps.csv")
-
-fsr90 <- data.frame(trace_fsr90,trace_fsr80,trace_90ls,trace_90crps)
-
-# add back dates to the fsr10 df, initial step = 1000
-
-fsr90 <- fsr90 %>% mutate(Date = logret$Date[1001:6000])
-
-# plot scores --- lower tail 
-fsr90$Date <- as.Date(fsr90$Date,format = "%Y-%m-%d")
-
-color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple","CRPS"="green")
-
-fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
-  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
-  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
-  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
-  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
-  labs(x="Year",y="",color="legend")+
-  #ggtitle("Figure 12: S&P500 Score traces-upper tail")+
-  scale_x_date(date_breaks = "years",date_labels = "%y")+
-  scale_color_manual(values = color2)+
-  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.05,label="Global Financial Crisis",color="darkred")+
-  theme_clean()
-
-# put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 4(a) Lower Tail","Figure 4(b) Upper Tail"))
-
-```
-
-## 4.3 Empirical results: prediction of Value-at-Risk
-### 4.3.1 Overview and preliminaries
-
-Density forecasts have great practical value in finance.
-They form the foundation of risk management, such as Value-at-Risk and are useful for asset allocation and derivative pricing.
-VaR is a commonly used risk measurement in finance.
-It can be obtained from a probability density function of returns over a chosen investment horizon.
-It is the p-quantile ($q_p$) of a predictive distribution of a portfolio’s profit/loss over a holding period, according to a given confidence interval $\alpha$ (Dowd, 2005).
-\begin{align}
-VaR = -q_p \\p=1-\alpha
-\end{align}
-It indicates that investors will not lose more than the amount as shown in VaR.
-It represents the largest possible investment loss in a given investment horizon with the given $\alpha$ confidence level.
-There are different methods to estimate VaR, but it is clear that predictive density plays an important role here.
-Therefore, a more accurate prediction can contribute to improving the accuracy of VaR prediction.
-
-Opschoor, van Dijk & van der Wel (2017) combine density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the focused score outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.
-
-We illustrate how optimal forecasts perform in estimating VaR by using predictions produced in simulation (Section 3) first, and expect that optimal forecasts based on FSR would give us a better prediction in tails.
-Specifically, VaR predictions at \{10%, 20%, 80%, 90%\} are conducted, since they correspond to the 10% and 20% expected loss of long and short portfolios.
-We assess VaR predictive accuracy by using the VaR backtesting method.
-The specific steps are as below:
-
-1. Using the sequence of predictive densities (p) produced by {LS, CRPS, FSR10, FSR20, FSR80, FSR90} in Section 3:
-
-    (a) $p_{LS}(y_{1001}|y_{1000})...p_{LS}(y_{5000}|y_{4999})$;
-    (b) $p_{CRPS}(y_{1001}|y_{1000})...p_{CRPS}(y_{5000}|y_{4999})$
-    (c) $p_{FSR10}(y_{1001}|y_{1000})...p_{FSR10}(y_{5000}|y_{4999})$
-    (d) $p_{FSR20}(y_{1001}|y_{1000})...p_{FSR20}(y_{5000}|y_{4999})$
-    (e) $p_{FSR80}(y_{1001}|y_{1000})...p_{FSR80}(y_{5000}|y_{4999})$
-    (f) $p_{FSR90}(y_{1001}|y_{1000})...p_{FSR90}(y_{5000}|y_{4999})$
-
-2. Construct the VaR at \{10%, 20%, 80%, 90%\} using predictive densities (a) - (f) in Step 1 for each scoring rule;
-
-3. Compare the true values of $y_{1001}...y_{5000}$ with $VaR_t$ and calculate the proportion of exceedances ($y_t < VaR_t$);
-
-The closer the proportion of exceedances, calculated in Step 3, to nominal VaR levels, the more accurate are VaR predictions and thus, the more accurate are the optimal probabilistic forecasts.
-An accurate prediction of the p% VaR is observed if the proportion of exceedances equals p%.
-
-Starting from the two different forms of model misspecification investigated in simulation analysis (Section 3), the values showed in the Table 9 and 10 refer to the out-of-sample proportion of exceedances over the nominal VaR level indicated by the column name.
-The focused score can provide the most accurate VaR prediction in the upper tail, while in the lower tail, it is not short of advantages by too much compared with CRPS.
-This conclusion does not vary much when we have different forms of model misspecification as illustrated in the Table 9 and 10.
-
-```{r}
-copula5var <- read.csv("copula5var.csv")
-
-VaR_0.1 <- as.numeric(copula5var[,c(1,5,9,13,17,21)])
-VaR_0.2 <- as.numeric(copula5var[,c(2,6,10,14,18,22)])
-VaR_0.8 <- as.numeric(copula5var[,c(3,7,11,15,19,23)])
-VaR_0.9 <- as.numeric(copula5var[,c(4,8,12,16,20,24)])
-
-Optimizers <- c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
-
-df <- data.frame(Optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
-df <- rename(df,"VaR at 10\\%"=VaR_0.1, "VaR at 20\\%"=VaR_0.2, "VaR at 80\\%"=VaR_0.8, "VaR at 90\\%"=VaR_0.9)
-
-df %>% 
-  mutate(
-    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
-    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
-    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
-    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F,booktabs=T, linesep = "") %>%
-  kable_styling("bordered",full_width = F) %>%
-  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 9: the true DGP is copula (shape = -5)"=5))
-```
-
-```{r}
-garch3var <- read.csv("garch3var.csv")
-
-VaR0.1 <- as.numeric(garch3var[,c(1,5,9,13,17,21)])
-VaR0.2 <- as.numeric(garch3var[,c(2,6,10,14,18,22)])
-VaR0.8 <- as.numeric(garch3var[,c(3,7,11,15,19,23)])
-VaR0.9 <- as.numeric(garch3var[,c(4,8,12,16,20,24)])
-
-df <- data.frame(Optimizers,VaR0.1,VaR0.2,VaR0.8,VaR0.9)
-df <- rename(df,"VaR at 10\\%"=VaR0.1, "VaR at 20\\%"=VaR0.2, "VaR at 80\\%"=VaR0.8, "VaR at 90\\%"=VaR0.9)
-
-df %>% 
-  mutate(
-    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
-    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
-    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
-    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs=T, linesep = "") %>%
-  kable_styling("bordered",full_width = F) %>%
-  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 10: the true DGP is GARCH with degree of freedom = 3"=5))
-```
-
-### 4.3.2 Empirical results: S&P 500
-
-The preliminary results obtained from the VaR predictions using simulated data in Section 4.3.1 help us understand what to expect in empirical VaR analysis.
-We now implement the VaR analysis to continuously compounded daily log returns of S&P 500 in U.S.A financial market.
-Learning from the trace plots in Section 4.2, the 2008 GFC is the turning point of the optimal forecasts' performance, especially for the focused scores.
-Therefore, we perform the VaR analysis over two different time periods, before the GFC and after the GFC.
-The results from Table 11 and 12 show that the focused score perform well enough in terms of estimating VaR for both long and short portfolios of S&P 500, but also CRPS is a very robust scoring rule which can provide relatively accurate predictions.
-Moreover, in Table 12, the focused score seems to perform better in 20% and 80% tails which have higher probability mass than 10% and 90% tails.
-If we think of the marginal distribution of S&P 500 estimated by histogram in Figure 3.B, the above results could be a consequence of the very sparse marginal distribution, which increases the difficulty of 'focusing' on the 10% and 90% tails.
-
-```{r}
-spvar <- read.csv("spvar1_table.csv")
-
-VaR_0.1 <- as.numeric(spvar[,c(1,5,9,13,17,21)])
-VaR_0.2 <- as.numeric(spvar[,c(2,6,10,14,18,22)])
-VaR_0.8 <- as.numeric(spvar[,c(3,7,11,15,19,23)])
-VaR_0.9 <- as.numeric(spvar[,c(4,8,12,16,20,24)])
-
-df <- data.frame(Optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
-df <- rename(df,"VaR at 10\\%"=VaR_0.1, "VaR at 20\\%"=VaR_0.2, "VaR at 80\\%"=VaR_0.8, "VaR at 90\\%"=VaR_0.9)
-
-df %>% 
-  mutate(
-    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
-    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
-    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
-    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs=T, linesep = "") %>%
-  kable_styling("bordered",full_width = F) %>%
-  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 11: VaR for S&P 500 before the GFC"=5))
-
-# formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
-```
-
-```{r}
-spvar <- read.csv("spvar2_table.csv")
-spvar <- round(spvar,digits = 4)
-
-VaR_0.1 <- as.numeric(spvar[,c(1,5,9,13,17,21)])
-VaR_0.2 <- as.numeric(spvar[,c(2,6,10,14,18,22)])
-VaR_0.8 <- as.numeric(spvar[,c(3,7,11,15,19,23)])
-VaR_0.9 <- as.numeric(spvar[,c(4,8,12,16,20,24)])
-
-df <- data.frame(Optimizers,VaR_0.1,VaR_0.2,VaR_0.8,VaR_0.9)
-df <- rename(df,"VaR at 10\\%"=VaR_0.1, "VaR at 20\\%"=VaR_0.2, "VaR at 80\\%"=VaR_0.8, "VaR at 90\\%"=VaR_0.9)
-
-df %>% 
-  mutate(
-    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
-    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
-    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
-    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs=T, linesep = "") %>%
-  kable_styling("bordered",full_width = F) %>%
-  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 12: VaR for S&P 500 after the GFC"=5))
-
-# formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
-```
-
-## 4.4 Empirical results: optimal portfolio allocation 
-...
-
-# 5. Empirical analysis: VIX
-## 5.1 Background and notation
-
-Time-varying volatility is an important part in finance modelling and an accurate prediction will give investors a better understanding of the risks they take on.
-GARCH-type models used in Section 3 and 4 are conditionally deterministic.
-That is, $\sigma_t^2$ is a deterministic function of given past returns.
-\begin{align}
-r_t=ln(\frac{P_t}{P_{t-1}})
-\end{align}
-\begin{align}
-r_t = \mu+\sigma_t\epsilon_t
-\end{align}
-\begin{align}
-\sigma_t^2=\alpha_0+\alpha_1(r_{t-1}-\mu)^2+\beta_1\sigma_{t-1}^2
-\end{align}
-where $P_t$ is the stock price and $\sigma_t$ is the volatility.
-
-GARCH models also neglect the fact that volatility in stock markets and derivative markets can have long memory, which means it slowly reverts to its long-run mean.
-They record changes usually in daily frequency and do not exploit the information in intraday data.
-Therefore, it is better off if we model volatility in a continuous-time model where $lnP_t$ and $\sigma_t$ are allowed to vary continuously over time.
-
-The realized volatility (RV) approach to modelling volatility allows us to exploit the information in intraday data, consider long memory feature, sudden jumps in the market and market microstructure.
-When the price follows the process as (20):
-\begin{align}
-d\ln(P_t)=\mu_tdt+\sigma_tdw_t
-\end{align}
-RV is a direct estimate of integrated volatility (IV) for $lnP_t$ based on continuously recorded observations of $P_t$ over the day.
-\begin{align}
-RV_t = \sum^{1/\Delta t}_{j=1}r^2_{t-1+j\Delta t} \xrightarrow{p} \int_{t-1}^t\sigma_s^2ds = IV_t \ as\ \Delta t \to 0
-\end{align}
-When considering the sudden jumps, that is, the price follows the process in (22).
-RV is also a consistent estimate of quadratic variation (QV) where $\kappa_s$ represents the sudden jump on day t and $q_t$ is the jump occasions.
-\begin{align}
-d\ln(P_t)=\mu_tdt+\sigma_tdw_t+\kappa_tdq_t
-\end{align}
-\begin{align}
-RV_t=\sum^{1/\Delta t}_{j=1}r^2_{t-1+j\Delta t} \xrightarrow{p} \int_{t-1}^t\sigma_s^2ds\ + \sum_{s=1}^{q_t}\kappa_s^2= QV_t=IV_t+\sum_{s=1}^{q_t}\kappa_s^2 \ as\ \Delta t \to 0
-\end{align}
-In addition to the fact that volatility is a direct measure of the risk of portfolios, it is also important for pricing derivatives, such as options, since it is the only unknown parameter to estimate.
-The famous Black-Scholes model assumes a constant volatility over time which does not hold in practice.
-Implied volatility allows us to incorporate the jumps and continuous variation of volatility over time.
-In other words, implied volatility is an estimate of QV extracted from option prices.
-
-VIX index estimates QV that is implied by option prices under a risk-neutral (22) process, using a finite number of strike prices of S&P 500 index (Chicago Board Options Exchange, 2020).
-It acknowledges the occurrence of jumps and the fact that assumptions of the Black-Scholes model do not hold in practice.
-Since both the VIX and RV are estimations of QV, it is reasonable to model the VIX with a HAR-RV model which is usually used for modelling RV in the literature (Andersen, Bollerslev & Diebold, 2007; Corsi, 2009; Martin, Reidy & Wright, 2009; Maneesoonthorn, Martin, Forbes & Grose, 2012).
-
-## 5.2 Preliminary diagnostics
-We collect daily VIX index data starting from 27 Aug,1996 to 30 July,2020. And the descriptive statistics of $log(VIX_t)$ are shown in Table 13 and Figure 5:
-
-Table 13 and Figure 5 show that $log(VIX_t)$ is volatile and shows strong persistence over time.
-It is positively skewed and the autocorrelation of its volatility is slowly decaying.
-From the descriptive statistics, we can see that the features of the VIX is similar to what we have observed from S&P 500 log returns.
-Similarly, there are unusual jumps happened during the GFC and the COVID-19.
-Thus, we expect that the focused score could outperform MLE and CRPS in predicting tails as in Section 4.2 and significantly improve accuracy after the GFC.
-
-```{r,message=F}
-# data cleaning and import 
-vix <- read.csv("^VIX.csv")
-vix <- vix %>% dplyr::select("Date","Adj.Close")
-
-vix$logvix <- log(vix$Adj.Close)
-
-# previous day log vix values
-prev <- matrix(0,nrow = nrow(vix)+1,ncol = 1)
-for (i in 1:nrow(vix)){
-  prev[1,1] <- c("NA")
-  prev[i+1,1] <- vix$logvix[i]
-}
-prev <- as.data.frame(prev)
-prev <- prev[-c(1:188,6189),1]
-
-# need to be very careful about the time index -- dependent variable starting with t+1
-MA5 <- matrix(0,nrow=nrow(vix)-5,ncol = 1)
-for (i in 1:(nrow(vix)-5)){
-  sum = 0
-  for (j in 1:5){
-    sum = sum + vix$logvix[i+j-1]
-  }
-  MA5[i,1] = (1/5)*sum
-}
-
-MA22 <- matrix(0,nrow = nrow(vix)-22,ncol = 1)
-for (i in 1:(nrow(vix)-22)){
-  sum = 0
-  for (j in 1:22){
-    sum = sum + vix$logvix[i+j-1]
-  }
-  MA22[i,1] = (1/22)*sum
-}
-
-#require(zoo)
-#MA5 <- rollmean(vix$logvix,5,align = "center")
-MA5 <- as.data.frame(MA5) # average of past week
-MA5 <- MA5[-c(1:183),1] # including only 6000 obs
-
-#MA22 <- rollmean(vix$logvix,22,align = "center")
-MA22 <- as.data.frame(MA22) # average of past month
-MA22 <- MA22[-c(1:166),1] # including only 6000 obs
-
-logvix <- vix[-c(1:188),c(1,3)] # delete the adjusted vix col, only keep 6000 obs
-logvix <- cbind(logvix,prev,MA5,MA22)
-# export the dataset to csv. including only trading days and log returns
-
-temp <- logvix[,2:5]
-write_csv(temp,"vixlog.csv")
-
-# the logvix, previous log vix and moving average values have the same length in the final file. 
-```
-
-```{r, results='hide'}
-# descriptive statistics 
-summary <- summary(vix$logvix) # ----> need to be tabulated 
-# range(vix$logvix)
-# some test results aginst normal dist h_null
-# JB test
-jb.norm.test(vix$logvix)
-# Ljung box test
-Box.test(vix$logvix,lag = 2,type = "Lj",fitdf = 1)
-
-vixsk <- skewness(vix$logvix)
-vixkt <- kurtosis(vix$logvix)
-```
-
-```{r}
-sum <- data.frame(Series="Log(VIX)",Min = as.numeric(summary[1]), Median = as.numeric(summary[3]), Mean = as.numeric(summary[4]), Max = as.numeric(summary[6]),Skewness= vixsk,Kurtosis=vixkt,JB.Test=410.77,LB.Test=11765)
-sum %>% 
-  kable("latex",booktabs = T) %>% 
-  kable_styling("bordered")%>% 
-  add_header_above(c("Table 13: Descriptive statistics"=9))
-```
-
-```{r,message=FALSE,fig.width=10,fig.height=5}
-
-# time series plot
-logvix$Date <- as.Date(logvix$Date,format = "%Y-%m-%d")
-
-p1 <- logvix %>% ggplot(aes(x = Date, y = logvix)) +
-  geom_line()+theme_classic()+labs(x="Year",y="Daily log(VIX) values")+
-  #ggtitle("Figure ?: Daily values for Log(VIX)")+
-  scale_x_date(date_breaks = "years",date_labels = "%y")+
-  #scale_y_continuous(labels = scales::percent) + 
-  annotate(geom = 'text',x=as.Date("2008-09-18"),y=2,label="Global Financial Crisis",color="red",size=3)+
-  annotate(geom = 'text',x=as.Date("2020-04-01"),y=2,label="COVID-19",color="red",size=3)+
-  theme_clean()
-
-# histogram plots
-p2 <- logvix %>% ggplot()+geom_histogram(aes(x=logvix))+
-  theme_clean()
-
-# ACF plots to see the autocorrelation 
-logvix <- logvix %>% 
-  mutate(trading_day = row_number()) %>%
-  as_tsibble(index = trading_day,regular = TRUE)
-
-p3 <- logvix %>% ACF((logvix)^2) %>% autoplot()+
-      xlab("number of lags")+ylab("ACF")+theme_clean()
-
-figure <- ggarrange(p1,                                                 
-          ggarrange(p2, p3, ncol = 2, labels = c("B", "C")), 
-          nrow = 2, 
-          labels = "A"                                        
-          ) 
-annotate_figure(figure, 
-                top = text_grob("Descriptive figures",face = "bold"),
-                fig.lab = "Figure 5",fig.lab.face = "bold"
-                )
-```
-
-## 5.3 Model specification
-
-Proposed by Corsi (2009), the HAR-RV model is a simple additive linear model which takes lagged squared returns as regressors.
-It does not belong to the class of long memory models, but it is able to produce the volatility persistence that is almost indistinguishable from what observed in financial markets through the simple autoregressive-type structure.
-
-We design the VIX analysis with different error term specifications of the HAR-RV model: 
-\begin{align}
-log(VIX_{t+1})=\beta_0+\beta_1log(VIX_t)+\beta_2log(VIX_{t-5,t})+\beta_3log(VIX_{t-22,t})+\sigma_{t+1}z_{t+1}
-\end{align}
-\begin{align}
-log(VIX_{t-5,t})=\frac{1}{5}[log(VIX_t)+...+log(VIX_{t-4})]
-\end{align}
-\begin{align}
-log(VIX_{t-22,t})=\frac{1}{22}[log(VIX_t)+...+log(VIX_{t-21})]
-\end{align}
-
-1. $z_{t+1} \sim N(0,1)$ and constant $\sigma$
-
-2. $z_{t+1} \sim Student-t(0,1,\nu)$ and constant $\sigma$
-
-3. $z_{t+1} \sim$ skewed Student-t distribution and constant $\sigma$
-
-4. $z_{t+1} \sim N(0,1)$ and time-varying $\sigma_{t+1}$ following GARCH process
-
-By using the same methodology in Section 3 with initial sample size = 1000 and out-of-sample size $\tau=T-1000=5000$, we produce and evaluate predictive densities with the assumed model as HAR-RV.
-The results are shown in the following sections.
-
-## 5.4 Empirical results 
-### 5.4.1 Results of specification 1: Normal error
-
-```{r}
-vix_table <- read.csv("vix_table.csv")
-vix_table <- rename(vix_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-vix_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
-
-vix_table %>% 
-  mutate(
-    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
-    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
-    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
-    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
-    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
-    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
-  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 14: Average scores for the VIX"=7))
-```
-
-```{r,fig.width=10,fig.height=5}
-# to compress all the calculated plotting average scores together in the same df 
-trace_fsr10 <- read.csv("vixfsr10.csv")
-trace_fsr20 <- read.csv("vixfsr20.csv")
-trace_10ls <- read.csv("vixfsr10_ls.csv")
-trace_10crps <- read.csv("vixfsr10_crps.csv")
-
-fsr10 <- data.frame(trace_fsr10,trace_fsr20,trace_10ls,trace_10crps)
-
-# add back dates to the fsr10 df, initial step = 1000
-
-fsr10 <- fsr10 %>% mutate(Date = vix$Date[1001:6000])
-
-# plot scores --- lower tail 
-fsr10$Date <- as.Date(fsr10$Date,format = "%Y-%m-%d")
-
-color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple","CRPS"="green")
-
-fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
-  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
-  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
-  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
-  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
-  labs(x="Year",y="Average Scores",color="legend")+
-  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
-  scale_x_date(date_breaks = "years",date_labels = "%y")+
-  scale_color_manual(values = color1)+
-  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.08,label="Global Financial Crisis",color="darkred")+
-  theme_clean()
-
-# plot scores --- upper tail 
-trace_fsr90 <- read.csv("vixfsr90.csv")
-trace_fsr80 <- read.csv("vixfsr80.csv")
-trace_90ls <- read.csv("vixfsr90_ls.csv")
-trace_90crps <- read.csv("vixfsr90_crps.csv")
-
-fsr90 <- data.frame(trace_fsr90,trace_fsr80,trace_90ls,trace_90crps)
-
-# add back dates to the fsr10 df, initial step = 1000
-
-fsr90 <- fsr90 %>% mutate(Date = vix$Date[1001:6000])
-
-# plot scores --- lower tail 
-fsr90$Date <- as.Date(fsr90$Date,format = "%Y-%m-%d")
-
-color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple","CRPS"="green")
-
-fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
-  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
-  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
-  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
-  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
-  labs(x="Year",y="",color="legend")+
-  #ggtitle("Figure 12: S&P500 Score traces-upper tail")+
-  scale_x_date(date_breaks = "years",date_labels = "%y")+
-  scale_color_manual(values = color2)+
-  annotate(geom = 'text',x=as.Date("2008-09-18"),y=-0.05,label="Global Financial Crisis",color="darkred")+
-  theme_clean()
-
-# put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 6(a) Lower Tail","Figure 6(b) Upper Tail"))
-
-```
-
-In Table 14, FSR performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
-The score trace plot, Figure 6, shows the predictions of optimizing four scoring rules evaluated by FSR10 (left panel) and FSR90 (right panel).
-It indicates how accurate these predictions are, according to their performance in 10 percentile and 90 percentile.
-In the lower tail, it seems that there is not much difference among four predictions, but zooming in, we can see that FSR is at the top of other scores, which means it can still provide the most accurate prediction.
-However, we only gain very little from using it.
-On the contrary, in the upper tail, FSR has a much bigger effect on improving accuracy after the GFC and this effect continues.
-One possible explanation could be that both LS and CRPS can predict the lower tail better if there is higher probability mass at that area, then the benefit of using FSR is not significant.
-Considering the marginal distribution shown in Figure 5.B of $log(VIX_t)$, we observe much more observations in the lower end than in the upper end so that it might be the reason why we observe the little improvement in predicting the lower tail in Figure 6(a).
-
-### 5.4.2 Results of specification 2: Student-t
-...
-
-# 6. Conclusions
-
-Conclusions:
-
-1.
-Optimal forecasts produce identical results in two different types of model misspecification investigated in this paper.
-The results indicate that the more misspecified the model is, the more benefits can be gained from using the focused score in improving the tail prediction accuracy.
-
-2.
-Score-focused predictions provide more accurate tail predictive performance than the conventional likelihood-based counterparts do.
-This result is particularly in evidence after the stock market turbulence.
-Optimal forecasts also give better Value-at-Risk prediction.
-
-3.
-In terms of modelling VIX index, the HAR-RV model with normal error term shows that score-focused prediction really makes a difference in predicting the upper tail, but no great improvement observed in the lower end.
-
-Caveats:
-
-1. The CLS focused prediction is based on the tail region of the marginal distribution and not of the predictive distribution. Therefore, there is a little mismatch when predicting VaR.
-
-2.
-The practical usage of VaR is often around 1%, while at this very small tail, the focused score might get less and less accurate since there are less observations and consequently, harder to focus on tails.
-
-\pagebreak
-
-# References
-
-```{r}
-#DON'T forget alphabetical order!! 
-#cite packages used in the draft
-#citation("knitr")
-```
-Andersen, T., Bollerslev, T., & Diebold, F.
-(2007).
-Roughing it Up: Including Jump Components in the Measurement, Modeling and Forecasting of Return Volatility.
-SSRN Electronic Journal.
-doi: 10.2139/ssrn.1150061
-
-Bernardo, J. (1979). Expected Information as Expected Utility. The Annals of Statistics, 7(3), 686-690. doi: 10.1214/aos/1176344689
-
-Bickel, E.J. (2007). Some Comparisons among Quadratic, Spherical and Logarithmic Scoring Rules. Decision Analysis, 4(2), 49-65. doi: 10.1287/deca.1070.0089
-
-Chicago Board Options Exchange. (2018). VIX FAQs. Retrieved from http://www.cboe.com/products/vix-index-volatility/vix-options-and-futures/vix-index/vix-faqs#1
-
-Corsi, F. (2009). A Simple Approximate Long-Memory Model of Realized Volatility. Journal of Financial Econometrics, 7(2), 174-196. doi: 10.1093/jjfinec/nbp001
-
-Diks, C., Panchenko, V., & van Dijk, D. (2011). Likelihood-based scoring rules for comparing density forecasts in tails. Journal of Econometrics, 163(2), 215-230. doi: 10.1016/j.jeconom.2011.04.001
-
-Dowd, K. (2005). Measuring market risk. Chichester: John Wiley.
-
-Fan, Y., & Patton, A. (2014). Copulas in Econometrics. Annual Review of Economics, 6(1), 179-200. doi: 10.1146/annurev-economics-080213-041221
-
-Gneiting, T., & Raftery, A. (2007). Strictly Proper Scoring Rules, Prediction, and Estimation. Journal of the American Statistical Association, 102(477), 359-378. doi: 10.1198/016214506000001437
-
-Gneiting, T., & Ranjan, R.
-(2011).
-Comparing Density Forecasts Using Threshold- and Quantile-Weighted Scoring Rules.
-Journal of Business & Economic Statistics, 29(3), 411-422.
-doi: 10.1198/jbes.2010.08110
-
-Loaiza-Maya, et al. (2020). Optimal Probabilistic Forecasts: when do they work? Manuscript in preparation.
-
-Loaiza-Maya, R., Martin, G., & Frazier, D. (2019). Focused Bayesian Prediction. Retrieved from http://arxiv.org/abs/1912.12571 (http://arxiv.org/abs/1912.12571)
-
-Maneesoonthorn, W., Martin, G., Forbes, C., & Grose, S. (2012). Probabilistic forecasts of volatility and its risk premia. Journal of Econometrics, 171(2), 217-236. doi: 10.1016/j.jeconom.2012.06.006
-
-Martin, G., Reidy, A., & Wright, J.
-(2009).
-Does the option market produce superior forecasts of noise-corrected volatility measures?.
-Journal of Applied Econometrics, 24(1), 77-104.
-doi: 10.1002/jae.1033
-
-Opschoor, A., van Dijk, D., & van der Wel, M. (2017). Combining density forecasts using focused scoring rules. Journal of Applied Econometrics, 32(7), 1298-1313. doi: 10.1002/jae.2575
-
-Smith, M., & Maneesoonthorn, W.
-(2018).
-Inversion copulas from nonlinear state space models with an application to inflation forecasting.
-International Journal of Forecasting, 34(3), 389-407.
-doi: 10.1016/j.ijforecast.2018.01.002
-
-Yahoo! finance. (2020). CBOE Volatility Index [Data file]. Retrieved from https://finance.yahoo.com/quote/%5EVIX/history?period1=1042761600&period2=1072915200&interval=1d&filter=history&frequency=1d
-
-Yahoo! finance. (2020). S&P 500 [Data file]. Retrieved from https://finance.yahoo.com/quote/%5EGSPC?p=^GSPC&.tsrc=fin-srch
-
-\pagebreak
-
 # Appendix 
@@
 The predictive density plots provide a straightforward way to visualize how optimal probabilistic forecasts match the shape of the true DGP distribution through the simulation.
-Here we provide 4 different ‘time points’ to show how these scoring rules work, especially the focused score in Figure 7 to 12.
+Here we provide 4 different ‘time points’ to show how these scoring rules work, especially the focused score in Figure ?
+to ?.
 The blue line is the marginal distribution from the true DGP, and these figures show that predictive density produced from optimizing LS fits the area with high probability mass the best, which is also what LS is designed for.
 However, it performs poorly in terms of predicting tails when the degree of model misspecification is high in both GARCH and copula examples.
-This is when we benefit from using the focused score, and we can see from Figure 9 and 12 that predictions produced from optimizing the focused score aim to match the shape of two tails of the true distribution.
+This is when we benefit from using the focused score, and we can see from Figure ?
+and ?
+that predictions produced from optimizing the focused score aim to match the shape of two tails of the true distribution.
 They outperform predictions from using the maximum likelihood estimation (MLE).

### 2020-09-12 Final.Rmd
delete the crps transform to positively oriented equation part

@@
 ```{r, message=FALSE}
-# library(formattable)
 library(dplyr)
@@
 
-With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification.
-Based on previous research on this topic, this paper conducts both numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score.
-In particular, the role of optimal forecasts in predicting Value-at-Risk and the VIX Volatility Index, and in optimizing portfolio allocation, is to be investigated.
-Results at the current stage have shown that the greater the degree of model misspecification, the more beneficial is optimal prediction.
-Empirical analysis shows that after the global financial crisis, predictions that are optimal according to the censored scoring rule that rewards predictive accuracy in a tail are substantially more accurate at predicting observations in said tail than the alternatives, including likelihood-based predictions.
-This indicates the potentially significant contribution to financial analyses of this approach.
+This paper conducts numerical and empirical analyses to explore the impact of the form and degree of model misspecification on optimal probabilistic forecasting method which is recently proposed to conduct a forecast using scoring rules instead of the conventional likelihood function in the frequentist econometrics.
+In particular, the role of optimal forecasts in predicting S&P 500 returns, the Value-at-Risk and the VIX Volatility Index.
+We find that the performance of optimal probabilistic forecasts is insensitive to the form of misspecification but improves as the degree of misspecification increases.
+After the Global financial crisis, predictions that are optimal according to the focused scoring rule that rewards predictive accuracy in a tail are substantially more accurate at predicting observations in said tail than the alternatives, including likelihood-based predictions.
 
@@
 
-This research paper will explore the question: ‘When do optimal probabilistic forecasts work’, with particular attention given to the usefulness of optimal forecasts in financial applications.
+This paper explores the question: ‘When do optimal probabilistic forecasts work’, with particular attention given to the usefulness of optimal probabilistic forecasts in financial applications.
 
@@
 
-Scoring rules are a type of criterion function that can be used in producing and evaluating probabilistic predictions.
-The crucial importance of the propriety of scoring rules must be emphasized for the usage of scoring rules.
+Optimal probabilistic forecasts discussed in this paper refer to the forecasts produced from a model that is ‘optimized’ based on a user-specified proper scoring rule will perform the best out-of-sample – according to that same score (Loaiza-Maya et al.,2020).
+
+Scoring rules are a type of criterion function that can be optimized to produce an optimal estimator and thus, a probabilistic prediction derived from this optimal estimator and an assumed model.
+They also play the role of encouraging forecasters to make careful and honest assessments in elicitation of subjectivist Bayesians, and evaluating and ranking competitive probabilistic forecasts, based on the predictive distribution and materialized events or values, by assigning a numerical score [@waite2005; @gneiting2007].
+Therefore, the crucial importance of the propriety of scoring rules must be emphasized for their usage because improper scoring rules will assign a higher average score to an incorrect density forecast (Gneiting & Raftery, 2007).
+Consequently, forecasts based on improper scoring rules will not be ‘optimal’.
+
 Suppose P and Q are predictive distributions and Q is the best forecast given all the available information.
@@
 
-An optimal estimator $\hat \theta_n$ can be obtained by maximizing a scoring rule $S_n(\theta)$ on the condition that $S_n$ is positively oriented. 
+In terms of producing probabilistic forecasts, scoring rules can replace the conventional likelihood function in frequentist and Bayesian predictions; see Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.
+(2020).
+Supposing the scoring rule is positively oriented, an estimator $\hat \theta_n$ obtained by maximizing a scoring rule $S_n(\theta)$ is said to be 'optimal' based on this scoring rule.
 \begin{equation} \label{eq:1}
@@
 where $\theta_0$ is the true parameter and T is the total sample size of a time series variable $y_t$.
-This idea is adopted in both Bayesian and frequentist predictions, where scoring rules replace the role conventionally played by the likelihood function in producing probabilistic forecasts; see Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.
-(2020).
-
-In addition, in terms of evaluating predictions, scoring rules assign numerical values to density forecasts, addressing both sharpness and calibration simultaneously (Gneiting & Reftery, 2007).
-It is usually the average score ($\bar S_n$) that is used to directly compare predictive accuracy among predictions produced by optimizing different scoring rules.
-For a positively oriented score, for example, a higher value will be assigned to a better forecast between two competing candidates.
-The idea of optimal probabilistic forecasts is that the forecasts produced from a model that is 'optimized' based on a user-specified proper scoring rule will perform the best out-of-sample - according to that same score (Loaiza-Maya et al.,2020).
-The propriety of scoring rules used in optimal forecasts is important, since improper scoring rules will assign a higher average score to an incorrect density forecast
-(Gneiting & Raftery, 2007). Consequently, forecasts based on improper scoring rules will not be 'optimal'.
+The predictions conditional on this optimal estimator, $p(y_{T+1}|M,\hat \theta_n,y_{1:T})$, is said to be produced from a model that is 'optimized' according to a proper scoring rule.
+^[M refers to the assumed model and it is omitted in the following notation for simplicity, since the assumed model does not change.]
+
+In addition, in terms of evaluating predictions, it is usually the average score ($\bar S_n$) that is used to directly compare predictive accuracy among predictions produced by optimizing different scoring rules (Gneiting & Reftery, 2007).
+\begin{equation} \label{eq:sbar}
+\bar S_n = \frac{1}{T}\sum_{t=1}^TS_n(p_{t+1},y_t)
+\end{equation}
+For a positively oriented score, for example, a higher value will be assigned to a better forecast between two competing candidates, on the condition the scoring rule being proper.
 
@@
 
-The logarithmic score is defined as $\eqref{eq:ls}$ where $p_t$ is the predictive density. 
+The logarithmic score is defined as in $\eqref{eq:ls}$ where $p_t$ is the predictive density. 
 \begin{equation} \label{eq:ls}
@@
 It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters (Bickel, 2007).
-Maximum likelihood estimation (MLE), as a flexible and asymptotically optimal method in econometrics, is based on the logarithmic score so that it is included as a benchmark in the following numerical and empirical investigations of optimal forecasts’ performance.
+One common usage of the logarithmic score in frequentist econometrics is the maximum likelihood estimation (MLE).
 \begin{equation} \label{eq:mle}
@@
 \end{equation}
+It is included as a benchmark in the following numerical and empirical investigations of the performance of optimal forecasts due to its asymptotically optimal and efficient characteristics under the correctly specified log-likelihood function.
+
 However, the logarithmic score is criticized for its unboundedness and its local property.
@@
 Gneiting & Raftery (2007) also argue that the logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event.
-Therefore, Gneiting & Raftery (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in $\eqref{eq:crps}$
+Gneiting & Raftery (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in $\eqref{eq:crps}$
 \begin{equation} \label{eq:crps}
@@
 
-CRPS is defined as a negatively oriented scoring rule, but it can be easily transformed to a positively oriented form as shown in $\eqref{eq:trans}$ for convenient comparison among scoring rules in the following sections.
-\begin{equation} \label{eq:trans}
-CRPS^*(N_{t-1},x_t)=\sigma[-\frac{1}{\sqrt{\pi}}+2\phi(\frac{x_t-\mu}{\sigma})+\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
-\end{equation}
 Both LS and CRPS are used for producing and evaluating the entire predictive densities.
@@
 \end{equation}
-  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:FSR}$:
+  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:FSR}$:^[The CRPS in $\eqref{eq:CRPS}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]
 
@@
 ...
-
-[@Diks2011]

### 2020-09-16 Final.Rmd
new thesis text changes in simulation design section (this is before I replace all FSR with CLS)!

@@
   - \usepackage{setspace}\doublespacing
+  - \usepackage[hyphens]{url}
+fontsize: 12pt
 geometry: margin=1in
-fontsize: 12pt
 output:
@@
     fig_width: 4.5
-    citation_package: natbib
 link-citations: yes
@@
 
+The degree of model misspecification impacts the performance of optimal forecasts.
+The greater the degree of misspecification is, the more benefits are gained from optimal forecasts in both Bayesian and frequentist predictions, conditional on the assumed predictive model being compatible; see [@fbp2019], [@optimal].
+The simulation analysis in this paper will extend the exploration in this field and ask the question ‘Will the performance of optimal forecasts change when a different form of misspecification occurs?’.
+
+In order to set the scene for the financial application analyses in following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and volatility.
+Specific simulation scenarios are listed in the following table ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).
+
+\begin{table}[!h]
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+\multicolumn{3}{|c|}{\textbf{Simulation design}} \\ \hline
+          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
+\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & Stochastic volatility inversion copula \\
+& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline
+
+\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
+\end{tabular}
+\end{table}
+
+GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock returns, and the negative marginal skewness will be incorporated by using a stochastic volatility inversion copula model, with the degree of marginal skewness controlled by the shape parameter.
+
+Copulas “reweight” the marginal densities to produce a joint density that captures the dependence among random variables, which can be applied to conditional distributions for forecasting purposes as shown in $\eqref{eq:copula}$.
+\begin{equation} \label{eq:copula}
+H_t(x,y|\mathcal{F}_{t-1})=C_t(F_t(x|\mathcal{F}_{t-1}),G_t(y|\mathcal{F}_{t-1})|\mathcal{F}_{t-1})
+\end{equation}
+where $X_t$ and $Y_t$ are random variables with conditional marginal densities denoted by $F_t$ and $G_t$, $\mathcal{F}_t$ is an information set available at time t, and $H_t$ denotes the conditional joint distribution of $X_t$ and $Y_t$ [@fan2014].
+
+The stochastic volatility inversion copula model used in this section allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns but is not allowed if we use state space models alone [@inversion2018].
+
+In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP in Scenario (i) and (ii).
+
 Optimal forecasts can outperform predictions produced by conventional methods out of sample; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.(2020); but the underlying reasons driving this phenomenon are still under investigation.
@@
 Building on the previous research in this field, we conduct a numerical analysis in this section to further investigate the effects of the form and degree of model misspecification on the performance of optimal forecasts.
-In order to set the scene for the financial application analysis in following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and volatility.
-Specifically, GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock returns, and the negative marginal skewness will be incorporated by using an inversion copula model, with the degree of marginal skewness controlled by the shape parameter.
-Copulas are functions used to describe the dependence among random variables, which “reweight” the marginal densities to produce a joint density that captures the dependence among random variables (Ref: Yanqin).
-It can be applied to conditional distributions for forecasting purposes as shown in $\eqref{eq:copula}$ where $X_t$ and $Y_t$ are random variables with conditional marginal densities denoted by $F_t$ and $G_t$, $\mathcal{F}_t$ is an information set available at time t, and $H_t$ denotes the conditional joint distribution of $X_t$ and $Y_t$ (Ref: Yanqin).
-\begin{equation} \label{eq:copula}
-H_t(x,y|\mathcal{F}_{t-1})=C_t(F_t(x|\mathcal{F}_{t-1}),G_t(y|\mathcal{F}_{t-1})|\mathcal{F}_{t-1})
-\end{equation}
-The copula-based model used in this section is the stochastic volatility inversion copula.
-It allows us to keep the dependence structure of a state space model and provides the flexibility of using an arbitrary marginal distribution that is not allowed if we use state space models alone (Ref: M).
-
-In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP in Scenario (i) and (ii).
-
-Specific simulation scenarios are listed in the following table ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).
-
-\begin{table}[!h]
-\centering
-\begin{tabular}{|c|c|c|}
-\hline
-\multicolumn{3}{|c|}{\textbf{Simulation design}} \\ \hline
-          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
-\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & Inversion copula \\
-& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline
-
-\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
-\end{tabular}
-\end{table}
 
@@
 \begin{equation} \label{eq:var}
-VaR = -q_p \\p=1-\alpha
+VaR = -q_p
+\end{equation}
+\begin{equation} \label{eq:p}
+p=1-\alpha
 \end{equation}
@@
 ...
+
+@optimal 
+@cboe
+@vixdata
+@spdata
+
+# References

### 2020-09-16 Final.Rmd
finished changing FSR to CLS (except figure 1,2,3). more text changes to follow

@@
 (2020).
-Among all these investigations, it is the censored likelihood score (CLS) or the focused score (FSR) proposed originally by Diks, Panchenko & van Dijk (2011), that captures our attention, since its ‘focusing’ feature has great potential in financial risk management.
-In other words, CLS/FSR allows a forecaster to focus on predicting any particular region of interest more accurately and, therefore, is expected to make an important contribution to risk prediction in financial settings.
+Among all these investigations, it is the censored likelihood score (CLS) proposed originally by Diks, Panchenko & van Dijk (2011), that captures our attention, since its ‘focusing’ feature has great potential in financial risk management.
+In other words, CLS allows a forecaster to focus on predicting any particular region of interest more accurately and, therefore, is expected to make an important contribution to risk prediction in financial settings.
 
@@
 Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy.
-It is defined as in $\eqref{eq:fsr}$
-\begin{equation} \label{eq:fsr}
+It is defined as in $\eqref{eq:cls}$
+\begin{equation} \label{eq:cls}
 S_{CLS}(p_{t-1}, y_t)=I(y_{t} \in A_t)log[ p_{t-1}(y_{t})]+I(y_{t} \in A_t^c)log[\int_{A_t^c} p_{t-1}(s)ds]
@@
 \end{equation}
-  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:FSR}$:^[The CRPS in $\eqref{eq:CRPS}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]
+  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:CLS}$:^[The CRPS in $\eqref{eq:CRPS}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]
 
@@
 \end{equation}
-\begin{equation} \label{eq:FSR}
-S_{FSR}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
+\begin{equation} \label{eq:CLS}
+S_{CLS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
 \end{equation}
@@
 GARCH_t12 <- read.csv("GARCH_t12__table.csv")
-GARCH_t12 <- rename(GARCH_t12, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-GARCH_t12$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+GARCH_t12 <- rename(GARCH_t12, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+GARCH_t12$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
 
 GARCH_t3 <- read.csv("GARCH_t3_table.csv")
-GARCH_t3 <- rename(GARCH_t3, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-GARCH_t3$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+GARCH_t3 <- rename(GARCH_t3, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+GARCH_t3$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
 
 ARCH_table <- read.csv("ARCH_table.csv")
-ARCH_table <- rename(ARCH_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-ARCH_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+ARCH_table <- rename(ARCH_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+ARCH_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
 
 Copula5_table <- read.csv("Copula5_table.csv")
-Copula5_table <- rename(Copula5_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-Copula5_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+Copula5_table <- rename(Copula5_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+Copula5_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
 
 Copula3_table <- read.csv("Copula3_table.csv")
-Copula3_table <- rename(Copula3_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-Copula3_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+Copula3_table <- rename(Copula3_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+Copula3_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
 
 Copula0_table <- read.csv("Copula0_table.csv")
-Copula0_table <- rename(Copula0_table, "In-sample optimizers" = Row, "FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-Copula0_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+Copula0_table <- rename(Copula0_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+Copula0_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
 
@@
     CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
-    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
-    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
-    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
-    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
+    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
+    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
+    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
+    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
   ) %>%
@@
 (2020).
-It simply means that we can improve prediction accuracy by using FSR in the presence of model misspecification under certain conditions.
+It simply means that we can improve prediction accuracy by using CLS in the presence of model misspecification under certain conditions.
 That is, we expect to gain more from optimal forecasts while the degree of model misspecification is high.
@@
 The predictive accuracy of tails is important for financial risk management.
-Therefore, we provide score trace plots to exhibit the comparison of MLE, CRPS and FSR’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails.
-The results in Section 3.2.1 shows that when the degree of model misspecification is high, FSR can perform the best compared with MLE and CRPS in predicting tails.
+Therefore, we provide score trace plots to exhibit the comparison of MLE, CRPS and CLS’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails.
+The results in Section 3.2.1 shows that when the degree of model misspecification is high, CLS can perform the best compared with MLE and CRPS in predicting tails.
 However, only the average score values at the end of each iteration of the simulation are recorded in the tables, while trace plots provide a dynamic view of how optimal forecasts perform.
 
-In the left panel of each trace plot, it shows the performance of each score evaluated by FSR 10%.
+In the left panel of each trace plot, it shows the performance of each score evaluated by CLS 10%.
 That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B.
 The right panel shows the same thing but is based on performance of predicting 90 percentile.
-From Figure 1 and 2, we could see that FSR almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, FSR starts to outperform CRPS and MLE in predicting tails.
-The more misspecified the model is, the more benefits can we gain from using FSR.
+From Figure 1 and 2, we could see that CLS almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, CLS starts to outperform CRPS and MLE in predicting tails.
+The more misspecified the model is, the more benefits can we gain from using CLS.
 It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.
@@
 More importantly, it is misspecified with a high degree of model misspecification.
-Therefore, based on the results shown in Section 3, we should expect that predictions produced by optimizing FSR do a better job in predicting two tails of the distribution.
+Therefore, based on the results shown in Section 3, we should expect that predictions produced by optimizing CLS do a better job in predicting two tails of the distribution.
 The results of Table 8 support our conjecture.
-However, the difference between using FSR10(80) and FSR20(90) is very small.
+However, the difference between using CLS10(80) and CLS20(90) is very small.
 
@@
 sp_table <- read.csv("sp_table.csv")
-sp_table <- rename(sp_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-sp_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+sp_table <- rename(sp_table, "In-sample optimizers" = Row,"CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+sp_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
 
@@
 # to compress all the calculated plotting average scores together in the same df 
+# this is assessed by cls10 for prediction accuracy
 trace_fsr10 <- read.csv("fsr10.csv")
+trace_fsr10 <- trace_fsr10 %>% rename("CLS10"=FSR10)
 trace_fsr20 <- read.csv("fsr20.csv")
+trace_fsr20 <- trace_fsr20 %>% rename("CLS20"=FSR20)
 trace_10ls <- read.csv("fsr10_ls.csv")
@@
 
-color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple","CRPS"="green")
+color1 <- c("CLS10"="red","CLS20"="black","MLE"="purple","CRPS"="green")
 
 fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
-  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
-  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
+  geom_line(aes(y = CLS10,color = "CLS10"),size=0.25)+
+  geom_line(aes(y = CLS20,color = "CLS20"),size=0.25)+
   geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
@@
 trace_fsr90 <- read.csv("fsr90.csv")
+trace_fsr90 <- trace_fsr90 %>% rename("CLS90"=FSR90)
 trace_fsr80 <- read.csv("fsr80.csv")
+trace_fsr80 <- trace_fsr80 %>% rename("CLS80"=FSR80)
 trace_90ls <- read.csv("fsr90_ls.csv")
@@
 
-color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple","CRPS"="green")
+color2 <- c("CLS90"="red","CLS80"="black","MLE"="purple","CRPS"="green")
 
 fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
-  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
-  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
+  geom_line(aes(y = CLS90,color = "CLS90"),size=0.25)+
+  geom_line(aes(y = CLS80,color = "CLS80"),size=0.25)+
   geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
@@
 
-We illustrate how optimal forecasts perform in estimating VaR by using predictions produced in simulation (Section 3) first, and expect that optimal forecasts based on FSR would give us a better prediction in tails.
+We illustrate how optimal forecasts perform in estimating VaR by using predictions produced in simulation (Section 3) first, and expect that optimal forecasts based on CLS would give us a better prediction in tails.
 Specifically, VaR predictions at \{10%, 20%, 80%, 90%\} are conducted, since they correspond to the 10% and 20% expected loss of long and short portfolios.
@@
 
-- $S_i= \{LS, CRPS, FSR10, FSR20, FSR80, FSR90\}$;
+- $S_i= \{LS, CRPS, CLS10, CLS20, CLS80, CLS90\}$;
 
@@
 
-Optimizers <- c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+Optimizers <- c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
 
@@
 Section 5.4.1 provides the result of Specification 1 where the predictive density of the VIX is normal distribution with a constant variance.
-In Table 14, FSR performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
-The score trace plot, Figure 7, shows the predictions of optimizing four scoring rules evaluated by FSR10 (left panel) and FSR90 (right panel).
+In Table 14, CLS performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
+The score trace plot, Figure 7, shows the predictions of optimizing four scoring rules evaluated by CLS10 (left panel) and CLS90 (right panel).
 It indicates how accurate these predictions are, according to their performance in 10 percentile and 90 percentile.
-In the lower tail, it seems that there is not much difference among four predictions, but zooming in, we can see that FSR is at the top of other scores, which means it can still provide the most accurate prediction.
+In the lower tail, it seems that there is not much difference among four predictions, but zooming in, we can see that CLS is at the top of other scores, which means it can still provide the most accurate prediction.
 However, we only gain very little from using it.
-On the contrary, in the upper tail, FSR has a much bigger effect on improving accuracy after the GFC and this effect continues.
-One possible explanation could be that both LS and CRPS can predict the lower tail better if there is higher probability mass at that area, then the benefit of using FSR is not significant.
+On the contrary, in the upper tail, CLS has a much bigger effect on improving accuracy after the GFC and this effect continues.
+One possible explanation could be that both LS and CRPS can predict the lower tail better if there is higher probability mass at that area, then the benefit of using CLS is not significant.
 Considering the marginal distribution shown in Figure 6.B of $log(VIX_t)$, we observe much more observations in the lower end than in the upper end so that it might be the reason why we observe the little improvement in predicting the lower tail in Figure 7(a).
@@
 vix_table <- read.csv("vix_table.csv")
-vix_table <- rename(vix_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-vix_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+vix_table <- rename(vix_table, "In-sample optimizers" = Row,"CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+vix_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
 
@@
 # to compress all the calculated plotting average scores together in the same df 
+# this the accuracy assessed by fsr10
 trace_fsr10 <- read.csv("vixfsr10.csv")
+trace_fsr10 <- trace_fsr10 %>% rename("CLS10"=FSR10)
 trace_fsr20 <- read.csv("vixfsr20.csv")
+trace_fsr20 <- trace_fsr20 %>% rename("CLS20"=FSR20)
 trace_10ls <- read.csv("vixfsr10_ls.csv")
@@
 
-# plot scores --- upper tail 
+# plot scores --- upper tail (assessed by fsr90)
 trace_fsr90 <- read.csv("vixfsr90.csv")
+trace_fsr90 <- trace_fsr90 %>% rename("CLS90"=FSR90)
 trace_fsr80 <- read.csv("vixfsr80.csv")
+trace_fsr80 <- trace_fsr80 %>% rename("CLS80"=FSR80)
 trace_90ls <- read.csv("vixfsr90_ls.csv")
@@
 Table 15 and Figure 8 show consistent performance of optimal forecasts compared with our investigations of simulated data and S&P 500 returns.
-That is, improvement of prediction accuracy by using FSR is still observed in the upper tail but the amount of improvement decreases as the degree of misspecification decreases.
+That is, improvement of prediction accuracy by using CLS is still observed in the upper tail but the amount of improvement decreases as the degree of misspecification decreases.
 
@@
 vix_table <- read.csv("vix_table_st.csv")
-vix_table <- rename(vix_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-vix_table$`In-sample optimizers`<-c("LS","FSR10","FSR20","FSR80","FSR90")
+vix_table <- rename(vix_table, "In-sample optimizers" = Row,"CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+vix_table$`In-sample optimizers`<-c("LS","CLS10","CLS20","CLS80","CLS90")
 
@@
     #CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
-    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
-    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
-    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
-    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
+    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
+    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
+    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
+    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
   ) %>%
@@
 trace_fsr10 <- read.csv("vixfsr10_st.csv")
+trace_fsr10 <- trace_fsr10 %>% rename("CLS10"=FSR10)
 trace_fsr20 <- read.csv("vixfsr20_st.csv")
+trace_fsr20 <- trace_fsr20 %>% rename("CLS20"=FSR20)
 trace_10ls <- read.csv("vixfsr10_ls_st.csv")
@@
 
-color1 <- c("FSR10"="red","FSR20"="black","MLE"="purple")
+color1 <- c("CLS10"="red","CLS20"="black","MLE"="purple")
 
 fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
-  geom_line(aes(y = FSR10,color = "FSR10"),size=0.25)+
-  geom_line(aes(y = FSR20,color = "FSR20"),size=0.25)+
+  geom_line(aes(y = CLS10,color = "CLS10"),size=0.25)+
+  geom_line(aes(y = CLS20,color = "CLS20"),size=0.25)+
   geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
@@
 trace_fsr90 <- read.csv("vixfsr90_st.csv")
+trace_fsr90 <- trace_fsr90 %>% rename("CLS90"=FSR90)
 trace_fsr80 <- read.csv("vixfsr80_st.csv")
+trace_fsr80 <- trace_fsr80 %>% rename("CLS80"=FSR80)
 trace_90ls <- read.csv("vixfsr90_ls_st.csv")
@@
 
-color2 <- c("FSR90"="red","FSR80"="black","MLE"="purple")
+color2 <- c("CLS90"="red","CLS80"="black","MLE"="purple")
 
 fsr90plot <- fsr90 %>% ggplot(aes(x=Date)) +
-  geom_line(aes(y = FSR90,color = "FSR90"),size=0.25)+
-  geom_line(aes(y = FSR80,color = "FSR80"),size=0.25)+
+  geom_line(aes(y = CLS90,color = "CLS90"),size=0.25)+
+  geom_line(aes(y = CLS80,color = "CLS80"),size=0.25)+
   geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
@@
 vix_table <- read.csv("vix_table_garch.csv")
-vix_table <- rename(vix_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-vix_table$`In-sample optimizers`<-c("LS","CRPS","FSR10","FSR20","FSR80","FSR90")
+vix_table <- rename(vix_table, "In-sample optimizers" = Row,"CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+vix_table$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
 
@@
 trace_fsr10 <- read.csv("vixfsr10_garch.csv")
+trace_fsr10 <- trace_fsr10 %>% rename("CLS10"=FSR10)
 trace_fsr20 <- read.csv("vixfsr20_garch.csv")
+trace_fsr20 <- trace_fsr20 %>% rename("CLS20"=FSR20)
 trace_10ls <- read.csv("vixfsr10_ls_gar.csv")
@@
 trace_fsr90 <- read.csv("vixfsr90_gar.csv")
+trace_fsr90 <- trace_fsr90 %>% rename("CLS90"=FSR90)
 trace_fsr80 <- read.csv("vixfsr80_gar.csv")
+trace_fsr80 <- trace_fsr80 %>% rename("CLS80"=FSR80)
 trace_90ls <- read.csv("vixfsr90_ls_gar.csv")
@@
 vix_table <- read.csv("vix_table_gst.csv")
-vix_table <- rename(vix_table, "In-sample optimizers" = Row,"FSR10" = FSR10, "FSR20"=FSR20, "FSR80"=FSR80,"FSR90"=FSR90)
-vix_table$`In-sample optimizers`<-c("LS","FSR10","FSR20","FSR80","FSR90")
+vix_table <- rename(vix_table, "In-sample optimizers" = Row,"CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+vix_table$`In-sample optimizers`<-c("LS","CLS10","CLS20","CLS80","CLS90")
 
@@
 trace_fsr10 <- read.csv("vixfsr10_gst.csv")
+trace_fsr10 <- trace_fsr10 %>% rename("CLS10"=FSR10)
 trace_fsr20 <- read.csv("vixfsr20_gst.csv")
+trace_fsr20 <- trace_fsr20 %>% rename("CLS20"=FSR20)
 trace_10ls <- read.csv("vixfsr10_ls_gst.csv")
@@
 trace_fsr90 <- read.csv("vixfsr90_gst.csv")
+trace_fsr90 <- trace_fsr90 %>% rename("CLS90"=FSR90)
 trace_fsr80 <- read.csv("vixfsr80_gst.csv")
+trace_fsr80 <- trace_fsr80 %>% rename("CLS80"=FSR80)
 trace_90ls <- read.csv("vixfsr90_ls_gst.csv")
@@
 
-One possible conjecture is that there are more observations in the lower tail of the VIX so that MLE or CRPS can still perform well and thus, less benefits are gained by using FSR.
+One possible conjecture is that there are more observations in the lower tail of the VIX so that MLE or CRPS can still perform well and thus, less benefits are gained by using CLS.
 However, it is impossible to know what the shape of the true conditional predictive distribution looks like, but due to the connection between marginal density and conditional density, this might be a reasonable conjecture to make.

### 2020-09-24 Final.Rmd
fixed problems in Ruben's comments.

@@
   - \usepackage[hyphens]{url}
+  - \usepackage{boondox-cal}
 fontsize: 12pt
@@
 
-This paper conducts numerical and empirical analyses to explore the impact of the form and degree of model misspecification on optimal probabilistic forecasting method which is recently proposed to conduct a forecast using scoring rules instead of the conventional likelihood function in the frequentist econometrics.
-In particular, the role of optimal forecasts in predicting S&P 500 returns, the Value-at-Risk and the VIX Volatility Index.
-We find that the performance of optimal probabilistic forecasts is insensitive to the form of misspecification but improves as the degree of misspecification increases.
-After the Global financial crisis, predictions that are optimal according to the focused scoring rule that rewards predictive accuracy in a tail are substantially more accurate at predicting observations in said tail than the alternatives, including likelihood-based predictions.
+With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification.
+Building off previous research, this paper conducts numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score.
+In particular, we assess the predictive performance of optimal forecasts in two empirical contexts: prediction of the Value-at-Risk and prediction of the VIX Volatility Index.
+Results show that the greater the degree of model misspecification, the more beneficial is optimal prediction, no matter which form of model misspecification is.
+Predictions that are optimal according to the censored likelihood score that rewards predictive accuracy in a tail are substantially more accurate at predicting extreme events in said tail than the alternatives, including likelihood-based predictions.
 
@@
 
-This paper explores the question: ‘When do optimal probabilistic forecasts work’, with particular attention given to the usefulness of optimal probabilistic forecasts in financial applications.
+This paper explores the question: ‘When do optimal probabilistic forecasts work’, with particular attention given to the usefulness of optimal forecasts in financial applications.
 
 Probabilistic forecasts can provide complete information about future uncertainty, which can be more valuable than point and interval forecasts to forecasters.
-However, previous approaches to prediction - including probabilistic methods - typically assume that the predictive model correctly specifies the process that has generated the observations.
-In practice, the assumed model underpinning the likelihood function will almost certainly differ from the unknown true data generating process (DGP).
-This model misspecification problem has been an ongoing issue for conventional likelihood-based prediction.
-
-As an alternative to likelihood-based prediction, scoring rules have been proposed as a means of producing probabilistic forecasts.
-A variety of alternative proper scoring rules allows users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand (Gneiting & Raftery, 2007).
-Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.
-(2020).
-Among all these investigations, it is the censored likelihood score (CLS) proposed originally by Diks, Panchenko & van Dijk (2011), that captures our attention, since its ‘focusing’ feature has great potential in financial risk management.
-In other words, CLS allows a forecaster to focus on predicting any particular region of interest more accurately and, therefore, is expected to make an important contribution to risk prediction in financial settings.
-
-The ‘optimal’ probabilistic forecast has been discussed in Loaiza-Maya et al.
-(2020).
-It refers to a predictive probability distribution that is optimal according to a user-specified scoring rule.
-Whilst some empirical investigations were undertaken, these were primarily illustrative, with there being much scope left for exploring the performance of optimal methods in forecasting different types of financial measures, and under different assumed models.
-
-This research paper extends the work of Loaiza-Maya et al.
-(2020) by investigating the effect of the form and degree of model misspecification on optimal forecast performance in particular financial settings; in particular by conducting an empirical analysis of how optimal forecasts perform in Value-at-Risk (VaR), Volatility Index (VIX) and portfolio optimization applications.
+However, previous approaches to prediction - including probabilistic methods – typically assume that the predictive model or the likelihood function correctly specifies the true data generating process (DGP) or the true DGP lies in the model pools, which is almost certainly untrue in practice.
+Optimal probabilistic forecasting refers to the construction of a predictive probability distribution that is optimal according to a user-specified proper scoring rule [@optimal].
+It is not constructed based on the conventional likelihood function but on a proper scoring rule that matches the specific problem at hand.
+Optimal probabilistic forecasts aim to improve the predictive accuracy of a misspecified model, whilst the conventional approaches to probabilistic forecasting focus on the development of increasingly less misspecified models that can potentially yield better probabilistic forecasts.
+
+A variety of proper scoring rules allows users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand [@gneiting2007].
+Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see @opschoor2017, @fbp2019 and @optimal.
+Among all these investigations, it is the censored likelihood score (CLS) proposed originally by @diks2011, that captures our attention for the purpose of demonstrating the application of optimal probabilistic forecasts in finance.
+Its ‘focusing’ feature has great potential in financial risk management.
+In other words, CLS allows a forecaster to focus on predicting any particular region of interest more accurately.
+Therefore, its usage in this context represents an important contribution to risk prediction in financial settings.
+
+Whilst some empirical investigations about the performance of optimal forecasts were undertaken in @optimal, these were primarily illustrative, and left much scope for exploring the performance of optimal probabilistic forecasting methods in forecasting different types of financial measures, and under different assumed models.
+
+This research paper extends the work of @optimal by investigating the effect of the form and degree of model misspecification on the performance of optimal probabilistic forecasts in financial settings; in particular by conducting empirical analyses of how optimal forecasts perform in predicting the Value-at-Risk (VaR) and the VIX Volatility Index (VIX).
 Importantly, the empirical dataset used extends over a period of time that precedes the 2008 global financial crisis (GFC) and that includes the latest period in which COVID-19 has had an impact on financial markets.
@@
 
-Optimal probabilistic forecasts discussed in this paper refer to the forecasts produced from a model that is ‘optimized’ based on a user-specified proper scoring rule will perform the best out-of-sample – according to that same score (Loaiza-Maya et al.,2020).
-
 Scoring rules are a type of criterion function that can be optimized to produce an optimal estimator and thus, a probabilistic prediction derived from this optimal estimator and an assumed model.
 They also play the role of encouraging forecasters to make careful and honest assessments in elicitation of subjectivist Bayesians, and evaluating and ranking competitive probabilistic forecasts, based on the predictive distribution and materialized events or values, by assigning a numerical score [@waite2005; @gneiting2007].
-Therefore, the crucial importance of the propriety of scoring rules must be emphasized for their usage because improper scoring rules will assign a higher average score to an incorrect density forecast (Gneiting & Raftery, 2007).
+Therefore, the crucial importance of the propriety of scoring rules must be emphasized for their usage because improper scoring rules will assign a higher average score to an incorrect density forecast [@gneiting2007].
 Consequently, forecasts based on improper scoring rules will not be ‘optimal’.
@@
 S(P,Q) denotes the expected value of S(P,$\cdot$) under Q.
-A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q (Gneiting & Raftery, 2007).
-
-In terms of producing probabilistic forecasts, scoring rules can replace the conventional likelihood function in frequentist and Bayesian predictions; see Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.
-(2020).
-Supposing the scoring rule is positively oriented, an estimator $\hat \theta_n$ obtained by maximizing a scoring rule $S_n(\theta)$ is said to be 'optimal' based on this scoring rule.
+A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q [@gneiting2007].
+
+In terms of producing probabilistic forecasts, scoring rules can replace the conventional likelihood function in frequentist and Bayesian predictions; see @fbp2019 and @optimal.
+Supposing the scoring rule is positively oriented, then an estimator $\hat \theta$ obtained by maximizing a scoring rule $S(\theta)$ is said to be 'optimal' based on this scoring rule.
 \begin{equation} \label{eq:1}
-\hat \theta_n=arg \max_\theta S_n(\theta)
-\end{equation}
-Under certain conditions, including that the scoring rule is 'proper', $\hat \theta_n \to \theta_0 \ as \ T \to \infty$,
-where $\theta_0$ is the true parameter and T is the total sample size of a time series variable $y_t$.
-The predictions conditional on this optimal estimator, $p(y_{T+1}|M,\hat \theta_n,y_{1:T})$, is said to be produced from a model that is 'optimized' according to a proper scoring rule.
+\hat \theta =arg \max_\theta S(\theta)
+\end{equation}
+Under certain conditions, including that the scoring rule is 'proper', $\hat \theta \to \theta_0 \ as \ \mathcal{T} \to \infty$,
+where $\theta_0$ is the true parameter value and $\mathcal{T}$ is the total sample size of a time series variable $y_t$.
+The predictive distribution based on this optimal estimator, $p(y_{T+1}|M,\hat \theta,y_{1:T})$, has been produced from the assumed model by optimizing a proper scoring rule.
 ^[M refers to the assumed model and it is omitted in the following notation for simplicity, since the assumed model does not change.]
 
-In addition, in terms of evaluating predictions, it is usually the average score ($\bar S_n$) that is used to directly compare predictive accuracy among predictions produced by optimizing different scoring rules (Gneiting & Reftery, 2007).
+In addition, in terms of evaluating predictions, scoring rules assign numerical values to density forecasts, addressing both sharpness and calibration simultaneously.
+It is usually the average score ($\bar S$) that is used to directly compare predictive accuracy among predictions produced by optimizing different scoring rules [@gneiting2007].
 \begin{equation} \label{eq:sbar}
-\bar S_n = \frac{1}{T}\sum_{t=1}^TS_n(p_{t+1},y_t)
-\end{equation}
-For a positively oriented score, for example, a higher value will be assigned to a better forecast between two competing candidates, on the condition the scoring rule being proper.
+\bar S = \frac{1}{T}\sum_{t=1}^T S(p_{t+1},y_t)
+\end{equation}
+For a positively oriented score, for example, a higher value will be assigned to a better forecast between two competing candidates, on the condition of the scoring rule being proper.
 
 ## 2.2 Some commonly used scoring rules
+
 A variety of scoring rules have been developed to tackle different problems.
@@
 \end{equation}
-It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters (Bickel, 2007).
+It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters [@bickel2007].
 One common usage of the logarithmic score in frequentist econometrics is the maximum likelihood estimation (MLE).
 \begin{equation} \label{eq:mle}
-\hat \theta_{MLE}=arg \max_\theta \{log[p(\boldsymbol y|\theta)]\}
-\end{equation}
-It is included as a benchmark in the following numerical and empirical investigations of the performance of optimal forecasts due to its asymptotically optimal and efficient characteristics under the correctly specified log-likelihood function.
+\hat \theta_{MLE}=arg \max_\theta \{log[p_{t-1}(y_t|\theta)]\}
+\end{equation}
+It provides an asymptotically optimal and efficient estimation under the correctly specified log-likelihood function and regularity.
 
 However, the logarithmic score is criticized for its unboundedness and its local property.
-Bernardo (1979) states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state".
-Gneiting & Raftery (2007) also argue that the logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event.
-Gneiting & Raftery (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in $\eqref{eq:crps}$
+@bernardo1979 states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state".
+@gneiting2007 also argue that the logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event.
+@gneiting2007 propose the continuously ranked probability score, which is sensitive to distance and is defined as in $\eqref{eq:crps}$
 \begin{equation} \label{eq:crps}
-CRPS(P_{t-1},x_t)=-\int_{-\infty}^{\infty}[P(y)-I(y\geq x_t)]^2dy
-\end{equation}
-where P is the cumulative distribution function, *I* is the indicator function, and x is the materialized event.
-
-The formula can be simplified to $\eqref{eq:crnorm}$ if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
+CRPS(P_{t-1},x_t)=-\int_{-\infty}^{\infty}[P_{t-1}(y)-I(y\geq x_t)]^2dy
+\end{equation}
+where $\mathcal{P}$ is the cumulative distribution function, *I* is the indicator function, and $x_t$ is the materialized event.
+
+The formula can be simplified to $\eqref{eq:crnorm}$ if the prediction distribution is Gaussian with mean $\mu$ and variance $\sigma^2$.
 \begin{equation} \label{eq:crnorm}
@@
 \end{equation}
-where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the Gaussian predictive distribution.
-
-Both LS and CRPS are used for producing and evaluating the entire predictive densities.
-In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011).
-Diks, Panchenko & van Dijk, (2011) propose the censored likelihood score, which allows users to assess forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast.
+where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the standard Gaussian distribution.
+
+Both LS and CRPS are used for producing predictive densities and evaluating the out-of-sample predictive performance.
+In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood [@gneiting2011].
+@diks2011 propose the censored likelihood score, which allows users to assess forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast.
 Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy.
@@
 where $p_t$ is the predictive probability density function, $A_t$ is the region of interest and $A_t^c$ is the complement of $A_t$.
-Opschoor, van Dijk & van der Wel (2017) prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.
+@opschoor2017 prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.
 
@@
 
-The degree of model misspecification impacts the performance of optimal forecasts.
-The greater the degree of misspecification is, the more benefits are gained from optimal forecasts in both Bayesian and frequentist predictions, conditional on the assumed predictive model being compatible; see [@fbp2019], [@optimal].
+Optimal forecasts can outperform predictions produced by conventional methods out of sample; see @opschoor2017, @fbp2019 abd @optimal; but the underlying reasons driving this phenomenon are still under investigation.
+Recent research show that the degree of model misspecification impacts the performance of optimal forecasts.
+The greater the degree of misspecification is, the more benefits are gained from optimal forecasts in both Bayesian and frequentist predictions, conditional on the assumed predictive model being compatible; see [@fbp2019] and [@optimal].
 The simulation analysis in this paper will extend the exploration in this field and ask the question ‘Will the performance of optimal forecasts change when a different form of misspecification occurs?’.
 
-In order to set the scene for the financial application analyses in following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and volatility.
-Specific simulation scenarios are listed in the following table ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).
-
-\begin{table}[!h]
+In order to set the scene for the financial application analyses in following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and their volatility.
+Specific simulation scenarios are listed in Table 1 ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).
+
+\begin{table}[!ht]
 \centering
-\begin{tabular}{|c|c|c|}
+\resizebox{\textwidth}{!}{
+\begin{tabular}{|c|c|c|c|}
 \hline
-\multicolumn{3}{|c|}{\textbf{Simulation design}} \\ \hline
-          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
-\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & Stochastic volatility inversion copula \\
-& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline
-
-\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$\\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$\\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$\\ \hline
-\end{tabular}
+\multicolumn{4}{|c|}{\textbf{Table 1: Simulation design}} \\ \hline
+          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} & \textbf{Scenario (iii)} \\ \hline
+\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & $y_t = \sigma_t \epsilon_t$ & Stochastic volatility inversion copula \\
+& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = \{0, -3, -5\} \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & & $\nu \in \{3,12\}$ & \\ \hline
+
+\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ \\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ \\ \hline
+\end{tabular}}
+\caption{It shows three simulation scenarios conducted in the numerical analysis sections where Scenario (i) shows the correct model specification, Scenario (ii) shows that the true DGP is GARCH with Student-t distribution while the assumed model creates normal distribution, and Scenario (iii) creates an asymmetric true DGP, while the assumed model can only produces symmetric predictive distribution.}
 \end{table}
@@
 
-Copulas “reweight” the marginal densities to produce a joint density that captures the dependence among random variables, which can be applied to conditional distributions for forecasting purposes as shown in $\eqref{eq:copula}$.
+Copula models are a flexible approach to represent the joint distribution function of a set of variables [@fan2014].
+In recent years, these models have been applied for modelling of serial dependence as shown in $\eqref{eq:copula}$ [@inversion2018].
 \begin{equation} \label{eq:copula}
-H_t(x,y|\mathcal{F}_{t-1})=C_t(F_t(x|\mathcal{F}_{t-1}),G_t(y|\mathcal{F}_{t-1})|\mathcal{F}_{t-1})
-\end{equation}
-where $X_t$ and $Y_t$ are random variables with conditional marginal densities denoted by $F_t$ and $G_t$, $\mathcal{F}_t$ is an information set available at time t, and $H_t$ denotes the conditional joint distribution of $X_t$ and $Y_t$ [@fan2014].
-
-The stochastic volatility inversion copula model used in this section allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns but is not allowed if we use state space models alone [@inversion2018].
-
-In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP in Scenario (i) and (ii).
-
-Optimal forecasts can outperform predictions produced by conventional methods out of sample; see Opschoor, van Dijk & van der Wel (2017), Loaiza-Maya, Martin & Frazier (2019) and Loaiza-Maya et al.(2020); but the underlying reasons driving this phenomenon are still under investigation.
-Loaiza-Maya, Martin & Frazier (2019) propose a new method, focused Bayesian prediction (FBP), which replaces the conventional likelihood function with the censored likelihood score.
-In their simulated and empirical analysis, Focused Bayes outperforms exact Bayes which uses the logarithmic score for updating the prior probability and they also point out that model misspecification plays a role in the performance of Focused Bayes since focusing incorrectly can harm.
-
-Loaiza-Maya et al.(2020) extend the above discussion to frequentist probability forecasting.
-They address questions about when we can/cannot benefit from optimal probabilistic forecasts out of sample.
-Loaiza-Maya et al.(2020) introduce the concepts of ‘coherence’ and ‘strict coherence’ for conveniently documenting the optimal forecasts’ performance.
+p_{t-1}(y_t)=c(P(y_t),P(y_{t-1}))p(y_{t-1})
+\end{equation}
+where $\mathcal{P}()$ and $\mathcal{p}$ denote the marginal distribution and density function of $y_t$ respectively, and c() is the copula density function that captures the dependence between $y_t$ and $y_{t-1}$.
+
+For the simulation exercise, the marginal distribution $\mathcal{P}()$ is chosen to be the standard skew-normal distribution, while c() is chosen to be the inversion copula of the stochastic volatility model described in @inversion2018.
+The stochastic volatility inversion copula model used in this section allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns [@inversion2018].
+
+In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP specifications in Scenario (ii) and (iii).
+
+We apply the scoring rules introduced in Section 2.2 and set CLS to focus on 10%, 20%, 80% and 90% tails of the empirical marginal distribution, corresponding to the risks of long and short portfolios of financial investments, and we label them as CLS10, CLS20, CLS80 and CLS90 in following tables and figures.
+Due to the fact that there is no reliable estimate of the true conditional densities, only the tails of the marginal distributions are set to be the standard when assessing the predictive accuracy by CLS, rather than the conditional distributions.
+Meanwhile, MLE is included as a benchmark for comparing whether optimal forecasts can provide benefits or not, since MLE is asymptotically optimal and efficient under the correct model specification and regularity.
+Even though this property does not hold under misspecification, MLE can still give insights about how conventional likelihood-based methods perform.
+
+We conduct Monte Carlo simulations using the methodology in @optimal and @fbp2019. Specific steps are as follows:
+
+Let $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ be the one-step-ahead predictive distribution function based on the assumed model and optimized according to the scoring rule $S_i$, and $p(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$ be the corresponding predictive density function at time $\mathcal{t}$.
+
+  1.	Generate T = 6000 observations for $y_t$ from the true DGP
+
+  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}^{[i]}$ in the assumed predictive model based on the positively oriented score $S_i$ where $\boldsymbol{\hat \theta}^{[i]} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}^{[i]}$
+
+\begin{equation} \label{eq:theta}
+\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
+\end{equation}
+\begin{equation} \label{eq:score}
+\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S_i(P_{\boldsymbol\theta}^{t-1},y_t)
+\end{equation}
+  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:CLS}$:^[The CRPS in $\eqref{eq:CRPS}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]
+
+\begin{equation} \label{eq:LS}
+S_{LS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
+\end{equation}
+\begin{equation} \label{eq:CRPS}
+S_{CRPS}^*(P_{\boldsymbol\theta}^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
+\end{equation}
+\begin{equation} \label{eq:CLS}
+S_{CLS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
+\end{equation}
+4.
+Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores:^[Out-of-sample size $\tau = 5000$ is sufficiently large to let the optimal forecasts take place; see @optimal for full discussion about sample size effects on optimal forecasts.]
+\begin{equation} \label{eq:avgscore}
+\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
+\end{equation}
+
+For the purpose of conveniently documenting and interpreting the results in the following sections consistently with previous literature, we introduce the concept of ‘coherence’ and ‘strict coherence’ here.
 Coherence means that the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score.
 Strict coherence happens when the optimal prediction is strictly preferable given that score.
-Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules: $S_1$ and $S_2$.
+Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules:$S_1$ and $S_2$.
 The predictive density $S_n(P^{t-1}_{\boldsymbol{\hat \theta_n}},y_t)$ is said to be coherent if
@@
 \end{equation}
-It is said to be strictly coherent if $\eqref{eq:coh1}$ and $\eqref{eq:coh2}$ are strict inequalities.
-
-Building on the previous research in this field, we conduct a numerical analysis in this section to further investigate the effects of the form and degree of model misspecification on the performance of optimal forecasts.
-
-MLE is a frequently used estimation method in frequentist prediction.
-It often works with the log-likelihood, which corresponds to the logarithmic scoring rule.
-Therefore, we use the predictions produced by MLE (LS) as the benchmark of the following comparisons.
-Besdies, the tails of a density are important for risk management in finance so that we decide to apply the focused scoring rule to the 10%, 20%, 80% and 90% tails of the distribution, corresponding to the risks of long and short portfolios.
-Certain aspects of the methodology used in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) are adopted here.
-We conduct each simulation scenario as follows:
-
-Let $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ be the one-step-ahead prediction based on the assumed model, and $p(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$ ($P(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$) be the predictive probabilistic (cumulative probabilistic) distribution at time t.
-
-  1.	Generate T = 6000 observations for $y_t$ from the true DGP
-
-  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}$ in the assumed predictive model based on the positively oriented score $S_i$ where $\boldsymbol{\hat \theta} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}$
-
-\begin{equation} \label{eq:theta}
-\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
-\end{equation}
-\begin{equation} \label{eq:score}
-\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
-\end{equation}
-  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:CLS}$:^[The CRPS in $\eqref{eq:CRPS}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]
-
-\begin{equation} \label{eq:LS}
-S_{LS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
-\end{equation}
-\begin{equation} \label{eq:CRPS}
-S_{CRPS}^*(P_{\boldsymbol\theta}^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
-\end{equation}
-\begin{equation} \label{eq:CLS}
-S_{CLS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
-\end{equation}
-4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
-\begin{equation} \label{eq:avgscore}
-\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
-\end{equation}
+It is said to be strictly coherent if $\eqref{eq:coh1}$ and $\eqref{eq:coh2}$ are strict inequalities [@optimal].
 
@@
 The bolded numbers are the largest values of $\bar S_j(\boldsymbol{\hat \theta^{[i]}})$ in each column.
-We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the evaluating scoring rule indicated by the column name.
+We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the scoring rule indicated by the column name.
+
+Table 2 shows the correct model specification: Scenario (i) where the optimal forecasting method does not reap benefits and there is no strict coherence observed in the table.
+Under correct specification, both likelihood-based forecasts and optimal forecasts will have estimators concentrated to true parameter values, which causes no improvement in predictive accuracy by using optimal forecasting approach [@optimal].
+
+Table 3 shows the results of Scenario (ii) where the assumed predictive model, ARCH(1), cannot capture the fat tails and long term volatility clustering feature of the data generated from GARCH(1,1) models with Student-t error, i.e.
+the true DGP.
+Hence, there is misspecification.
+Table 3 replicates some parts of the simulation results in previous literature; see @fbp2019, @optimal.
+Optimal forecasts are expected to reap more benefits as the degree of model misspecification increases, and predictions based on CLS at 80% and 90% perform poorly when assessed by LS, CRPS, CLS at 10% and CLS at 20%.
+The question is whether these characteristics of optimal forecasts will change if we move to a different form of model misspecification.
+
+Table 4 shows another type of model misspecification listed in Scenario (iii) where the ARCH(1) model cannot capture the asymmetric feature of the data generated from copula models (the true DGP).
+Table 4 shows similar results as in Table 3.
+As the shape parameter decreases, the degree of negative marginal skewness increases, and optimal forecasts provide more benefits.
+Even though, strictly speaking, we do not observe strict coherence in Panel C, the most misspecified case, it is close enough to conclude that optimal forecasts perform in the same way even when we have different forms of model misspecification.
+^[Tables are produced by R package: @kableextra.]
 
@@
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 1: the true DGP is ARCH(1)"=7))
-```
-
-```{r}
-GARCH_t12 %>% 
+  add_header_above(c("Table 2: the true DGP is ARCH(1)"=7))
+```
+
+```{r}
+GARCH_t12 <- GARCH_t12 %>% 
   mutate(
@@
     `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
-  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 2: the true DGP is GARCH(1,1) with degree of freedom = 12"=7))
-```
-
-```{r}
-GARCH_t3 %>% 
+  )
+
+GARCH_t3 <- GARCH_t3 %>% 
   mutate(
@@
     `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
-  ) %>%
+  ) 
+garch <- rbind(GARCH_t12,GARCH_t3)
+
+garch %>%
   kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
+  kable_styling("bordered",full_width = F) %>%
+  pack_rows("Panel A: degree of freedom = 12", 1,6) %>%
+  pack_rows("Panel B: degree of freedom = 3", 7,12) %>%
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 3: the true DGP is GARCH(1,1) with degree of freedom = 3"=7))
-```
-
-```{r}
-
-Copula0_table %>% 
+  add_header_above(c("Table 3: the true DGP is GARCH(1,1) with Student-t error"=7))
+```
+
+```{r}
+Copula0_table <- Copula0_table %>% 
   mutate(
@@
     `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
-  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 4: the true DGP is copula with shape parameter = 0"=7))
-```
-
-```{r}
-Copula3_table %>% 
+  )
+
+Copula3_table <- Copula3_table %>% 
   mutate(
@@
     `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
-  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 5: the true DGP is copula with shape parameter = -3"=7))
-```
-
-```{r}
-Copula5_table %>% 
+  )
+
+Copula5_table <- Copula5_table %>% 
   mutate(
@@
     `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
-  ) %>%
+  )
+
+copula <- rbind(Copula0_table,Copula3_table,Copula5_table)
+copula %>% 
   kable("latex",escape = F, booktabs = T, linesep = "") %>%
-  kable_styling("bordered",full_width = F)%>%
+  kable_styling("bordered",full_width = F) %>%
+  pack_rows("Panel A: shape = 0", 1,6) %>%
+  pack_rows("Panel B: shape = -3", 7,12) %>%
+  pack_rows("Panel C: shape = -5", 13,18) %>%
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 6: the true DGP is copula with shape parameter = -5"=7))
-```
-
-The results from Table 1-3 show one particular type of model misspecification.
-That is, the assumed predictive model, ARCH(1), cannot capture the long term volatility clustering feature of the data generated from GARCH(1,1) models, i.e.
-the true DGP.
-Hence, there is misspecification.
-When the degrees of freedom parameter in the error term of GARCH(1,1) is large enough, the ARCH(1) model is correctly specified as shown in Table 1.
-As the degrees of freedom decreases, the degree of model misspecification increases.
-
-From Table 1, the correct specification case, we could observe coherence and strict coherence in Table 3 when the degree of model misspecification is high.
-These results are consistent with conclusions from Loiaza-Maya et al.
-(2020).
-It simply means that we can improve prediction accuracy by using CLS in the presence of model misspecification under certain conditions.
-That is, we expect to gain more from optimal forecasts while the degree of model misspecification is high.
-
-Table 4-6 show another type of model misspecification where 
-the ARCH(1) model cannot capture the asymmetric feature of the data generated from copula models (the true DGP).
-From Table 4-6, as the shape parameter decreases, the degree of negative marginal skewness increases, and thus the degrees of model misspecification increases.
-The results give similar conclusions to Table 1-3.
-It proves that optimal forecasts perform in the same way even when we have different types of model misspecification.
-
-### 3.2.2 Trace plots
+  add_header_above(c("Table 4: the true DGP is stochastic volatility inversion copula"=7))
+```
+
+### 3.2.2 Trace plots & predictive density
 
@@
 Therefore, we provide score trace plots to exhibit the comparison of MLE, CRPS and CLS’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails.
-The results in Section 3.2.1 shows that when the degree of model misspecification is high, CLS can perform the best compared with MLE and CRPS in predicting tails.
+The results in Section 3.2.1 shows that when the degree of model misspecification is high, CLS can perform the best compared with MLE and CRPS in predicting both tails.
 However, only the average score values at the end of each iteration of the simulation are recorded in the tables, while trace plots provide a dynamic view of how optimal forecasts perform.
@@
 That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B.
-The right panel shows the same thing but is based on performance of predicting 90 percentile.
-From Figure 1 and 2, we could see that CLS almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, CLS starts to outperform CRPS and MLE in predicting tails.
+The right panel shows the same thing but is based on the performance of predicting 90 percentile.
+From panels (a) and (b) in Figures 1 and 2, we could see that CLS almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, CLS starts to outperform CRPS and MLE in predicting tails.
 The more misspecified the model is, the more benefits can we gain from using CLS.
+Besides, more improvement of predictive accuracy in the upper tail than in the lower tail, especially in Figure 2 where we have a negative skewed marginal distribution.
+This result is consistent with @fbp2019.
 It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.
@@
 
+From the average out-of-sample score tables and trace plots above, we can see that optimal forecasts provide most benefits in improving prediction accuracy under the most misspecified case.
+In order to provide a more complete view of how optimal forecasts work, the predictive densities of the most misspecified case are plotted in Figure 3.
+The shape of true conditional predictive distributions plays a role in deciding how much we can gain by using optimal forecasts, since predictions obtained from optimizing CLS aim to match the shape of tails of the true conditional predictive distributions.
+And CLS focusing on upper tails (80%, 90%) is expected to perform poorly in the lower tail so the forecasters should have a clear expectation about what they aim to achieve [@fbp2019].
+However, in practice, the shape of true conditional predictive distributions is usually unknown and it might create the difficulty of determining which tail we can reap more benefits from optimal forecasts without analysing a particular problem beforehand.
+
 ```{r,fig.align="center"}
@@
 
-Moreover, the predictive density plots show that predictions obtained from optimizing the focused score aim to match the shape of tails of the true conditional predictive distributions.
-It indicates that the shape of the true conditional predictive distributions plays a role in deciding how much we can gain by using optimal forecasts.
-One must note that in practice, the shape of the true DGP is unknown, but it still is a vital reason why the performance of optimal forecasts varies.^[The predictive density plots in Appendix 1 show the changes of optimal forecasts over time/iterations.]
-
 # 4. Empirical analysis: financial returns 
@@
 
-From the results in Section 3.2, we can conclude that optimal forecasts based on the focused score can improve the prediction accuracy in tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification.
+From the results in Section 3.2, we can conclude that optimal forecasts based on the censored likelihood score can improve the prediction accuracy in tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification.
 In Section 4, we apply the same method adopted in Section 3 to an empirical setting and investigate how it performs in practice.
 
-The data used in the analysis is the continuously compounded daily log returns of S&P 500 listed in U.S.A financial market over a broad time period from 27 Sep,1996 to 30 July,2020.
-It aims to include two very volatile periods, the GFC and the recent COVID-19 pandemic.
+The data used in the analysis is the continuously compounded daily log returns of S&P 500 listed in U.S.A financial market over a broad time period from 27 Sep,1996 to 30 July,2020.^[Data retrieved from @spdata] It aims to include two very volatile periods, the GFC and the recent COVID-19 pandemic.
 The initial training sample size and out-of-sample observations are kept consistent with what is in Section 3 with initial training sample size = 1000 and out-of-sample evaluations = 5000.
+
+The descriptive statistics show that the distribution of S&P 500 log returns is negatively skewed and has fat tails and strong serial correlation in its volatility.
+Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.
 
@@
   kable_styling("bordered",font_size = 10) %>% 
-  add_header_above(c("Table 7: Descriptive statistics"=9))
+  add_header_above(c("Table 5: Descriptive statistics"=9))
 ```
@@
 
-The descriptive statistics show that the distribution of S&P 500 log returns is negatively skewed and has fat tails and strong serial correlation in its volatility.
-Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.
-
 ## 4.2 Empirical results: predictive distributions for returns
 
-We still use ARCH(1) model in Section 3 as the assumed predictive model since it is a reasonable model to predict stock returns and volatility.
-More importantly, it is misspecified with a high degree of model misspecification.
-Therefore, based on the results shown in Section 3, we should expect that predictions produced by optimizing CLS do a better job in predicting two tails of the distribution.
-The results of Table 8 support our conjecture.
+From the wide-usage of ARCH models in modelling financial returns and volatility, and the strict coherence observed in Section 3.2.1, ARCH(1) should be a ‘compatible’ and sufficiently misspecified model to forecast S&P 500 series.
+The results in Table 8 show that the CLS outperforms other alternative scores in both lower and upper tails, which closely follows the results and conclusions drawn in the numerical analysis in Section 3.
 However, the difference between using CLS10(80) and CLS20(90) is very small.
@@
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 8: Average scores for S&P 500"=7))
+  add_header_above(c("Table 6: Average scores for S&P 500"=7))
 ```
@@
 Unlike in the simulation example, the score trace plots now show how different scoring rules perform at time points that correspond to some actual historical events.
-In Figure 5, one interesting phenomenon is that after the GFC, the focused score performs much better than CRPS and MLE compared with before, in terms of predicting both upper and lower tails.
-And this 'jump' effect continues until the very recent date.
-It indicates that optimal probabilistic forecasts might predict financial markets better in and after times of stock market turbulence, which could represent a great contribution to the existing financial analyses of risks and returns.
+In Figure 5, one interesting phenomenon is that after the GFC, the censored likelihood score performs much better than CRPS and MLE, in terms of predicting both upper and lower tails.
+It indicates that optimal probabilistic forecasts based on CLS can predict extreme events, such as the GFC, more accurately than other alternatives.
+This improvement brings up the average score of CLS optimizer after the GFC as shown in Figure 5.
+The difference between CLS and MLE/CRPS gets smaller and smaller over time until the recent COVID-19 pandemic.
+It is also worth noticing that CLS does not appear to provide more benefits in the upper tail than in the lower tail, which is different from the simulation results.
 
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 5(a) 10 percentile","Figure 5(b) 90 percentile"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 5(a) CLS10","Figure 5(b) CLS90")) + 
+  labs(caption = "Figure 5: the predictive distributions of S&P 500 are produced by the ARCH(1)") +
+  theme(plot.caption = element_text(hjust = 0))
 
@@
 It can be obtained from a probability density function of returns over a chosen investment horizon.
-It is the p-quantile ($q_p$) of a predictive distribution of a portfolio’s profit/loss over a holding period, according to a given confidence interval $\alpha$ (Dowd, 2005).
+It is the p-quantile ($q_p$) of a predictive distribution of a portfolio’s returns over a holding period, according to a given confidence interval $\alpha$ [@dowd2007].
 \begin{equation} \label{eq:var}
@@
 \end{equation}
-It indicates that investors will not lose more than the amount as shown in VaR.
-It represents the largest possible investment loss in a given investment horizon with the given $\alpha$ confidence level.
+VaR represents the largest possible investment loss in a given investment horizon with the given $\alpha$ confidence level.
 There are different methods to estimate VaR, but it is clear that predictive density plays an important role here.
-Therefore, a more accurate prediction can contribute to improving the accuracy of VaR prediction.
-
-Opschoor, van Dijk & van der Wel (2017) combine density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the focused score outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.
-
-We illustrate how optimal forecasts perform in estimating VaR by using predictions produced in simulation (Section 3) first, and expect that optimal forecasts based on CLS would give us a better prediction in tails.
-Specifically, VaR predictions at \{10%, 20%, 80%, 90%\} are conducted, since they correspond to the 10% and 20% expected loss of long and short portfolios.
-We assess VaR predictive accuracy by using the VaR backtesting method.
-The specific steps are as below:
+Therefore, a more accurate probabilistic prediction can contribute to improving the accuracy of VaR prediction.
+
+@opschoor2017 combine density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the censored likelihood score outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.
+
+We illustrate how optimal forecasts perform in estimating VaR by using predictions produced through simulation (Section 3) first, and expect that optimal forecasts based on CLS would give us a better prediction in tails.
+Specifically, VaR predictions at \{10%, 20%, 80%, 90%\} are conducted, corresponding to the 10% and 20% expected loss of long and short portfolios.
+More importantly, we keep the percentage of VaR prediction the same as CLS focused tail because, as mentioned before, CLS at \{10%, 20%, 80%, 90%\} is computed from the marginal distribution due to computational burden and keeping the percentage the same reduce the error caused by this mismatch.
+
+We assess VaR predictive accuracy by using the VaR backtesting method. The specific steps are as below:
 
@@
 
-- Conditional out-of-sample predictives: $p_{S_i}(y_{1001}|y_{1000})...p_{S_i}(y_{5000}|y_{4999})$;
+- Conditional out-of-sample predictions: $p_{S_i}(y_{1001}|y_{1000})...p_{S_i}(y_{5000}|y_{4999})$;
 
@@
 The closer the proportion of exceedances, calculated in Step 3, to nominal VaR levels, the more accurate are VaR predictions and thus, the more accurate are the optimal probabilistic forecasts.
-An accurate prediction of the p% VaR is observed if the proportion of exceedances equals p%.
+An accurate prediction of the $\mathcal{p}$ % VaR is observed if the proportion of exceedances equals $\mathcal{p}$ %.
 
 Starting from the two different forms of model misspecification investigated in simulation analysis (Section 3), the values showed in the Table 9 and 10 refer to the out-of-sample proportion of exceedances over the nominal VaR level indicated by the column name.
-The focused score can provide the most accurate VaR prediction in the upper tail, while in the lower tail, it is not short of advantages by too much compared with CRPS.
+The censored likelihood score can provide the most accurate VaR prediction in the upper tail, while in the lower tail, it is not short of advantages by too much compared with CRPS.
 This conclusion does not vary much when we have different forms of model misspecification as illustrated in the Table 9 and 10.
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 9: the true DGP is copula (shape = -5)"=5))
+  add_header_above(c("Table 7: the true DGP is copula (shape = -5)"=5))
 ```
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 10: the true DGP is GARCH with degree of freedom = 3"=5))
+  add_header_above(c("Table 8: the true DGP is GARCH with degree of freedom = 3"=5))
 ```
@@
 We now implement the VaR analysis to continuously compounded daily log returns of S&P 500 in U.S.A financial market.
-Learning from the trace plots in Section 4.2, the 2008 GFC is the turning point of the optimal forecasts' performance, especially for the focused scores.
+Learning from the trace plots in Section 4.2, the 2008 GFC is the turning point of the optimal forecasts' performance, especially for the censored likelihood scores.
 Therefore, we perform the VaR analysis over two different time periods, before the GFC and after the GFC.
-The results from Table 11 and 12 show that the focused score perform well enough in terms of estimating VaR for both long and short portfolios of S&P 500, but also CRPS is a very robust scoring rule which can provide relatively accurate predictions.
-Moreover, in Table 12, the focused score seems to perform better in 20% and 80% tails which have higher probability mass than 10% and 90% tails.
-If we think of the marginal distribution of S&P 500 estimated by histogram in Figure 4.B, the above results could be a consequence of the very sparse marginal distribution, which increases the difficulty of 'focusing' on the 10% and 90% tails.
+The results from Table 11 and 12 show that the censored likelihood score perform well enough in terms of estimating VaR for both long and short portfolios of S&P 500, but also CRPS is a very robust scoring rule which can provide relatively accurate predictions.
+Moreover, in Table 12, the censored likelihood score seems to perform better in 20% and 80% tails which have higher probability mass than 10% and 90% tails.
+If we think of the marginal distribution of S&P 500 estimated by histogram in Figure 4.B, the above results could be a consequence of the very sparse marginal distribution or simply because there is no enough data in the tails to produce an accurate estimate of the CLS optimizer, which increases the difficulty of 'focusing' on the 10% and 90% tails.
 
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 11: VaR for S&P 500 before the GFC"=5))
+  add_header_above(c("Table 9: VaR for S&P 500 before the GFC"=5))
 
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 12: VaR for S&P 500 after the GFC"=5))
+  add_header_above(c("Table 10: VaR for S&P 500 after the GFC"=5))
 
@@
 
-VIX index estimates QV that is implied by option prices under a risk-neutral $\eqref{eq:jump}$ process, using a finite number of strike prices of S&P 500 index (Chicago Board Options Exchange, 2020).
+The VIX index estimates QV that is implied by option prices under a risk-neutral $\eqref{eq:jump}$ process, using a finite number of strike prices of S&P 500 index [@cboe].
 It acknowledges the occurrence of jumps and the fact that assumptions of the Black-Scholes model do not hold in practice.
-Since both the VIX and RV are estimations of QV, it is reasonable to model the VIX with a HAR-RV model which is usually used for modelling RV in the literature (Andersen, Bollerslev & Diebold, 2007; Corsi, 2009; Martin, Reidy & Wright, 2009; Maneesoonthorn, Martin, Forbes & Grose, 2012).
+Since both the VIX and RV are estimations of QV, it is reasonable to model the VIX with a HAR-RV model which is usually used for modelling RV in the literature [@andersen2007; @corsi2009; @m2009does; @manee2012probabilistic].
 
 ## 5.2 Preliminary diagnostics
-We collect daily VIX index data starting from 27 Aug,1996 to 30 July,2020. And the descriptive statistics of $log(VIX_t)$ are shown in Table 13 and Figure 6:
+We collect daily VIX index data starting from 27 Aug,1996 to 30 July,2020.^[Data retrieved from @vixdata] The descriptive statistics of $log(VIX_t)$ are shown in Table 13 and Figure 6:
 
@@
 Similarly, there are unusual jumps happened during the GFC and the COVID-19.
-Thus, we expect that the focused score could outperform MLE and CRPS in predicting tails as in Section 4.2 and significantly improve accuracy after the GFC.
+Thus, we expect that the censored likelihood score could outperform MLE and CRPS in predicting tails as in Section 4.2 and significantly improve accuracy after the GFC.
 
@@
   kable_styling("bordered",font_size = 10)%>% 
-  add_header_above(c("Table 13: Descriptive statistics"=9))
+  add_header_above(c("Table 11: Descriptive statistics"=9))
 ```
@@
 
-Proposed by Corsi (2009), the HAR-RV model is a simple additive linear model which takes lagged squared returns as regressors.
-It does not belong to the class of long memory models, but it is able to produce the volatility persistence that is almost indistinguishable from what observed in financial markets through the simple autoregressive-type structure.
+Proposed by @corsi2009, the HAR-RV model is a simple additive linear model which takes lagged squared returns as regressors.
+It does not belong to the class of long memory models, but it is able to produce the volatility persistence that is almost indistinguishable from what is observed in financial markets through the simple autoregressive-type structure.
 
@@
 \end{equation}
-By using the same methodology in Section 3 with initial sample size = 1000 and out-of-sample size $\tau=T-1000=5000$, we produce and evaluate predictive densities with the assumed model as HAR-RV.
+By using the same expanding window design in Section 3 with initial sample size = 1000 and out-of-sample size $\tau=T-1000=5000$, we produce and evaluate predictive densities with the assumed model as HAR-RV.
 The results are shown in the following sections.
@@
 
-Section 5.4.1 provides the result of Specification 1 where the predictive density of the VIX is normal distribution with a constant variance.
-In Table 14, CLS performs better in predicting upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
+Section 5.4.1 provides the result of Specification 1 where the predictive density of the VIX is the normal distribution with a constant variance.
+In Table 14, CLS performs better in predicting the upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
 The score trace plot, Figure 7, shows the predictions of optimizing four scoring rules evaluated by CLS10 (left panel) and CLS90 (right panel).
@@
 However, we only gain very little from using it.
-On the contrary, in the upper tail, CLS has a much bigger effect on improving accuracy after the GFC and this effect continues.
-One possible explanation could be that both LS and CRPS can predict the lower tail better if there is higher probability mass at that area, then the benefit of using CLS is not significant.
-Considering the marginal distribution shown in Figure 6.B of $log(VIX_t)$, we observe much more observations in the lower end than in the upper end so that it might be the reason why we observe the little improvement in predicting the lower tail in Figure 7(a).
+On the contrary, in the upper tail, CLS has a much bigger effect on improving accuracy after the GFC.
+One possible explanation could be that the HAR model is more misspecified in the upper tail than in the lower tail.
+Thus, we benefit more from CLS optimal forecasts in the upper tail.
 
@@
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 14: Average scores for the VIX"=7))
+  add_header_above(c("Table 12: Average scores for the VIX with Gaussian error"=7))
 ```
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) 10 percentile","Figure 7(b) 90 percentile"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) CLS10","Figure 7(b) CLS90"))
 
@@
   add_header_above(c("","Average out-of-sample scores"=5)) %>% 
-  add_header_above(c("Table 15: Average scores for the VIX Student-t error"=6))
+  add_header_above(c("Table 13: Average scores for the VIX with Student-t error"=6))
 ```
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) 10 percentile","Figure 8(b) 90 percentile"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) CLS10","Figure 8(b) CLS90"))
 ```
@@
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 16: Average scores for the VIX ARCH normal error"=7))
+  add_header_above(c("Table 14: Average scores for the VIX with ARCH normal error"=7))
 ```
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) 10 percentile","Figure 9(b) 90 percentile"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) CLS10","Figure 9(b) CLS90"))
 
@@
   add_header_above(c("","Average out-of-sample scores"=5)) %>% 
-  add_header_above(c("Table 17: Average scores for the VIX ARCH Student-t error"=6))
+  add_header_above(c("Table 15: Average scores for the VIX with ARCH Student-t error"=6))
 ```
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 10(a) 10 percentile","Figure 10(b) 90 percentile"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 10(a) CLS10","Figure 10(b) CLS90"))
 
@@
 
-According to the numerical and empirical results, the benefits of optimal forecasts can be observed when we have model misspecification and their performance does not vary between two different types of model misspecification investigated in this paper.
-By mainly focusing on investigating the tail performance of optimal forecasts, the results show that the more misspecified the model is, the more benefits can be gained from using the focused score in improving the tail prediction accuracy in comparison with the conventional likelihood-based counterparts.
+According to the numerical and empirical results, the benefits of optimal forecasts can be observed when we have model misspecification, subject to the assumed predictive model is compatible, and their performance does not vary between two different types of model misspecification investigated in this paper.
+By mainly focusing on investigating the tail performance of optimal forecasts, the results show that the more misspecified the model is, the more benefits can be gained from using the censored likelihood score in improving the tail prediction accuracy in comparison with the conventional likelihood-based counterparts.
 This result is particularly in evidence after the stock market turbulence in both financial returns and the VIX index.
@@
 
-One possible conjecture is that there are more observations in the lower tail of the VIX so that MLE or CRPS can still perform well and thus, less benefits are gained by using CLS.
-However, it is impossible to know what the shape of the true conditional predictive distribution looks like, but due to the connection between marginal density and conditional density, this might be a reasonable conjecture to make.
-Nevertheless, these results bring great values to financial applications.
-For the financial returns, optimal forecasts can give better VaR predictions and for the VIX index, the upper tail, which indicates higher volatility in the market, is more of an interest to investors in terms of making profits, hedging risks, and trading of derivatives.
-
-...
-
-@optimal 
-@cboe
-@vixdata
-@spdata
+There are some caveats as well.
+Firstly, the predictions conducted by CLS is based on the tail regions of the marginal distribution, while VaR is calculated from the conditional predictive distribution which is updated through each iteration.
+Therefore, there is a slight mismatch in distributions when predicting VaR.
+Secondly, the practical usage of VaR is often around 1% or 5%, but at this very small tail, CLS might be less accurate than predicting 10% or 20% tail, since there are less observations in the tail and consequently, harder to focus correctly.
+However, this drawback might be corrected by changing to a more suitable assumed predictive model which provides a heavy tail distribution.
+As mentioned above, the difference between optimal forecasts’ performance in S&P 500 log returns and in the VIX Index is hard to interpret.
+The performance of optimal forecasts depends on the true conditional predictive distribution, which is always unknown in practice.
+Even though the marginal distributions can provide some insights about the shape of true conditional predictive distribution, it still creates a problem for determining which tail could optimal forecasts reap significant benefits.
+More importantly, the reasons why we can gain considerably from optimal forecasts after the GFC needs further investigation.
+
+Nevertheless, the results in this paper provide important insights to the financial forecasting literature.
+In terms of financial returns, optimal forecasts can give better VaR predictions when it comes to the VIX index, the improvement of predictive accuracy in the upper tail - which indicates that higher volatility in the market is more accurately predicted - is an important contribution to literature on hedging risks and trading derivatives in financial market.
 

### 2020-10-14 Final.Rmd
thesis v3 changes (before due date 18 Oct)

@@
   - \usepackage{amsmath}
+  - \usepackage{amsfonts}
   - \usepackage{setspace}\doublespacing
   - \usepackage[hyphens]{url}
-  - \usepackage{boondox-cal}
+  - \usepackage{float}
 fontsize: 12pt
@@
 \pagebreak
+
+# Abstract
+
+With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification.
+Building on previous research, this paper conducts numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score.
+In particular, we assess the predictive performance of optimal forecasts in two empirical contexts: prediction of the Value-at-Risk of a financial return and prediction of the VIX volatility index.
+Results show that the greater the degree of model misspecification, the more beneficial is optimal prediction, no matter what the form of model misspecification.
+Most notably, predictions that are optimal according to the censored likelihood score, which rewards predictive accuracy in a tail are substantially more accurate at predicting extreme events in said tail than the alternatives, including likelihood-based predictions.
+
+\pagebreak
+
+```{=latex}
+% Trigger ToC creation in LaTex
+\setcounter{tocdepth}{2}
+\tableofcontents
+```
+
+\pagebreak
+
+# 1. Introduction
+
+This paper explores the question: ‘When do optimal probabilistic forecasts work’, with particular attention given to the usefulness of optimal forecasts in financial applications.
+
+Probabilistic forecasts can provide complete information about future uncertainty, which can be more valuable to forecasters than point and interval forecasts.
+However, previous approaches to prediction - including probabilistic methods – typically assume that the predictive model, or the likelihood function, correctly specifies the true data generating process (DGP) or that the true DGP lies in a specified set of models, which is almost certainly untrue in practice.
+Optimal probabilistic forecasting refers to the construction of a predictive probability distribution that is optimal according to a user-specified proper scoring rule [@optimal].
+It is not based on the conventional likelihood function but on a proper scoring rule that matches the specific problem at hand.
+Optimal probabilistic forecasts aim to yield accurate predictions in the presence of a misspecified predictive model, whilst the conventional approaches to probabilistic forecasting are tied more closely to the predictive model, and are only as accurate as that model itself.
+
+Particular proper scoring rules allow users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand [@gneiting2007].
+Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see @opschoor2017, @fbp2020 and @optimal.
+Among all these investigations, it is the censored likelihood score (CLS) proposed originally by @diks2011, that captures our attention for the purpose of demonstrating the application of optimal probabilistic forecasts in finance.
+Its ‘focusing’ feature has great potential in financial risk management.
+In other words, CLS allows a forecaster to focus on predicting any particular region of interest accurately.
+Therefore, its use in this context represents an important contribution to risk prediction in financial settings.
+
+Whilst some empirical investigations of the performance of optimal forecasts were undertaken in @optimal, these were primarily illustrative, and left much scope for exploring the performance of optimal probabilistic forecasting methods in forecasting different types of financial measures, and under different assumed models.
+This research paper extends the work of @optimal by investigating the effect of the form and degree of model misspecification on the performance of optimal probabilistic forecasts in financial settings; in particular by conducting empirical analyses of how optimal forecasts perform in predicting the Value-at-Risk (VaR) and the VIX volatility index (VIX).
+Importantly, the empirical dataset used extends over a period of time that precedes the 2008 global financial crisis (GFC) and that includes the latest period in which COVID-19 has had an impact on financial markets.
+
+The paper proceeds as follows.
+Section 2 explains the basic idea about how scoring rules are applied in producing and evaluating density forecasts, and provides the definitions of some commonly used scoring rules.
+Section 3 focuses on investigating the effects of different forms and degrees of model misspecification on the performance of optimal forecasts, using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and inversion copula models.
+The assumed predictive model is fixed as a Gaussian ARCH(1) model for the purpose of controlling the degree of model misspecification.
+In Section 4, we emulate the simulation exercise in an empirical example for financial returns on the S&P 500 stock index, including the prediction of the VaR.
+The results illustrate the practical contributions of our predictive approach to financial risk management.
+The empirical analysis of the VIX is provided in Section 5, where the predictive model is the heterogeneous autoregressive-realized volatility (HAR-RV) model with different error term specifications.
+We conclude and discuss any possible caveats in Section 6.
+
+# 2. Scoring rules in prediction
+## 2.1 Overview and notation
+
+Scoring rules $S(\cdot,\cdot)$ are a type of criterion function that can be optimized to produce an optimal estimator and hence, a probabilistic prediction derived from this optimal estimator.
+They also play the role of evaluating and ranking competing probabilistic forecasts, based on materialized events or values, by assigning a numerical score [@gneiting2007].
+That is, if the forecaster produces a predictive distribution $\mathit{P}$ and the event $y$ materializes, then the reward to this prediction given by a scoring rule is denoted by $S(P,y)$.
+For a positively-oriented score, a higher value will be assigned to a better forecast between two competing candidates, on the condition of the scoring rule being proper.
+The propriety of the scoring rule is crucial here, as an improper scoring rule may assign a higher average score to an incorrect density forecast [@gneiting2007].
+Consequently, only proper scoring rules are used in the production of optimal forecasts.
+
+Suppose $P$ is the predictive distribution and $Q_0$ is the true DGP. $\mathbb{S}(P,Q_0)$ denotes the expected score of $S(P,\cdot)$ under $Q_0$. That is,
+\begin{equation} \label{eq:score}
+\mathbb{S}(P,Q_0)=\int_{y \in \Omega}S(P,y)dQ_0(y)
+\end{equation}
+where $\Omega$ is a probability space. 
+A scoring rule is said to be proper if $\mathbb{S}(Q_0,Q_0) \geq \mathbb{S}(P,Q_0)$ for all $P$ and $Q_0$, and is strictly proper if $\mathbb{S}(Q_0,Q_0) = \mathbb{S}(P,Q_0)$ only when $P = Q_0$ [@gneiting2007].
+This ensures that a proper scoring rule is maximized when the prediction reveals the truth, on the condition that the predictive distribution class $\mathcal{P}$ contains $Q_0$.
+
+However, in practice, the expected score $\mathbb{S}(\cdot,Q_0)$ is unknown and cannot be obtained, but we can use a sample average $\bar S(\cdot)$ as a reasonable estimation.
+Asymptotically, the true predictive distribution can be recovered by optimizing a sample criterion of any proper scoring rule, if the true predictive is contained in the predictive class over which the maximization occurs.
+Even when $Q_0$ is not contained in the predictive distribution class $\mathcal{P}$ proposed by the forecaster, it does not change the fact that a proper scoring rule will reward a particular form of forecast accuracy and hence, select the best forecast within the proposed predictive distribution class, according to this scoring rule.
+
+Assume the scoring rule is positively-oriented and the unknown parameters of the assumed predictive model are denoted as $\boldsymbol \theta \in \Theta$, and let $P^{t-1}_{\boldsymbol{\theta}}$ := $P(\cdot|\mathcal{F}_{t-1},\boldsymbol \theta)$ be the one-step-ahead predictive distribution function based on the assumed model where $\mathcal{F}_{t-1}$ represents all the information available at time $t-1$, and $p^{t-1}_{\boldsymbol{\theta}}$ := $p(\cdot|\mathcal{F}_{t-1},\boldsymbol \theta)$ be the corresponding predictive density function at time $t$.
+Then an estimator $\boldsymbol{\hat \theta}$ obtained by maximizing $\bar S(\boldsymbol{\theta})$ is said to be 'optimal' based on this scoring rule and $P^{t-1}_{\boldsymbol{\hat \theta}}$ is referred to as the optimal predictive.
+Specifically, we define 
+\begin{equation} \label{eq:1}
+\boldsymbol{\hat \theta} =arg \max_{\boldsymbol{\theta} \in \Theta} \bar S(\boldsymbol{\theta})
+\end{equation}
+where 
+\begin{equation} \label{eq:sbar}
+\bar S = \frac{1}{T-\tau+1}\sum_{t=2}^{T-\tau} S(P_{\boldsymbol{\theta}}^{t-1},y_t)
+\end{equation}
+with $\mathit{T}$ the total number of observations on a time series variable $y_t$ and $\tau$ the out-of-sample size.
+Under certain conditions, including that the scoring rule is proper and that the predictive model is correctly specified, $\boldsymbol{\hat \theta} \to \boldsymbol{\theta}_0 \ as \ \mathit{T} \to \infty$ where $\boldsymbol{\theta}_0$ represent the true (vector) parameter.
+
+## 2.2 Some commonly used scoring rules
+
+A variety of scoring rules have been developed to tackle different problems.
+Some commonly used proper scoring rules are adopted in the analyses in this paper, such as the logarithmic score (LS), the continuously ranked probability score (CRPS) and the CLS.
+
+The LS is defined as
+\begin{equation} \label{eq:ls}
+S_{LS}(P^{t-1}_{\boldsymbol \theta}, y_t) = ln[p(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})]
+\end{equation}
+where $p(\cdot|\mathcal{F}_{t-1},\boldsymbol{\theta})$ is the predictive density function.
+It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters [@bickel2007].
+One common usage of the LS in frequentist econometrics is maximum likelihood estimation (MLE).
+That is,
+\begin{equation} \label{eq:mle}
+\boldsymbol{\hat \theta}_{MLE}=arg \max_{\boldsymbol{\theta} \in \Theta} \{\frac{1}{T} \sum_{t=1}^T ln[p(y_t|\mathcal{F}_{t-1},\boldsymbol \theta)]\}
+\end{equation}
+LS yields an asymptotically efficient estimator of $\boldsymbol \theta$ under correct specification and regularity.
+
+However, the LS is criticized for its unboundedness and its local property.
+@bernardo1979 states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state".
+@gneiting2007 also argue that the LS is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event.
+@gneiting2007 propose the continuously ranked probability score, which is sensitive to distance and is defined as
+\begin{equation} \label{eq:crps}
+S_{CRPS}(P^{t-1}_{\boldsymbol \theta},y_t)=-\int_{-\infty}^{\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol{\theta})-I(y\geq y_t)]^2dy
+\end{equation}
+where $\mathit{P}(\cdot|\mathcal{F}_{t-1},\boldsymbol{\theta})$ is the predictive cumulative distribution function, *I* is the indicator function, and $y_t$ is the materialized event.
+
+The formula can be simplified as follows if the predictive distribution is Gaussian with mean $\mu$ and variance $\sigma^2$, 
+\begin{equation} \label{eq:crnorm}
+S_{CRPS}(N^{t-1}_{\boldsymbol \theta},y_t)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{y_t-\mu}{\sigma})-\frac{y_t-\mu}{\sigma}(2\Phi(\frac{y_t-\mu}{\sigma})-1)]
+\end{equation}
+where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the standard Gaussian distribution.
+
+Both LS and CRPS are used for producing predictive densities and evaluating the out-of-sample predictive performance.
+In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood [@gneiting2011].
+@diks2011 propose the CLS, which allows users to reward forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast.
+Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy.
+It is defined as
+\begin{equation} \label{eq:cls}
+S_{CLS}(P^{t-1}_{\boldsymbol \theta}, y_t)=I(y_{t} \in A)ln p(y_{t}|\mathcal{F}_{t-1},\boldsymbol{\theta})+I(y_{t} \in A^c)ln[\int_{A^c} p(y|\mathcal{F}_{t-1},\boldsymbol{\theta})dy]
+\end{equation}
+where $p(\cdot|\mathcal{F}_{t-1},\boldsymbol{\theta})$ is the predictive probability density function, $A$ is the region of interest and $A^c$ is the complement of $A$.
+@opschoor2017 prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.
+
+# 3. Numerical investigation of optimal predictions
+## 3.1 Simulation design
+
+Optimal forecasts can outperform predictions produced by conventional methods out-of-sample; see @opschoor2017, @fbp2020 abd @optimal; but the underlying reasons driving this phenomenon are still under investigation.
+Recent research show that the degree of model misspecification impacts the performance of optimal forecasts.
+The greater the degree of misspecification is, the more benefits are gained from optimal forecasts in both Bayesian and frequentist predictions, conditional on the assumed predictive model being broadly 'compatible' with the true DGP; see @fbp2020 and @optimal.
+The simulation analysis in this paper will extend the exploration in this field and ask the question ‘Will the performance of optimal forecasts change when a different form of misspecification occurs?’.
+
+In order to set the scene for the financial application analyses in the following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and their volatility.
+Specific simulation scenarios are listed in Table 1 ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).
+
+*Table 1: The three simulation scenarios used in the numerical analysis.
+Scenario (i) represents correct model specification; Scenario (ii) represents a form of misspecification where the true DGP is GARCH with Student-t distribution while the assumed model is Gaussian ARCH(1); Scenario (iii) represents a more extreme form of misspecification, where the true DGP is an stochastic volatility model with a non-Gaussian marginal distribution while the assumed model is Gaussian ARCH(1).*
+
+\begin{table}[H]
+\centering
+\resizebox{\textwidth}{!}{
+\begin{tabular}{|c|c|c|c|}
+\hline
+\multicolumn{4}{|c|}{\textbf{Table 1: Simulation design}} \\ \hline
+          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} & \textbf{Scenario (iii)} \\ \hline
+\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & $y_t = \sigma_t \epsilon_t$ & Stochastic volatility inversion copula \\
+& $\sigma_t^2 = 1 + 0.2y_{t-1}^2$ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = \{0, -3, -5\} \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & & $\nu \in \{3,12,35\}$ & \\ \hline
+
+\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ \\ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ \\ \hline
+\end{tabular}}
+\end{table}
+
+GARCH models are used to capture the volatility clustering and serial dependence that are usually observed in empirical stock returns, and the negative marginal skewness will be incorporated by using a stochastic volatility inversion copula model, with the degree of marginal skewness controlled by the shape parameter.
+
+Copula models are a flexible way of representing the joint distribution function of a set of variables [@fan2014].
+In recent years, these models have been applied to modelling serial dependence, which can be constructed as:
+\begin{equation} \label{eq:copula}
+p_{t-1}(y_t)=c(P(y_t),P(y_{t-1}))p(y_{t-1})
+\end{equation}
+where $\mathit{P}()$ and $\mathit{p}$() denote the marginal distribution and density function of $y_t$ respectively, and c() is the copula density function that captures the dependence between $y_t$ and $y_{t-1}$.
+
+For the simulation exercise, the marginal distribution $\mathit{P}()$ is chosen to be the standard skew-normal distribution, while c() is chosen to be the inversion copula of the stochastic volatility model described in @inversion2018.
+The stochastic volatility inversion copula model allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns [@inversion2018].
+
+In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP specifications in Scenario (ii) and (iii).
+
+We apply the scoring rules introduced in Section 2.2 and set CLS to focus on the 10%, 20%, 80% and 90% tails of the empirical marginal distribution, corresponding to the risks of long and short portfolios of financial investments, and we label them as CLS10, CLS20, CLS80 and CLS90 in the following tables and figures.
+Due to the fact that there is no reliable estimate of the true conditional densities, only the tails of the marginal distributions are set to be the standard when assessing the predictive accuracy by CLS, rather than the conditional distributions.
+Meanwhile, LS gives insights about the performance of the conventional likelihood-based methods and is used as a benchmark for comparing whether optimal forecasts can provide benefits or not.
+
+We conduct Monte Carlo simulations using the methodology in @optimal and @fbp2020. Specific steps are as follows:
+
+Let $P^{t-1}_{\boldsymbol{\hat \theta^{[i]}}}$ be the one-step-ahead predictive distribution function based on the Gaussian ARCH(1) model and optimized according to the scoring rule $S_i$, and $p(y_t|\mathcal{F}_{t-1},\boldsymbol{\hat \theta^{[i]}})$ be the corresponding predictive density function at time $\mathit{t}$.
+
+  1.	Generate T = 6000 observations of $y_t$ from the true DGP
+
+  2.	Use observations $y_t$ where $t = 1,2,...,1000$ to estimate $\boldsymbol{\hat \theta}^{[i]} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}^{[i]}$ as in $\eqref{eq:1}$ based on $S_i$, $i \in \{LS, CRPS, CSL10,CSL20,CSL80,CSL90\}$ where $S_i$ refers to $\eqref{eq:ls}$ $\eqref{eq:crps}$ $\eqref{eq:cls}$
+
+  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta^{[i]}}}$, and compute the out-of-sample score $S_j$, $j \in \{LS, CRPS, CSL10,CSL20,CSL80,CSL90\}$
+where $S_j$ refers to $\eqref{eq:ls}$ $\eqref{eq:crps}$ $\eqref{eq:cls}$:^[The CRPS in $\eqref{eq:crps}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]
+
+  4.
+Expand estimation window by one observation and repeat steps 2-3 with $\tau = T-1000$ times and compute the average scores:^[Out-of-sample size $\tau = 5000$ is sufficiently large to let the optimal forecasts take place; see @optimal for full discussion about sample size effects on optimal forecasts.]
+
+\begin{equation} \label{eq:avgscore}
+\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
+\end{equation}
+
+For the purpose of conveniently documenting and interpreting the results consistently with previous literature, we introduce the concept of ‘coherence’ and ‘strict coherence’ here.
+Coherence means that the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score.
+Strict coherence happens when the optimal prediction is strictly preferable given that score.
+Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules:$S_1$ and $S_2$.
+Then the optimal predictions $P^{t-1}_{\boldsymbol{\hat \theta_1}}$ and $P^{t-1}_{\boldsymbol{\hat \theta_2}}$ can be derived from $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$.
+The coherent results are observed if
+\begin{equation} \label{eq:coh1}
+\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
+\end{equation}
+\begin{equation} \label{eq:coh2}
+\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
+\end{equation}
+It is said to be strictly coherent if $\eqref{eq:coh1}$ and $\eqref{eq:coh2}$ are strict inequalities [@optimal].
+
+## 3.2 Simulation results
+### 3.2.1 Average out-of-sample scores
+
+The first column of each of the following tables presents the labels for the $S_i$ that we used to produce predictions and the third-row shows $S_j$, which is used for the forecast's evaluation.
+The bolded numbers are the largest values of $\bar S_j(\boldsymbol{\hat \theta^{[i]}})$ in each column.
+We use all positively-oriented scoring rules, and therefore, the column maximum indicates the optimal prediction based on the scoring rule indicated by the column name.
+
+Table 2 shows the correct model specification - Scenario (i) - where the optimal forecasting method does not reap benefits and there is no strict coherence observed in the table.
+Under correct specification, no matter what the score rewards, estimators produced from $S_i$ are expected to concentrate to the same true parameter values as $T$ approches to infinity, which causes no distinct improvement in predictive accuracy among different scoring rules [@optimal].
+
+Table 3 shows the results of Scenario (ii) where the assumed predictive model, ARCH(1), cannot capture the fat tails and volatility clustering feature of the data generated from the GARCH(1,1) model with Student-t error, i.e.
+the true DGP.
+Hence, there is misspecification.
+Tables 2 and 3 replicate some parts of the simulation results in previous literature; see @fbp2020, @optimal.
+Optimal forecasts are expected to reap more benefits as the degree of model misspecification increases, and predictions based on CLS at 80% and 90% perform poorly when assessed by LS, CRPS, CLS at 10% and CLS at 20%.
+The question is whether these characteristics of optimal forecasts will change if we move to a different form of model misspecification.
+
+Table 4 shows another type of model misspecification, listed in Scenario (iii), where the ARCH(1) model cannot capture the asymmetric feature of the data generated from the stochastic volatility inversion copula model (the true DGP).
+Table 4 shows similar results as in Table 3.
+As the shape parameter decreases, the degree of negative marginal skewness increases, and optimal forecasts provide more benefits.
+Even though, strictly speaking, we do not observe strict coherence in Panel C, the most misspecified case, it is close enough to conclude that optimal forecasts perform in the same way even when we have different forms of model misspecification.
+^[Tables are produced by R package: @kableextra and @knitr.]
+
+*Table 2: It shows the results of Scenario (i), the correct model specification case. Both the true DGP and assumed predictive model are ARCH(1) with Gaussian error.*
 
@@
 
-# Abstract
-
-With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification.
-Building off previous research, this paper conducts numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score.
-In particular, we assess the predictive performance of optimal forecasts in two empirical contexts: prediction of the Value-at-Risk and prediction of the VIX Volatility Index.
-Results show that the greater the degree of model misspecification, the more beneficial is optimal prediction, no matter which form of model misspecification is.
-Predictions that are optimal according to the censored likelihood score that rewards predictive accuracy in a tail are substantially more accurate at predicting extreme events in said tail than the alternatives, including likelihood-based predictions.
-
-\pagebreak
-
-```{=latex}
-% Trigger ToC creation in LaTex
-\setcounter{tocdepth}{2}
-\tableofcontents
-```
-
-\pagebreak
-
-# 1. Introduction
-
-This paper explores the question: ‘When do optimal probabilistic forecasts work’, with particular attention given to the usefulness of optimal forecasts in financial applications.
-
-Probabilistic forecasts can provide complete information about future uncertainty, which can be more valuable than point and interval forecasts to forecasters.
-However, previous approaches to prediction - including probabilistic methods – typically assume that the predictive model or the likelihood function correctly specifies the true data generating process (DGP) or the true DGP lies in the model pools, which is almost certainly untrue in practice.
-Optimal probabilistic forecasting refers to the construction of a predictive probability distribution that is optimal according to a user-specified proper scoring rule [@optimal].
-It is not constructed based on the conventional likelihood function but on a proper scoring rule that matches the specific problem at hand.
-Optimal probabilistic forecasts aim to improve the predictive accuracy of a misspecified model, whilst the conventional approaches to probabilistic forecasting focus on the development of increasingly less misspecified models that can potentially yield better probabilistic forecasts.
-
-A variety of proper scoring rules allows users to produce probabilistic predictions that are designed to perform well according to the forecasting metric that is important to the problem at hand [@gneiting2007].
-Some recent research shows that forecasts produced using a given scoring rule can yield better out-of-sample accuracy - measured by that scoring rule - than conventional likelihood-based forecasts, in particular in the presence of model misspecification; see @opschoor2017, @fbp2019 and @optimal.
-Among all these investigations, it is the censored likelihood score (CLS) proposed originally by @diks2011, that captures our attention for the purpose of demonstrating the application of optimal probabilistic forecasts in finance.
-Its ‘focusing’ feature has great potential in financial risk management.
-In other words, CLS allows a forecaster to focus on predicting any particular region of interest more accurately.
-Therefore, its usage in this context represents an important contribution to risk prediction in financial settings.
-
-Whilst some empirical investigations about the performance of optimal forecasts were undertaken in @optimal, these were primarily illustrative, and left much scope for exploring the performance of optimal probabilistic forecasting methods in forecasting different types of financial measures, and under different assumed models.
-
-This research paper extends the work of @optimal by investigating the effect of the form and degree of model misspecification on the performance of optimal probabilistic forecasts in financial settings; in particular by conducting empirical analyses of how optimal forecasts perform in predicting the Value-at-Risk (VaR) and the VIX Volatility Index (VIX).
-Importantly, the empirical dataset used extends over a period of time that precedes the 2008 global financial crisis (GFC) and that includes the latest period in which COVID-19 has had an impact on financial markets.
-
-The paper proceeds as follows.
-Section 2 explains the basic idea about how scoring rules are applied in producing and evaluating density forecasts, and provides the definitions of some commonly used scoring rules.
-Section 3 focuses on investigating the effects of different forms and degrees of model misspecification on the performance of optimal forecasts, using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and inversion copula models.
-The assumed predictive model is fixed as ARCH(1) for the purpose of manipulating the degree of model misspecification.
-Although the simulation design is introduced in this section, it forms the foundation of methodologies used in all experiments conducted in other sections of this paper.
-In Section 4, we emulate the simulation exercise on an empirical example for financial returns of the S&P 500 index, including the prediction of the Value-at-Risk (VaR).
-The results illustrate the practical contributions to financial risk management.
-The empirical analysis of the VIX is provided in Section 5, where the predictive model is the heterogeneous autoregressive-realized volatility (HAR-RV) model with different error term specifications.
-We conclude and discuss any possible caveats in Section 6.
-
-# 2. Scoring rules in prediction
-## 2.1 Overview and notation
-
-Scoring rules are a type of criterion function that can be optimized to produce an optimal estimator and thus, a probabilistic prediction derived from this optimal estimator and an assumed model.
-They also play the role of encouraging forecasters to make careful and honest assessments in elicitation of subjectivist Bayesians, and evaluating and ranking competitive probabilistic forecasts, based on the predictive distribution and materialized events or values, by assigning a numerical score [@waite2005; @gneiting2007].
-Therefore, the crucial importance of the propriety of scoring rules must be emphasized for their usage because improper scoring rules will assign a higher average score to an incorrect density forecast [@gneiting2007].
-Consequently, forecasts based on improper scoring rules will not be ‘optimal’.
-
-Suppose P and Q are predictive distributions and Q is the best forecast given all the available information.
-S(P,Q) denotes the expected value of S(P,$\cdot$) under Q.
-A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q [@gneiting2007].
-
-In terms of producing probabilistic forecasts, scoring rules can replace the conventional likelihood function in frequentist and Bayesian predictions; see @fbp2019 and @optimal.
-Supposing the scoring rule is positively oriented, then an estimator $\hat \theta$ obtained by maximizing a scoring rule $S(\theta)$ is said to be 'optimal' based on this scoring rule.
-\begin{equation} \label{eq:1}
-\hat \theta =arg \max_\theta S(\theta)
-\end{equation}
-Under certain conditions, including that the scoring rule is 'proper', $\hat \theta \to \theta_0 \ as \ \mathcal{T} \to \infty$,
-where $\theta_0$ is the true parameter value and $\mathcal{T}$ is the total sample size of a time series variable $y_t$.
-The predictive distribution based on this optimal estimator, $p(y_{T+1}|M,\hat \theta,y_{1:T})$, has been produced from the assumed model by optimizing a proper scoring rule.
-^[M refers to the assumed model and it is omitted in the following notation for simplicity, since the assumed model does not change.]
-
-In addition, in terms of evaluating predictions, scoring rules assign numerical values to density forecasts, addressing both sharpness and calibration simultaneously.
-It is usually the average score ($\bar S$) that is used to directly compare predictive accuracy among predictions produced by optimizing different scoring rules [@gneiting2007].
-\begin{equation} \label{eq:sbar}
-\bar S = \frac{1}{T}\sum_{t=1}^T S(p_{t+1},y_t)
-\end{equation}
-For a positively oriented score, for example, a higher value will be assigned to a better forecast between two competing candidates, on the condition of the scoring rule being proper.
-
-## 2.2 Some commonly used scoring rules
-
-A variety of scoring rules have been developed to tackle different problems.
-Some commonly used proper scoring rules are adopted in the analyses in this paper, such as the logarithmic score (LS), the continuously ranked probability score (CRPS) and the censored likelihood score (CLS).
-
-The logarithmic score is defined as in $\eqref{eq:ls}$ where $p_t$ is the predictive density. 
-\begin{equation} \label{eq:ls}
-S_{LS}(p_{t-1}, y_t) = log[p_{t-1}(y_t)]
-\end{equation}
-It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of the nonlinear utility function used is a concern for forecasters [@bickel2007].
-One common usage of the logarithmic score in frequentist econometrics is the maximum likelihood estimation (MLE).
-\begin{equation} \label{eq:mle}
-\hat \theta_{MLE}=arg \max_\theta \{log[p_{t-1}(y_t|\theta)]\}
-\end{equation}
-It provides an asymptotically optimal and efficient estimation under the correctly specified log-likelihood function and regularity.
-
-However, the logarithmic score is criticized for its unboundedness and its local property.
-@bernardo1979 states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state".
-@gneiting2007 also argue that the logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event.
-@gneiting2007 propose the continuously ranked probability score, which is sensitive to distance and is defined as in $\eqref{eq:crps}$
-\begin{equation} \label{eq:crps}
-CRPS(P_{t-1},x_t)=-\int_{-\infty}^{\infty}[P_{t-1}(y)-I(y\geq x_t)]^2dy
-\end{equation}
-where $\mathcal{P}$ is the cumulative distribution function, *I* is the indicator function, and $x_t$ is the materialized event.
-
-The formula can be simplified to $\eqref{eq:crnorm}$ if the prediction distribution is Gaussian with mean $\mu$ and variance $\sigma^2$.
-\begin{equation} \label{eq:crnorm}
-CRPS(N_{t-1},x_t)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x_t-\mu}{\sigma})-\frac{x_t-\mu}{\sigma}(2\Phi(\frac{x_t-\mu}{\sigma})-1)]
-\end{equation}
-where $\phi$ and $\Phi$ are the probability density function and cumulative distribution function of the standard Gaussian distribution.
-
-Both LS and CRPS are used for producing predictive densities and evaluating the out-of-sample predictive performance.
-In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood [@gneiting2011].
-@diks2011 propose the censored likelihood score, which allows users to assess forecasts only on a region (regions) of interest instead of using weights to emphasize a particular part of the entire density forecast.
-Moreover, it can be easily used to combine density forecasts and yield better predictive accuracy.
-It is defined as in $\eqref{eq:cls}$
-\begin{equation} \label{eq:cls}
-S_{CLS}(p_{t-1}, y_t)=I(y_{t} \in A_t)log[ p_{t-1}(y_{t})]+I(y_{t} \in A_t^c)log[\int_{A_t^c} p_{t-1}(s)ds]
-\end{equation}
-where $p_t$ is the predictive probability density function, $A_t$ is the region of interest and $A_t^c$ is the complement of $A_t$.
-@opschoor2017 prove that weighted density forecasts based on optimizing CLS outperform those on LS and CRPS.
-
-# 3. Numerical investigation of optimal predictions
-## 3.1 Simulation design
-
-Optimal forecasts can outperform predictions produced by conventional methods out of sample; see @opschoor2017, @fbp2019 abd @optimal; but the underlying reasons driving this phenomenon are still under investigation.
-Recent research show that the degree of model misspecification impacts the performance of optimal forecasts.
-The greater the degree of misspecification is, the more benefits are gained from optimal forecasts in both Bayesian and frequentist predictions, conditional on the assumed predictive model being compatible; see [@fbp2019] and [@optimal].
-The simulation analysis in this paper will extend the exploration in this field and ask the question ‘Will the performance of optimal forecasts change when a different form of misspecification occurs?’.
-
-In order to set the scene for the financial application analyses in following sections of this paper, we simulate a time series variable $y_t$ that mimics the behavior of financial returns and their volatility.
-Specific simulation scenarios are listed in Table 1 ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).
-
-\begin{table}[!ht]
-\centering
-\resizebox{\textwidth}{!}{
-\begin{tabular}{|c|c|c|c|}
-\hline
-\multicolumn{4}{|c|}{\textbf{Table 1: Simulation design}} \\ \hline
-          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} & \textbf{Scenario (iii)} \\ \hline
-\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & $y_t = \sigma_t \epsilon_t$ & Stochastic volatility inversion copula \\
-& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = \{0, -3, -5\} \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & & $\nu \in \{3,12\}$ & \\ \hline
-
-\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ \\ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 \sigma_{t-1}^2$ \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ \\ \hline
-\end{tabular}}
-\caption{It shows three simulation scenarios conducted in the numerical analysis sections where Scenario (i) shows the correct model specification, Scenario (ii) shows that the true DGP is GARCH with Student-t distribution while the assumed model creates normal distribution, and Scenario (iii) creates an asymmetric true DGP, while the assumed model can only produces symmetric predictive distribution.}
-\end{table}
-
-GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock returns, and the negative marginal skewness will be incorporated by using a stochastic volatility inversion copula model, with the degree of marginal skewness controlled by the shape parameter.
-
-Copula models are a flexible approach to represent the joint distribution function of a set of variables [@fan2014].
-In recent years, these models have been applied for modelling of serial dependence as shown in $\eqref{eq:copula}$ [@inversion2018].
-\begin{equation} \label{eq:copula}
-p_{t-1}(y_t)=c(P(y_t),P(y_{t-1}))p(y_{t-1})
-\end{equation}
-where $\mathcal{P}()$ and $\mathcal{p}$ denote the marginal distribution and density function of $y_t$ respectively, and c() is the copula density function that captures the dependence between $y_t$ and $y_{t-1}$.
-
-For the simulation exercise, the marginal distribution $\mathcal{P}()$ is chosen to be the standard skew-normal distribution, while c() is chosen to be the inversion copula of the stochastic volatility model described in @inversion2018.
-The stochastic volatility inversion copula model used in this section allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns [@inversion2018].
-
-In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model and then adjust degrees of freedom and shape parameters of the true DGP specifications in Scenario (ii) and (iii).
-
-We apply the scoring rules introduced in Section 2.2 and set CLS to focus on 10%, 20%, 80% and 90% tails of the empirical marginal distribution, corresponding to the risks of long and short portfolios of financial investments, and we label them as CLS10, CLS20, CLS80 and CLS90 in following tables and figures.
-Due to the fact that there is no reliable estimate of the true conditional densities, only the tails of the marginal distributions are set to be the standard when assessing the predictive accuracy by CLS, rather than the conditional distributions.
-Meanwhile, MLE is included as a benchmark for comparing whether optimal forecasts can provide benefits or not, since MLE is asymptotically optimal and efficient under the correct model specification and regularity.
-Even though this property does not hold under misspecification, MLE can still give insights about how conventional likelihood-based methods perform.
-
-We conduct Monte Carlo simulations using the methodology in @optimal and @fbp2019. Specific steps are as follows:
-
-Let $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ be the one-step-ahead predictive distribution function based on the assumed model and optimized according to the scoring rule $S_i$, and $p(y_t|\mathcal{F}_{t-1},\boldsymbol{\theta})$ be the corresponding predictive density function at time $\mathcal{t}$.
-
-  1.	Generate T = 6000 observations for $y_t$ from the true DGP
-
-  2.	Use $y_{1:1000}$ to estimate $\boldsymbol{\hat \theta}^{[i]}$ in the assumed predictive model based on the positively oriented score $S_i$ where $\boldsymbol{\hat \theta}^{[i]} = \{\hat \mu, \hat \alpha_0, \hat \alpha_1\}^{[i]}$
-
-\begin{equation} \label{eq:theta}
-\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
-\end{equation}
-\begin{equation} \label{eq:score}
-\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S_i(P_{\boldsymbol\theta}^{t-1},y_t)
-\end{equation}
-  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to $\eqref{eq:LS}$ $\eqref{eq:CRPS}$ $\eqref{eq:CLS}$:^[The CRPS in $\eqref{eq:CRPS}$ is transformed to a positively-oriented score for the purpose of convenient comparison among all scores.]
-
-\begin{equation} \label{eq:LS}
-S_{LS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
-\end{equation}
-\begin{equation} \label{eq:CRPS}
-S_{CRPS}^*(P_{\boldsymbol\theta}^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
-\end{equation}
-\begin{equation} \label{eq:CLS}
-S_{CLS}(P_{\boldsymbol\theta}^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
-\end{equation}
-4.
-Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores:^[Out-of-sample size $\tau = 5000$ is sufficiently large to let the optimal forecasts take place; see @optimal for full discussion about sample size effects on optimal forecasts.]
-\begin{equation} \label{eq:avgscore}
-\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
-\end{equation}
-
-For the purpose of conveniently documenting and interpreting the results in the following sections consistently with previous literature, we introduce the concept of ‘coherence’ and ‘strict coherence’ here.
-Coherence means that the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score.
-Strict coherence happens when the optimal prediction is strictly preferable given that score.
-Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules:$S_1$ and $S_2$.
-The predictive density $S_n(P^{t-1}_{\boldsymbol{\hat \theta_n}},y_t)$ is said to be coherent if
-\begin{equation} \label{eq:coh1}
-\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
-\end{equation}
-\begin{equation} \label{eq:coh2}
-\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)
-\end{equation}
-It is said to be strictly coherent if $\eqref{eq:coh1}$ and $\eqref{eq:coh2}$ are strict inequalities [@optimal].
-
-## 3.2 Simulation results
-### 3.2.1 Average out-of-sample scores
-
-The first column of each of the following tables presents the labels for the $S_i$ that we used to produce predictions and the third-row shows $S_j$, which is used for the forecast's evaluation.
-The bolded numbers are the largest values of $\bar S_j(\boldsymbol{\hat \theta^{[i]}})$ in each column.
-We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the scoring rule indicated by the column name.
-
-Table 2 shows the correct model specification: Scenario (i) where the optimal forecasting method does not reap benefits and there is no strict coherence observed in the table.
-Under correct specification, both likelihood-based forecasts and optimal forecasts will have estimators concentrated to true parameter values, which causes no improvement in predictive accuracy by using optimal forecasting approach [@optimal].
-
-Table 3 shows the results of Scenario (ii) where the assumed predictive model, ARCH(1), cannot capture the fat tails and long term volatility clustering feature of the data generated from GARCH(1,1) models with Student-t error, i.e.
-the true DGP.
-Hence, there is misspecification.
-Table 3 replicates some parts of the simulation results in previous literature; see @fbp2019, @optimal.
-Optimal forecasts are expected to reap more benefits as the degree of model misspecification increases, and predictions based on CLS at 80% and 90% perform poorly when assessed by LS, CRPS, CLS at 10% and CLS at 20%.
-The question is whether these characteristics of optimal forecasts will change if we move to a different form of model misspecification.
-
-Table 4 shows another type of model misspecification listed in Scenario (iii) where the ARCH(1) model cannot capture the asymmetric feature of the data generated from copula models (the true DGP).
-Table 4 shows similar results as in Table 3.
-As the shape parameter decreases, the degree of negative marginal skewness increases, and optimal forecasts provide more benefits.
-Even though, strictly speaking, we do not observe strict coherence in Panel C, the most misspecified case, it is close enough to conclude that optimal forecasts perform in the same way even when we have different forms of model misspecification.
-^[Tables are produced by R package: @kableextra.]
-
 ```{r}
@@
 
-GARCH_t12 <- read.csv("GARCH_t12__table.csv")
+GARCH_t35 <- read.csv("data/GARCH35.csv")
+GARCH_t35 <- rename(GARCH_t35, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
+GARCH_t35$`In-sample optimizers`<-c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
+
+GARCH_t12 <- read.csv("data/GARCH_t12__table.csv")
 GARCH_t12 <- rename(GARCH_t12, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
@@
 
-GARCH_t3 <- read.csv("GARCH_t3_table.csv")
+GARCH_t3 <- read.csv("data/GARCH_t3_table.csv")
 GARCH_t3 <- rename(GARCH_t3, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
@@
 
-ARCH_table <- read.csv("ARCH_table.csv")
+ARCH_table <- read.csv("data/ARCH_table.csv")
 ARCH_table <- rename(ARCH_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
@@
 
-Copula5_table <- read.csv("Copula5_table.csv")
+Copula5_table <- read.csv("data/Copula5_table.csv")
 Copula5_table <- rename(Copula5_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
@@
 
-Copula3_table <- read.csv("Copula3_table.csv")
+Copula3_table <- read.csv("data/Copula3_table.csv")
 Copula3_table <- rename(Copula3_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
@@
 
-Copula0_table <- read.csv("Copula0_table.csv")
+Copula0_table <- read.csv("data/Copula0_table.csv")
 Copula0_table <- rename(Copula0_table, "In-sample optimizers" = Row, "CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
@@
 
-```{r}
-GARCH_t12 <- GARCH_t12 %>% 
+*Table 3: It corresponds to Scenario (ii) where the assumed predictive model is ARCH(1) with Gaussian error and the true DGP is GARCH(1,1) with Student-t error*
+
+```{r}
+GARCH_t35 <- GARCH_t35 %>% 
   mutate(
@@
 
-GARCH_t3 <- GARCH_t3 %>% 
+GARCH_t12 <- GARCH_t12 %>% 
   mutate(
@@
   )
-garch <- rbind(GARCH_t12,GARCH_t3)
+
+GARCH_t3 <- GARCH_t3 %>% 
+  mutate(
+    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
+    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
+    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
+    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
+    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
+    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
+  ) 
+garch <- rbind(GARCH_t35,GARCH_t12,GARCH_t3)
 
@@
   kable_styling("bordered",full_width = F) %>%
-  pack_rows("Panel A: degree of freedom = 12", 1,6) %>%
-  pack_rows("Panel B: degree of freedom = 3", 7,12) %>%
+  pack_rows("Panel A: degree of freedom = 35", 1,6) %>%
+  pack_rows("Panel B: degree of freedom = 12", 7,12) %>%
+  pack_rows("Panel C: degree of freedom = 3",13,18) %>%
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
@@
 ```
+
+*Table 4: It corresponds to Scenario (iii) where the assumed model is ARCH(1) with Gaussian error and the true DGP is stochastic volatility inversion copula.*
 
@@
 
-### 3.2.2 Trace plots & predictive density
-
-The predictive accuracy of tails is important for financial risk management.
+### 3.2.2 Trace plots & predictive densities
+
+Accurate prediction of extreme values is important for financial risk management.
 Therefore, we provide score trace plots to exhibit the comparison of MLE, CRPS and CLS’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails.
-The results in Section 3.2.1 shows that when the degree of model misspecification is high, CLS can perform the best compared with MLE and CRPS in predicting both tails.
+The results in Section 3.2.1 show that when the degree of model misspecification is high, CLS can perform the best compared with MLE and CRPS in predicting both tails.
 However, only the average score values at the end of each iteration of the simulation are recorded in the tables, while trace plots provide a dynamic view of how optimal forecasts perform.
@@
 The right panel shows the same thing but is based on the performance of predicting 90 percentile.
-From panels (a) and (b) in Figures 1 and 2, we could see that CLS almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, CLS starts to outperform CRPS and MLE in predicting tails.
+From panels (a) and (b) in Figures 1 and 2, we can see that CLS almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as the misspecification increases, CLS starts to outperform CRPS and MLE in predicting tails.
 The more misspecified the model is, the more benefits can we gain from using CLS.
-Besides, more improvement of predictive accuracy in the upper tail than in the lower tail, especially in Figure 2 where we have a negative skewed marginal distribution.
-This result is consistent with @fbp2019.
+Furthermore, more improvement in predictive accuracy occurs in the upper tail than in the lower tail, especially in Figure 2 where we have a negatively skewed marginal distribution.
+This result is consistent with @fbp2020.
 It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.
@@
 # need to adjust the size. 
-knitr::include_graphics("figure1.pdf")
-```
-
-```{r}
-knitr::include_graphics("figure 2.pdf")
-```
-
-From the average out-of-sample score tables and trace plots above, we can see that optimal forecasts provide most benefits in improving prediction accuracy under the most misspecified case.
+knitr::include_graphics("figure/figure1.pdf")
+```
+
+```{r}
+knitr::include_graphics("figure/figure 2.pdf")
+```
+
+From the average out-of-sample score tables and trace plots above, we can see that optimal forecasts provide the most benefits in improving prediction accuracy under the most misspecified case.
 In order to provide a more complete view of how optimal forecasts work, the predictive densities of the most misspecified case are plotted in Figure 3.
 The shape of true conditional predictive distributions plays a role in deciding how much we can gain by using optimal forecasts, since predictions obtained from optimizing CLS aim to match the shape of tails of the true conditional predictive distributions.
-And CLS focusing on upper tails (80%, 90%) is expected to perform poorly in the lower tail so the forecasters should have a clear expectation about what they aim to achieve [@fbp2019].
+CLS focusing on upper tails (80%, 90%) is expected to perform poorly in the lower tail so the forecasters should have a clear expectation about what they aim to achieve [@fbp2020].
 However, in practice, the shape of true conditional predictive distributions is usually unknown and it might create the difficulty of determining which tail we can reap more benefits from optimal forecasts without analysing a particular problem beforehand.
@@
 ```{r,fig.align="center"}
-knitr::include_graphics("figure_pred.pdf")
+knitr::include_graphics("figure/figure_pred.pdf")
 ```
@@
 
-From the results in Section 3.2, we can conclude that optimal forecasts based on the censored likelihood score can improve the prediction accuracy in tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification.
+From the results in Section 3.2, we can conclude that optimal forecasts based on the CLS can improve the prediction accuracy in tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification.
 In Section 4, we apply the same method adopted in Section 3 to an empirical setting and investigate how it performs in practice.
@@
 
-The descriptive statistics show that the distribution of S&P 500 log returns is negatively skewed and has fat tails and strong serial correlation in its volatility.
-Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.
+The descriptive statistics in Table 5 show that the distribution of S&P 500 log returns is negatively skewed and has fat tails and strong serial correlation in its volatility.
+Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.^[Descriptive statistics are produced by R packages: @dplyr, @tidyverse, @tsibble, @tsibbledata, @feasts, @normtest, @moments.]
 
@@
 
-From the wide-usage of ARCH models in modelling financial returns and volatility, and the strict coherence observed in Section 3.2.1, ARCH(1) should be a ‘compatible’ and sufficiently misspecified model to forecast S&P 500 series.
-The results in Table 8 show that the CLS outperforms other alternative scores in both lower and upper tails, which closely follows the results and conclusions drawn in the numerical analysis in Section 3.
+From the wide-usage of ARCH models in modelling financial returns and volatility, and the strict coherence observed in Section 3.2.1, ARCH(1) should be a ‘compatible’ and sufficiently misspecified model to forecast S&P 500 series and to observe the difference made by adopting optimal forecasts.
+The results in Table 6 show that the CLS outperforms other alternative scores in both lower and upper tails, which closely follows the results and conclusions drawn in the numerical analysis in Section 3.
 However, the difference between using CLS10(80) and CLS20(90) is very small.
@@
 ```{r}
-sp_table <- read.csv("sp_table.csv")
+sp_table <- read.csv("data/sp_table.csv")
 sp_table <- rename(sp_table, "In-sample optimizers" = Row,"CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
@@
 Unlike in the simulation example, the score trace plots now show how different scoring rules perform at time points that correspond to some actual historical events.
-In Figure 5, one interesting phenomenon is that after the GFC, the censored likelihood score performs much better than CRPS and MLE, in terms of predicting both upper and lower tails.
+In Figure 5, one interesting phenomenon is that after the GFC, the CLS performs much better than CRPS and MLE, in terms of predicting both upper and lower tails.
 It indicates that optimal probabilistic forecasts based on CLS can predict extreme events, such as the GFC, more accurately than other alternatives.
@@
 The difference between CLS and MLE/CRPS gets smaller and smaller over time until the recent COVID-19 pandemic.
-It is also worth noticing that CLS does not appear to provide more benefits in the upper tail than in the lower tail, which is different from the simulation results.
+It is also worth noticing that CLS does not appear to provide more benefits in the upper tail than in the lower tail, which is different from the simulation results.^[The figures are produced by R packages: @ggplot2, @ggthemes, @ggpubr.]
 
@@
 # this is assessed by cls10 for prediction accuracy
-trace_fsr10 <- read.csv("fsr10.csv")
+trace_fsr10 <- read.csv("data/fsr10.csv")
 trace_fsr10 <- trace_fsr10 %>% rename("CLS10"=FSR10)
-trace_fsr20 <- read.csv("fsr20.csv")
+trace_fsr20 <- read.csv("data/fsr20.csv")
 trace_fsr20 <- trace_fsr20 %>% rename("CLS20"=FSR20)
-trace_10ls <- read.csv("fsr10_ls.csv")
-trace_10crps <- read.csv("fsr10_crps.csv")
+trace_10ls <- read.csv("data/fsr10_ls.csv")
+trace_10crps <- read.csv("data/fsr10_crps.csv")
 
@@
 
-color1 <- c("CLS10"="red","CLS20"="black","MLE"="purple","CRPS"="green")
+color1 <- c("CLS10"="blue","CLS20"="red","MLE"="green","CRPS"="black")
 
@@
 # plot scores --- upper tail 
-trace_fsr90 <- read.csv("fsr90.csv")
+trace_fsr90 <- read.csv("data/fsr90.csv")
 trace_fsr90 <- trace_fsr90 %>% rename("CLS90"=FSR90)
-trace_fsr80 <- read.csv("fsr80.csv")
+trace_fsr80 <- read.csv("data/fsr80.csv")
 trace_fsr80 <- trace_fsr80 %>% rename("CLS80"=FSR80)
-trace_90ls <- read.csv("fsr90_ls.csv")
-trace_90crps <- read.csv("fsr90_crps.csv")
+trace_90ls <- read.csv("data/fsr90_ls.csv")
+trace_90crps <- read.csv("data/fsr90_crps.csv")
 
@@
 
-color2 <- c("CLS90"="red","CLS80"="black","MLE"="purple","CRPS"="green")
+color2 <- c("CLS90"="blue","CLS80"="red","MLE"="green","CRPS"="black")
 
@@
 ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 5(a) CLS10","Figure 5(b) CLS90")) + 
-  labs(caption = "Figure 5: the predictive distributions of S&P 500 are produced by the ARCH(1)") +
+  labs(caption = "Figure 5: the predictive distributions are produced by ARCH(1) with Gaussian error term") +
   theme(plot.caption = element_text(hjust = 0))
@@
 Density forecasts have great practical value in finance.
-They form the foundation of risk management, such as Value-at-Risk and are useful for asset allocation and derivative pricing.
+They form the foundation of risk management, such as Value-at-Risk, and are useful for asset allocation and derivative pricing.
 VaR is a commonly used risk measurement in finance.
 It can be obtained from a probability density function of returns over a chosen investment horizon.
-It is the p-quantile ($q_p$) of a predictive distribution of a portfolio’s returns over a holding period, according to a given confidence interval $\alpha$ [@dowd2007].
+It is the *p*th quantile ($q_p$) of a predictive distribution of a portfolio’s returns over a holding period, according to a given confidence interval $\alpha$ [@dowd2007].
 \begin{equation} \label{eq:var}
@@
 
-@opschoor2017 combine density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the censored likelihood score outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.
+@opschoor2017 combine density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the CLS outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.
 
@@
 The closer the proportion of exceedances, calculated in Step 3, to nominal VaR levels, the more accurate are VaR predictions and thus, the more accurate are the optimal probabilistic forecasts.
-An accurate prediction of the $\mathcal{p}$ % VaR is observed if the proportion of exceedances equals $\mathcal{p}$ %.
-
-Starting from the two different forms of model misspecification investigated in simulation analysis (Section 3), the values showed in the Table 9 and 10 refer to the out-of-sample proportion of exceedances over the nominal VaR level indicated by the column name.
-The censored likelihood score can provide the most accurate VaR prediction in the upper tail, while in the lower tail, it is not short of advantages by too much compared with CRPS.
-This conclusion does not vary much when we have different forms of model misspecification as illustrated in the Table 9 and 10.
-
-```{r}
-copula5var <- read.csv("copula5var.csv")
+An accurate prediction of the $p$% VaR is observed if the proportion of exceedances equals $p$%.
+
+Starting from the two different forms of model misspecification investigated in simulation analysis (Section 3), the values showed in the Table 7 and 8 refer to the out-of-sample proportion of exceedances over the nominal VaR level indicated by the column name.
+The CLS can provide the most accurate VaR prediction in the upper tail, while in the lower tail, it is not short of advantages by too much compared with CRPS.
+This conclusion does not vary much when we have different forms of model misspecification as illustrated in the Table 7 and 8.
+
+*Table 7: The predictive distributions are produced by ARCH(1) with Gaussian error while the true DGP is stochastic volatility inversion copula with the highest negative marginal skewness in our simulation.
+The values show the out-of-sample exceedances of each optimizer.*
+
+```{r}
+copula5var <- read.csv("data/copula5var.csv")
 
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 7: the true DGP is copula (shape = -5)"=5))
-```
-
-```{r}
-garch3var <- read.csv("garch3var.csv")
+  add_header_above(c("Table 7: the true DGP is stochastic volatility inversion copula (shape = -5)"=5))
+```
+
+*Table 8: The predictive distributions are produced by ARCH(1) with Gaussian error and the true DGP is GARCH(1,1) with Student-t error where $t_\nu$ = 3.
+The values show the out-of-sample exceedances of each optimizer.*
+
+```{r}
+garch3var <- read.csv("data/garch3var.csv")
 
@@
 We now implement the VaR analysis to continuously compounded daily log returns of S&P 500 in U.S.A financial market.
-Learning from the trace plots in Section 4.2, the 2008 GFC is the turning point of the optimal forecasts' performance, especially for the censored likelihood scores.
+Learning from the trace plots in Section 4.2, the 2008 GFC is the turning point of the optimal forecasts' performance, especially for the CLS.
 Therefore, we perform the VaR analysis over two different time periods, before the GFC and after the GFC.
-The results from Table 11 and 12 show that the censored likelihood score perform well enough in terms of estimating VaR for both long and short portfolios of S&P 500, but also CRPS is a very robust scoring rule which can provide relatively accurate predictions.
-Moreover, in Table 12, the censored likelihood score seems to perform better in 20% and 80% tails which have higher probability mass than 10% and 90% tails.
+The results from Table 9 and 10 show that the CLS perform well enough in terms of estimating VaR for both long and short portfolios of S&P 500, but also CRPS is a very robust scoring rule which can provide relatively accurate predictions.
+Moreover, in Table 10, the CLS seems to perform better in 20% and 80% tails which have higher probability mass than 10% and 90% tails.
 If we think of the marginal distribution of S&P 500 estimated by histogram in Figure 4.B, the above results could be a consequence of the very sparse marginal distribution or simply because there is no enough data in the tails to produce an accurate estimate of the CLS optimizer, which increases the difficulty of 'focusing' on the 10% and 90% tails.
 
-```{r}
-spvar <- read.csv("spvar1_table.csv")
+*Table 9: The estimation of VaR through out-of-sample exceedances is based on predictive distributions produced by ARCH(1) with Gaussian error.
+This table shows the VaR prediction of S&P 500 before the GFC.*
+
+```{r}
+spvar <- read.csv("data/spvar1_table.csv")
 
@@
 
-# formattable(df,list(VaR_0.1 = max_bold1,VaR_0.2 = max_bold2,VaR_0.8 = max_bold8,VaR_0.9 = max_bold9))
-```
-
-```{r}
-spvar <- read.csv("spvar2_table.csv")
+```
+
+*Table 10: The estimation of VaR through out-of-sample exceedances is based on predictive distributions produced by ARCH(1) with Gaussian error.
+This table shows the VaR prediction of S&P 500 after the GFC.*
+
+```{r}
+spvar <- read.csv("data/spvar2_table.csv")
 spvar <- round(spvar,digits = 4)
@@
 ## 5.2 Preliminary diagnostics
-We collect daily VIX index data starting from 27 Aug,1996 to 30 July,2020.^[Data retrieved from @vixdata] The descriptive statistics of $log(VIX_t)$ are shown in Table 13 and Figure 6:
-
-Table 13 and Figure 6 show that $log(VIX_t)$ is volatile and shows strong persistence over time.
+We collect daily VIX index data starting from 27 Aug,1996 to 30 July,2020.^[Data retrieved from @vixdata] The descriptive statistics of $log(VIX_t)$ are shown in Table 11 and Figure 6:
+
+Table 11 and Figure 6 show that $log(VIX_t)$ is volatile and shows strong persistence over time.
 It is positively skewed and the autocorrelation of its volatility is slowly decaying.
@@
 Similarly, there are unusual jumps happened during the GFC and the COVID-19.
-Thus, we expect that the censored likelihood score could outperform MLE and CRPS in predicting tails as in Section 4.2 and significantly improve accuracy after the GFC.
+Thus, we expect that the CLS could outperform MLE and CRPS in predicting tails as in Section 4.2 and significantly improve accuracy after the GFC.
 
@@
 $z_{t+1} \sim Student-t(0,1,\nu)$ and constant $\sigma$ ^[We specify $z_{t+1}$ as standardised Student-t distribution so that $\sigma^2$ can reflect the variance of the predicted VIX series.
-The CRPS is removed in Specification 2 and 4, since there is no closed form for this score.]
+The CRPS is removed in Specification 2 and 4, since there is no closed form for this score.
+@crpst2016 provides a way to evaluate CRPS for Student-t distribution numerically.]
 
@@
 Section 5.4.1 provides the result of Specification 1 where the predictive density of the VIX is the normal distribution with a constant variance.
-In Table 14, CLS performs better in predicting the upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
+In Table 12, CLS performs better in predicting the upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
 The score trace plot, Figure 7, shows the predictions of optimizing four scoring rules evaluated by CLS10 (left panel) and CLS90 (right panel).
@@
 
-```{r}
-vix_table <- read.csv("vix_table.csv")
+*Table 12: The predictive distributions for VIX are produced by HAR-RV model with Gaussian error and constant volatility.*
+
+```{r}
+vix_table <- read.csv("data/vix_table.csv")
 vix_table <- rename(vix_table, "In-sample optimizers" = Row,"CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
@@
 # this the accuracy assessed by fsr10
-trace_fsr10 <- read.csv("vixfsr10.csv")
+trace_fsr10 <- read.csv("data/vixfsr10.csv")
 trace_fsr10 <- trace_fsr10 %>% rename("CLS10"=FSR10)
-trace_fsr20 <- read.csv("vixfsr20.csv")
+trace_fsr20 <- read.csv("data/vixfsr20.csv")
 trace_fsr20 <- trace_fsr20 %>% rename("CLS20"=FSR20)
-trace_10ls <- read.csv("vixfsr10_ls.csv")
-trace_10crps <- read.csv("vixfsr10_crps.csv")
+trace_10ls <- read.csv("data/vixfsr10_ls.csv")
+trace_10crps <- read.csv("data/vixfsr10_crps.csv")
 
@@
 # plot scores --- upper tail (assessed by fsr90)
-trace_fsr90 <- read.csv("vixfsr90.csv")
+trace_fsr90 <- read.csv("data/vixfsr90.csv")
 trace_fsr90 <- trace_fsr90 %>% rename("CLS90"=FSR90)
-trace_fsr80 <- read.csv("vixfsr80.csv")
+trace_fsr80 <- read.csv("data/vixfsr80.csv")
 trace_fsr80 <- trace_fsr80 %>% rename("CLS80"=FSR80)
-trace_90ls <- read.csv("vixfsr90_ls.csv")
-trace_90crps <- read.csv("vixfsr90_crps.csv")
+trace_90ls <- read.csv("data/vixfsr90_ls.csv")
+trace_90crps <- read.csv("data/vixfsr90_crps.csv")
 
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) CLS10","Figure 7(b) CLS90"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) CLS10","Figure 7(b) CLS90"))+ 
+  labs(caption = "Figure 7: the predictive distributions are produced by HAR-RV model with Gaussian error and constant volatility") +
+  theme(plot.caption = element_text(hjust = 0))
 
@@
 Moving from Specification 1 to Specification 2, fatter tails are allowed in the predictive distribution and thus, the assumed model is less misspecified.
-Table 15 and Figure 8 show consistent performance of optimal forecasts compared with our investigations of simulated data and S&P 500 returns.
+Table 13 and Figure 8 show consistent performance of optimal forecasts compared with our investigations of simulated data and S&P 500 returns.
 That is, improvement of prediction accuracy by using CLS is still observed in the upper tail but the amount of improvement decreases as the degree of misspecification decreases.
 
-```{r}
-vix_table <- read.csv("vix_table_st.csv")
+*Table 13: The predictive distributions for VIX are produced by HAR-RV model with Student-t error and constant volatility.*
+
+```{r}
+vix_table <- read.csv("data/vix_table_st.csv")
 vix_table <- rename(vix_table, "In-sample optimizers" = Row,"CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
@@
 # to compress all the calculated plotting average scores together in the same df 
-trace_fsr10 <- read.csv("vixfsr10_st.csv")
+trace_fsr10 <- read.csv("data/vixfsr10_st.csv")
 trace_fsr10 <- trace_fsr10 %>% rename("CLS10"=FSR10)
-trace_fsr20 <- read.csv("vixfsr20_st.csv")
+trace_fsr20 <- read.csv("data/vixfsr20_st.csv")
 trace_fsr20 <- trace_fsr20 %>% rename("CLS20"=FSR20)
-trace_10ls <- read.csv("vixfsr10_ls_st.csv")
+trace_10ls <- read.csv("data/vixfsr10_ls_st.csv")
 #trace_10crps <- read.csv("vixfsr10_crps.csv")
@@
 
-color1 <- c("CLS10"="red","CLS20"="black","MLE"="purple")
+color1 <- c("CLS10"="blue","CLS20"="red","MLE"="green")
 
@@
 # plot scores --- upper tail 
-trace_fsr90 <- read.csv("vixfsr90_st.csv")
+trace_fsr90 <- read.csv("data/vixfsr90_st.csv")
 trace_fsr90 <- trace_fsr90 %>% rename("CLS90"=FSR90)
-trace_fsr80 <- read.csv("vixfsr80_st.csv")
+trace_fsr80 <- read.csv("data/vixfsr80_st.csv")
 trace_fsr80 <- trace_fsr80 %>% rename("CLS80"=FSR80)
-trace_90ls <- read.csv("vixfsr90_ls_st.csv")
+trace_90ls <- read.csv("data/vixfsr90_ls_st.csv")
 #trace_90crps <- read.csv("vixfsr90_crps_st.csv")
@@
 
-color2 <- c("CLS90"="red","CLS80"="black","MLE"="purple")
+color2 <- c("CLS90"="blue","CLS80"="red","MLE"="green")
 
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) CLS10","Figure 8(b) CLS90"))
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) CLS10","Figure 8(b) CLS90"))+ 
+  labs(caption = "Figure 8: the predictive distributions are produced by HAR-RV model with Student-t error and constant volatility") +
+  theme(plot.caption = element_text(hjust = 0))
 ```
@@
 
-```{r}
-vix_table <- read.csv("vix_table_garch.csv")
+Specification 3 and 4 move from the constant variance of the predictive distribution to the time-varying variance, which is better specified since strong serial correlation of the volatility is observed in the VIX series as shown in Figure 6.C.
+Table 14 and Figure 9 illustrate the performance of optimal forecasts in Specification 3.
+The amount of improvement decreased very slightly, compared with results of Specification 1 which also specifies a Gaussian error term.
+Similar conclusions can be drawn from comparing Table 15 and Figure 10 with the results of Specification 2.
+However, overall, as the model becomes less misspecified, we gain less from optimal forecasts in predicting the upper tail of VIX.
+
+*Table 14: The predictive distributions for VIX are produced by HAR-RV model with Gaussian error and time-varying volatility which is modelled by ARCH(1).*
+
+```{r}
+vix_table <- read.csv("data/vix_table_garch.csv")
 vix_table <- rename(vix_table, "In-sample optimizers" = Row,"CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
@@
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 14: Average scores for the VIX with ARCH normal error"=7))
+  add_header_above(c("Table 14: Average scores for the VIX with ARCH Gaussian error"=7))
 ```
@@
 # to compress all the calculated plotting average scores together in the same df 
-trace_fsr10 <- read.csv("vixfsr10_garch.csv")
+trace_fsr10 <- read.csv("data/vixfsr10_garch.csv")
 trace_fsr10 <- trace_fsr10 %>% rename("CLS10"=FSR10)
-trace_fsr20 <- read.csv("vixfsr20_garch.csv")
+trace_fsr20 <- read.csv("data/vixfsr20_garch.csv")
 trace_fsr20 <- trace_fsr20 %>% rename("CLS20"=FSR20)
-trace_10ls <- read.csv("vixfsr10_ls_gar.csv")
-trace_10crps <- read.csv("vixfsr10_crps_gar.csv")
+trace_10ls <- read.csv("data/vixfsr10_ls_gar.csv")
+trace_10crps <- read.csv("data/vixfsr10_crps_gar.csv")
 
@@
 # plot scores --- upper tail 
-trace_fsr90 <- read.csv("vixfsr90_gar.csv")
+trace_fsr90 <- read.csv("data/vixfsr90_gar.csv")
 trace_fsr90 <- trace_fsr90 %>% rename("CLS90"=FSR90)
-trace_fsr80 <- read.csv("vixfsr80_gar.csv")
+trace_fsr80 <- read.csv("data/vixfsr80_gar.csv")
 trace_fsr80 <- trace_fsr80 %>% rename("CLS80"=FSR80)
-trace_90ls <- read.csv("vixfsr90_ls_gar.csv")
-trace_90crps <- read.csv("vixfsr90_crps_gar.csv")
+trace_90ls <- read.csv("data/vixfsr90_ls_gar.csv")
+trace_90crps <- read.csv("data/vixfsr90_crps_gar.csv")
 
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) CLS10","Figure 9(b) CLS90"))
-
-```
-
-```{r}
-vix_table <- read.csv("vix_table_gst.csv")
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) CLS10","Figure 9(b) CLS90"))+ 
+  labs(caption = "Figure 9: the predictive distributions are produced by HAR-RV model with Gaussian error and time-varying volatility") +
+  theme(plot.caption = element_text(hjust = 0))
+
+```
+
+*Table 15: The predictive distributions for VIX are produced by HAR-RV model with Student-t error and time-varying volatility which is modelled by ARCH(1).*
+
+```{r}
+vix_table <- read.csv("data/vix_table_gst.csv")
 vix_table <- rename(vix_table, "In-sample optimizers" = Row,"CLS10" = FSR10, "CLS20"=FSR20, "CLS80"=FSR80,"CLS90"=FSR90)
@@
 # to compress all the calculated plotting average scores together in the same df 
-trace_fsr10 <- read.csv("vixfsr10_gst.csv")
+trace_fsr10 <- read.csv("data/vixfsr10_gst.csv")
 trace_fsr10 <- trace_fsr10 %>% rename("CLS10"=FSR10)
-trace_fsr20 <- read.csv("vixfsr20_gst.csv")
+trace_fsr20 <- read.csv("data/vixfsr20_gst.csv")
 trace_fsr20 <- trace_fsr20 %>% rename("CLS20"=FSR20)
-trace_10ls <- read.csv("vixfsr10_ls_gst.csv")
+trace_10ls <- read.csv("data/vixfsr10_ls_gst.csv")
 #trace_10crps <- read.csv("vixfsr10_crps.csv")
@@
 # plot scores --- upper tail 
-trace_fsr90 <- read.csv("vixfsr90_gst.csv")
+trace_fsr90 <- read.csv("data/vixfsr90_gst.csv")
 trace_fsr90 <- trace_fsr90 %>% rename("CLS90"=FSR90)
-trace_fsr80 <- read.csv("vixfsr80_gst.csv")
+trace_fsr80 <- read.csv("data/vixfsr80_gst.csv")
 trace_fsr80 <- trace_fsr80 %>% rename("CLS80"=FSR80)
-trace_90ls <- read.csv("vixfsr90_ls_gst.csv")
+trace_90ls <- read.csv("data/vixfsr90_ls_gst.csv")
 #trace_90crps <- read.csv("vixfsr90_crps.csv")
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 10(a) CLS10","Figure 10(b) CLS90"))
-
-```
-
-Specification 3 and 4 move from the constant variance of the predictive distribution to the time-varying variance, which is better specified since strong serial correlation of the volatility is observed in the VIX series as shown in Figure 6.C.
-Table 16 and Figure 9 illustrate the optimal forecast performance in Model specification 3.
-The amount of improvement decreased very slightly, compared with results of Specification 1 which also specifies a normal error term.
-Similar conclusions can be drawn from comparing Table 17 and Figure 10 with the results of Specification 2.
-
-The above comparisons indicate that the amount of improvement of prediction accuracy might mainly depend on how the shape of predictive density matches the shape of true density.
-Moreover, the significant improvement of prediction accuracy in the upper tail brings great values in financial applications.
-Firstly, high values of the VIX indicates that the stock market is expected to be more volatile (high volatility), which is an opportunity for either long or short position investors to gain profits or hedge risks, since no one can make money if the stock price doesn’t change at all.
-Besides, investors are typically risk averse, which makes the higher risk (upper tail) is more a concern or an interest to them, compared with the lower risk (lower tail).
-At last, CBOE provides futures contracts written on the VIX, and higher volatility indicates higher price of futures contracts.
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 10(a) CLS10","Figure 10(b) CLS90"))+ 
+  labs(caption = "Figure 10: predictive distributions are produced by HAR-RV model with Student-t error and time-varying volatility") +
+  theme(plot.caption = element_text(hjust = 0))
+
+```
+
+Comparing the results obtained in VIX prediction with the results in returns prediction, it indicates that the amount of improvement of prediction accuracy might mainly depend on how the shape of predictive density matches the shape of true density or how misspecified the assumed predictive model is in terms of predicting the tails.
+
+Even though optimal forecasts can only reap significant benefits in the upper tail of the VIX prediction, there is still great practical value in finance.
+Firstly, by definition, high values of the VIX indicates that the S&P 500, or the stock market in general, is expected to be more volatile (high volatility), which is an opportunity for either long or short position investors to gain profits or hedge risks, since no one can make money if the stock price doesn’t change at all.
+Besides, investors are typically risk averse, which makes the higher risk (the upper tail) is more of an interest to them, compared with the lower risk (the lower tail).
+More importantly, volatility is treated as an asset class and market participants are provided with liquid volatility products to trade in the market.
+For example, @cboefutures introduces futures contracts written on the VIX Index and a better prediction of VIX could be helpful for better futures pricing.
+Besides, there is literature discussing VIX futures and trading strategies based on different volatility forecasting techniques like in @vixfutures2020.
+Our results will make a contribution to the literature in this field as well.
 
@@
 According to the numerical and empirical results, the benefits of optimal forecasts can be observed when we have model misspecification, subject to the assumed predictive model is compatible, and their performance does not vary between two different types of model misspecification investigated in this paper.
-By mainly focusing on investigating the tail performance of optimal forecasts, the results show that the more misspecified the model is, the more benefits can be gained from using the censored likelihood score in improving the tail prediction accuracy in comparison with the conventional likelihood-based counterparts.
+By mainly focusing on investigating the tail performance of optimal forecasts, the results show that the more misspecified the model is, the more benefits can be gained from using the CLS in improving the tail prediction accuracy in comparison with the conventional likelihood-based counterparts.
 This result is particularly in evidence after the stock market turbulence in both financial returns and the VIX index.
@@
 More importantly, the reasons why we can gain considerably from optimal forecasts after the GFC needs further investigation.
-
 Nevertheless, the results in this paper provide important insights to the financial forecasting literature.
 In terms of financial returns, optimal forecasts can give better VaR predictions when it comes to the VIX index, the improvement of predictive accuracy in the upper tail - which indicates that higher volatility in the market is more accurately predicted - is an important contribution to literature on hedging risks and trading derivatives in financial market.
-
-# References

### 2020-10-15 Final.Rmd
fixed vix trace plot date error

@@
 fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
-  geom_line(aes(y = CLS10,color = "CLS10"),size=0.25)+
-  geom_line(aes(y = CLS20,color = "CLS20"),size=0.25)+
-  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
-  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
+  geom_line(aes(y = CLS10,color = "CLS10"),size=0.3,linetype = "dashed")+
+  geom_line(aes(y = CLS20,color = "CLS20"),size=0.5,linetype = "dotted")+
+  geom_line(aes(y = MLE,color = "MLE"),size=0.3,linetype = "solid")+
+  geom_line(aes(y = CRPS,color = "CRPS"),size=0.3, linetype = "longdash")+
   labs(x="Year",y="Average Scores",color="legend")+
@@
 
-fsr10 <- fsr10 %>% mutate(Date = vix$Date[1001:6000])
+fsr10 <- fsr10 %>% mutate(Date = logvix$Date[1001:6000])
 
@@
 
-fsr90 <- fsr90 %>% mutate(Date = vix$Date[1001:6000])
+fsr90 <- fsr90 %>% mutate(Date = logvix$Date[1001:6000])
 

### 2020-10-30 Final.Rmd
fixed the body paragraph of the thesis.

@@
   - \usepackage{float}
+  - \usepackage[bottom]{footmisc}
 fontsize: 12pt
@@
 
-\pagebreak
+\newpage
 
@@
 Results show that the greater the degree of model misspecification, the more beneficial is optimal prediction, no matter what the form of model misspecification.
-Most notably, predictions that are optimal according to the censored likelihood score, which rewards predictive accuracy in a tail are substantially more accurate at predicting extreme events in said tail than the alternatives, including likelihood-based predictions.
-
-\pagebreak
+Most notably, predictions that are optimal according to the censored likelihood score, which rewards predictive accuracy in a tail are substantially more accurate at predicting extreme events in said tail than the alternatives, including likelihood-based predictions.^[I would like to thank my supervisors: Professor Gael Martin and Dr.
+Ruben Loaiza-Maya, for the very constructive and detailed comments on my thesis and their support and help during this particularly difficult year.]
+
+\newpage
 
@@
 \begin{equation} \label{eq:sbar}
-\bar S = \frac{1}{T-\tau+1}\sum_{t=2}^{T-\tau} S(P_{\boldsymbol{\theta}}^{t-1},y_t)
+\bar S = \frac{1}{T-(\tau+1)}\sum_{t=2}^{T-\tau} S(P_{\boldsymbol{\theta}}^{t-1},y_t)
 \end{equation}
@@
 Specific simulation scenarios are listed in Table 1 ($t_\nu$ indicates a Student-t distribution with $\nu$ degrees of freedom).
-
-*Table 1: The three simulation scenarios used in the numerical analysis.
-Scenario (i) represents correct model specification; Scenario (ii) represents a form of misspecification where the true DGP is GARCH with Student-t distribution while the assumed model is Gaussian ARCH(1); Scenario (iii) represents a more extreme form of misspecification, where the true DGP is an stochastic volatility model with a non-Gaussian marginal distribution while the assumed model is Gaussian ARCH(1).*
 
@@
 
-\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ \\ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ \\ \hline
+\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ \\ & $\sigma_t^2 = \alpha_0 + \alpha_1 (y_{t-1}-\mu)^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 (y_{t-1}-\mu)^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 (y_{t-1}-\mu)^2$ \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ \\ \hline
 \end{tabular}}
+\caption{The three simulation scenarios used in the numerical analysis.
+Scenario (i) represents correct model specification; Scenario (ii) represents a form of misspecification where the true DGP is GARCH with Student-t distribution while the assumed model is Gaussian ARCH(1); Scenario (iii) represents a more extreme form of misspecification, where the true DGP is an stochastic volatility model with a non-Gaussian marginal distribution while the assumed model is Gaussian ARCH(1).}
 \end{table}
@@
 
-Copula models are a flexible way of representing the joint distribution function of a set of variables [@fan2014].
-In recent years, these models have been applied to modelling serial dependence, which can be constructed as:
+Copulas are functions that describe the dependence between random variables or the serial dependence.
+Copula theory allows one to decompose the joint density of dependent random variables to the product of the marginal densities and the ‘copula density’ denoted as $c(\cdot)$, where the dependent structure is completely described by ‘copula density’.
+Since the marginal density and the copula does not require to be from the same family of distributions, it makes the choice of marginal density more flexible when one uses the copula-based models [@fan2014].
+In this simulation, we aim to have a true DGP that captures two main features of financial returns – the volatility clustering and negative skewness in the marginal distribution.
+Thus, we only consider the use of copula in describing the serial dependence.
+Then the ‘decomposition’ can be represented as:
 \begin{equation} \label{eq:copula}
@@
 \end{equation}
-where $\mathit{P}()$ and $\mathit{p}$() denote the marginal distribution and density function of $y_t$ respectively, and c() is the copula density function that captures the dependence between $y_t$ and $y_{t-1}$.
-
-For the simulation exercise, the marginal distribution $\mathit{P}()$ is chosen to be the standard skew-normal distribution, while c() is chosen to be the inversion copula of the stochastic volatility model described in @inversion2018.
+where $\mathit{P}()$ and $\mathit{p}$() denote the marginal distribution and density function of $y_t$ respectively.
+
+Specifically, it is the stochastic volatility inversion copula model used in the simulation Scenario (iii).
+The marginal distribution $\mathit{P}()$ is chosen to be the standard skew-normal distribution, while $c(\cdot)$ is chosen to be the inversion copula of the stochastic volatility model described in @inversion2018.
 The stochastic volatility inversion copula model allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns [@inversion2018].
@@
 Due to the fact that there is no reliable estimate of the true conditional densities, only the tails of the marginal distributions are set to be the standard when assessing the predictive accuracy by CLS, rather than the conditional distributions.
-Meanwhile, LS gives insights about the performance of the conventional likelihood-based methods and is used as a benchmark for comparing whether optimal forecasts can provide benefits or not.
+Meanwhile, LS gives insights about the performance of the conventional likelihood-based methods and is used as a benchmark for comparing whether forecasts that are optimal according to alternative scoring rules can provide benefits or not.
 
@@
 Tables 2 and 3 replicate some parts of the simulation results in previous literature; see @fbp2020, @optimal.
+In Panels A and B of Table 3, when the degree of model misspecification is relatively low, the six optimizers cannot produce distinguishable enough probabilistic predictions to yield significantly different out-of-sample performance.
+There is no strict coherence observed.
+As the degree of model misspecification increases, in Panel C, the strict coherence is observed.
+The ARCH(1) model with Gaussian errors is now misspecified enough to let these optimisers produce very distinct predictions and the optimal prediction produced based on one scoring rule cannot be beaten out-of-sample according to that same scoring rule.
+
 Optimal forecasts are expected to reap more benefits as the degree of model misspecification increases, and predictions based on CLS at 80% and 90% perform poorly when assessed by LS, CRPS, CLS at 10% and CLS at 20%.
@@
 Table 4 shows similar results as in Table 3.
-As the shape parameter decreases, the degree of negative marginal skewness increases, and optimal forecasts provide more benefits.
+In Panel A, when the true DGP is symmetric (shape = 0), optimal predictions are non-distinguishable and hence, yield very similar out-of-sample performance.
+There are no significant benefits reaped from using optimal probabilistic forecasts.
+However, as the shape parameter decreases, the degree of negative marginal skewness increases, as shown in Panels B and C, optimal predictions produced are more different from each other and yield different average out-of-sample scores.
 Even though, strictly speaking, we do not observe strict coherence in Panel C, the most misspecified case, it is close enough to conclude that optimal forecasts perform in the same way even when we have different forms of model misspecification.
 ^[Tables are produced by R package: @kableextra and @knitr.]
-
-*Table 2: It shows the results of Scenario (i), the correct model specification case. Both the true DGP and assumed predictive model are ARCH(1) with Gaussian error.*
 
@@
 
-*Table 3: It corresponds to Scenario (ii) where the assumed predictive model is ARCH(1) with Gaussian error and the true DGP is GARCH(1,1) with Student-t error*
+Table 2: Average out-of-sample scores under the correctly specified ARCH(1) model with Gaussian errors, corresponding to Scenario (i) in Table 1.
+The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer.
+The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function.
 
@@
 
-*Table 4: It corresponds to Scenario (iii) where the assumed model is ARCH(1) with Gaussian error and the true DGP is stochastic volatility inversion copula.*
+Table 3: Average out-of-sample scores under the misspecified ARCH(1) model with Gaussian errors, corresponding to Scenario (ii) in Table 1.
+The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer.
+The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function.
+Panel A, B and C shows the average out-of-sample scores of the true DGP - GARCH(1,1) with $t_{\nu=35}$, $t_{\nu=12}$, $t_{\nu=3}$ errors.
 
@@
 
+Table 4: Average out-of-sample scores under the misspecified ARCH(1) model with Gaussian errors, corresponding to Scenario (iii) in Table 1.
+The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer.
+The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function.
+Panel A, B and C shows the average out-of-sample scores of the true DGP – stochastic volatility inversion copula model with shape parameter specified as {0, -3, -5} respectively.
+
 ### 3.2.2 Trace plots & predictive densities
@@
 Accurate prediction of extreme values is important for financial risk management.
-Therefore, we provide score trace plots to exhibit the comparison of MLE, CRPS and CLS’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails.
-The results in Section 3.2.1 show that when the degree of model misspecification is high, CLS can perform the best compared with MLE and CRPS in predicting both tails.
+Therefore, we provide score trace plots to exhibit the comparison of LS, CRPS and CLS’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails.
+The trace plots demonstrate the cumulative average out-of-sample score over an expanding evaluation period of CLS10 (left panel) and CLS90 (right panel) for four optimizers \{LS, CRPS, CLS10(80), CLS20(90)\}.
+The results in Section 3.2.1 show that when the degree of model misspecification is high, CLS can perform the best compared with LS and CRPS in predicting both tails.
 However, only the average score values at the end of each iteration of the simulation are recorded in the tables, while trace plots provide a dynamic view of how optimal forecasts perform.
@@
 The right panel shows the same thing but is based on the performance of predicting 90 percentile.
-From panels (a) and (b) in Figures 1 and 2, we can see that CLS almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as the misspecification increases, CLS starts to outperform CRPS and MLE in predicting tails.
-The more misspecified the model is, the more benefits can we gain from using CLS.
-Furthermore, more improvement in predictive accuracy occurs in the upper tail than in the lower tail, especially in Figure 2 where we have a negatively skewed marginal distribution.
+
+Figure 1 shows the correct specification case, corresponding to Scenario (i) and Table 2, it is impossible to distinguish these 4 lines in both lower and upper tails, which suggests that the cumulative average out-of-sample scores of these four optimisers are almost identical.
+It indicates that their out-of-sample performance are almost the same over the expanding evaluation period.
+Figure 2 corresponds to Scenario (ii) and Table 3 where the ARCH(1) model is misspecified for the GARCH(1,1) model with Student-t error.
+In panels (a) and (b), the least misspecified case, we can see that CLS almost makes no difference compared with other scoring rules, but as the misspecification increases, in panels (c) to (f), CLS starts to outperform CRPS and LS in predicting tails.
+Especially in panels (e) and (f), the gap between CLS10/90 (the blue line) and LS (the green line) is easily observed, which indicates that the more misspecified the model is, the more benefits can we gain from using CLS.
+Similar findings can be observed in Figure 3, which shows another type of model misspecification as in Scenario (iii).
+The increasing gap between CLS90 and LS, in panels (c) to (f), suggests that CLS makes more improvement in terms of the prediction accuracy in tails as the degree of model misspecification increases.
+Furthermore, the gap between CLS10/90 and LS tends to be bigger in the upper tail, compared with in the lower tail, especially in Figure 3.
+It suggests that more improvement is made in predictive accuracy occurs in the upper tail than in the lower tail.
 This result is consistent with @fbp2020.
@@
 
-```{r}
+```{r,fig.align="center"}
 # need to adjust the size. 
@@
 
+Figure 1: Cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) over an expanding evaluation period under the correctly specified ARCH(1) model with Gaussian errors, corresponding to Scenario (i) in Table 1.
 ```{r}
@@
 
+Figure 2: Cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) over an expanding evaluation period under the misspecified ARCH(1) model with Gaussian errors, corresponding to Scenario (ii) in Table 1.
+The two subplots in each row represents the cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) of the true DGP – GARCH(1,1) with $t_{\nu=35}$, $t_{\nu=12}$, $t_{\nu=3}$ errors.
+
+```{r}
+knitr::include_graphics("figure/figure 3.pdf")
+```
+
+Figure 3: Cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) over an expanding evaluation period under the misspecified ARCH(1) model with Gaussian errors, corresponding to Scenario (iii) in Table 1.
+The two subplots in each row represents the cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) of the true DGP – stochastic volatility inversion copula model with shape parameter specified as {0, -3, -5} respectively.
+
 From the average out-of-sample score tables and trace plots above, we can see that optimal forecasts provide the most benefits in improving prediction accuracy under the most misspecified case.
-In order to provide a more complete view of how optimal forecasts work, the predictive densities of the most misspecified case are plotted in Figure 3.
+In order to provide a more complete view of how optimal forecasts work, the predictive densities of the most misspecified case are plotted in Figure 4.
 The shape of true conditional predictive distributions plays a role in deciding how much we can gain by using optimal forecasts, since predictions obtained from optimizing CLS aim to match the shape of tails of the true conditional predictive distributions.
-CLS focusing on upper tails (80%, 90%) is expected to perform poorly in the lower tail so the forecasters should have a clear expectation about what they aim to achieve [@fbp2020].
+
+In the left panel of Figure 4, CLS90 (the red line) matches the shape of the upper tail of the true distribution (the pink line) perfectly but did a very poor job in predicting the lower tail.
+It is the same for CLS10 (the blue line) to match the shape of the lower tail of the true distribution perfectly.
+This visualizes how CLS reward the prediction accuracy in the region of interest to the forecaster.
+While in the right panel of Figure 4, it shows another type of model misspecification, and CLS does not manage to match the shape of the tails of the true distribution, but it still does a better job than LS in both tails.
+This suggests that when it comes to determining when the optimal probabilistic forecasts work, it actually depends on the shape of the true distribution, the assumed model specification, and the scoring rules.
 However, in practice, the shape of true conditional predictive distributions is usually unknown and it might create the difficulty of determining which tail we can reap more benefits from optimal forecasts without analysing a particular problem beforehand.
@@
 
+Figure 4: The conditional predictive density produced by LS, CLS10 and CLS90 under the misspecified ARCH(1) model with Gaussian errors, corresponding to Panel C in Tables 3 and 4.
+The left panel is the conditional predictive density at a randomly picked time $t = 2001$ with the true DGP as stochastic volatility inversion copula (shape = -3), and the right panel is the conditional predictive density at a randomly picked time $t = 2501$ with the true DGP as GARCH(1,1) with $t_{\nu = 3}$ errors.
+
 # 4. Empirical analysis: financial returns 
@@
 
-From the results in Section 3.2, we can conclude that optimal forecasts based on the CLS can improve the prediction accuracy in tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification.
+From the results in Section 3.2, we can conclude that optimal forecasts based on the CLS can improve the prediction accuracy in the tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification.
 In Section 4, we apply the same method adopted in Section 3 to an empirical setting and investigate how it performs in practice.
 
-The data used in the analysis is the continuously compounded daily log returns of S&P 500 listed in U.S.A financial market over a broad time period from 27 Sep,1996 to 30 July,2020.^[Data retrieved from @spdata] It aims to include two very volatile periods, the GFC and the recent COVID-19 pandemic.
-The initial training sample size and out-of-sample observations are kept consistent with what is in Section 3 with initial training sample size = 1000 and out-of-sample evaluations = 5000.
-
-The descriptive statistics in Table 5 show that the distribution of S&P 500 log returns is negatively skewed and has fat tails and strong serial correlation in its volatility.
-Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.^[Descriptive statistics are produced by R packages: @dplyr, @tidyverse, @tsibble, @tsibbledata, @feasts, @normtest, @moments.]
+The data used in the analysis is the continuously compounded daily log returns of S&P 500 listed in U.S.A financial market over a broad time period from 27 September,1996 to 30 July,2020.^[Data retrieved from @spdata] It aims to include two very volatile periods, the GFC and the recent COVID-19 pandemic.
+The initial training sample size and out-of-sample observations are kept consistent with what is in Section 3 with an initial training sample size of 1000 and out-of-sample evaluations of 5000.
+
+The descriptive statistics in Table 5 show that the distribution of S&P 500 log returns is negatively skewed, has fat tails and strong serial correlation in its volatility.
+Moreover, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.^[Descriptive statistics are produced by R packages: @dplyr, @tidyverse, @tsibble, @tsibbledata, @feasts, @normtest, @moments.]
 
@@
 jb.norm.test(logret$log.returns)
+# qchisq(.95, df=2)
 # Ljung box test
-Box.test(logret$log.returns,lag = 2,type = "Lj",fitdf = 1)
+Box.test((logret$log.returns)^2,lag = 2,type = "Lj",fitdf = 1)
+# qchisq(.95, df=lags)
 
@@
 ```{r}
-sum <- data.frame(Stock="S&P500",Min=as.numeric(summary[1]),Median=as.numeric(summary[3]),Mean=as.numeric(summary[4]),Max=as.numeric(summary[5]),Skewness=sk,Kurtosis=kt,JB.Test=28270,LB.Test=61.489)
+sum <- data.frame(Stock="S&P500",Min=as.numeric(summary[1]),Median=as.numeric(summary[3]),Mean=as.numeric(summary[4]),Max=as.numeric(summary[5]),Skewness=sk,Kurtosis=kt,JB.Test=27066,LB.Test=1742.7)
 sum %>% 
@@
   kable_styling("bordered",font_size = 10) %>% 
-  add_header_above(c("Table 5: Descriptive statistics"=9))
-```
+  add_header_above(c("Table 5: Descriptive statistics for S&P500 log returns"=9))
+```
+
+Table 5: Descriptive statistics for S&P 500 index log returns.
+The Min and Max are the smallest and largest value of the sample series, respectively.
+Skewness is a measure of the asymmetry and kurtosis is a measure of fat tails with the normal distribution having kurtosis equals to three.
+‘JB.Test’ is the test statistic for the Jarque-Bera test of normality, with a critical value of 5.99.
+‘LB.Test’ is the test of serial correlation of the squared returns, with a critical value based on 2 lags as 5.99.
 
@@
   #ggtitle("Figure 11:Squared log returns autocorrelation")+
-  xlab("number of lags")+ylab("ACF for variance")+theme_clean()
+  xlab("number of lags")+ylab("ACF of squared returns")+theme_clean()
 # +labs(caption = "Figure 11: the autocorrelation plot shows there is a strong serial correlation in volatility of S&P500")
@@
 annotate_figure(figure, 
-                top = text_grob("Descriptive figures",face = "bold"),
-                fig.lab = "Figure 4",fig.lab.face = "bold"
+                top = text_grob("Descriptive figures for S&P500 log returns",face = "bold"),
+                fig.lab = "Figure 5",fig.lab.face = "bold"
                 )
@@
 
+Figure 5: The descriptive figures for S&P 500 log returns.
+Panel A is the time series plot of S&P 500 log returns.
+High volatility is observed during the GFC and the recent COVID-19 pandemic.
+Panel B is the histogram which illustrates the estimated marginal distribution of log returns.
+Panel C represents the autocorrelation function (ACF) plot of the squared returns, which indicates strong autocorrelation in volatility of log returns.
+
 ## 4.2 Empirical results: predictive distributions for returns
 
-From the wide-usage of ARCH models in modelling financial returns and volatility, and the strict coherence observed in Section 3.2.1, ARCH(1) should be a ‘compatible’ and sufficiently misspecified model to forecast S&P 500 series and to observe the difference made by adopting optimal forecasts.
-The results in Table 6 show that the CLS outperforms other alternative scores in both lower and upper tails, which closely follows the results and conclusions drawn in the numerical analysis in Section 3.
+From the wide-usage of ARCH models in modelling financial returns and volatility, and the strict coherence observed in Section 3.2.1, ARCH(1) should be a ‘compatible’, but sufficiently misspecified model to forecast S&P 500 series and to observe the difference made by adopting optimal forecasts.
+The results in Table 6 show that the CLS outperforms other alternative scores in both the lower and upper tails, which closely follows the results and conclusions drawn in the numerical analysis in Section 3.
 However, the difference between using CLS10(80) and CLS20(90) is very small.
@@
   add_header_above(c("","Average out-of-sample scores"=6)) %>% 
-  add_header_above(c("Table 6: Average scores for S&P 500"=7))
-```
+  add_header_above(c("Table 6: Average scores for S&P 500 log returns"=7))
+```
+
+Table 6: Average out-of-sample scores for S&P log returns, under the misspecified Gaussian ARCH(1) model.
+The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer.
+The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function.
 
 Unlike in the simulation example, the score trace plots now show how different scoring rules perform at time points that correspond to some actual historical events.
-In Figure 5, one interesting phenomenon is that after the GFC, the CLS performs much better than CRPS and MLE, in terms of predicting both upper and lower tails.
-It indicates that optimal probabilistic forecasts based on CLS can predict extreme events, such as the GFC, more accurately than other alternatives.
-This improvement brings up the average score of CLS optimizer after the GFC as shown in Figure 5.
-The difference between CLS and MLE/CRPS gets smaller and smaller over time until the recent COVID-19 pandemic.
-It is also worth noticing that CLS does not appear to provide more benefits in the upper tail than in the lower tail, which is different from the simulation results.^[The figures are produced by R packages: @ggplot2, @ggthemes, @ggpubr.]
+From Figure 6(a), the out-of-sample performance of these four optimizers are almost identical before the 2008 GFC.
+However, the gap between CLS10 (the blue line) and LS (the green line) becomes distinguishable after the GFC.
+It indicates that CLS10 outperforms LS and CRPS significantly in terms of the predictive accuracy of lower tails.
+The gap then becomes smaller and smaller over time until the very recent COVID-19 pandemic.
+This interesting phenomenon suggests that optimal probabilistic forecasts based on CLS can predict extreme events, such as the GFC, more accurately than other alternatives.
+Hence, CLS yield a much higher out-of-sample score which brings up the cumulative average out-of-sample score that we observed in Figure 6(a).
+While in Figure 6(b), the similar results can be observed after the GFC in the upper tail.
+If we compare the gap between CLS and LS in Figure 6(b) with the gap in Figure 6(a), it is also worth noticing that CLS does not appear to provide more benefits in the upper tail than in the lower tail, which is different from the simulation results.^[The figures are produced by R packages: @ggplot2, @ggthemes, @ggpubr.]
 
@@
 trace_10ls <- read.csv("data/fsr10_ls.csv")
+trace_10ls <- trace_10ls %>% rename("LS"=MLE)
 trace_10crps <- read.csv("data/fsr10_crps.csv")
@@
 
-color1 <- c("CLS10"="blue","CLS20"="red","MLE"="green","CRPS"="black")
+color1 <- c("CLS10"="blue","CLS20"="red","LS"="green","CRPS"="black")
 
 fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
-  geom_line(aes(y = CLS10,color = "CLS10"),size=0.3,linetype = "dashed")+
-  geom_line(aes(y = CLS20,color = "CLS20"),size=0.5,linetype = "dotted")+
-  geom_line(aes(y = MLE,color = "MLE"),size=0.3,linetype = "solid")+
-  geom_line(aes(y = CRPS,color = "CRPS"),size=0.3, linetype = "longdash")+
+  geom_line(aes(y = CLS10,color = "CLS10"),size=0.3)+
+  geom_line(aes(y = CLS20,color = "CLS20"),size=0.3)+
+  geom_line(aes(y = LS,color = "LS"),size=0.3)+
+  geom_line(aes(y = CRPS,color = "CRPS"),size=0.3)+
   labs(x="Year",y="Average Scores",color="legend")+
@@
 trace_90ls <- read.csv("data/fsr90_ls.csv")
+trace_90ls <- trace_90ls %>% rename("LS"=MLE)
 trace_90crps <- read.csv("data/fsr90_crps.csv")
@@
 
-color2 <- c("CLS90"="blue","CLS80"="red","MLE"="green","CRPS"="black")
+color2 <- c("CLS90"="blue","CLS80"="red","LS"="green","CRPS"="black")
 
@@
   geom_line(aes(y = CLS80,color = "CLS80"),size=0.25)+
-  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
+  geom_line(aes(y = LS,color = "LS"),size=0.25)+
   geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 5(a) CLS10","Figure 5(b) CLS90")) + 
-  labs(caption = "Figure 5: the predictive distributions are produced by ARCH(1) with Gaussian error term") +
-  theme(plot.caption = element_text(hjust = 0))
-
-```
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 6(a) CLS10","Figure 6(b) CLS90")) 
+  #labs(caption = "Figure 6: the predictive distributions are produced by ARCH(1) with Gaussian error term") +
+  #theme(plot.caption = element_text(hjust = 0))
+```
+
+Figure 6: Cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) over an expanding evaluation period, for predicting S&P 500 log returns under the misspecified Gaussian ARCH(1) model.
+Panel (a) shows the measure of performance in predicting the lower tail by optimizing CLS10, CLS20, CRPS and LS.
+Panel (b) shows the measure of performance in predicting the upper tail by optimizing CLS80, CLS90, CRPS and LS.
 
@@
 Density forecasts have great practical value in finance.
-They form the foundation of risk management, such as Value-at-Risk, and are useful for asset allocation and derivative pricing.
+They form the foundation of risk management, such as VaR, and are useful for asset allocation and derivative pricing.
 VaR is a commonly used risk measurement in finance.
 It can be obtained from a probability density function of returns over a chosen investment horizon.
-It is the *p*th quantile ($q_p$) of a predictive distribution of a portfolio’s returns over a holding period, according to a given confidence interval $\alpha$ [@dowd2007].
+It is the $p$th quantile ($q_p$) of a predictive distribution of a portfolio’s returns over a holding period, according to a given confidence interval $\alpha$ [@dowd2007].
+That is,
 \begin{equation} \label{eq:var}
@@
 \end{equation}
+where 
 \begin{equation} \label{eq:p}
@@
 VaR represents the largest possible investment loss in a given investment horizon with the given $\alpha$ confidence level.
-There are different methods to estimate VaR, but it is clear that predictive density plays an important role here.
+There are different methods to estimate VaR, but it is clear that the predictive density plays an important role here.
 Therefore, a more accurate probabilistic prediction can contribute to improving the accuracy of VaR prediction.
@@
 
-We illustrate how optimal forecasts perform in estimating VaR by using predictions produced through simulation (Section 3) first, and expect that optimal forecasts based on CLS would give us a better prediction in tails.
+We illustrate how optimal forecasts perform in estimating VaR by using predictions produced through simulation first, using the specifications from Section 3, and expect that optimal forecasts based on CLS would give us a better prediction in the tails.
 Specifically, VaR predictions at \{10%, 20%, 80%, 90%\} are conducted, corresponding to the 10% and 20% expected loss of long and short portfolios.
-More importantly, we keep the percentage of VaR prediction the same as CLS focused tail because, as mentioned before, CLS at \{10%, 20%, 80%, 90%\} is computed from the marginal distribution due to computational burden and keeping the percentage the same reduce the error caused by this mismatch.
+More importantly, we keep the percentage of VaR prediction the same as CLS focused tail because, as mentioned before, CLS at \{10%, 20%, 80%, 90%\} is computed from the marginal distribution due to computational burden and keeping the percentage the same reduces the error caused by this mismatch.
 
@@
 
-Starting from the two different forms of model misspecification investigated in simulation analysis (Section 3), the values showed in the Table 7 and 8 refer to the out-of-sample proportion of exceedances over the nominal VaR level indicated by the column name.
-The CLS can provide the most accurate VaR prediction in the upper tail, while in the lower tail, it is not short of advantages by too much compared with CRPS.
-This conclusion does not vary much when we have different forms of model misspecification as illustrated in the Table 7 and 8.
-
-*Table 7: The predictive distributions are produced by ARCH(1) with Gaussian error while the true DGP is stochastic volatility inversion copula with the highest negative marginal skewness in our simulation.
-The values show the out-of-sample exceedances of each optimizer.*
+Starting from the two different forms of model misspecification investigated in the simulation analysis of Section 3, Table 7 and 8 illustrates the assessment of the predictive VaR corresponding to the most misspecified cases in Sceanrio (ii) and (iii) in Table 1.
+The values recorded in Table 7 and 8 refer to the proportion of times that the observed out-of-sample values exceed the predictive VaR.
+The bolded figure shows the out-of-sample proportion of exceedances that is the closest to the nominal tail probability indicated by the column name.
+In Table 7, CLS80 and CLS90 optimisers produce the best performing VaR predictions for the upper tails, while CRPS is the best performing optimiser in terms of predicting VaR at 10% and 20% but CLS10 and CLS20 are not short of advantages by too much compared with CRPS.
+In Table 8 which shows predictive VaR assessment under another type of model misspecification – modelling stochastic volatility inversion copula with Gaussian ARCH(1) model, it is obvious that CLS performs the best in predicting VaR in both lower and upper tails.
+Therefore, from the results of these two tables, CLS can improve the VaR predictive accuracy when the model is sufficiently misspecified, no matter what the form of model misspecification.
+
+```{r}
+garch3var <- read.csv("data/garch3var.csv")
+
+VaR0.1 <- as.numeric(garch3var[,c(1,5,9,13,17,21)])
+VaR0.2 <- as.numeric(garch3var[,c(2,6,10,14,18,22)])
+VaR0.8 <- as.numeric(garch3var[,c(3,7,11,15,19,23)])
+VaR0.9 <- as.numeric(garch3var[,c(4,8,12,16,20,24)])
+
+Optimizers <- c("LS","CRPS","CLS10","CLS20","CLS80","CLS90")
+
+df <- data.frame(Optimizers,VaR0.1,VaR0.2,VaR0.8,VaR0.9)
+df <- rename(df,"VaR at 10\\%"=VaR0.1, "VaR at 20\\%"=VaR0.2, "VaR at 80\\%"=VaR0.8, "VaR at 90\\%"=VaR0.9)
+
+df %>% 
+  mutate(
+    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
+    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
+    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
+    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
+  ) %>%
+  kable("latex",escape = F, booktabs=T, linesep = "") %>%
+  kable_styling("bordered",full_width = F) %>%
+  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
+  add_header_above(c("Table 7: the true DGP is GARCH with degree of freedom = 3"=5))
+```
+
+Table 7: Predictive VaR assessment corresponding to the most misspecified case in Scenario (ii) in Table 1, where the assumed predictive model is Gaussian ARCH(1) and the true DGP is GARCH(1,1) with $t_{\nu} = 3$ error.
+The figures are the proportion of times that the observed out-of-sample values exceed the predictive $VaR_{\alpha}$ indicated by the column name.
+The bolded figure indicates the empirical out-of-sample exceedance that is the closest to the nominal tail probability.
 
@@
   add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 7: the true DGP is stochastic volatility inversion copula (shape = -5)"=5))
-```
-
-*Table 8: The predictive distributions are produced by ARCH(1) with Gaussian error and the true DGP is GARCH(1,1) with Student-t error where $t_\nu$ = 3.
-The values show the out-of-sample exceedances of each optimizer.*
-
-```{r}
-garch3var <- read.csv("data/garch3var.csv")
-
-VaR0.1 <- as.numeric(garch3var[,c(1,5,9,13,17,21)])
-VaR0.2 <- as.numeric(garch3var[,c(2,6,10,14,18,22)])
-VaR0.8 <- as.numeric(garch3var[,c(3,7,11,15,19,23)])
-VaR0.9 <- as.numeric(garch3var[,c(4,8,12,16,20,24)])
-
-df <- data.frame(Optimizers,VaR0.1,VaR0.2,VaR0.8,VaR0.9)
-df <- rename(df,"VaR at 10\\%"=VaR0.1, "VaR at 20\\%"=VaR0.2, "VaR at 80\\%"=VaR0.8, "VaR at 90\\%"=VaR0.9)
-
-df %>% 
-  mutate(
-    `VaR at 10\\%` = cell_spec(format(`VaR at 10\\%`,4),"latex",bold = ifelse(abs(`VaR at 10\\%`-0.1) == min(abs(`VaR at 10\\%`-0.1)),TRUE,FALSE)),
-    `VaR at 20\\%` = cell_spec(format(`VaR at 20\\%`,4),"latex",bold = ifelse(abs(`VaR at 20\\%`-0.2) == min(abs(`VaR at 20\\%`-0.2)),TRUE,FALSE)),
-    `VaR at 80\\%` = cell_spec(format(`VaR at 80\\%`,4),"latex",bold = ifelse(abs(`VaR at 80\\%`-0.8) == min(abs(`VaR at 80\\%`-0.8)),TRUE,FALSE)),
-    `VaR at 90\\%` = cell_spec(format(`VaR at 90\\%`,4),"latex",bold = ifelse(abs(`VaR at 90\\%`-0.9) == min(abs(`VaR at 90\\%`-0.9)),TRUE,FALSE))
-  ) %>%
-  kable("latex",escape = F, booktabs=T, linesep = "") %>%
-  kable_styling("bordered",full_width = F) %>%
-  add_header_above(c(" ","Out-of-sample exceedances"=4)) %>%
-  add_header_above(c("Table 8: the true DGP is GARCH with degree of freedom = 3"=5))
-```
+  add_header_above(c("Table 8: the true DGP is stochastic volatility inversion copula (shape = -5)"=5))
+```
+
+Table 8: Predictive VaR assessment corresponding to the most misspecified case in Scenario (iii) in Table 1, where the assumed predictive model is Gaussian ARCH(1) and the true DGP is the stochastic volatility inversion copula model with the highest negative marginal skewness (shape = -5).
+The figures are the proportion of times that the observed out-of-sample values exceed the predictive $VaR_{\alpha}$ indicated by the column name.
+The bolded figure indicates the empirical out-of-sample exceedance that is the closest to the nominal tail probability.
 
@@
 Therefore, we perform the VaR analysis over two different time periods, before the GFC and after the GFC.
-The results from Table 9 and 10 show that the CLS perform well enough in terms of estimating VaR for both long and short portfolios of S&P 500, but also CRPS is a very robust scoring rule which can provide relatively accurate predictions.
+Table 9 and 10 show that the CLS performs well enough in terms of estimating VaR for both long and short portfolios of S&P 500, but also CRPS is a very robust scoring rule which can provide relatively accurate predictions.
+The results from Table 9 show the performance of optimizers in predicting VaR of S&P 500 log returns before the GFC.
+Compared with the results obtained in Table 7 and 8 under simulation scenarios, the answer to whether CLS significantly improve the VaR predictive accuracy is less obvious.
+Looking at the bolded values, CLS20 and CLS90 can provide the best VaR predictions for 10% and 80% tails, respectively.
+While CRPS is the optimiser that can provide the best VaR predictions for 20% and 90% among all optimisers.
+Even though CRPS outperforms CLS in these situations, there is only slight difference between CRPS and CLS.
+The predictive VaR assessment after the GFC is shown in Table 10 where the similar results can be observed.
+The bolded values indicate that CLS10 and CLS90 are the best performing optimizers in terms of predicting VaR at 20% and 80%, respectively, and CRPS still outperforms other optimizers in VaR prediction at 10% and 90%.
 Moreover, in Table 10, the CLS seems to perform better in 20% and 80% tails which have higher probability mass than 10% and 90% tails.
-If we think of the marginal distribution of S&P 500 estimated by histogram in Figure 4.B, the above results could be a consequence of the very sparse marginal distribution or simply because there is no enough data in the tails to produce an accurate estimate of the CLS optimizer, which increases the difficulty of 'focusing' on the 10% and 90% tails.
-
-*Table 9: The estimation of VaR through out-of-sample exceedances is based on predictive distributions produced by ARCH(1) with Gaussian error.
-This table shows the VaR prediction of S&P 500 before the GFC.*
+If we think of the marginal distribution of S&P 500 estimated by histogram in Figure 5.B, the above results could be a consequence of the very sparse marginal distribution or simply because there is no enough data in the tails to produce an accurate estimate of the CLS optimizer, which increases the difficulty of 'focusing' on the 10% and 90% tails.
 
@@
 
-*Table 10: The estimation of VaR through out-of-sample exceedances is based on predictive distributions produced by ARCH(1) with Gaussian error.
-This table shows the VaR prediction of S&P 500 after the GFC.*
+Table 9: Predictive VaR assessment for S&P 500 log returns before the GFC, where the assumed predictive model is Gaussian ARCH(1).
+The figures are the proportion of times that the observed out-of-sample values exceed the predictive $VaR_{\alpha}$ indicated by the column name.
+The bolded figure indicates the empirical out-of-sample exceedance that is the closest to the nominal tail probability.
 
@@
 
+Table 10: Predictive VaR assessment for S&P 500 log returns after the GFC, where the assumed predictive model is Gaussian ARCH(1).
+The figures are the proportion of times that the observed out-of-sample values exceed the predictive $VaR_{\alpha}$ indicated by the column name.
+The bolded figure indicates the empirical out-of-sample exceedance that is the closest to the nominal tail probability.
+
 # 5. Empirical analysis: VIX
@@
 Time-varying volatility is an important part in finance modelling and an accurate prediction will give investors a better understanding of the risks they take on.
-GARCH-type models used in Section 3 and 4 are conditionally deterministic.
-That is, $\sigma_t^2$ is a deterministic function of given past returns.
+GARCH-type models used in Section 3 and 4, which are defined as:
+\begin{equation} \label{eq:reg}
+r_t = \mu+\sigma_t\epsilon_t
+\end{equation}
+and 
+\begin{equation} \label{eq:garch}
+\sigma_t^2=\alpha_0+\alpha_1(r_{t-1}-\mu)^2+\beta_1\sigma_{t-1}^2
+\end{equation}
+where 
 \begin{equation} \label{eq:ret}
@@
 \end{equation}
-\begin{equation} \label{eq:reg}
-r_t = \mu+\sigma_t\epsilon_t
-\end{equation}
-\begin{equation} \label{eq:garch}
-\sigma_t^2=\alpha_0+\alpha_1(r_{t-1}-\mu)^2+\beta_1\sigma_{t-1}^2
-\end{equation}
-where $P_t$ is the stock price and $\sigma_t$ is the volatility.
+with $P_t$ the stock price and $\sigma_t$ the volatility, are conditionally deterministic. That is, $\sigma_t^2$ is a deterministic function of given past returns.
 
@@
 The realized volatility (RV) approach to modelling volatility allows us to exploit the information in intraday data, consider long memory feature, sudden jumps in the market and market microstructure.
-When the price follows the process as $\eqref{eq:gbm}$:
+When the price follows the process as in:
 \begin{equation} \label{eq:gbm}
@@
 \end{equation}
-RV is a direct estimate of integrated volatility (IV) for $lnP_t$ based on continuously recorded observations of $P_t$ over the day.
+RV is a direct estimate of integrated volatility (IV) for $lnP_t$ based on continuously recorded observations of $P_t$ over the day, and is defined as:
 \begin{equation} \label{eq:RV}
@@
 \end{equation}
-When considering the sudden jumps, that is, the price follows the process in $\eqref{eq:jump}$.
-RV is also a consistent estimate of quadratic variation (QV) where $\kappa_s$ represents the sudden jump on day t and $q_t$ is the jump occasions.
+When considering the sudden jumps, that is, the price follows the process in:  
 \begin{equation} \label{eq:jump}
@@
 \end{equation}
+RV is also a consistent estimate of quadratic variation (QV) where $\kappa_s$ represents the sudden jump on day t and $q_t$ is the jump occasions, which is defined as: 
 \begin{equation} \label{eq:RV2}
@@
 \end{equation}
-In addition to the fact that volatility is a direct measure of the risk of portfolios, it is also important for pricing derivatives, such as options, since it is the only unknown parameter to estimate.
-The famous Black-Scholes model assumes a constant volatility over time which does not hold in practice.
-Implied volatility allows us to incorporate the jumps and continuous variation of volatility over time.
-In other words, implied volatility is an estimate of QV extracted from option prices.
-
-The VIX index estimates QV that is implied by option prices under a risk-neutral $\eqref{eq:jump}$ process, using a finite number of strike prices of S&P 500 index [@cboe].
-It acknowledges the occurrence of jumps and the fact that assumptions of the Black-Scholes model do not hold in practice.
-Since both the VIX and RV are estimations of QV, it is reasonable to model the VIX with a HAR-RV model which is usually used for modelling RV in the literature [@andersen2007; @corsi2009; @m2009does; @manee2012probabilistic].
+In addition to the fact that volatility is a direct measure of the risk of portfolios, it is also important for pricing derivatives, such as options.
+Thus, option-implied volatility has been used for measuring volatility.
+The option-implied volatility using the famous Black-Scholes (BS) model is less accurate since the BS model misspecifies the volatility as constant over time.
+Therefore, the model-free option-implied volatility has been introduced to better reflect the market and to construct the VIX, which allows for stochastic volatility with jumps.
+More specifically, the VIX index estimates QV using the prices of options written on the S&P 500 index, and under a risk-neutral version of the process in $\eqref{eq:jump}$ [@cboe].
+It thus acknowledges the occurrence of jumps and the fact that assumptions of the famous Black-Scholes option pricing model, i.e.
+that returns on the index are normal with a constant variance, do not hold in practice.
+Since both the VIX and RV are estimations of QV, it is reasonable to model the VIX with a HAR-RV model, which is usually used for modelling RV in the literature [@andersen2007; @corsi2009; @m2009does; @manee2012probabilistic].
 
 ## 5.2 Preliminary diagnostics
-We collect daily VIX index data starting from 27 Aug,1996 to 30 July,2020.^[Data retrieved from @vixdata] The descriptive statistics of $log(VIX_t)$ are shown in Table 11 and Figure 6:
-
-Table 11 and Figure 6 show that $log(VIX_t)$ is volatile and shows strong persistence over time.
+We collect daily VIX index data starting from 27 August,1996 to 30 July,2020.^[Data retrieved from @vixdata] The descriptive statistics of $log(VIX_t)$ are shown in Table 11 and Figure 7.
+
+Table 11 and Figure 7 show that $log(VIX_t)$ is volatile and shows strong persistence over time.
 It is positively skewed and the autocorrelation of its volatility is slowly decaying.
@@
 # Ljung box test
-Box.test(vix$logvix,lag = 2,type = "Lj",fitdf = 1)
+Box.test((vix$logvix)^2,lag = 2,type = "Lj",fitdf = 1)
 
@@
 ```{r}
-sum <- data.frame(Series="Log(VIX)",Min = as.numeric(summary[1]), Median = as.numeric(summary[3]), Mean = as.numeric(summary[4]), Max = as.numeric(summary[6]),Skewness= vixsk,Kurtosis=vixkt,JB.Test=410.77,LB.Test=11765)
+sum <- data.frame(Series="Log(VIX)",Min = as.numeric(summary[1]), Median = as.numeric(summary[3]), Mean = as.numeric(summary[4]), Max = as.numeric(summary[6]),Skewness= vixsk,Kurtosis=vixkt,JB.Test=410.77,LB.Test=11763)
 sum %>% 
@@
   kable_styling("bordered",font_size = 10)%>% 
-  add_header_above(c("Table 11: Descriptive statistics"=9))
-```
+  add_header_above(c("Table 11: Descriptive statistics for log(VIX)"=9))
+```
+
+Table 11: Descriptive statistics for logarithmic of the VIX volatility index.
+The Min and Max are the smallest and largest value of the sample series, respectively.
+Skewness is a measure of the asymmetry and kurtosis is a measure of fat tails with the normal distribution having kurtosis equals to three.
+‘JB.Test’ is the test statistic for the Jarque-Bera test of normality, with a critical value of 5.99.
+‘LB.Test’ is the test of serial correlation of the squared volatility, with a critical value based on 2 lags as 5.99.
 
@@
 
-p3 <- logvix %>% ACF((logvix)^2) %>% autoplot()+
-      xlab("number of lags")+ylab("ACF")+theme_clean()
+p3 <- logvix %>% ACF(logvix) %>% autoplot()+
+      xlab("number of lags")+ylab("ACF of log(VIX)")+theme_clean()
+
+#p4 <- logvix %>% ACF(logvix) %>% autoplot()+
+  #xlab("number of lags")+ylab("ACF of log(VIX)")+theme_clean()
 
@@
 annotate_figure(figure, 
-                top = text_grob("Descriptive figures",face = "bold"),
-                fig.lab = "Figure 6",fig.lab.face = "bold"
+                top = text_grob("Descriptive figures for log(VIX)",face = "bold"),
+                fig.lab = "Figure 7",fig.lab.face = "bold"
                 )
@@
 
+Figure 7: The descriptive figures for logarithmic of the VIX volatility index.
+Panel A is the time series plot of log(VIX).
+Panel B is the histogram which illustrates the estimated marginal distribution of log(VIX).
+Panel C represents the ACF plot of the squared log(VIX), which indicates strong autocorrelation in volatility of the VIX volatility index.
+
 ## 5.3 Model specification
@@
 Proposed by @corsi2009, the HAR-RV model is a simple additive linear model which takes lagged squared returns as regressors.
-It does not belong to the class of long memory models, but it is able to produce the volatility persistence that is almost indistinguishable from what is observed in financial markets through the simple autoregressive-type structure.
+It does not belong to the class of long memory models, but it is able to produce the volatility persistence that is almost indistinguishable from what is observed in financial markets, through the simple autoregressive-type structure.
 
@@
 
-1. $z_{t+1} \sim N(0,1)$ and constant $\sigma$
+1. $z_{t+1} \sim N(0,1)$ and constant $\sigma$.
 
 2.
-$z_{t+1} \sim Student-t(0,1,\nu)$ and constant $\sigma$ ^[We specify $z_{t+1}$ as standardised Student-t distribution so that $\sigma^2$ can reflect the variance of the predicted VIX series.
+$z_{t+1} \sim Student-t(0,1,\nu)$ and constant $\sigma$.
+^[We specify $z_{t+1}$ as standardised Student-t distribution so that $\sigma^2$ can reflect the variance of the predicted VIX series.
 The CRPS is removed in Specification 2 and 4, since there is no closed form for this score.
@@
 
-3. $z_{t+1} \sim N(0,1)$ and time-varying $\sigma_{t+1}$ following ARCH process
-
-4. $z_{t+1} \sim Student-t(0,1,\nu)$ and time-varying $\sigma_{t+1}$ following ARCH process
+3. $z_{t+1} \sim N(0,1)$ and time-varying $\sigma_{t+1}$ following ARCH(1) process.
+
+4. $z_{t+1} \sim Student-t(0,1,\nu)$ and time-varying $\sigma_{t+1}$ following ARCH(1) process.
 ^[Specification 1 and 2 are based on equations $\eqref{eq:HAR}$-$\eqref{eq:ma22}$; Specification 3 and 4 are based on equations $\eqref{eq:ma22}$-$\eqref{eq:arch}$]
+
+The HAR-RV itself is defined as:
 
@@
 \end{equation}
+where 
 \begin{equation} \label{eq:ma5}
@@
 \end{equation}
-
+or in Specification 3 and 4, it is 
 \begin{equation} \label{eq:HAR2}
@@
 \begin{equation} \label{eq:arch}
-\sigma_{t+1}^2=\alpha_0+\alpha_1e^2_t
-\end{equation}
+\sigma_{t+1}^2=\alpha_0+\alpha_1 (\sigma_t z_t)^2
+\end{equation}
+where $log(VIX_{t-5,t})$ and $log(VIX_{t-22,t})$ are defined as in $\eqref{eq:ma5}$ and $\eqref{eq:ma22}$ respectively. 
 By using the same expanding window design in Section 3 with initial sample size = 1000 and out-of-sample size $\tau=T-1000=5000$, we produce and evaluate predictive densities with the assumed model as HAR-RV.
@@
 
-Section 5.4.1 provides the result of Specification 1 where the predictive density of the VIX is the normal distribution with a constant variance.
-In Table 12, CLS performs better in predicting the upper tail as expected and does a relatively good job in predicting lower tail as well, even though CRPS ranks the best in terms of forecasting 20 percentile of the distribution.
-The score trace plot, Figure 7, shows the predictions of optimizing four scoring rules evaluated by CLS10 (left panel) and CLS90 (right panel).
+Section 5.4.1 provides the result of Specification 1 where the conditional predictive density of the VIX is the normal distribution with a conditional mean produced by the HAR-RV model and a constant variance.
+In Table 12, CLS produces a better prediction for the upper tail as expected and does a relatively good job for the lower tail as well, even though CRPS is the optimizer that produce the best predictive for the 20th percentile of the true distribution.
+The score trace plot, Figure 8, shows the predictions of optimizing four scoring rules evaluated by CLS10 (left panel) and CLS90 (right panel).
 It indicates how accurate these predictions are, according to their performance in 10 percentile and 90 percentile.
@@
 However, we only gain very little from using it.
-On the contrary, in the upper tail, CLS has a much bigger effect on improving accuracy after the GFC.
+On the contrary, in the upper tail, CLS has a much bigger effect in improving accuracy after the GFC.
 One possible explanation could be that the HAR model is more misspecified in the upper tail than in the lower tail.
 Thus, we benefit more from CLS optimal forecasts in the upper tail.
-
-*Table 12: The predictive distributions for VIX are produced by HAR-RV model with Gaussian error and constant volatility.*
 
@@
 
+Table 12: Average out-of-sample scores under model specification 1 where the HAR-RV model has a constant $\sigma$ and normally distributed $z_{t+1}$.
+The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer.
+The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function.
+
 ```{r,fig.width=10,fig.height=5}
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) CLS10","Figure 7(b) CLS90"))+ 
-  labs(caption = "Figure 7: the predictive distributions are produced by HAR-RV model with Gaussian error and constant volatility") +
-  theme(plot.caption = element_text(hjust = 0))
-
-```
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) CLS10","Figure 8(b) CLS90"))
+  #labs(caption = "Figure 8: the predictive distributions are produced by HAR-RV model with Gaussian error and constant volatility") +
+  #theme(plot.caption = element_text(hjust = 0))
+
+```
+
+Figure 8: Cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) over an expanding evaluation period, for predicting log(VIX) under the misspecified HAR-RV model with constant $\sigma$ and normally distributed $z_{t+1}$.
+Panel (a) shows the measure of performance in predicting the lower tail by optimizing CLS10, CLS20, CRPS and LS.
+Panel (b) shows the measure of performance in predicting the upper tail by optimizing CLS80, CLS90, CRPS and LS.
 
@@
 The numerical results in Section 3 show that the more misspecified the model is, the more benefits are gained in improving prediction accuracy.
-According to the marginal distribution estimated by histogram in Figure 6.B, the conditional prediction distribution of the VIX is likely to be positively skewed and has fatter tails than the normal distribution.
+According to the marginal distribution estimated by histogram in Figure 7.B, the conditional prediction distribution of the VIX is likely to be positively skewed and has fatter tails than the normal distribution.
 Moving from Specification 1 to Specification 2, fatter tails are allowed in the predictive distribution and thus, the assumed model is less misspecified.
-Table 13 and Figure 8 show consistent performance of optimal forecasts compared with our investigations of simulated data and S&P 500 returns.
+Table 13 and Figure 9 show consistent performance of optimal forecasts compared with our investigations of simulated data and S&P 500 returns.
 That is, improvement of prediction accuracy by using CLS is still observed in the upper tail but the amount of improvement decreases as the degree of misspecification decreases.
-
-*Table 13: The predictive distributions for VIX are produced by HAR-RV model with Student-t error and constant volatility.*
 
@@
 
+Table 13: Average out-of-sample scores under model specification 2 where the HAR-RV model has a constant $\sigma$ and $z_{t+1}$ is from a standardized Student-t distribution.
+The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer.
+The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function.
+
 ```{r,fig.width=10,fig.height=5}
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) CLS10","Figure 8(b) CLS90"))+ 
-  labs(caption = "Figure 8: the predictive distributions are produced by HAR-RV model with Student-t error and constant volatility") +
-  theme(plot.caption = element_text(hjust = 0))
-```
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) CLS10","Figure 9(b) CLS90")) 
+  #labs(caption = "Figure 9: the predictive distributions are produced by HAR-RV model with Student-t error and constant volatility") +
+  #theme(plot.caption = element_text(hjust = 0))
+```
+
+Figure 9: Cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) over an expanding evaluation period, for predicting log(VIX) under the misspecified HAR-RV model with constant $\sigma$ and $z_{t+1}$ from the standardized Student-t distribution.
+Panel (a) shows the measure of performance in predicting the lower tail by optimizing CLS10, CLS20, CRPS and LS.
+Panel (b) shows the measure of performance in predicting the upper tail by optimizing CLS80, CLS90, CRPS and LS.
 
@@
 
-Specification 3 and 4 move from the constant variance of the predictive distribution to the time-varying variance, which is better specified since strong serial correlation of the volatility is observed in the VIX series as shown in Figure 6.C.
-Table 14 and Figure 9 illustrate the performance of optimal forecasts in Specification 3.
+Specification 3 and 4 move from the constant variance of the predictive distribution to the time-varying variance, which is better specified since strong serial correlation of the volatility is observed in the VIX series as shown in Figure 7.C.
+Table 14 and Figure 10 illustrate the performance of optimal forecasts in Specification 3.
 The amount of improvement decreased very slightly, compared with results of Specification 1 which also specifies a Gaussian error term.
-Similar conclusions can be drawn from comparing Table 15 and Figure 10 with the results of Specification 2.
+Similar conclusions can be drawn from comparing Table 15 and Figure 11 with the results of Specification 2.
 However, overall, as the model becomes less misspecified, we gain less from optimal forecasts in predicting the upper tail of VIX.
-
-*Table 14: The predictive distributions for VIX are produced by HAR-RV model with Gaussian error and time-varying volatility which is modelled by ARCH(1).*
 
@@
 
+Table 14: Average out-of-sample scores under model specification 3 where the HAR-RV model has a time-varying $\sigma$ following ARCH(1) process and normally distributed $z_{t+1}$.
+The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer.
+The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function.
+
 ```{r,fig.width=10,fig.height=5}
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) CLS10","Figure 9(b) CLS90"))+ 
-  labs(caption = "Figure 9: the predictive distributions are produced by HAR-RV model with Gaussian error and time-varying volatility") +
-  theme(plot.caption = element_text(hjust = 0))
-
-```
-
-*Table 15: The predictive distributions for VIX are produced by HAR-RV model with Student-t error and time-varying volatility which is modelled by ARCH(1).*
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 10(a) CLS10","Figure 10(b) CLS90"))
+  #labs(caption = "Figure 10: the predictive distributions are produced by HAR-RV model with Gaussian error and time-varying volatility") +
+  #theme(plot.caption = element_text(hjust = 0))
+
+```
+
+Figure 10: Cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) over an expanding evaluation period, for predicting log(VIX) under the misspecified HAR-RV model with time-varying $\sigma$ and normally distributed $z_{t+1}$.
+Panel (a) shows the measure of performance in predicting the lower tail by optimizing CLS10, CLS20, CRPS and LS.
+Panel (b) shows the measure of performance in predicting the upper tail by optimizing CLS80, CLS90, CRPS and LS.
 
@@
 
+Table 15: Average out-of-sample scores under model specification 4 where the HAR-RV model has a time-varying $\sigma$ following ARCH(1) process and $z_{t+1}$ from the standardized Student-t distribution.
+The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer.
+The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function.
+
 ```{r,fig.width=10,fig.height=5}
@@
 # put two plots side by side 
-ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 10(a) CLS10","Figure 10(b) CLS90"))+ 
-  labs(caption = "Figure 10: predictive distributions are produced by HAR-RV model with Student-t error and time-varying volatility") +
-  theme(plot.caption = element_text(hjust = 0))
-
-```
+ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 11(a): CLS10","Figure 11(b): CLS90"))
+  #labs(caption = "Figure 11: predictive distributions are produced by HAR-RV model with Student-t error and time-varying volatility") +
+  #theme(plot.caption = element_text(hjust = 0))
+
+```
+
+Figure 11: Cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) over an expanding evaluation period, for predicting log(VIX) under the misspecified HAR-RV model with time-varying $\sigma$ and $z_{t+1}$ from the standardized Student-t distribution.
+Panel (a) shows the measure of performance in predicting the lower tail by optimizing CLS10, CLS20, CRPS and LS.
+Panel (b) shows the measure of performance in predicting the upper tail by optimizing CLS80, CLS90, CRPS and LS.
 
@@
 
-According to the numerical and empirical results, the benefits of optimal forecasts can be observed when we have model misspecification, subject to the assumed predictive model is compatible, and their performance does not vary between two different types of model misspecification investigated in this paper.
-By mainly focusing on investigating the tail performance of optimal forecasts, the results show that the more misspecified the model is, the more benefits can be gained from using the CLS in improving the tail prediction accuracy in comparison with the conventional likelihood-based counterparts.
-This result is particularly in evidence after the stock market turbulence in both financial returns and the VIX index.
-What is interesting is that significant improvement of prediction accuracy is observed in both lower and upper tails of S&P 500 log returns but in the VIX index, it only shows up in the upper tail.
+According to the numerical and empirical results, the benefits of optimal forecasts can be observed when we have sufficiently misspecified model, subject to the assumed predictive model being compatible, and their performance does not vary among multiple types of model misspecification investigated in this paper.
+By mainly focusing on investigating the tail performance of optimal forecasts, the results show that the more misspecified the model is, the more benefits can be gained from using the censored likelihood score in improving the tail prediction accuracy in comparison with the conventional likelihood-based counterparts.
+From the empirical investigation results, the censored likelihood score tends to significantly improve the predictive accuracy for extreme events.
+This result is in evidence for both financial returns and the VIX volatility index when the stock market is extremely volatile during the 2008 Global financial crisis and the COVID-19 pandemic.
+What is interesting is that significant improvement of prediction accuracy is observed in both lower and upper tails of S&P 500 log returns but in the VIX volatility index, it only shows up in the upper tail.
 
 There are some caveats as well.
-Firstly, the predictions conducted by CLS is based on the tail regions of the marginal distribution, while VaR is calculated from the conditional predictive distribution which is updated through each iteration.
-Therefore, there is a slight mismatch in distributions when predicting VaR.
-Secondly, the practical usage of VaR is often around 1% or 5%, but at this very small tail, CLS might be less accurate than predicting 10% or 20% tail, since there are less observations in the tail and consequently, harder to focus correctly.
+Firstly, the predictions produced by the censored likelihood score are based on the tail regions of the marginal distribution, while Value-at-Risk is calculated from the conditional predictive distribution which is updated through each iteration.
+Therefore, there is a slight mismatch in distributions when predicting Value-at-Risk.
+Secondly, the practical usage of Value-at-Risk is often around 1% or 5%, but at this very small tail, the censored likelihood score might be less accurate than predicting 10% or 20% tail, since there are less observations in the tail and consequently, harder to focus correctly.
 However, this drawback might be corrected by changing to a more suitable assumed predictive model which provides a heavy tail distribution.
-As mentioned above, the difference between optimal forecasts’ performance in S&P 500 log returns and in the VIX Index is hard to interpret.
+As mentioned above, the difference between the performance of optimal forecasts in S&P 500 log returns and in the VIX volatility index is hard to interpret.
 The performance of optimal forecasts depends on the true conditional predictive distribution, which is always unknown in practice.
 Even though the marginal distributions can provide some insights about the shape of true conditional predictive distribution, it still creates a problem for determining which tail could optimal forecasts reap significant benefits.
-More importantly, the reasons why we can gain considerably from optimal forecasts after the GFC needs further investigation.
+More importantly, the reasons why we can gain considerably from optimal forecasts after the Global financial crisis needs further investigation.
 Nevertheless, the results in this paper provide important insights to the financial forecasting literature.
-In terms of financial returns, optimal forecasts can give better VaR predictions when it comes to the VIX index, the improvement of predictive accuracy in the upper tail - which indicates that higher volatility in the market is more accurately predicted - is an important contribution to literature on hedging risks and trading derivatives in financial market.
+Optimal probabilistic forecasts can produce better Value-at-Risk predictions for the financial returns or for the VIX volatility index.
+This method also can improve the predictive accuracy in the upper tail of the VIX volatility index distribution, which suggests that extremely high volatility in the market can be more accurately predicted.
+It is an important contribution to hedging risks and trading derivatives in the financial market.

### 2021-05-23 portfolio.Rmd
The portfolio management of VIX - trading strategy 1 and 2.

---
title: "Portfolio"
author: "Yuru"
date: "16/05/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
link-citations: yes
bibliography: portfolio_ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Assumed predictive model

\begin{equation} \label{eq:HAR2}
log(VIX_{t+1})=\beta_0+\beta_1log(VIX_t)+\beta_2log(VIX_{t-5,t})+\beta_3log(VIX_{t-22,t})+\sigma_{t+1}z_{t+1}
\end{equation}
\begin{equation}
\epsilon_t = \sigma_t z_t
\end{equation}

\begin{equation}
z_t \sim N(0,1)
\end{equation}

\begin{equation} \label{eq:arch}
\sigma_{t+1}^2=\alpha_0+\alpha_1 \epsilon_t^2+\alpha_2 \sigma_t^2
\end{equation}

\begin{equation} \label{eq:ma5}
log(VIX_{t-5,t})=\frac{1}{5}[log(VIX_t)+...+log(VIX_{t-4})]
\end{equation}
\begin{equation} \label{eq:ma22}
log(VIX_{t-22,t})=\frac{1}{22}[log(VIX_t)+...+log(VIX_{t-21})]
\end{equation}

# Trading strategy 1 (Taylor,2019)

The trading strategy return is adjusted by the transaction cost and is defined as:
$$f(R_{t+1},\omega_t,\tau_t)=\frac{1+\omega_tR_{t+1}}{1+\tau_t},$$
where $R_{t+1}$ is the the return of the asset at time t+1, $\tau_t = \kappa|\omega_t-\omega_{t-1}|$ is the total transaction costs and $\kappa$ is the proportional transaction cost associated with the trading in the market.

The investor can take a long position, a short position or no position based on the next-day forecasted returns and the transaction costs incurred. The investor will take a long position if a long position generates the highest trading strategy return - $f(R_{t+1},\omega_t,\tau_t)$, compared with taking a short position or no position. Meanwhile, everytime the position changes, there are transaction costs generated. The trading strategy that takes transaction costs into account is referred as $\tau$-informed strategy. If the investor incorrectly assumes the transaction cost is zero, then it is referred as $\tau$-ignorant strategy.

The performances of these trading strategies are compared with three benchmark strategies.

1. Cash-only strategy: $f(R_{t+1},0,0)$

2. Long-only strategy: $f(R_{t+1},1,0)$

3. Short-only strategy: $f(R_{t+1},-1,0)$

The difference between the trading strategy returns and benchmarks are used to produce the Sharpe ratios. The average Sharpe ratios are listed in the tables.

```{r,message=FALSE}
library(dplyr)
library(tidyverse)
library(kableExtra)
```

```{r}
names <- matrix(c("Daily","Annulized"),2,1)
names <- as.data.frame(names)

# for CLS10 prediction 
cls10_inf <- read.csv("data/sharpe_inf10.csv")
cls10_inf_y <- cls10_inf*sqrt(252) # annualize sharpe ratio
cls10 <- cls10_inf %>% summarise_if(is.numeric,mean) %>% rbind(cls10_inf_y %>% summarise_if(is.numeric,mean))
cls10 <- cbind(names, cls10)
cls10 <- rename(cls10," " = V1)
cls10_ig <- read.csv("data/sharpe_fsr1.csv")
cls10_ig_y <- cls10_ig*sqrt(252)
cls10_ig <- cls10_ig %>% summarise_if(is.numeric,mean) %>% rbind(cls10_ig_y %>% summarise_if(is.numeric,mean))
cls10_ig <- cbind(names, cls10_ig)
cls10_ig <- rename(cls10_ig," "=V1)

# for cls90 prediction
cls90_inf <- read.csv("data/sharpe_inf90.csv")
cls90_inf_y <- cls90_inf*sqrt(252)
cls90 <- cls90_inf %>% summarise_if(is.numeric,mean) %>% rbind(cls90_inf_y %>% summarise_if(is.numeric,mean))
cls90 <- cbind(names, cls90)
cls90 <- rename(cls90," " = V1)

cls90_ig <- read.csv("data/sharpe_fsr4.csv")
cls90_ig_y <- cls90_ig*sqrt(252)
cls90_ig <- cls90_ig %>% summarise_if(is.numeric,mean) %>% rbind(cls90_ig_y %>% summarise_if(is.numeric,mean))
cls90_ig <- cbind(names, cls90_ig)
cls90_ig <- rename(cls90_ig," "=V1)

# for LS prediction 
ls_inf <- read.csv("data/sharpe_inf_LS.csv")
ls_inf_y <- ls_inf*sqrt(252)
ls <- ls_inf %>% summarise_if(is.numeric,mean) %>% rbind(ls_inf_y %>% summarise_if(is.numeric,mean))
ls <- cbind(names, ls)
ls <- rename(ls," "=V1)

ls_ig <- read.csv("data/taylor_LS.csv")
ls_ig_y <- ls_ig*sqrt(252)
ls_ig <- ls_ig %>% summarise_if(is.numeric,mean) %>% rbind(ls_ig_y %>% summarise_if(is.numeric,mean))
ls_ig <- cbind(names, ls_ig)
ls_ig <- rename(ls_ig," "=V1)

cls10_ig %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c("T1:Tau ignorant Sharpe ratio (CLS10)"=4))

cls10 %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c("T2:Tau informed Sharpe ratio (CLS10)"=4))

cls90_ig %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c("T3:Tau ignorant Sharpe ratio (CLS90)"=4))

cls90 %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c("T4:Tau informed Sharpe ratio (CLS90)"=4))

ls_ig %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c("T5:Tau ignorant Sharpe ratio (LS)"=4))

ls %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c("T6:Tau informed Sharpe ratio (LS)"=4))
```

# Trading strategy 2

To evaluate the economic significance of the optimal probabilistic forecasts, we adopt the trading strategy based on interval forecasts in @kon2008 and calculate the corresponding Sharpe ratios. The rational of their strategy is that if the VIX price at time $t$ is close to the upper (lower) bound of the next day's predictive interval, then the price is likely to rise (decrease). It is then suggested that the investor takes a long (short) position. If the price does not show a sign of increasing (decreasing), then hold the current position, which means do nothing. That is,

if $log(VIX_t) < (>) \frac{U_{t+1|t}(\alpha)+L_{t+1|t}(\alpha)}{2}$, then take a long (short) position;

if $log(VIX_t) = \frac{U_{t+1|t}(\alpha)+L_{t+1|t}(\alpha)}{2}$, then hold the position.

$U_{t+1|t}$ and $L_{t+1|t}$ are the upper and lower bounds of the conditional predictive interval, which is constructed from optimal probabilistic forecasts.

Since CLS10 and CLS90 can predict the upper and lower tails of the conditional predictive distribution better, $U_{t+1|t}$ and $L_{t+1|t}$ are determined by CLS90 and CLS10 separately. That is, the trading strategy based on the CLS optimal forecasts is determined by the values of $log(VIX_t)$ and $\frac{U_{t+1|t}^{CLS90}+L_{t+1|t}^{CLS10}}{2}$.

We bring in the interval score (IS) as an optimizers to produce the optimal forecasts as in Section 3.1. By comparing the performance of IS and CLS, it might give us a better idea if forecasters can generate economic benefits from using CLS. The IS is defined as in @gneiting2007:

$$S_{IS}(P^{t-1}_{\boldsymbol{\theta}},y_t)=(u-l)+\frac{2}{\alpha}(l-y_t)I(y_t<l)+\frac{2}{\alpha}(y_t-u)I(y_t>u),$$
where $u$ and $l$ are the $1-\frac{\alpha}{2}$ and $\frac{\alpha}{2}$ quantiles of the $(1-\alpha)$x$100\%$ interval forecast.

We calculate the Sharpe ratio associated with the above trading strategies, which is used to measure the risk-adjusted return and the Sharpe ratio is defined as:

$$Sharpe \ ratio = \frac{R^p_t - rf_t}{\sigma^p_t}$$ 
$$R_t^p = log(VIX_{t+1}) - log(VIX_t),$$
where $R_t^p$ is the portfolio return at time $t$, $\sigma_t^p$ is the volatility of the portfolio at time $t$, and $rf_t$ is the risk-free rate at time $t$, which is approximated by the 10-year treasury constant maturity rate.

When the short position is taken at time $t$,
$$R_t^p = log(VIX_t)-log(VIX_{t+1})$$
The table below shows the daily and annualized average Sharpe ratios for the CLS, LS and IS optimal forecasts.

```{r}
cls_sharpe <- read.csv("data/sharpe_cls.csv")
cls_sharpe_y <- cls_sharpe*sqrt(252)
cls <- cls_sharpe %>% summarise_if(is.numeric,mean) %>% rbind(cls_sharpe_y %>% summarise_if(is.numeric,mean))
cls <- cbind(names, cls)
cls <- rename(cls," "=V1)

ls_sharpe <- read.csv("data/sharpe_LS.csv")
ls_sharpe_y <- ls_sharpe*sqrt(252)
ls_sharpe <- ls_sharpe %>% summarise_if(is.numeric,mean) %>% rbind(ls_sharpe_y %>% summarise_if(is.numeric,mean))
ls_sharpe <- cbind(names, ls_sharpe)
ls_sharpe <- rename(ls_sharpe," "=V1)

df <- cls

df %>% mutate(Sharpe_ls <- ls_sharpe) %>%
  kable("latex",escape = T, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F) %>%
  add_header_above(c("T7: Sharpe ratio"=3))
```

# References
